### 2019-02-04 Article/article.tex
First draft upto related work

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs} %
\usepackage{graphicx} % Used for displaying a sample figure. If possible, figure
% files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\usepackage[utf8]{inputenc}
%%\usepackage{amsmath}
%%\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{threeparttable}
\usepackage{graphicx}
\usepackage{color}
\usepackage{paralist}
\usepackage{framed}
\usepackage{caption}
\usepackage{todonotes}
%%\newtheorem{theorem}{Theorem}
%%\newtheorem{corollary}{Corollary}[theorem]
%%\newtheorem{lemma}[theorem]{Lemma}
%%
%%\newtheorem*{example}{Example}
%%\newtheorem{remark}{Remark}

\usepackage[shortlabels]{enumitem}

\usepackage{algorithmic}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage[cmex10,fleqn]{amsmath}
\usepackage{amsfonts}

\newcommand{\hp}{{\sc HeteroPrio}\xspace}
\SetKw{continue}{continue}

%%\pagenumbering{gobble}

\begin{document} %
	%	\title{Contribution Title\thanks{Supported by organization x.}}
%%	\title{Order of Data Transfers between CPU and GPU: A Case Study}
	\title{Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels}
	%\titlerunning{Abbreviated paper title}
	% If the paper title is too long for the running head, you can set
	% an abbreviated paper title here
	%
	\author{}
%%%%	\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and Second
%%%%		Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and Third
%%%%		Author\inst{3}\orcidID{2222--3333-4444-5555}} %
%%%%	\authorrunning{F. Author et al.} % First names are abbreviated in the running
	% head.
	% If there are more than two authors, 'et al.' is used.
	%
	\institute{Princeton University, Princeton NJ 08544, USA \and Springer
		Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
		\email{lncs@springer.com}\\
		\url{http://www.springer.com/gp/computer-science/lncs} \and ABC Institute,
		Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
		\email{\{abc,lncs\}@uni-heidelberg.de}} %
	\maketitle              % typeset the header of the contribution
	%
	\begin{abstract} 
%%		
%%		The abstract should briefly summarize the contents of the
%%		paper in 150--250 words.

With increasing complexity of hardwares, systems with different memory nodes are ubiquitous in high performance computing (HPC). It is paramount to develop strategies to overlap the data transfers between memory nodes with the computation in order to exploit the full potential of these systems. In this article, we consider the problem of deciding the  order of data transfers between two memory nodes for a set of independent tasks  with the objective to minimize the makespan. We propose an optimal heuristic to obtain the order of data transfers when there is not any restriction on memory limit. We also show that with finite memory capacity obtaining the optimal order of data transfers is an NP-complete problem. We propose several heuristics for this problem and provide analysis of them on traces obtained by running 3 molecular chemistry kernels, namely, Hartree–Fock , Cholesky contraction, and CCSD on 16 nodes of an HPC system. Our results show that some of our heuristics achieve \% overlap for intermediate memory capacities and are very close to the lower bound of makespan.
		\begin{itemize}
			\item Task-based systems
%%			\item goal is to provide analysis of different scheduling strategies
%%			\item Problem with simple assumption is NP-hard
%%			\item compare with the lower bound of performance
		\end{itemize}
		\keywords{Communication Scheduling  \and Memory Nodes \and Molecular Chemistry.}
	\end{abstract} %
	%
	%

	\section{Introduction}

%%	\begin{itemize}
%%%%		\item limitation of previous approaches
%%%%		\item scheduling problems are NP-complete, several  phenomena are added to inherent NP-hard optimization problems
%%%%		\item hard to precisely predict the performance of both computations and communications
%%%%		\item number of architectures have increased drastically in recent years
%%%%		\item Task based runtime systems
%%%%		\item Communication is one of the main bottleneck on hpc systems (cite Gullium Aupy work)
%%%%		\item Stress on communication avoidance algorithms (Communication avoidance algorithm)
%%%%		\item A lot of work on the computation scheduling
%%%%		\item Assume communications can be completely overlapped for dense linear algebra computations (Our citations)
%%%%		\item Our framework can be easily extended to any system which operates on different types of memory
%%%%		\item To think what are the bottlenecks, which would restrict us from parallel communications
%%%%		\item Focus and contributions of this paper
%%				
%%	\end{itemize}

	With the advent of multicore, and the use of accelerators, it is notoriously cumbersome to exploit the full capacity of a machine. Indeed, there are several challenges come into picture. First, every architecture provides its own efficacy and interface. Therefore, a steep learning curve is required for programmers to take good utilization of all resources. Second, scheduling is a well known NP-Complete optimization problem, and hybrid and distributed resources make this problem harder (we refer ~\cite{webpagescheduling} for a survey on the complexity of scheduling problems and ~\cite{bleuse2015scheduling} for a recent survey in the case of hybrid nodes). Third, due to shared buses, parallel resources, it is hard to obtain a precise model based on prediction of computation and communication timings. Fourth, number of architectures has increased drastically in recent years, therefore it is almost impossible to develop hand tune optimized code for all these architectures. All these observations led to the development of different task based runtime systems. Among several runtimes, we may cite QUARK~\cite{YarKhan:2011:Quark:Manual} and PaRSEC~\cite{parsec} from from ICL, Univ. of Tennessee Knoxville (USA), StarPU~\cite{starpu} form INRIA Bordeaux (FRANCE), Legion~\cite{legion12} from Stanford Univ. (USA), StarSs~\cite{ompss} from Barcelona Supercomputing Center (Spain), KAPPI~\cite{kaapi} from INRIA Grenoble (France). All these runtime systems allow programmers to express their algorithms at the abstract level in the form of direct acyclic graphs, where vertices represent computations and edges represent dependencies among them. Sometimes some static information such as distance to exit (last) node as a priority or affinity of computation towards resources is also provided along with the DAG. Then runtime manages scheduling of computations and communications, data transfer among different memories, computation-communication overlap, load balance in the best possible way.

%%	Historically there is a great focus on the design of parallel algorithms and to minimize the complexity of the computations. Also In the last decade, there is a drastic improvement in the hardware to provide perminent rate of computation, but little improvement has been achieved for the rate of data movement. With extreme scale computing, supercomputers face bottlenecks due to ever growing need of data. Therefore focus of HPC community is now changing towards avoiding, hiding and minimizing communications. (Kyelick work and http://science.energy.gov/~/media/ascr/ ascac/pdf/meetings/20140210/Top10reportFEB14.pdf )

	 In the last few decades, there is a drastic improvement in the hardware to provide perminent rate of computation, but little improvement has been achieved for the rate of data movement. With extreme scale computing, supercomputers face bottlenecks due to the need of large amount of data~\cite{ascaccommitteereport2014,yelick2016}. Therefore focus of HPC community is now changing towards avoiding, hiding and minimizing communication costs.

	Certain applications such as dense linear algebra kernels have regular structure. Therefore it is possible to associate priorities, based on the task graph structure, with computations, which runtime uses to make the execution efficient. In some applications, such as sparse linear algebra kernels, where programmers do not know the precise structure of the tasks graphs in advance,  tasks are added recursively based on certain sentinel constraints. For such applications, runtime sees a set of independent ready tasks and schedule them on different processing units. It is extremely important for runtimes to decide the order of data transfers for these scheduled computations such that overlap between computations and communications can be maximised. This is the main topic of this paper. We propose different strategies for runtimes such that it can maximize the overlap of computation and communication for kernels running on two different memory nodes. We prove that one of our proposed strategies is an optimal one when we do not have any restriction on the capacity of memory node. We also prove that order of communication on two memory nodes  with the objective of minimizing the makespan is  NP-Complete. We evaluate our strategies on a cluster of homogeneous nodes. But our approach is generic and easily adaptable to any system which operates on different memory spaces. Here are the important contributions of this paper.

	\renewcommand{\labelitemi}{$\bullet$}
	\begin{itemize}
		\item Proposed different scheduling strategies with the objective to minimize the makespan
		\item An optimal strategy and its proof, when there is not any memory capacity constraint on target machine
		\item NP-Completeness proof for the general data-transfer problem  
		\item Linear programming formulation of the problem
		\item Numerous  experiments to assess the effectiveness of our strategies on molecular chemistry kernels 
	\end{itemize}

\section{Related Work}

Historically there has been a great emphasis on the development of parallel algorithms and minimizing the complexity of computations. As the number of computation cores has increased drastically in recent years, supercomputers face bottleneck due to communication required by an application. Hence, in recent years the focus has changed towards developing communication avoiding algorithms, strategies to hiding communications and  minimizing the data accessed by applications~\cite{yelick2016}.

The problem of scheduling tasks has been highly studied in literature and this problem is known to be NP-Complete~\cite{GareyJohnson}.  Many static and dynamic strategies have been proposed and analyzed for this problem~\cite{heft-Topcuoglu,hipc16multiresource,ipdps16starpu}. There ia also a number of studies in the direction of task scheduling with the emphasis of improving locality and minimizing the communication cost~\cite{starpu,heft-Topcuoglu}. Stanisic et. al proposed a heuristic to schedule tasks on a computing resource where most of its data is available~\cite{luka-dmdar}. Similar approach has been adopted by Agullo et. al for the scheduling of sparse linear algebra kernels~\cite{agullo_fmm}.  Predari et.al  proposed  heuristics to  partition the task graph across a number of processors such that inter processor communication can be minimized ~\cite{predari:tel-01518956}.

The problem considered in this paper also can be viewed as a flow shop problem. Communication and computation timings of a task can be considered as processing timings on different machines.  Johnson has provided scheduling strategies for 2 and 3-machine flow shop problems with infinite memory case~\cite{johnson}. 2-machine flow shop problem with finite memory capacity has been proven NP-Complete by Papadimitriou et. al~\cite{Papadimitriou:1980:FSL:322203.322213}. The main difference with the our approach is that they consider unit buffer requirement on 1st machine after job completion. On the contrary, our approach is designed for tasks appearing in scientific workloads whose sizes are highly irregular and memory is acquired before starting the communication.

There is also a numerous study pertaining to the scheduling with limited memory and storage, since the work of Sethi and Ulman, register allocation for arithmetic expressions~\cite{Sethi:1970:GOC:321607.321620}.  Sarkar et. al  worked on the scheduling of graphs of smaller-grain tasks with limited memory, where each task requires homogeneous data size ~\cite{vsarkar-pact}. The same work has been extend by Loris et. al for task graphs where memory requirement of each task is highly irregular~\cite{loris-ipdps18}.

\begin{itemize}
	%%	\item Papadimitriou work
	%%	\item Johnson's work
	%%	\item Kethrin Yelik work
	%%	\item Task graph work by Loris
	%%	\item Vivek Sarkar work
	%%	\item Register coloring by Sethi
	\item roofline model
	\item theoretical/performance work on molecular chemistry kernels
\end{itemize}

%%	\begin{itemize} 
%%%%		\item may consider transfer between two memory nodes
%%%%		 \item perform experiments for transfer between CPU and GPU 
%%%%%%		\item Task based approach, communication-computation maximum overlap 
%%%%%%		\item concurrent execution of multiple kernels 
%%%%%%		\item proof for maximum computation-communication overlap with infinite memory 
%%%%%%		\item Problem statement : NP complete problem
%%%%%%		\item extended version of NP complete problem 
%%%%%%		\item Different proposed heuristics for order of data transfers 
%%%%		\item Simulation results for all proposed heuristics 
%%%%%%%		\item Experiments on actual platform with the best proposed heuristic 
%%	\end{itemize}
	\todo[inline]{SKumar: Modify both proofs }
	\section{Data Transfer problem formulation}

%%	\newpage 
	\section*{Order of data transfers}

	To exploit the full potential of a system tasks may get scheduled on processing
	units where all of their data does not reside. A task may require all of its data
	in local memory before starting the execution. There may be multiple tasks
	scheduled on a processing unit, which require to transfer data from the same
	memory node. Order of data transfers for such tasks is very crucial for the
	communication-computation overlap, thus for the overall performance. Tasks may
	also produce some output data, which, in general, is very less.  It is often the case that future tasks running on the same memory node require output data of the past tasks. Therefore, most runtime systems transfer data to other memory nodes based on the demand -- not immediately. It is possible that all output data can be stored in a preallocated separate buffer on a memory node. Hence, we do not consider output data separately in our analysis and assume that output data is negligible (zero or stored in a separate buffer) for each task. We prove that order of execution of such tasks with finite memory capacity, is an NP-complete problem.

	\subsection{Infinite Memory Case}
	Let $S$ be the set of tasks assigned on processor $P$ with memory unit $M$, and this set of tasks  need input data from another memory unit $M'$. We assume that size of $M$ is very large and there will not be any memory capacity restriction for tasks.

	\begin{algorithm}
	\caption{\label{alg:OrderOfExecutionInfinteMemory}Algorithm to determine the order of processing for a set of ready tasks (infinite memory case)}
	\begin{algorithmic}[1]
		\STATE Divide ready tasks in two sets $S_1$ and $S_2$. If computation time of a task $T$is not less than its communication time, then $T$ is in $S_1$ otherwise $S_2$.
		\STATE Sort $S_1$ in queue $Q_1$ by non-decreasing communication times
		\STATE Sort $S_2$ in queue $Q_2$ by non-increasing computation times
		\WHILE{all tasks did not complete}
		\IF{$Q_1 \neq \emptyset$}
		\STATE remove a task $T$ from beginning of $Q_1$ for processing
		\ELSE 
		\STATE remove a task $T$ from beginning of $Q_2$ for processing
		\ENDIF
		\ENDWHILE
	\end{algorithmic}
\end{algorithm}

	\noindent \textbf{Claim} : Order provided by Algorithms~\ref{alg:OrderOfExecutionInfinteMemory} achives the optimal makespan for a set of ready tasks.

	\begin{proof}
		Let us first define some notations which we need for this proof.
%%		\todo[inline]{SKumar: Specify the destination for all notations}
		\begin{align*}
		t : & \text{Time at which data transfer for task A started in original schedule}\\
		S_A : & \text{ Start of computation  time of task A in original schedule}\\
		S_B : & \text{ Start of computation time of task B in original schedule}\\
		S'_A : & \text{ Start of computation time of task A in swapped schedule}\\
		S'_B : & \text{ Start of computation time of task B in swapped schedule}\\
		CM(A) : & \text{ Data transfer time for task A}\\
		CM(B) : & \text{ Data transfer time for task B}\\
		CP(A) : & \text{ Computation time of of task A}\\
		CP(B) : & \text{ Computation time of task B}\\
		\rho : & \text{ ratio of length of task and data transfer time}
		\end{align*}
	\end{proof}

	Let $S$ be the schedule obtained by the above heuristic and $O$ be an optimal schedule. We prove the above claim by converting $S$ to $O$ and showing that at each step completing time of intermediate schedule is not less than the completion time of original schedule $S$. In order to do so, we make sure order of two tasks in both schedules $S$ and $O$ is same. If not, We perform swapping of two tasks.

	\noindent If we prove the swapping strategy for two contiguous tasks holds, then the same strategy transitively hold for any two tasks of Schedule $S$

	Let $A$ and $B$ are two contiguous tasks of schedule $S$, which need to be swapped.
	\todo[inline]{SKumar: draw an equivalent xfig diagram}
	\begin{figure}[htb]
		\centering
		\includegraphics[width=\textwidth, height=0.5\textheight, 
		keepaspectratio]{Figs/swappedSchedule.jpg}
		\caption{ \label{fig:bothSchedule} Original and Swapped Schedule}
	\end{figure}

	We can write the following constraints based on the two schedules of the Fig~\ref{fig:bothSchedule}.

	\begin{eqnarray*}
		S_A & = & max(CM(A), l) \\
		S_B & = & max(S_A + CP(A), CM(A) + CM(B))
	\end{eqnarray*}

	Completion time in original Schedule = $S_B + CP(B)$
	\begin{eqnarray*}
		S'_B & = & max(CM(B), l) \\
		S'_A & = & max(S'_B + CP(B), CM(A) + CM(B))
	\end{eqnarray*}

	Completion time in swapped Schedule = $S'_A + CP(A)$

	Our goal is to prove the following inequality.
	\begin{eqnarray*}
		S_B + CP(B) & \le & S'_A + CP(A)
	\end{eqnarray*}
	\begin{proof}
		\begin{eqnarray*}
			S_B + CP(B) & = & max(S_A + CP(A)+CP(B), CM(A) + CM(B) + CP(B))\\
			& = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) 
		\end{eqnarray*}
		Case I: $A, B\in ST_1, CM(A) \le CM(B), CP(A) \ge CM(A), CP(B) \ge CM(B)$
		\begin{eqnarray*}
			S_B + CP(B) & = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) \\
			& \le & max(CM(A) + CP(B), l+CP(B), CM(B)+CP(B)) + CP(A)\\
			& = & max(CM(B) + CP(B), l + CP(B)) + CP(A) \\
			& = & max(max(CM(B), l) + CP(B), CM(A) + CM(B)) + CP(A) \\
			& = & max(S'_B + CP(B), CM(A) +CM(B)) + CP(A) \\
			& = & S'_A + CP(A)
		\end{eqnarray*}
		Case II: $A, B\in ST_2, CP(A) \ge CP(B), CP(A) < CM(A), CP(B) < CM(B)$
		\begin{eqnarray*}
			S_B + CP(B) & = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) \\
			& \le & max(CM(A) + CP(B), l+CP(B), CM(A)+CM(B)) + CP(A)\\
			& = & max(CM(A) + CM(B), l + CP(B)) + CP(A) \\
			& = & max(CM(B) + CP(B), l + CP(B), CM(A) + CM(B)) + CP(A) \\
			& = & max(max(CM(B), l) + CP(B), CM(A) + CM(B)) + CP(A) \\
			& = & max(S'_B + CP(B), CM(A) +CM(B)) + CP(A) \\
			& = & S'_A + CP(A)
		\end{eqnarray*}
		Case III: $A \in ST_1, B\in ST_2, CP(A) \ge CM(A), CP(B) < CM(B)$
		\begin{eqnarray*}
			S_B + CP(B) & = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) \\
			& \le & max(CM(A) + CP(B), l + CP(B), CM(B) + CP(B)) + CP(A)\\
			& \le & max(CM(A) + CM(B), l + CP(B), CM(B) + CP(B)) + CP(A) \\
			& = & max(max(CM(B), l) + CP(B), CM(A) + CM(B)) + CP(A) \\
			& = & max(S'_B + CP(B), CM(A) +CM(B)) + CP(A) \\
			& = & S'_A + CP(A)
		\end{eqnarray*}
	\end{proof}

This problem can be expressed as 2-machine flowshop problem with infinite storage, where communication time is the processing time on first machine and computation time is the processing time on second machine and the goal is to minimize the overall makespan. In [], Johnson's algorithm also achieves the optimal makespan but the proof techniques and algorithm are quite different from ours.
	\subsection{Finite Memory}

	In general, order of task execution with input and output data transfers can be 
	viewed as  3-machine flowshop problem, where processing time on 1st machine is 
	input data transfer time,  processing time on 2nd machine is task execution time, 
	processing time on 3rd machine is output data transfer time  and the objective is 
	to minimize the total makespan. This is a well known NP-complete problem.

	\noindent\textbf{Probelm  $DT$} : A set of tasks $ST=\{T_1, \cdots, T_n\}$ is scheduled on a processing 
	unit $P$  with memory unit $M$ of capacity $C$. Input data for tasks of $ST$ reside on 
	another memory unit $M'$. $comm_i$ is the time to transfer input data from $M'$ to $M$ for task 
	$T_i$,  $e_i$ is the execution time of task $T_i$ on $P$. We assume that these tasks  do not produce any output data.  Given $L$, is there a feasible schedule $S$ for $ST$ such that makespan of $S$, $\mu(S) \le L$?
%%	What is the order of execution of $ST$ on $P$ such that 
%%	makespan of	$ST$ is minimal? 
%%	
	\begin{theorem}
		Problem $DT$ is NP-complete.
	\end{theorem}
   \begin{proof}

   	Proving $DT$ is NP-complete requires first to show that decision version of this problem can be 
   	verified by a polynomial time nondeterministic algorithm, and then showing that a known 
   	NP-complete problem is polynomially reducible to this problem. As usual first job is simple and can 
   	be 
   	done in linear time, given a schedule we can check that at each change point memory capacity is 
   	restricted and a task starts execution only after its input data is transferred to $M$. In our case, the 
   	known NP-complete problem that can be reduced to problem $DT$ is the following.

   	\noindent \textbf{Three Partition Problem (3PAR)} : Given a set of $3m$ integers $A = \{ a_1,  
   	\cdots, a_{3m }\}$, is there a partition of $A$ into $m$ triplets $TR_i = \{a_{i_1}, a_{i_2}, a_{i_3}\}$, 
   	such that $\forall i, a_{i_1} + a_{i_2}  + a_{i_3}  = b$, where $b=(1/m) \sum a_i $?

   	This problem is known to be NP-complete.

   	\noindent Let us first show that $3PAR$ problem reduces in polynomial time to problem $DT$.  
   	Suppose that we 
   	are given an instance  $A = \{ a_1,  \cdots, a_{3m }\}$ of $3PAR$ problem. It is immediately obvious 
   	that $a_i>1$, since we can always add sufficiently large integers to $a_i$'s and scale the problem 
   	accordingly.  This scaling will not affect in any way the existence of a solution for the instance of $3PAR$ problem. Consequently, given any instance of the $3PAR$ problem, we construct an instance $I$ of the problem $DT$ such that $I$ has a schedule with makespan bounded by $L$ iff the instance 
   	$I$ of $3PAR$ problem has a solution. The instance of problem $DT$ will have $4m+1$ tasks.

   		\begin{table*}[htb]
   			\begin{tabular}{ |c|c|c| }
   				\hline
   				Task & Input Transfer time ($comm_i$)& Computation time ($e_i$)\\ \hline
   				$K_0$ & $0$ & $3$ \\ \hline
   				$K_1, \cdots, K_{m-1}$ & $b'=b+3x$ & $3$\\ \hline
   				$K_m$ & $b'=b+3x$ & $0$ \\ \hline
   				$1\le i \le 3m, A_i$ & $1$ & $a_i' = a_i +x$\\ \hline
   			\end{tabular}
   		\end{table*}
   	Where $x= 2 max\{a_i:1\le i\le 3m\}$\\ 
   	Memory capacity $C=b'+3$ and $L=m(b'+3)$, this completes the construction of instance $I$ of the 
   	problem $DT$.

   	$Transfer time = Latency + \frac{Data Volume}{Bandwidth}$, for simplicity we consider Latency=0 
   	and Bandwidth=1, (implies Input data volume = Input transfer time), otherwise we can adjust $C$ in 
   	a way such that at any point in a schedule at max one $K_i$ and three $A_i$ tasks can be active.

   	We show that $I$ has a schedule $S$ with $\mu(S) \le L$ iff the original instance of $3PAR$ 
   	problem  has a solution. Notice that sum of transfer times and sum of computation times, both are 
   	equal to $L$, therefore $\mu(S) \le L$ iff $\mu(S)=L$  and there is no idle time on both channels in 
   	$S$. It indicates that first task is $K_0$ and last task is $K_m$.
%%   	
%%   	\todo[inline]{SK: Unable to argue why only $A_i$ tasks will run on communication channel when 
%%   	$K_0$ is running on computation channel.}

   	Now we prove that any feasible schedule of $I$ corresponds to a decomposition of $A$ into m 
   	triplets $TR_i = \{a_{i_1}, a_{i_2}, a_{i_3}\}$ such that $\forall i, a_{i_1} + a_{i_2}  + a_{i_3}  = b$. Every 
   	feasible schedule has to consist of $m$ segments like the one shown in Fig~\ref{fig:firstSegment}. Each segment provides a triplet  $\{a_{i_1}, a_{i_2}, a_{i_3}\} $such that  $a_{i_1} + a_{i_2}  + a_{i_3}  = b$.

	Any schedule $S$ of $I$ having no idle time must start with $K_0$. No other $K_i$ tasks can be active with $K_0$, otherwise we would get idle time on computation channel ($b'>3, b'-2>max\{a_i':1\le i\le 3m\},  \text{and } b'-1 > 2 max\{a_i':1\le i\le 3m\}$). Hence three $A_i$ tasks must follow $K_0$.   	 
   	Memory requirement of other $K_i$ tasks is $b'$ and $2b'>C$, therefore at any point in schedule at max one $K_i$ task can be active. Sum of duration of all $K_i$ tasks = $3 + (m-1)(b'+3) + b' = m (b'+3)=L$, hence at each point in $S$ exactly one $K_i$ task is active. When $K_i$ task is in computation phase, no other $K_i$ tasks can be active in that duration, therefore  $3A_i$ tasks must complete data transfers in that duration. After that next task must be a 
   	$K_i$ task, otherwise total makespan would be more than $\sum(transfertime(k_i))  + 
   	\sum(computetime(k_i)) =L$. When communication for  $K_i$ task starts we exactly have $3A_i$ 
   	tasks whose data is available in local memory. Hence three $A_i$ tasks are scheduled for computation. Now we must prove that $a_{i_1}' + a_{i_2}'  + a_{i_3}'  = b'$.

   	This is true because if $a_{i_1}' + a_{i_2}'  + a_{i_3}'  > b'$, total used memory after the data transfer 
   	for  $K_i$ task finishes is atleast $b'+1$, hence only $A_i$ tasks can be considered, which will lead to a schedule in which at a point only $A_i$ tasks are active on both channels, therefore length of 
   	schedule would be more than $L$, and if $a_{i_1}' + a_{i_2}'  + a_{i_3}'  < b'$, then we have idle time on computation channel.

   	Conversely, if such a partition of $A$ is achievable, then we can construct a feasible schedule $S$ 
   	without idle times by the pattern depicted in Fig~\ref{fig:firstSegment}. We have shown that $3PAR$ 
   	problem reduces to $DT$, and hence problem $DT$ is NP-complete.

   	\begin{figure}[htb]
   		\centering
   		\includegraphics[scale=0.07]{3PARToSched.jpg}
   		\caption{ \label{fig:firstSegment} First segment of Schedule $S$}
   	\end{figure}

   \end{proof}

Each task may require some intermediate buffer. As problem $DT$ is NP-complete and intermediate 
memory requirement of each task is zero (which is a special case of problem with intermediate memory 
requirement). Hence, problem $DT$ with intermediate memory requirement is also NP-complete.

The proof of the above theorem is inspired from work by [Papadimitriou et. al], which applies a similar 
technique for 2-machine flowshop problem, where each machine can hold fixed amount of jobs. The 
main difference with the our approach is that they consider unit buffer requirement on 1st machine 
after job completion. On the contrary, our approach is designed where there is not any restriction on 
requested input data and memory is acquired before starting the data transfer on communication 
channel(1st machine).

	\section{Order of Data Transfer and Computation heuristics}
	\begin{itemize}
		\item Talk about optimal strategy
		\item Order of computations and communications are same
		\item Static strategy
		\item Dynamic strategies
		\item Combination of Static and dynamic strategies
		\item strategies based on linear program 
	\end{itemize}

The heuristic proposed in the Section provides the optimal makespan when there is not any constraint on memory capacity. This optimal value indicates a lower bound on the makespan. We use $optimal_makespan_infinite_memory$ to represent this value. We assess the efficiency of other proposed heuristics in limited memory capacity in Section~\ref{sec:exp} with respect to this lower bound, $optimal_makespan_infinite_memory$.

We classify our heuristics into mainly three categories. In the first category, the order of all computations and communications is computed in advanced and the same order is followed on both channels. While in the second category, the best suited next task is chosen based on different criteria. In the last category, which is based on combination of strategies of the other two categories, we precompute the order and try to follow it as much as possible, but when the precomputed schedule induces idle time then we look for the best suited next task. In all of our strategies (except linear programming based strategy) order of communications and computations, are same.

\subsection{Static Ordering}
In this class of strategies, we compute the order of both computations and communications in advance based on criteria such as communication time, compute time, accelerated tasks. After computing the order, we follow the same order on computation and communication channels and make sure that at each point in the schedule memory capacity is respected.

In strategy (cite optimal strategy), compute intensive tasks (step 1) are sorted in increasing order of communication times. It allows tasks to utilize the computation channel maximally and make enough space on communication channel to accommodate more communication intensive tasks with maximum overlap. Communication intensive tasks are sorted in decreasing order of communication time, which allows tasks to utilize the gap created on communicated channel. Hence,  in this section, we obtain the orders by sorting tasks based on different combinations of communication and computation times.

%%%%name = "optimal_time_infinite_case";
%%%%string alg_name="order_of_optimal_strategy_infinite_memory";
%%%%string alg_name="increasing_order_of_communication_strategy";
%%%%string alg_name="decreasing_order_of_computation_strategy";
%%%%string alg_name="increasing_order_of_communication_plus_computation_strategy";
%%%%string alg_name="decreasing_order_of_communication_plus_computation_strategy";
%%%%string alg_name="optimal_order_infinite_memory_largest_communication_task_respects_memory_restriction";
%%%%string alg_name="optimal_order_infinite_memory_smallest_communication_task_respects_memory_restriction";
%%%%string alg_name="optimal_order_infinite_memory_maximum_accelerated_task_respects_memory_restriction";
\begin{itemize}[a)]
	\item $order_of_optimal_strategy_infinite_memory $: Order of communications and computations is obtained by the infinite memory heuristic. At each point in the schedule memory capacity is respected. Hence the makespan of this heuristic may be completely different from $optimal_makespan_infinite_memory$.

	\item $increasing_order_of_communication_strategy$: Order is obtained by sorting all tasks in non-decreasing order of communication time.

	\item $decreasing_order_of_computation_strategy$: Order is obtained by sorting all tasks in non-increasing order of computation time. 
	\item $increasing_order_of_communication_plus_computation_strategy$: Order is obtained by sorting all tasks in non-decreasing order of sum of communication and computation times.
	\item $decreasing_order_of_communication_plus_computation_strategy$: Order is obtained by sorting all tasks in non-increasing order of sum of communication and computation times.

\end{itemize}
\todo[inline]{SKumar: equivalent tikz figure}

\begin{figure}[htb]

	\includegraphics[scale=0.05]{Figs/staticOrderSchedules}
			\caption{Task set and schedules where orders are precomputed based on different heuristics.}
	\label{fig:staticOrderExample}
\end{figure}

Fig~\ref{fig:staticOrderExample} shows schedules for all proposed heuristics of this class for task set of Table (ref).
\subsection{Dynamic Selection}
%%%%string alg_name="largest_communication_task_respects_memory_restriction";
%%%%string alg_name="smallest_communication_task_respects_memory_restriction";
%%%%string alg_name="maximum_accelerated_task_respects_memory_restriction";

In this class of strategy, when communication channel is idle, a task is chosen which satisfies the selection criteria maximally among other tasks. For example, if the selection criteria is to choose a highly compute intensive task, than  we calculate the ratio of compute time and communication time for all tasks, and the task with the  maximum ratio is selected (ties are broken randomly). As we assume that order on both channels is same, hence order on compute channel will follow the order of communication channel.

\begin{itemize}[a)]
	\item $largest_communication_task_respects_memory_restriction$:  We select a set of tasks which induce minimum idle time on compute channel. A task with the largest communication time is chosen from this set.  Memory requirement of this task should not be more than presently available memory. 
	\item $smallest_communication_task_respects_memory_restriction$: A task with the smallest communication time is chosen.  Memory requirement of this task should not be more than presently available memory. 
	\item $maximum_accelerated_task_respects_memory_restriction$:  We select a set of tasks which induce minimum idle time on compute channel. A task with the maximum ratio of compute time to communication time  is chosen from this set.  Memory requirement of this task should not  be more than presently available memory.

\end{itemize}
\todo[inline]{SKumar: equivalent tikz figure}

\begin{figure}[htb]

\includegraphics[scale=0.05]{Figs/dynamiSelectionSchedules}
\caption{Task set and schedules where orders are precomputed based on different heuristics.}
\label{fig:dynamicSelectionExample}
\end{figure}

Fig~\ref{fig:dynamicSelectionExample} shows schedules for all proposed heuristics of this class for task set of Table (ref).

\subsection{Static Order with dynamic Corrections}

In this class of strategy, we precompute the order of tasks based on different criteria and then try to follow the same order as much as possible. But when communication channel is idle due to memory requirement of the next task in the obtained order, then we select a task similar to previous strategy. After a task is selected then we update the remaining order without this task. This class of strategy takes advantage of  static information in the form of precomputed order and dynamic correction to minimize the idle time due to memory constraint.
%%%%alg_name="optimal_order_infinite_memory_largest_communication_task_respects_memory_restriction";
%%%%string alg_name="optimal_order_infinite_memory_smallest_communication_task_respects_memory_restriction";
%%%%string alg_name="optimal_order_infinite_memory_maximum_accelerated_task_respects_memory_restriction";

Initial order is obtained by infinity memory heuristic. When communication channel is idle due to memory requirement of the next task in the order, then we select a set of tasks which induce minimum idle time on compute channel and satisfy memory requirement. We define the following heuristics based on how we select a task from this set. After that order of remaining  tasks is updated without this task.

\begin{itemize}[a)]
	\item $optimal_order_infinite_memory_largest_communication_task_respects_memory_restriction$: A task with the largest communication time is chosen from the set.
	\item $optimal_order_infinite_memory_smallest_communication_task_respects_memory_restriction$:  A task with the smallest communication time is chosen from the set.
	\item $optimal_order_infinite_memory_maximum_accelerated_task_respects_memory_restriction$: A task,  whose ratio of compute time to communication time is maximum, is chosen from the set .
\end{itemize}

\todo[inline]{SKumar: equivalent tikz figure}
\begin{figure}[htb]
\includegraphics[scale=0.05]{Figs/staticOrderDynamicCorrectionsSchedules}
\caption{Task set and schedules where orders are precomputed based on different heuristics.}
\label{fig:staticOrderDynamicCorrectionsExample}
\end{figure}

Fig~\ref{fig:staticOrderDynamicCorrectionsExample} shows schedules for all proposed heuristics of this class for task set of Table (ref).

\subsection{Solving Linear Program Iteratively}
%%\subsection{Solving Linear Program Iteratively}
We use a mixed integer linear program  to obtain the order of data transfers and computations. We are unable to mange the optimal solution for the complete set $S$ in limited amount of time.  Hence, we construct and solve the linear program iteratively for a small subset of size $k$ . $CP(i)$ and $CM(i)$ represent computation and communication timings of task $T_i$. $TM(i)$ denotes intermediate memory requirement of task $T_i$ . Memory capacity of the  target system is $C$. In the linear program formulation, $s_i$ and $e_i$ (resp. $s'_i$ and $e'_i$) represent start and end time of communication (resp. computation) for task $T_i$. The formulation contains $i)$ n-1 boolean variables, $a_{ij}$, for each task $T_i$ to denote the order of $T_i$ and $T_j$  on communication channel   $ii)$ n-1 boolean variables, $b_{ij}$, for each task $T_i$ to denote the order of $T_i$ and $T_j$  on computation channel $iii)$ n-1 boolean variables, $c_{ij}$, for each task $T_i$ to denote the order of $s_i$ and $e'_j$, and $iv)$ (optional, if we consider temporary buffer requirement for each task) n-1 boolean variables, $d_{ij}$, for each task $T_i$ to denote the order of $e'_i$ and $s_j$.

\noindent Let $L=\sum_i (CP(i) + CM(i))$. It is evident that $e_i =s_i + CM(i)$ and $e'_i =s'_i + CP(i)$. The constraints are following.

\vspace*{-0.5cm}
\begin{align*}
& \text{minimize } l \text{ such that }\\
\forall i, \quad & \text{computation of task } T_i \text{ completes:}\\
& e'_i \leq l\\
\forall i, \quad & \text{computation stars after communication ends:}\\
& e_i \leq s'_i\\
\forall i, \forall j\ne i, \quad & \text{exclusive communication of task }T_i \text{ on communication channel:}\\
& e_j \leq s_i +(1-a_{ij})L\\
& e_i\leq s_j +a_{ij}L\\
\forall i, \forall j\ne i, \quad & \text{exclusive computation of task }T_i \text{ on computation channel:}\\
& e'_j \leq s'_i +(1-b_{ij})L\\
& e'_i\leq s'_j +b_{ij}L\\
\forall i, \forall j\ne i, \quad & \text{task }T_i \text{ respects memory capacity on communication channel:}\\
& e'_j \leq s_i +(1-c_{ij})L\\
& s_i< e'_j +c_{ij}L\\
& \sum_r (a_{ir} - c_{ir})CM(r) + CM(i) \le C\\
\forall i, \forall j\ne i, \quad & \text{task }T_i \text{ respects memory capacity on computation channel:}\\
& s_j < e'_i +(1-d_{ij})L\\
& e'_i\leq s_j +d_{ij}L\\
& \sum_r (d_{ir} - b_{ir})CM(r) + TM(i) \le C\\
\end{align*}

	\section{Experimental Results}
	\label{sec:exp}

	\todo[inline]{SKumar: Evaluate different metrics for HF, Cholesky and CCSD applications}
	\todo[inline]{SKumar: decide metrics: ratio to optimal, percentage overlap, 100 - percentage non overlap}
	\begin{itemize}
		\item Machine description
		\item temporary data requirement
		\item Description of all kernels (Molecular Chemistry Kernels)
		\item Think about results and graphs (Most probably results in $R$ plots)
	\end{itemize}
	\section{Conclusion and Perspectives}
	\begin{itemize}
		\item Evaluated different heuristics
		\item proved NP-complete problem
		\item Plan to implement the best heuristic in a runtime system  for NWChem algorithms and evaluation on Summit supercomputer
	\end{itemize}
%%%%	\section{First Section}
%%%%	 \subsection{A Subsection Sample} Please note that the
%%%%	first paragraph of a section or subsection is not indented. The first paragraph
%%%%	that follows a table, figure, equation etc. does not need an indent, either.
%%%%	
%%%%	Subsequent paragraphs, however, are indented.
%%%%	
%%%%	\subsubsection{Sample Heading (Third Level)} Only two levels of headings should
%%%%	be numbered. Lower level headings remain unnumbered; they are formatted as
%%%%	run-in headings.
%%%%	
%%%%	\paragraph{Sample Heading (Fourth Level)} The contribution should contain no
%%%%	more than four levels of headings. Table~\ref{tab1} gives a summary of all
%%%%	heading levels.
%%%%	
%%%%	\begin{table} \caption{Table captions should be placed above the
%%%%			tables.}\label{tab1} \begin{tabular}{|l|l|l|} \hline Heading level &  Example &
%%%%			Font size and style\\ \hline Title (centered) &  {\Large\bfseries Lecture
%%%%				Notes} & 14 point, bold\\ 1st-level heading &  {\large\bfseries 1 Introduction}
%%%%			& 12 point, bold\\ 2nd-level heading & {\bfseries 2.1 Printing Area} & 10
%%%%			point, bold\\ 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text
%%%%			follows & 10 point, bold\\ 4th-level heading & {\itshape Lowest Level Heading.}
%%%%			Text follows & 10 point, italic\\ \hline \end{tabular} \end{table}
%%%%	
%%%%	
%%%%	\noindent Displayed equations are centered and set on a separate line.
%%%%	\begin{equation} x + y = z \end{equation} Please try to avoid rasterized images
%%%%	for line-art diagrams and schemas. Whenever possible, use vector graphics
%%%%	instead (see Fig.~\ref{fig1}).
%%%%	
%%%%	\begin{figure} \includegraphics[width=\textwidth]{fig1.eps} \caption{A figure
%%%%			caption is always placed below the illustration. Please note that short
%%%%			captions are centered, while long ones are justified by the macro package
%%%%			automatically.} \label{fig1} \end{figure}
%%%%	
%%%%	\begin{theorem} This is a sample theorem. The run-in heading is set in bold,
%%%%		while the following text appears in italics. Definitions, lemmas, propositions,
%%%%		and corollaries are styled the same way. \end{theorem} %
%%%%	% the environments 'definition', 'lemma', 'proposition', 'corollary',
%%%%	% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%%%%	%
%%%%	\begin{proof} Proofs, examples, and remarks have the initial word in italics,
%%%%		while the following text appears in normal font. \end{proof} For citations of
%%%%	references, we prefer the use of square brackets and consecutive numbers.
%%%%	Citations using labels or the author/year convention are also acceptable. The
%%%%	following bibliography provides a sample reference list with entries for
%%%%	journal articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
%%%%	book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1}, and a
%%%%	homepage~\cite{ref_url1}. Multiple citations are grouped
%%%%	\cite{ref_article1,ref_lncs1,ref_book1},
%%%%	\cite{ref_article1,ref_book1,ref_proc1,ref_url1}. %
%%%%	% ---- Bibliography ----
%%%%	%
%%%%	% BibTeX users should specify bibliography style 'splncs04'.
%%%%	% References will then be sorted and formatted in the correct style.
%%%%	%
%%%%	% \bibliographystyle{splncs04}
%%%%	% \bibliography{mybibliography}
%%%%	%
%%%%	\begin{thebibliography}{8} \bibitem{ref_article1} Author, F.: Article title.
%%%%		Journal \textbf{2}(5), 99--110 (2016)
%%%%		
%%%%		\bibitem{ref_lncs1} Author, F., Author, S.: Title of a proceedings paper. In:
%%%%		Editor, F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
%%%%		Springer, Heidelberg (2016). \doi{10.10007/1234567890}
%%%%		
%%%%		\bibitem{ref_book1} Author, F., Author, S., Author, T.: Book title. 2nd edn.
%%%%		Publisher, Location (1999)
%%%%		
%%%%		\bibitem{ref_proc1} Author, A.-B.: Contribution title. In: 9th International
%%%%		Proceedings on Proceedings, pp. 1--2. Publisher, Location (2010)
%%%%		
%%%%		\bibitem{ref_url1} LNCS Homepage, \url{http://www.springer.com/lncs}. Last
%%%%		accessed 4 Oct 2017 \end{thebibliography}

\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{article}

\end{document}

### 2019-03-22 Article/article.tex
different heuristics and their favorable situation

@@
    		\centering
-   		\includegraphics[scale=0.07]{3PARToSched.jpg}
+   		\includegraphics[scale=0.07]{Figs/3PARToSched.jpg}
    		\caption{ \label{fig:firstSegment} First segment of Schedule $S$}
@@
 	\end{itemize}
+\newpage
+The following table exhibits favorable scenarios for different heuristics.
+This table allows programmers to use appropriate strategies to maximize communication-computation overlap for their applications.
+
+\begin{table}[htb]
+	\scriptsize
+	\begin{tabular}{|c|p{3cm}|}
+		\hline
+		\textbf{Heuristic} & \textbf{Favorable Situation} \\ \hline
+		order\_of\_optimal\_strategy\_infinite\_memory & Unlimited memory capacity (\textcolor{green}{Optimal}) \\ \hline
+		increasing\_order\_of\_communication\_strategy & Unlimited memory capacity and tasks are compute intensive (\textcolor{green}{Optimal}) \\ \hline
+		decreasing\_order\_of\_computation\_strategy & Unlimited memory capacity and tasks are communication intensive (\textcolor{green}{Optimal}) \\ \hline
+		increasing\_order\_of\_communication\_plus\_computation\_strategy & Moderate memory capacity and most tasks are compute intensive \\ \hline
+		decreasing\_order\_of\_communication\_plus\_computation\_strategy & Moderate memory capacity and most tasks are communication intensive \\ \hline
+		largest\_communication\_task\_respects\_memory\_restriction &  Limited memory capacity and significant percentage of tasks are communication intensive \\ \hline
+		smallest\_communication\_task\_respects\_memory\_restriction & Limited memory capacity and most tasks are compute intensive \\ \hline
+		maximum\_accelerated\_task\_respects\_memory\_restriction &  Limited memory capacity and number of communication and compute intensive tasks are approximately equal \\ \hline
+		optimal\_order\_infinite\_memory\_largest\_communication\_task\_respects\_memory\_restriction & Moderate memory capacity and significant percentage of tasks are communication intensive\\ \hline
+		optimal\_order\_infinite\_memory\_smallest\_communication\_task\_respects\_memory\_restriction & Moderate memory capacity and most tasks are compute intensive \\ \hline
+		optimal\_order\_infinite\_memory\_maximum\_accelerated\_task\_respects\_memory\_restriction & Moderate   memory capacity and number of communication and compute intensive tasks are approximately equal \\ \hline
+	\end{tabular}\caption{~\label{tab:heuristicsAndFavorableScenarios}Heuristics and their favorable scenarios}
+\end{table}
+
+Here moderate memory capacity refers to limited capacity but close to the maximum memory  requirement of the considered application.
+
+\newpage
 	\section{Conclusion and Perspectives}

### 2019-03-25 Article/article.tex
platform description and more todos

@@
 
+	\todo[inline]{Machine information and our model}
+
+	We consider a machine, Cascade, available at PNNL, for our experiments.
+We obtain traces by running  two molecular chemistry applications,  double precision version of Hartree-Fock (HF) and Coupled Cluster Single Double (CCSD) of NWChem package on 10 nodes of this machine.
+Each node is composed of 16 Intel Xeon E5-2670 cores, hence we use 160 processes for the execution.
+NWChem takes advantages of a Partitioned Global Address Space Programming Model, Global Arrays (GA), to use shared-memory programming APIs  on distributed memory computers.
+Our data transfer model is quite simple and  we consider that all data transfers between each process's local memory and GA memory take the same route.
+Modeling of different routes of data transfers for the same source-destination pair, bandwidth sharing for different source-destination pairs and network congestion is more challenging and part of our future work.
+Our model is simple yet it provides insight to the application developers (or runtime system) that  in what-order all data transfer  are issued for the same source-destination pair to maximise communication-computation overlap.
+Our model is easily adaptable to any source-destination where there is one fixed route between source and destination (such as between CPU and GPU, one copy engine to transfer data from CPU (resp.
+GPU) to GPU (resp.
+CPU) ).
+	\todo[inline]{More about tiling}
+	Both application mainly perform two types of computations, tensor transpose and tensor contractions.
+HF expects to specify a tile size and we set it to 100, so that each core can be efficiently utilize.
+CCSD automatically determines tile sizes at different program points based on the input (molecule?).
+Hence, HF operates on almost homogeneous tiles while CCSD on heterogeneous tiles.
+
+	\todo[inline]{Scheduled based on Gilmore-Gomory algorithm and its performance }
+	\todo[inline]{Skumar: HF performance plots}
+	\begin{figure}[htb]
+		\includegraphics[scale=0.25]{../HFPlots/ratio_to_optimal.pdf}
+		\caption{HF Performance.}
+		\label{fig:staticOrderDynamicCorrectionsExample}
+	\end{figure}
+	\begin{figure}[htb]
+	\includegraphics[scale=0.25]{../CCSDPlots/best_ccsd.pdf}
+	\caption{HF best Performance.}
+	\label{fig:staticOrderDynamicCorrectionsExample}
+\end{figure}
+	\todo[inline]{Skumar: CCSD performance plots}
+		\begin{figure}[htb]
+		\includegraphics[scale=0.25]{../CCSDPlots/ratio_to_optimal_ccsd.pdf}
+		\caption{CCSD Performance.}
+		\label{fig:staticOrderDynamicCorrectionsExample}
+	\end{figure}
+	\begin{figure}[htb]
+		\includegraphics[scale=0.25]{../CCSDPlots/best_ccsd.pdf}
+		\caption{CCSD best Performance.}
+		\label{fig:staticOrderDynamicCorrectionsExample}
+	\end{figure}
+	\todo[inline]{Skumar: Effect of Random memory with HF or CCSD}
+
+	\begin{figure}[htb]
+	\includegraphics[scale=0.25]{../HFPlots/ratio_to_optimal_random_memory.pdf}
+	\caption{HF Performance with random memory requirement of a task.}
+	\label{fig:staticOrderDynamicCorrectionsExample}
+\end{figure}	
 	\todo[inline]{SKumar: Evaluate different metrics for HF, Cholesky and CCSD applications}
@@
 \newpage
-The following table exhibits favorable scenarios for different heuristics.
-This table allows programmers to use appropriate strategies to maximize communication-computation overlap for their applications.
+\noindent The following table exhibits favorable scenarios for different heuristics.
+This table allows programmers to use the appropriate strategies to maximize communication-computation overlap for their applications.
 

### 2019-03-27 Article/article.tex
Experimental Results and Plots

@@
 
-	We consider a machine, Cascade, available at PNNL, for our experiments.
-We obtain traces by running  two molecular chemistry applications,  double precision version of Hartree-Fock (HF) and Coupled Cluster Single Double (CCSD) of NWChem package on 10 nodes of this machine.
+	We consider a machine called Cascade, available at PNNL, for our experiments.
+We obtain traces by running  two molecular chemistry applications,  double precision version of Hartree-Fock (HF) and Coupled Cluster Single Double (CCSD) of NWChem package with 4 Uracil molecules input on 10 nodes of this machine.
 Each node is composed of 16 Intel Xeon E5-2670 cores, hence we use 160 processes for the execution.
+Each process executes 300-800 tasks.
 NWChem takes advantages of a Partitioned Global Address Space Programming Model, Global Arrays (GA), to use shared-memory programming APIs  on distributed memory computers.
@@
 
-	\todo[inline]{Scheduled based on Gilmore-Gomory algorithm and its performance }
+%%	\todo[inline]{Scheduled based on Gilmore-Gomory algorithm and its performance }
+	We also consider an algorithm, proposed by Gilmore and Gomory, to obtain the minimal cost sequence for a set of jobs.
+In this algorithm, each job has a start and end state and a cost is associated to change the state.
+In our context, this cost can be seen as non-overlap time of computation for two adjacent jobs.
+Here is the main idea of this algorithm.
+Initially partial sequence of jobs is represented by a graph such that their overlap is maximum.
+Subsequently edges are added to this graph which minimized the total non-overlap cost  and connects two components.
+When all nodes of this graph is connected then an edge interchange mechanism is taken into account to determine the sequence of jobs, which ensures that the sequence has minimal cost.
+
+	We refer ~\cite{Gilmore-Gomory:1964} for the detailed algorithm and ~\cite{gitworkrepo} for our implementation.
+This algorithm does not take memory capacity into consideration and only provides the sequence of processing.
+We applied the same sequence with different memory capacity restrictions for our experiments and call this heuristic as \textit{Gilmore-Gomory}.
+
 	\todo[inline]{Skumar: HF performance plots}

### 2019-03-27 ExperimentalData/Gilmore_Gomory.cpp

@@ -1,0 +1,400 @@
+#include <iostream>
+#include <string>
+#include <algorithm>
+#include <list>
+#include <queue>
+#include <vector>
+#include <utility>
+#include <cassert>
+
+#include <limits>
+#include <iomanip>
+#include <fstream>
+#include <sstream>
+
+#define MAXNUMBEROFTASKS 10000
+#define MAXNUMBEROFJOBS MAXNUMBEROFTASKS
+
+#define LARGENUMBER 1.0e+18
+
+#ifndef CAPACITY
+#define CAPACITY 0
+#endif
+
+#ifndef PRINTCOMPLETESCHEDULE
+#define PRINTCOMPLETESCHEDULE 0
+#endif
+using namespace std;
+
+class Job
+{
+    public:
+        int id;
+        int new_id;
+        double A;
+        double B;
+};
+class ChangeCost
+{
+    public:
+        double cost;
+        int id;
+};
+
+
+class Task
+{
+    public:
+        int rank;
+        unsigned int task_id;
+
+        double input_comm_time, comp_time, output_comm_time;
+        long unsigned int input_volume, output_volume;
+
+        double start_comm_time, end_comm_time;
+        double start_comp_time, end_comp_time;
+
+        long unsigned int internal_memory_requirement;
+        long unsigned int memory_requirement;
+
+        long unsigned int available_memory_after_comm_scheduling = CAPACITY;
+        long unsigned int available_memory_after_comp_scheduling = CAPACITY;
+        std::string task_name;
+        //private:
+        long unsigned int getMemoryRequirement() { return input_volume + internal_memory_requirement; }
+};
+
+bool sortByRank(Task x, Task y) {return x.rank <= y.rank;}
+bool sortByValue(ChangeCost& x, ChangeCost& y) {return x.cost  < y.cost;}
+bool sortByB(Job x, Job y) {return x.B <= y.B;}
+bool sortByA(Job x, Job y) {return x.A <= y.A;}
+bool sortByNewId(Job x, Job y) { return x.new_id <= y.new_id;}
+
+
+void compute_schedule_for_specified_order(Task tasks[], int ntasks, long unsigned int capacity)
+{
+    long unsigned int available_memory_for_present_task = capacity;
+    double early_available_comm_time = 0;
+    double early_available_comp_time = 0;
+    std::queue<Task> computation_queue;
+
+    long unsigned int i=0;
+    //k denotes the index of next task in computation channel 
[…]

### 2019-03-27 ExperimentalData/heuristics.cpp

@@ -20,22 +20,22 @@ using namespace std;
 class Task
 {
     public:
-        unsigned int task_id;
+        long unsigned int task_id;
 
         double input_comm_time, comp_time, output_comm_time;
-        unsigned int input_volume, output_volume;
+        long unsigned int input_volume, output_volume;
 
         double start_comm_time, end_comm_time;
         double start_comp_time, end_comp_time;
 
-        unsigned int internal_memory_requirement;
-        unsigned int memory_requirement;
+        long unsigned int internal_memory_requirement;
+        long unsigned int memory_requirement;
 
-        unsigned int available_memory_after_comm_scheduling = CAPACITY;
-        unsigned int available_memory_after_comp_scheduling = CAPACITY;
+        long unsigned int available_memory_after_comm_scheduling = CAPACITY;
+        long unsigned int available_memory_after_comp_scheduling = CAPACITY;
         std::string task_name;
         //private:
-        unsigned int getMemoryRequirement() { return input_volume + internal_memory_requirement; }
+        long unsigned int getMemoryRequirement() { return input_volume + internal_memory_requirement; }
 };
 
 //TODO: don't think how we can use it as the first step of quick sort
@@ -50,7 +50,7 @@ bool commPlusCompDecrease(Task x, Task y) { return x.input_comm_time + x.comp_ti
 void optimal_order_infinite_memory(Task tasks[], int ntasks)
 {
     Task tmp = tasks[ntasks-1];
-    unsigned int i = ntasks-1;
+    long unsigned int i = ntasks-1;
 
     for(int j=ntasks-2; j>=0; j--)
     {
@@ -75,14 +75,14 @@ void optimal_order_infinite_memory(Task tasks[], int ntasks)
 
 void compute_schedule_for_specified_order(Task tasks[], int ntasks)
 {
-    unsigned int available_memory_for_present_task = CAPACITY;
+    long unsigned int available_memory_for_present_task = CAPACITY;
     double early_available_comm_time = 0;
     double early_available_comp_time = 0;
     std::queue<Task> computation_queue;
 
-    unsigned int i=0;
+    long unsigned int i=0;
     //k denotes the index of next task in computation channel 
-    unsigned int k=0;
+    long unsigned int k=0;
     //While all tasks complete on computation channel
     while(k<ntasks)
     {
@@ -144,8 +144,8 @@ void print_schedule(string alg_name, Task tasks[], int ntasks)
[…]

### 2019-03-27 ExperimentalData/scripts/all_Gilmore_Gomory.sh

@@ -1,0 +1,48 @@
+#!/bin/bash
+
+nfiles=$1
+min_memory_requirement=0
+
+
+for((k=0; k<$nfiles; k++))
+do
+input=output_readable_${k}.txt
+cat $input | tail -n +2 >temp1
+Y=$(awk 'BEGIN{max_memory=0;}{if(($1) *8 >max_memory)max_memory= $1 * 8;}END{printf("%d", max_memory);}' temp1)
+if [ $min_memory_requirement -lt $Y ];
+then
+min_memory_requirement=$Y
+fi
+
+done;
+
+echo "#Capacity Gilmore_Gomory_makespan" >results_Gilmore_Gomory.txt
+
+for((k=0; k<$nfiles; k++))
+do
+input=output_readable_${k}.txt
+cat $input | tail -n +2 >temp1
+#echo "#input_volume comm_time comp_time" >temp2
+awk '{printf("%d %0.9f %0.9f\n", ($1)*8, ($2)/1, $NF - $2-$4);}' temp1 >temp2
+
+rm temp1
+
+mv temp2 input.txt
+
+
+
+
+X=$min_memory_requirement
+g++-7  ~/DataTransferSimulation/exp/Gilmore_Gomory.cpp -DCAPACITY=$X  -o Gilmore_Gomory
+./Gilmore_Gomory >> results_Gilmore_Gomory.txt
+#INC=$((min_memory_requirement/10))
+#for((i=0; i<10; i++))
+#do
+##echo "Memory Capacity = $X"
+#g++-7  ~/DataTransferSimulation/exp/Gilmore_Gomory.cpp -DCAPACITY=$X  -o Gilmore_Gomory
+#./Gilmore_Gomory >> results_Gilmore_Gomory.txt
+#
+#X=$((X+INC))
+#done
+
+done

### 2019-03-27 ExperimentalData/scripts/all_algorithms.sh

@@ -1,0 +1,74 @@
+#!/bin/bash
+
+nfiles=$1
+min_memory_requirement=0
+
+
+for((k=0; k<$nfiles; k++))
+do
+input=output_readable_${k}.txt
+cat $input | tail -n +2 >temp1
+Y=$(awk 'BEGIN{max_memory=0;}{if(($1) *8 >max_memory)max_memory= $1 * 8;}END{printf("%d", max_memory);}' temp1)
+if [ $min_memory_requirement -lt $Y ];
+then
+min_memory_requirement=$Y
+fi
+
+done;
+
+
+>capacity_values.txt
+>makespan_values.txt
+
+for((k=0; k<$nfiles; k++))
+do
+input=output_readable_${k}.txt
+cat $input | tail -n +2 >temp1
+#echo "#input_volume comm_time comp_time" >temp2
+awk '{printf("%d %0.9f %0.9f\n", ($1)*8, ($2)/1, $NF - $2-$4);}' temp1 >temp2
+
+awk 'BEGIN{sum_comm=0; sum_comp=0;}{sum_comm+= $2; sum_comp+= $3;}END{printf("%0.9f %0.9f %0.9f %0.9f", sum_comm,
+                                                                              sum_comp,
+                                                                              sum_comm>sum_comp?sum_comm:sum_comp,
+                                                                              sum_comm+sum_comp);}' temp2 >temp1
+
+#echo "Min_memory_required($i) = $Y"
+sum_comm=$(awk '{print $1}' temp1)
+sum_comp=$(awk '{print $2}' temp1)
+min_time=$(awk '{print $3}' temp1)
+sum_comm_comp=$(awk '{print $4}' temp1)
+
+rm temp1
+
+mv temp2 input.txt
+
+
+nalgs=13
+
+
+X=$min_memory_requirement
+INC=$((min_memory_requirement/10))
+for((i=0; i<10; i++))
+do
+g++  ~/DataTransferSimulation/exp/heuristics.cpp -DCAPACITY=$X  -o heuristics
+for((j=0; j<$nalgs; j++))
+do
+./heuristics $j 
+done > temp
+awk '{print $2}' temp | sed ':a;N;$!ba;s/\n/ /g' >>makespan_values.txt
+echo $X $sum_comm_comp $min_time $sum_comm $sum_comp>>capacity_values.txt
+
+
+X=$((X+INC))
+done
+
+done
+
[…]

### 2019-03-27 ExperimentalData/scripts/generate_concise_trace.sh

@@ -1,0 +1,17 @@
+#!/bin/bash
+
+
+nfiles=$1
+mkdir -p readable
+for((i=0; i<$nfiles; i++))
+do
+input=output_${i}.txt
+grep rank $input >tmp
+output=output_readable_${i}.txt
+{
+echo "#input_size get_time acc_size acc_time op_type overall_time";
+awk '{ if($9 == "get_time="){ $4 += $8; $6+=$10;} printf("%d %0.9f %d %0.9f %s %0.9f\n", $4, $6,
+        $(NF-6), $(NF-4), $(NF-1), $NF); }' tmp
+}>readable/$output
+rm tmp
+done;

### 2019-03-27 ExperimentalResults/insight.R

@@ -1,0 +1,25 @@
+#!/usr/bin/env Rscript
+insights_func <-function(file_name)
+{
+library(ggplot2)
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+
+
+dftest[,1:ncol(dftest)]<-dftest[,1:ncol(dftest)]/dftest[,5]
+dftest[,5]<-NULL
+dftestMelted<-melt(dftest)
+names(dftestMelted)<-c( "Parameter", "ratio_to_optimal")
+p<-ggplot(dftestMelted, aes(x=Parameter, y=ratio_to_optimal, color=Parameter))  + geom_boxplot(outlier.color="black") + geom_hline(yintercept=1, linetype="dashed", color = "red")
+p <- p + theme(plot.title = element_text(hjust = 0.5), legend.position='none') +  ggtitle("Application Properties") + scale_y_continuous(breaks=seq(0.0, 2.0, 0.5), limits=c(0, 2))
+#p <- p + theme(plot.title = element_text(hjust = 0.5), legend.position='none') +  ggtitle("Application Properties") 
+
+return (p)
+}
+p<-insights_func('insight_hf.txt')
+ggsave(file="application_properties_hf.pdf", p, width=23.6, height=13.4)
+
+p<-insights_func('insight_ccsd.txt')
+ggsave(file="application_properties_ccsd.pdf", p, width=23.6, height=13.4)
+
+

### 2019-03-27 ExperimentalResults/inverse_ratio_to_optimal-best.R

@@ -1,0 +1,26 @@
+#!/usr/bin/env Rscript
+inverse_ratio_to_optimal_best_func <-function(file_name)
+{
+library(ggplot2)
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
+
+dftest[,8]<-NULL
+dftest[,c(2:6)]<-NULL
+dftest$static_best<-do.call('pmin', c(dftest[,3:7]))
+dftest$dynamic_best<-do.call('pmin', c(dftest[,8:10]))
+dftest$static_dynamic_best<-do.call('pmin', c(dftest[,11:13]))
+dftest<-dftest[,c(1,2,14:16)]
+dftestMelted<-melt(dftest, "capacity")
+names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
+p<-ggplot(dftestMelted, aes(x=capacity, y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth()
+p<-p + ylab("inverse(ratio_to_optimal)") + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Performance With Best of all categories")
+return (p)
+}
+p<-inverse_ratio_to_optimal_best_func('all_results_hf.txt')
+ggsave(file="inverse_ratio_to_optimal_hf-best.pdf", p, width=23.6, height=13.4)
+
+p<-inverse_ratio_to_optimal_best_func('all_results_ccsd.txt')
+ggsave(file="inverse_ratio_to_optimal_ccsd-best.pdf", p, width=23.6, height=13.4)
+

### 2019-03-27 ExperimentalResults/ratio_to_optimal.R

@@ -1,0 +1,19 @@
+#!/usr/bin/env Rscript
+ratio_to_optimal_func <-function(file_name)
+{
+library(ggplot2)
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
+dftest[,2:6]<-NULL
+dftestMelted<-melt(dftest, "capacity")
+names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
+p<-ggplot(dftestMelted, aes(x=Heuristic, y=ratio_to_optimal, color=Heuristic)) + geom_boxplot(outlier.color="black") +facet_wrap(~capacity)  + theme(axis.ticks = element_blank(), axis.text.x = element_blank()) + xlab("")
+p <- p + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Ratio to Optimal")
+return (p)
+}
+p<-ratio_to_optimal_func('all_results_hf.txt')
+ggsave(file="ratio_to_optimal_hf.pdf", p, width=23.6, height=13.4)
+
+p<-ratio_to_optimal_func('all_results_ccsd.txt')
+ggsave(file="ratio_to_optimal_ccsd.pdf", p, width=23.6, height=13.4)

### 2019-03-27 exp/all_algorithms.sh

@@ -1,39 +1,0 @@
-#!/bin/bash
-
-input=$1
-cat $input | tail -n +2 >temp1
-#echo "#input_volume comm_time comp_time" >temp2
-awk '{printf("%d %0.9f %0.9f\n", ($1)*8, $2, $NF - $2-$4);}' temp1 >temp2
-rm temp1
-Y=$(awk 'BEGIN{max_memory=0;}{if($1>max_memory)max_memory=$1;}END{printf("%d", max_memory);}' temp2)
-SCC=$(awk 'BEGIN{sum=0;}{sum+= $2 + $3;}END{printf("%0.9f", sum);}' temp2)
-#echo "Y=$Y"
-mv temp2 input.txt
-
-
-nalgs=12
-
-echo "#capacity sum_comm_cmp" >capacity.txt
-
->makespans.txt
-X=$Y
-INC=$((Y/10))
-for((i=0; i<10; i++))
-do
-g++ -g heuristics.cpp -DCAPACITY=$X  -o heuristics
-for((j=0; j<$nalgs; j++))
-do
-./heuristics $j 
-done > temp
-awk '{print $2}' temp | sed ':a;N;$!ba;s/\n/ /g' >>makespans.txt
-echo $X $SCC>>capacity.txt
-
-
-X=$((X+INC))
-done
-
-awk '{print $1}' temp | sed ':a;N;$!ba;s/\n/ /g' >header.txt
-rm temp
-
-cat makespans.txt >>header.txt
-paste capacity.txt header.txt

### 2019-03-28 Article/article.tex
description of performance plots

@@
 \usepackage{framed}
-\usepackage{caption}
+%%\usepackage{caption}
+\usepackage{subcaption}
 \usepackage{todonotes}
@@
 
-	\section{Experimental Results}
-	\label{sec:exp}
-
-	\todo[inline]{Machine information and our model}
-
-	We consider a machine called Cascade, available at PNNL, for our experiments.
-We obtain traces by running  two molecular chemistry applications,  double precision version of Hartree-Fock (HF) and Coupled Cluster Single Double (CCSD) of NWChem package with 4 Uracil molecules input on 10 nodes of this machine.
-Each node is composed of 16 Intel Xeon E5-2670 cores, hence we use 160 processes for the execution.
-Each process executes 300-800 tasks.
-NWChem takes advantages of a Partitioned Global Address Space Programming Model, Global Arrays (GA), to use shared-memory programming APIs  on distributed memory computers.
-Our data transfer model is quite simple and  we consider that all data transfers between each process's local memory and GA memory take the same route.
-Modeling of different routes of data transfers for the same source-destination pair, bandwidth sharing for different source-destination pairs and network congestion is more challenging and part of our future work.
-Our model is simple yet it provides insight to the application developers (or runtime system) that  in what-order all data transfer  are issued for the same source-destination pair to maximise communication-computation overlap.
-Our model is easily adaptable to any source-destination where there is one fixed route between source and destination (such as between CPU and GPU, one copy engine to transfer data from CPU (resp.
-GPU) to GPU (resp.
-CPU) ).
-	\todo[inline]{More about tiling}
-	Both application mainly perform two types of computations, tensor transpose and tensor contractions.
-HF expects to specify a tile size and we set it to 100, so that each core can be efficiently utilize.
-CCSD automatically determines tile sizes at different program points based on the input (molecule?).
-Hence, HF operates on almost homogeneous tiles while CCSD on heterogeneous tiles.
-
-%%	\todo[inline]{Scheduled based on Gilmore-Gomory algorithm and its performance }
-	We also consider an algorithm, proposed by Gilmore and Gomory, to obtain the minimal cost sequence for a set of jobs.
-In this algorithm, each job has a start and end state and a cost is associated to change the state.
-In our context, this cost can be seen as non-overlap time of computation for two adjacent jobs.
-Here is the main idea of this algorithm.
-Initially partial sequence of jobs is represented by a graph such that their overlap is maximum.
-Subsequently edges are added to this graph which minimized the total non-overlap cost  and connects two components.
-When all nodes of this graph is connected then an edge interchange mechanism is taken into account to determine the sequence of jobs, which ensures that the sequence has minimal cost.
-
-	We refer ~\cite{Gilmore-Gomory:1964} for the detailed algorithm and ~\cite{gitworkrepo} for our implementation.
-This algorithm does not take memory capacity into consideration and only provides the sequence of processing.
-We applied the same sequence with different memory capacity restrictions for our experiments and call this heuristic as \textit{Gilmore-Gomory}.
-
-	\todo[inline]{Skumar: HF performance plots}
-	\begin{figure}[htb]
-		\includegraphics[scale=0.25]{../HFPlots/ratio_to_optimal.pdf}
-		\caption{HF Performance.}
-		\label{fig:staticOrderDynamicCorrectionsExample}
-	\end{figure}
-	\begin{figure}[htb]
-	\includegraphics[scale=0.25]{../CCSDPlots/best_ccsd.pdf}
-	\caption{HF best Performance.}
-	\label{fig:staticOrderDynamicCorrectionsExample}
-\end{figure}
-	\todo[inline]{Skumar: CCSD performance plots}
-		\begin{figure}[htb]
-		\includegraphics[scale=0.25]{../CCSDPlots/ratio_to_optimal_ccsd.pdf}
-		\caption{CCSD Performance.}
-		\label{fig:staticOrderDynamicCorrectionsExample}
-	\end{figure}
-	\begin{figure}[htb]
-		\includegraphics[scale=0.25]{../CCSDPlots/best_ccsd.pdf}
-		\caption{CCSD best Performance.}
-		\label{fig:staticOrderDynamicCorrectionsExample}
-	\end{figure}
-	\todo[inline]{Skumar: Effect of Random memory with HF or CCSD}
-
-	\begin{figure}[htb]
-	\includegraphics[scale=0.25]{../HFPlots/ratio_to_optimal_random_memory.pdf}
-	\caption{HF Performance with random memory requirement of a task.}
-	\label{fig:staticOrderDynamicCorrectionsExample}
-\end{figure}	
-	\todo[inline]{SKumar: Evaluate different metrics for HF, Cholesky and CCSD applications}
-	\todo[inline]{SKumar: decide metrics: ratio to optimal, percentage overlap, 100 - percentage non overlap}
-	\begin{itemize}
-		\item Machine description
-		\item temporary data requirement
-		\item Description of all kernels (Molecular Chemistry Kernels)
-		\item Think about results and graphs (Most probably results in $R$ plots)
-	\end{itemize}
-\newpage
+\subsection{Favorable Situation for Heuristics}
 \noindent The following table exhibits favorable scenarios for different heuristics.
@@
 
-\newpage
+	\section{Experimental Results}
+	\label{sec:exp}
+
+	\todo[inline]{Machine information and our model}
+
+	We consider a machine called Cascade, available at PNNL, for our experiments.
+We obtain traces by running  two molecular chemistry applications,  double precision version of Hartree-Fock (HF) and Coupled Cluster Single Double (CCSD) of NWChem package with 4 Uracil molecules input on 10 nodes of this machine.
+Each node is composed of 16 Intel Xeon E5-2670 cores, hence we use 160 processes for the execution.
+Each process executes 300-800 tasks.
+NWChem takes advantages of a Partitioned Global Address Space Programming Model, Global Arrays (GA), to use shared-memory programming APIs  on distributed memory computers.
+Our data transfer model is quite simple and  we consider that all data transfers between each process's local memory and GA memory take the same route.
+Modeling of different routes of data transfers for the same source-destination pair, bandwidth sharing for different source-destination pairs and network congestion is more challenging and part of our future work.
+Our model is simple yet it provides insight to the application developers (or runtime system) that  in what-order all data transfer  are issued for the same source-destination pair to maximise communication-computation overlap.
+Our model is easily adaptable to any source-destination where there is one fixed route between source and destination (such as between CPU and GPU, one copy engine to transfer data from CPU (resp.
+GPU) to GPU (resp.
+CPU) ).
+	\todo[inline]{More about tiling}
+	Both applications mainly perform two types of computations, tensor transpose and tensor contractions.
+HF expects to specify a tile size and we set it to 100, so that each core can be efficiently utilize.
+CCSD automatically determines tile sizes at different program points based on the input (molecule?).
+Hence, HF operates on almost homogeneous tiles while CCSD on heterogeneous tiles.
+
+%%	\todo[inline]{Scheduled based on Gilmore-Gomory algorithm and its performance }
+	We also consider an algorithm, proposed by Gilmore and Gomory, to obtain the minimal cost sequence for a set of jobs.
+In this algorithm, each job has a start and end state and a cost is associated to change the state.
+In our context, this cost can be seen as non-overlap time of computation for two adjacent jobs.
+Here is the main idea of this algorithm.
+Initially partial sequence of jobs is represented by a graph such that their overlap is maximum.
+Subsequently edges are added to this graph which minimized the total non-overlap cost  and connects two components.
+When all nodes of this graph is connected then an edge interchange mechanism is taken into account to determine the sequence of jobs, which ensures that the sequence has minimal cost.
+
+	We refer ~\cite{Gilmore-Gomory:1964} for the detailed algorithm and ~\cite{gitworkrepo} for our implementation.
+This algorithm does not take memory capacity into consideration and only provides the sequence of processing.
+We applied the same sequence with different memory capacity restrictions for our experiments and call this heuristic as \textit{Gilmore-Gomory}.
+
+	\todo[inline]{may convert 10 subplots to 8 in all performance diagrams}
+	\todo[inline]{increase font size in all plots, may be free scale-y}
+	\todo[inline]{SKumar: decide metrics: ratio to optimal, percentage overlap, 100 - percentage non overlap}
+
+	IWe evaluate different data transfer heuristics for the several memory capacities.
+From the obtained traces, first we determine the minimum requirement of the memory capacity $m_c$ to execute all tasks.
+Then we observe the behavior of all heuristics with memory capacity  $m_c$ to $2m_c$, in the gap of $0.1m_c$.
+Our performance metric is $ratio\_to\_optimal$, which is defined as the following.
+Let the makespan of a heuristic $H$ is $M_H$ and the makespan of the $optimal  case$ with infinite memory is $M_O$, then  $ratio\_to\_optimal (H)$ is $\frac{M_H}{M_O}$ (lower value is better).
+This value would be  greater or equal to $1$.
+A value closer to $1$ indicates that suitability of a particular heuristic and maximum possible communication-computation overlap has been achieved for that heuristic.
+
+	Figures ~\ref{fig:ratio_to_optimal_hf} and ~\ref{fig:ratio_to_optimal_ccsd} depict the distribution of the performance  of each heuristic for all considered memory capacities, where plots are categorized by memory capacities.
+For each memory capacity and each heuristic, the box on the plot displays the median, first and last quartile, and the whiskers indicate minimum and maximum values, with outliers are shown by black dots.
+\subsection{HF Performance}	
+	\begin{figure}[htb]
+		\includegraphics[scale=0.3]{../ExperimentalResults/ratio_to_optimal_hf.pdf}
+		\caption{Comparison of different heuristics for HF.}
+		\label{fig:ratio_to_optimal_hf}
+	\end{figure}
+ As indicated above, HF tasks are highly homogeneous, this is also noticeable in Figure~\ref{fig:ratio_to_optimal_hf}.
+All heuristics depict similar behavior for minimum memory capacity $m_c$  and  increasing the memory capacity slightly does not change the performance of all heuristics.
+As memory capacity increased further, dynamic variants of heuristics starts performing better and for the moderate memory capacities (close to $2m_c$ ), staticOrderDynamicCorrection variants outperforms others.
+\textit{Gilmore-Gomory} heuristic does not achieve good performance.
+it can be understand from the fact that task sequence is obtained considering no extra memory is available, but here we apply the same sequence for a different scenario,  overall memory consumed at each point is limited to memory capacity.
+
+	\begin{figure}[htb]
+	\includegraphics[scale=0.25]{../ExperimentalResults/inverse_ratio_to_optimal_hf-best.pdf}
+	\caption{Comparision of best variants of all categories for HF.}
+	\label{fig:ratio_to_optimal_best_hf}
+	\end{figure}
+
+Figure~\ref{fig:ratio_to_optimal_best_hf} shows the performance comparison of best variants of all categories with the $order_of_submission$ strategy.
+Static strategies are expected to perform better when there is not any memory capacity restriction, hence this plot indicates that static strategies face capacity bottleneck and underperform.
+Dynamic strategies achieve better performance with limited memory capacity and staticOrderDynamicCorrection  strategies suit in moderate memory capacity scenarios.
+
+\subsection{CCSD Performance}
+
+	\begin{figure}[htb]
+	\includegraphics[scale=0.3]{../ExperimentalResults/ratio_to_optimal_ccsd.pdf}
+	\caption{Comparison of different heuristics for CCSD.}
+	\label{fig:ratio_to_optimal_ccsd}
+	\end{figure}
+
+CCSD application operates on tasks of different sizes, hence different heuristics depict distinct behaviors even at minimum memory capacity $m_c$ .
+Heterogeneity favors to dynamic strategies, therefore both dynamic and static+dynamic correction based strategies perform good than  static based strategies.
+Similar to HF,  static+dynamic correction based strategies outperform others as memory capacity becomes moderate.
+
+	\begin{figure}[htb]
+	\includegraphics[scale=0.25]{../ExperimentalResults/inverse_ratio_to_optimal_ccsd-best.pdf}
+	\caption{Comparision of best variants of all categories for CCSD.}
+	\label{fig:ratio_to_optimal_best_ccsd}
+	\end{figure}
+
+Figure~\ref{fig:ratio_to_optimal_best_ccsd} shows that best variants of dynamic and static+dynamic strategies achieve similar performance at minimum memory capacity $m_c$.
+But as memory capacity increases hterogeneity allows static+dynamic strategies to take advantage of static knowledge to get maximum overlap and dynamic correction to select another task in case of memory capacity limitation.
+Static strategies also start performing better at the end, which indicates that this application has potential for significant communication-computation overlap and pure dynamic strategies are unable to take scheduling decision based on this information.
+
+\subsection{HF and CCSD Characteristics}
+
+\begin{figure}[htb]
+	\centering
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=.95\linewidth]{../ExperimentalResults/application_properties_hf.pdf}
+		\caption{HF workloads}
+		\label{fig:hfProperties}
+	\end{subfigure}%
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=.95\linewidth]{../ExperimentalResults/application_properties_ccsd.pdf}
+		\caption{CCSD workloads}
+		\label{fig:ccsdProperties}
+	\end{subfigure}
+	\caption{HF and CCSD tasks characteristics.}
+	\label{fig:ApplicationProperties}
+\end{figure}
+
+To get more insights into the considered applications, we also look in to their workloads.
+Figure~\ref{fig:ApplicationProperties} exhibits that HF is a communication intensive application and maximum 20\%  can be expected in the best scenario.
+While in CCSD , communications and computations are almost evenly distributed and  40-75\% communication-computation overlap is possible.
+
+\subsection{LP Formulation}
+%%\todo[inline]{SKumar: LP evaluation and discussion}
+%%
+%%	\todo[inline]{Skumar: Effect of Random memory with HF or CCSD}
+%%	
+\subsection{Impact of heterogeneity on different heuristics}
+
+	\begin{figure}[htb]
+	\includegraphics[scale=0.3]{../ExperimentalResults/ccsd-random/ratio_to_optimal_ccsd_random.pdf}
+	\caption{Comparison of different heuristics for CCSD with highly heterogeneous tasks.}
+	\label{fig:ratio_to_optimal_ccsd_random}
+	\end{figure}
+
+To know the affect of heterogeneity, we set the memory requirement of each task in CCSD trace randomly between 100 to 900 and observe the behavior of different heuristics in  Figure~\ref{fig:ratio_to_optimal_ccsd_random}.
+This plot also exhibits that static+dynamic variants make good use of static information to maximize communication-computation overlap and dynamic mechanism to minimize the penalty caused by memory capacity limitation.
+Pure static strategies suffer from memory capacity imitation and pure dynamic strategies are unable to maximize communication-computation overlap.
+
+\subsection{Tasks in Batches}
+%%	\begin{figure}[htb]
+%%	\includegraphics[scale=0.25]{../ExperimentalResults/ccsd-random/ratio_to_optimal_ccsd_random.pdf}
+%%	\caption{HF Performance with random memory requirement of a task.}
+%%	\label{fig:staticOrderDynamicCorrectionsExample}
+%%\end{figure}
+
 \section{Conclusion and Perspectives}
@@
 \end{itemize}
+
+%%	\begin{itemize}
+%%		\item Machine description
+%%		\item temporary data requirement
+%%		\item Description of all kernels (Molecular Chemistry Kernels)
+%%		\item Think about results and graphs (Most probably results in $R$ plots)
+%%	\end{itemize}
+
 %%%%	\section{First Section}

### 2019-03-28 Article/article.tex
MILP results

@@
 \subsection{Solving Linear Program Iteratively}
-%%\subsection{Solving Linear Program Iteratively}
+\label{subsec:linearprogrammingformulation}
 We use a mixed integer linear program  to obtain the order of data transfers and computations.
@@
 
-\subsection{LP Formulation}
+\subsection{MILP Based Strategy}
+ We use GLPK solver v4.65 to solve the MILP problem described in Section~\ref{subsec:linearprogrammingformulation}.
+The solver was unable to handle number of variables required to solve MILP at the scale of our interest.
+Hence, we solve the linear program iteratively for a small subset of size $k=3,4,5$ (solver was unable to handle number of variables required for $k\ge6$ ) and represent the makespan calculated by this heuristic as $lp.k$.
+At the boundary of two iterations we fixed the event (communication or computation) of an unfinished task who has  started before the boundary point and consider other events flexible.
+We compute various  $lp.k$ values for different memory capacities and observe that most of the other heuristics perform better than this heuristic.
+Figure~\ref{fig:iterativeLpSolution} shows the comparison of different heuristics with MILP based heuristic for various memory capacities of a single trace file.
+
+	\begin{figure}[htb]
+	\includegraphics[scale=0.25]{../ExperimentalResults/makespan_with_lp.pdf}
+	\caption{Comparision of different heuristics with MILP solution based heuristic.}
+	\label{fig:iterativeLpSolution}
+\end{figure}
+
 %%\todo[inline]{SKumar: LP evaluation and discussion}
@@
 
-\subsection{Tasks in Batches}
+%%\subsection{Tasks in Batches}
 %%	\begin{figure}[htb]

### 2019-03-28 ExperimentalData/communication_lp.h

@@ -1,0 +1,563 @@
+/* first_glpk.c */
+#include <stdio.h>
+#include <stdlib.h>
+#include <glpk.h>
+#include <assert.h>
+
+#define EPS 0.000000001
+
+
+static int counter = 0;
+
+void formulate_lp(int n, unsigned int capacity, double* CM, double* CP, unsigned int* cap, unsigned int* tm, int* fixed_start_comm_time, double* start_comm_time, int* fixed_start_comp_time, double* start_comp_time)
+{
+    glp_prob *lp;
+    int ia[1+1000];
+    int ja[1+1000];
+
+    double ar[1+1000];
+
+
+    int iter1, iter2;
+    double L = 0;
+
+    for(iter1 = 1; iter1 <= n; iter1++)
+        L += CM[iter1] + CP[iter1];
+
+    lp = glp_create_prob();
+
+    glp_set_prob_name(lp, "lp_formulation_for_communication_proble");
+    glp_set_obj_dir(lp, GLP_MIN);
+
+    int ncols = 4 * n * (n+1) + 1 + 1;
+    glp_add_cols(lp, ncols);
+
+    int icol = 0;
+
+    //n s_i variables to denote the start time of communication
+    for(iter1 = 1; iter1 <= n; iter1++)
+    {
+        ++icol;
+
+        char name[100];
+        sprintf(name, "s%d", iter1); 
+        glp_set_col_name(lp, icol, name);
+
+        if(fixed_start_comm_time[iter1])
+            glp_set_col_bnds(lp, icol, GLP_FX, start_comm_time[iter1], 0.0); 
+        else
+            glp_set_col_bnds(lp, icol, GLP_LO, 0.0, 0.0); 
+
+    }
+
+    //n e_i variables to denote the end time of communication
+    for(iter1 = 1; iter1 <= n; iter1++)
+    {
+        ++icol;
+
+        char name[100];
+        sprintf(name, "e%d", iter1); 
+        glp_set_col_name(lp, icol, name);
+
+        if(fixed_start_comm_time[iter1])
+            glp_set_col_bnds(lp, icol, GLP_FX, start_comm_time[iter1] + CM[iter1], 0.0); 
+        else
+            glp_set_col_bnds(lp, icol, GLP_LO, 0.0, 0.0); 
+
+    }
+
[…]

### 2019-03-28 ExperimentalData/solve_milp_iteratively.cpp

@@ -1,0 +1,265 @@
+#include <iostream>
+#include <string>
+#include <algorithm>
+#include <queue>
+#include <limits>
+#include <iomanip>
+#include <fstream>
+#include <sstream>
+
+#include <communication_lp.h>
+
+#define MAXNUMBEROFTASKS 10000
+#define SUBSETMAXNUMBEROFTASKS 15
+
+#ifndef CAPACITY
+#define CAPACITY 0
+#endif
+
+#ifndef SCALEFACTOR
+#define SCALEFACTOR 1
+#endif
+
+#ifndef PRINTCOMPLETESCHEDULE
+#define PRINTCOMPLETESCHEDULE 0
+#endif
+
+using namespace std;
+
+class Task
+{
+    public:
+        unsigned int task_id;
+
+        double input_comm_time, comp_time, output_comm_time;
+        unsigned int input_volume, output_volume;
+
+        double start_comm_time, end_comm_time;
+        double start_comp_time, end_comp_time;
+
+        unsigned int internal_memory_requirement;
+        unsigned int memory_requirement;
+
+        unsigned int available_memory_after_comm_scheduling = CAPACITY;
+        unsigned int available_memory_after_comp_scheduling = CAPACITY;
+        std::string task_name;
+        //private:
+        unsigned int getMemoryRequirement() { return input_volume + internal_memory_requirement; }
+};
+
+//Print scheduling trace
+//void print_schedule(string alg_name, Task tasks[], int ntasks, ofstream outputfile)
+void print_schedule(string alg_name, Task tasks[], int ntasks)
+{
+    double makespan = 0;
+    if(PRINTCOMPLETESCHEDULE)
+        cout<<"#TaskId start_comm end_comm avail_mem_after_comm_sched start_comp end_comp avail_mem_after_comp_sched\n";
+    for(auto i=0; i<ntasks; i++)
+    {
+        if(tasks[i].end_comp_time > makespan)
+            makespan = tasks[i].end_comp_time;
+
+        if(PRINTCOMPLETESCHEDULE)
+            cout<<tasks[i].task_id<<" "<<tasks[i].start_comm_time<<" "<<tasks[i].end_comm_time<<" "<<tasks[i].available_memory_after_comm_scheduling<< " "<<tasks[i].start_comp_time<<" "<<tasks[i].end_comp_time<<" "<<tasks[i].available_memory_after_comp_scheduling<<endl;
+    }
[…]

### 2019-03-28 Article/article.tex
minor

@@
 \usepackage{subcaption}
+\captionsetup{compatibility=false}
 \usepackage{todonotes}
@@
 \section{Conclusion and Perspectives}
-\begin{itemize}
-	\item Evaluated different heuristics
-	\item proved NP-complete problem
-	\item Plan to implement the best heuristic in a runtime system  for NWChem algorithms and evaluation on Summit supercomputer
-\end{itemize}
+
+In this article, we consider the problem of deciding the order of data transfers between two memory nodes such that overlap of communication and  computation is maximized.
+With Exascale computing, applications face bottlenecks due to communications.
+Hence, it is extremely important to achieve the maximum overlap of computation and communication in order to exploit the full potential of the system.
+We show that determining the order of data transfers is an NP complete problem.
+We proposed multiple data transfer heuristics and evaluated them on two molecular chemistry kernels, HF and CCSD.
+Our results show that some of our heuristics achieve significant overlap and perform very close to the lower bound of makespan.
+We plan to evaluate our strategies on different applications coming from multiple domains.
+We also plan to study the behavior of our strategies in the context of overlapping CPU-GPU communications with computation.
+A runtime system aims at exposing different heuristics, to maximize the communication-computation overlap, at developer level and automatically selecting the best one is currently underway.
 
@@
 
-%%%%	\section{First Section}
-%%%%	 \subsection{A Subsection Sample} Please note that the
-%%%%	first paragraph of a section or subsection is not indented. The first paragraph
-%%%%	that follows a table, figure, equation etc. does not need an indent, either.
-%%%%	
-%%%%	Subsequent paragraphs, however, are indented.
-%%%%	
-%%%%	\subsubsection{Sample Heading (Third Level)} Only two levels of headings should
-%%%%	be numbered. Lower level headings remain unnumbered; they are formatted as
-%%%%	run-in headings.
-%%%%	
-%%%%	\paragraph{Sample Heading (Fourth Level)} The contribution should contain no
-%%%%	more than four levels of headings. Table~\ref{tab1} gives a summary of all
-%%%%	heading levels.
-%%%%	
-%%%%	\begin{table} \caption{Table captions should be placed above the
-%%%%			tables.}\label{tab1} \begin{tabular}{|l|l|l|} \hline Heading level &  Example &
-%%%%			Font size and style\\ \hline Title (centered) &  {\Large\bfseries Lecture
-%%%%				Notes} & 14 point, bold\\ 1st-level heading &  {\large\bfseries 1 Introduction}
-%%%%			& 12 point, bold\\ 2nd-level heading & {\bfseries 2.1 Printing Area} & 10
-%%%%			point, bold\\ 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text
-%%%%			follows & 10 point, bold\\ 4th-level heading & {\itshape Lowest Level Heading.}
-%%%%			Text follows & 10 point, italic\\ \hline \end{tabular} \end{table}
-%%%%	
-%%%%	
-%%%%	\noindent Displayed equations are centered and set on a separate line.
-%%%%	\begin{equation} x + y = z \end{equation} Please try to avoid rasterized images
-%%%%	for line-art diagrams and schemas. Whenever possible, use vector graphics
-%%%%	instead (see Fig.~\ref{fig1}).
-%%%%	
-%%%%	\begin{figure} \includegraphics[width=\textwidth]{fig1.eps} \caption{A figure
-%%%%			caption is always placed below the illustration. Please note that short
-%%%%			captions are centered, while long ones are justified by the macro package
-%%%%			automatically.} \label{fig1} \end{figure}
-%%%%	
-%%%%	\begin{theorem} This is a sample theorem. The run-in heading is set in bold,
-%%%%		while the following text appears in italics. Definitions, lemmas, propositions,
-%%%%		and corollaries are styled the same way. \end{theorem} %
-%%%%	% the environments 'definition', 'lemma', 'proposition', 'corollary',
-%%%%	% 'remark', and 'example' are defined in the LLNCS documentclass as well.
-%%%%	%
-%%%%	\begin{proof} Proofs, examples, and remarks have the initial word in italics,
-%%%%		while the following text appears in normal font. \end{proof} For citations of
-%%%%	references, we prefer the use of square brackets and consecutive numbers.
-%%%%	Citations using labels or the author/year convention are also acceptable. The
-%%%%	following bibliography provides a sample reference list with entries for
-%%%%	journal articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
-%%%%	book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1}, and a
-%%%%	homepage~\cite{ref_url1}. Multiple citations are grouped
-%%%%	\cite{ref_article1,ref_lncs1,ref_book1},
-%%%%	\cite{ref_article1,ref_book1,ref_proc1,ref_url1}. %
-%%%%	% ---- Bibliography ----
-%%%%	%
-%%%%	% BibTeX users should specify bibliography style 'splncs04'.
-%%%%	% References will then be sorted and formatted in the correct style.
-%%%%	%
-%%%%	% \bibliographystyle{splncs04}
-%%%%	% \bibliography{mybibliography}
-%%%%	%
-%%%%	\begin{thebibliography}{8} \bibitem{ref_article1} Author, F.: Article title.
-%%%%		Journal \textbf{2}(5), 99--110 (2016)
-%%%%		
-%%%%		\bibitem{ref_lncs1} Author, F., Author, S.: Title of a proceedings paper. In:
-%%%%		Editor, F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
-%%%%		Springer, Heidelberg (2016). \doi{10.10007/1234567890}
-%%%%		
-%%%%		\bibitem{ref_book1} Author, F., Author, S., Author, T.: Book title. 2nd edn.
-%%%%		Publisher, Location (1999)
-%%%%		
-%%%%		\bibitem{ref_proc1} Author, A.-B.: Contribution title. In: 9th International
-%%%%		Proceedings on Proceedings, pp. 1--2. Publisher, Location (2010)
-%%%%		
-%%%%		\bibitem{ref_url1} LNCS Homepage, \url{http://www.springer.com/lncs}. Last
-%%%%		accessed 4 Oct 2017 \end{thebibliography}
-
 \bibliographystyle{IEEEtran}

### 2019-03-29 HFPlots/script.sh
deleting few unrelated files

@@ -1,12 +1,0 @@
-dftest<-read.table('results_all_comm_one_fourth.txt', header=T)
-dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
-colnames(dftest)
-dftest[5]<-NULL
-dftest[5]<-NULL
-dftestMelted<-melt(dftest, "capacity")
-names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
-p<-ggplot(dftestMelted, aes(x=Heuristic, y=ratio_to_optimal, color=Heuristic)) + geom_boxplot(outlier.color="black") +facet_wrap(~capacity)  + theme(axis.ticks = element_blank(), axis.text.x = element_blank()) + xlab("") 
-p + theme(plot.title = element_text(hjust = 0.5)) + ggtitle("Comm_one_fourth")
-p + theme(plot.title = element_text(hjust = 0.5)) + ggtitle("Communication_one_fourth")
-ggsave(file="ratio_to_optimal_comm_one_fourth.pdf")
-

### 2019-03-31 Article/article.tex
Adding Makefile
Results for batch experiments

@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.20 of 2017/10/04
 %
 \documentclass[runningheads]{llncs} %
-\usepackage{graphicx} % Used for displaying a sample figure. If possible, figure
-% files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
+\usepackage{graphicx}
 
@@
 \usepackage{todonotes}
-%%\newtheorem{theorem}{Theorem}
-%%\newtheorem{corollary}{Corollary}[theorem]
-%%\newtheorem{lemma}[theorem]{Lemma}
-%%
-%%\newtheorem*{example}{Example}
-%%\newtheorem{remark}{Remark}
 
@@
 
+%%to comment all todos
+%\renewcommand{\todo}{}
+
 \newcommand{\hp}{{\sc HeteroPrio}\xspace}
@@
 	%	\title{Contribution Title\thanks{Supported by organization x.}}
-%%	\title{Order of Data Transfers between CPU and GPU: A Case Study}
 	\title{Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels}
@@
 We also show that with finite memory capacity obtaining the optimal order of data transfers is an NP-complete problem.
-We propose several heuristics for this problem and provide analysis of them on traces obtained by running 3 molecular chemistry kernels, namely, Hartree–Fock , Cholesky contraction, and CCSD on 16 nodes of an HPC system.
-Our results show that some of our heuristics achieve \% overlap for intermediate memory capacities and are very close to the lower bound of makespan.
-		\begin{itemize}
-			\item Task-based systems
-%%			\item goal is to provide analysis of different scheduling strategies
-%%			\item Problem with simple assumption is NP-hard
-%%			\item compare with the lower bound of performance
-		\end{itemize}
+We propose several heuristics for this problem and provide analysis of them on traces obtained by running 2 molecular chemistry kernels, namely, Hartree–Fock (HF)  and CCSD on 10 nodes of an HPC system.
+Our results show that some of our heuristics achieve significant overlap for moderate memory capacities and are very close to the lower bound of makespan.
+
 		\keywords{Communication Scheduling  \and Memory Nodes \and Molecular Chemistry.}
 	\end{abstract} %
-	%
-	%
 
 	\section{Introduction}
-
-%%	\begin{itemize}
-%%%%		\item limitation of previous approaches
-%%%%		\item scheduling problems are NP-complete, several  phenomena are added to inherent NP-hard optimization problems
-%%%%		\item hard to precisely predict the performance of both computations and communications
-%%%%		\item number of architectures have increased drastically in recent years
-%%%%		\item Task based runtime systems
-%%%%		\item Communication is one of the main bottleneck on hpc systems (cite Gullium Aupy work)
-%%%%		\item Stress on communication avoidance algorithms (Communication avoidance algorithm)
-%%%%		\item A lot of work on the computation scheduling
-%%%%		\item Assume communications can be completely overlapped for dense linear algebra computations (Our citations)
-%%%%		\item Our framework can be easily extended to any system which operates on different types of memory
-%%%%		\item To think what are the bottlenecks, which would restrict us from parallel communications
-%%%%		\item Focus and contributions of this paper
-%%				
-%%	\end{itemize}
 
@@
 Among several runtimes, we may cite QUARK~\cite{YarKhan:2011:Quark:Manual} and PaRSEC~\cite{parsec} from from ICL, Univ.
-of Tennessee Knoxville (USA), StarPU~\cite{starpu} form INRIA Bordeaux (FRANCE), Legion~\cite{legion12} from Stanford Univ.
+of Tennessee Knoxville (USA), StarPU~\cite{starpu} form INRIA Bordeaux (France), Legion~\cite{legion12} from Stanford Univ.
 (USA), StarSs~\cite{ompss} from Barcelona Supercomputing Center (Spain), KAPPI~\cite{kaapi} from INRIA Grenoble (France).
@@
 \begin{itemize}
-	%%	\item Papadimitriou work
-	%%	\item Johnson's work
-	%%	\item Kethrin Yelik work
-	%%	\item Task graph work by Loris
-	%%	\item Vivek Sarkar work
-	%%	\item Register coloring by Sethi
-	\item roofline model
 	\item theoretical/performance work on molecular chemistry kernels
@@
 
-%%	\begin{itemize} 
-%%%%		\item may consider transfer between two memory nodes
-%%%%		 \item perform experiments for transfer between CPU and GPU 
-%%%%%%		\item Task based approach, communication-computation maximum overlap 
-%%%%%%		\item concurrent execution of multiple kernels 
-%%%%%%		\item proof for maximum computation-communication overlap with infinite memory 
-%%%%%%		\item Problem statement : NP complete problem
-%%%%%%		\item extended version of NP complete problem 
-%%%%%%		\item Different proposed heuristics for order of data transfers 
-%%%%		\item Simulation results for all proposed heuristics 
-%%%%%%%		\item Experiments on actual platform with the best proposed heuristic 
-%%	\end{itemize}
 	\todo[inline]{SKumar: Modify both proofs }
 	\section{Data Transfer problem formulation}
-
-%%	\newpage 
-	\section*{Order of data transfers}
+%%	\section*{Order of data transfers}
 
@@
 	\section{Order of Data Transfer and Computation heuristics}
-	\begin{itemize}
-		\item Talk about optimal strategy
-		\item Order of computations and communications are same
-		\item Static strategy
-		\item Dynamic strategies
-		\item Combination of Static and dynamic strategies
-		\item strategies based on linear program 
-	\end{itemize}
+%%	\begin{itemize}
+%%		\item Talk about optimal strategy
+%%		\item Order of computations and communications are same
+%%		\item Static strategy
+%%		\item Dynamic strategies
+%%		\item Combination of Static and dynamic strategies
+%%		\item strategies based on linear program 
+%%	\end{itemize}
 
@@
 
-%%\todo[inline]{SKumar: LP evaluation and discussion}
-%%
-%%	\todo[inline]{Skumar: Effect of Random memory with HF or CCSD}
-%%	
+\subsection{Scheduling In Batches}
+In most applications, scheduler can only observe a limited batch of independent tasks.
+Therefore we organize tasks of each trace file in the group of 100 and apply each heuristic on them consecutively.
+Figure~\ref{fig:best_variants_batch} shows performance of the best variants of all categories for both applications.
+The plots exhibit behavior similar to Figures~\ref{fig:ratio_to_optimal_best_hf} and ~\ref{fig:ratio_to_optimal_best_CCSD}, static+dynamic variants attain maximum communication-computation overlap and outperform other heuristics.
+\todo[inline]{SKumar:combine both plots}
+\begin{figure}[htb]
+	\centering
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=.95\linewidth]{../ExperimentalResults/batch-100/inverse_ratio_to_optimal_hf_batch-best.pdf}
+		\caption{Best variants of HF.}
+		\label{fig:hf_best_variants_batch}
+	\end{subfigure}%
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=.95\linewidth]{../ExperimentalResults/batch-100/inverse_ratio_to_optimal_ccsd_batch-best.pdf}
+		\caption{Best variants of CCSD.}
+		\label{fig:hf_best_variants_batch}
+	\end{subfigure}
+	\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
+	\label{fig:best_variants_batch}
+\end{figure}
+
 \subsection{Impact of heterogeneity on different heuristics}
@@
 Pure static strategies suffer from memory capacity imitation and pure dynamic strategies are unable to maximize communication-computation overlap.
-
-%%\subsection{Tasks in Batches}
-%%	\begin{figure}[htb]
-%%	\includegraphics[scale=0.25]{../ExperimentalResults/ccsd-random/ratio_to_optimal_ccsd_random.pdf}
-%%	\caption{HF Performance with random memory requirement of a task.}
-%%	\label{fig:staticOrderDynamicCorrectionsExample}
-%%\end{figure}
 

### 2019-03-31 ExperimentalData/scripts/inverse_ratio_to_optimal_batch-best.R

@@ -1,0 +1,25 @@
+#!/usr/bin/env Rscript
+inverse_ratio_to_optimal_best_func <-function(file_name)
+{
+library(ggplot2)
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
+
+dftest[,c(2:6)]<-NULL
+dftest$static_best<-do.call('pmin', c(dftest[,3:7]))
+dftest$dynamic_best<-do.call('pmin', c(dftest[,8:10]))
+dftest$static_dynamic_best<-do.call('pmin', c(dftest[,11:13]))
+dftest<-dftest[,c(1,2,14:16)]
+dftestMelted<-melt(dftest, "capacity")
+names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
+p<-ggplot(dftestMelted, aes(x=capacity, y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth()
+p<-p + ylab("inverse(ratio_to_optimal)") + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Performance With Best of all categories")
+return (p)
+}
+p<-inverse_ratio_to_optimal_best_func('results_hf_batch.txt')
+ggsave(file="inverse_ratio_to_optimal_hf_batch-best.pdf", p, width=23.6, height=13.4)
+
+p<-inverse_ratio_to_optimal_best_func('results_ccsd_batch.txt')
+ggsave(file="inverse_ratio_to_optimal_ccsd_batch-best.pdf", p, width=23.6, height=13.4)
+

### 2019-04-01 Article/article.tex
minor

@@
 \usepackage{framed}
-%%\usepackage{caption}
-\usepackage{subcaption}
+\usepackage{caption}
+%%\usepackage{subcaption}
 \captionsetup{compatibility=false}
 \usepackage{todonotes}
+\usepackage{subfig}
 
@@
 \SetKw{continue}{continue}
+
+\usepackage{tikz}
+\usetikzlibrary{fit,calc,positioning,decorations.pathreplacing,matrix}
 
@@
 We also show that with finite memory capacity obtaining the optimal order of data transfers is an NP-complete problem.
-We propose several heuristics for this problem and provide analysis of them on traces obtained by running 2 molecular chemistry kernels, namely, Hartree–Fock (HF)  and CCSD on 10 nodes of an HPC system.
+We propose several heuristics for this problem and provide details about their favorable situations.
+We present analysis of our heuristics on traces obtained by running 2 molecular chemistry kernels, namely, Hartree–Fock (HF)  and Coupled Cluster Single Double (CCSD) on 10 nodes of an HPC system.
 Our results show that some of our heuristics achieve significant overlap for moderate memory capacities and are very close to the lower bound of makespan.
@@
 
+\todo[inline]{Add outline of this article (in the end)}
 \section{Related Work}
@@
 Communication and computation timings of a task can be considered as processing timings on different machines.
-Johnson has provided scheduling strategies for 2 and 3-machine flow shop problems with infinite memory case~\cite{johnson}.
+Johnson has provided scheduling strategies for 2 and 3-machine flow shop problems with infinite memory capacity~\cite{johnson}.
 2-machine flow shop problem with finite memory capacity has been proven NP-Complete by Papadimitriou et.
@@
 
-	\noindent \textbf{Claim} : Order provided by Algorithms~\ref{alg:OrderOfExecutionInfinteMemory} achives the optimal makespan for a set of ready tasks.
-
+	\noindent \textbf{Claim} : Order provided by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} achives the optimal makespan for a set of ready tasks.
+	\todo[inline]{SKumar:rewrite this proof}
 	\begin{proof}
@@
 		\begin{align*}
-		t : & \text{Time at which data transfer for task A started in original schedule}\\
+		t : & \text{Time at which data transfer for task A starts in original schedule}\\
 		S_A : & \text{ Start of computation  time of task A in original schedule}\\
@@
 This problem can be expressed as 2-machine flowshop problem with infinite storage, where communication time is the processing time on first machine and computation time is the processing time on second machine and the goal is to minimize the overall makespan.
-In [], Johnson's algorithm also achieves the optimal makespan but the proof techniques and algorithm are quite different from ours.
+In ~\cite{GareyJohnson}, Johnson's algorithm also achieves the optimal makespan but the proof techniques and algorithm are quite different from ours.
 	\subsection{Finite Memory}
@@
 	to minimize the total makespan. This is a well known NP-complete problem. 
+	\todo{Skumar: Need a citation}
+	As stated earlier, we do not consider output data separately in our analysis and assume that output data is zero or stored in a separate buffer.
+Hence, problem considered in this article is simpler than general 3-machine flowshop problem.
 
@@
    	This problem is known to be NP-complete.
+ 	\todo{Skumar: Need a citation}
 
@@
 \subsection{Static Ordering}
-In this class of strategies, we compute the order of both computations and communications in advance based on criteria such as communication time, compute time, accelerated tasks.
+In this class of strategies, we compute the order of both computations and communications in advance based on criteria such as communication time, compute time and accelerated tasks.
 After computing the order, we follow the same order on computation and communication channels and make sure that at each point in the schedule memory capacity is respected.
 
-In strategy (cite optimal strategy), compute intensive tasks (step 1) are sorted in increasing order of communication times.
+In Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}, compute intensive tasks (step 1) are sorted in increasing order of communication times.
 It allows tasks to utilize the computation channel maximally and make enough space on communication channel to accommodate more communication intensive tasks with maximum overlap.
-Communication intensive tasks are sorted in decreasing order of communication time, which allows tasks to utilize the gap created on communicated channel.
+Communication intensive tasks are sorted in decreasing order of computation time, which allows tasks to utilize the gap created on communication channel.
 Hence,  in this section, we obtain the orders by sorting tasks based on different combinations of communication and computation times.
@@
 \todo[inline]{SKumar: equivalent tikz figure}
+\begin{tabular}{|l|l|l|}
+\hline
+Task & Comm Time & Comp Time\\ \hline
+A & 3 & 2\\ \hline
+B & 1 & 3\\ \hline
+C & 4 & 4\\ \hline
+D & 2 & 1\\ \hline
+\end{tabular}
+	\begin{figure}[htb]
+	\centering
+%% 	\subfloat[Optimal schedule]{
+		\begin{tikzpicture}[decoration={brace, amplitude=5},scale=1, every node/.style={scale=1}]
+		\node(t1) at (0,0) {};       		
+		\node[above right=0cm and 0cm of t1.mid, draw, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b11) {$B$};
+
+		\node[below right=0cm and 0cm of b11.south east, draw, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b12) {$B$};
+
+		\node[above right=0cm and 0cm of b11.south east, draw, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c11) {$C$};
+
+		\node[below right=0cm and 0cm of c11.south east, draw, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c12) {$C$};
+
+		\node[above right=0cm and 0cm of c11.south east, draw, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a11) {$A$};
+
+		\node[below right=0cm and 0cm of c12.north east, draw, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a12) {$A$};
+
+		\node[above right=0cm and 0cm of a11.south east, draw, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d11) {$D$};
+
+		\node[below right=0cm and 0cm of a12.north east, draw, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d12) {$D$};
+
+%%		\draw[->]	(5,-1)-- (b11.west, b11.south)	;
+
+%%		\draw[->] ([xshift=-0.1cm, yshift=-1cm] b11.south west)--([xshift=13cm, yshift=-1cm] b11.south west);
+		\tikzstyle{legend}=[below=0.25, anchor=mid] 	
+		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
+             -- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
+             -- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.5] {$1$}
+             -- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
+             -- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.5] {$5$}
+             -- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}
+             -- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.5] {$9$}
+             -- ([shift={(10, -0.65)}] t1.mid)node[legend,scale=0.5] {$10$}
+             -- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.5] {$11$}
+             -- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5] {$12$}                                      
+              --([shift={(13, -0.65)}] t1.mid) node[right,scale=0.5] {$t$};
+
+      \foreach \x in {0, 1, 4, 5, 8, 9, 10, 11, 12} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
+
+      \node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BCAD$};
+
+%%      \node[above right=-1.15cm and -2cm of t1.mid, scale=1, rotate=0] {$Hello BCAD$};
+
+ 		\node(t1) at ([shift={(0, -2)}] t1.mid) {};       		
+		 \node[above right=0cm and 0cm of t1.mid, draw, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b11) {$B$};
+
+%%  \draw ([yshift=-0.5mm] second0.north)
+%%		-- ([yshift=-0.5mm, xshift=0.5mm] second0.north)
+%%		-- ([xshift=0.5mm] second0.north);
+
+%%		\node[above left=0.15cm and 0cm of t2.south west, scale=0.5, rotate=0] {$GPU$};
+%%		\node[above left=0.15cm and 0cm of t3.south west, scale=0.5, rotate=0] {$CPU$};		
+%%		
+%%		\tikzstyle{legend}=[below=0.35, anchor=mid] 	
+%%		\draw[->] (-0.1, -0.1) -- (0, -0.1)  node[legend,scale=0.5] {$0$} --(1,-0.1) node [legend,scale=0.5] {$1$} --(1.5, -0.1) node[right,scale=0.5] {$t$}; 
+%%		
+%%		\foreach \x in {0cm, 1cm} \draw (\x, -0.12) -- (\x, -0.08);
+%%		%%			To align both figures of subfloat-- an object without drawing at the same depth
+%%		\path (-0.1, -0.5) -- (1.5, -0.5);
+
+		\end{tikzpicture}
+%%	} %\hspace{0.01\textwidth} %\hfill% or \hspace{5mm} or \hspace{0.3\textwidth}
+%%	\subfloat[HP schedule]{
+%%		\begin{tikzpicture}[decoration={brace, amplitude=5},scale=1.8, every node/.style={scale=1.8}]
+%%		\node(t1) at (0,0) {};      		
+%%		
+%%		\node[above right=0cm and 0cm of t1.mid, draw, minimum height=0.5cm, minimum width=0.618cm,draw,fill=white](t2) {$Y$};
+%%		
+%%		\node[above right=0.5cm and 0cm of t2.north west, draw, minimum height=0.5cm, minimum width=1.618cm,draw,fill=white](t3) {$X$};								
+%%		
+%%		\tikzstyle{legend}=[below=0.35, anchor=mid] 	
+%%		\draw[->] (-0.1, -0.1) -- (0, -0.1)  node[legend,scale=0.5] {$0$} --(0.618,-0.1) node [legend,scale=0.5] {$\tfrac{1}{\phi}$} --(1.618,-0.1) node [legend,scale=0.5] {$\phi$} --(2, -0.1) node[right,scale=0.5] {$t$};
+%%		
+%%		\foreach \x in {0cm, 0.618cm, 1.618cm} \draw (\x, -0.12) -- (\x, -0.08);
+%%		%%			To align both figures of subfloat -- an object without drawing at the same depth
+%%		
+%%		\path (-0.1, -0.5) -- (2, -0.5);
+%%		
+%%		\end{tikzpicture}
+%%	} 
+	\caption{ \label{fig:staticSchedules} Static.}
+\end{figure}
 
@@
 In this class of strategy, when communication channel is idle, a task is chosen which satisfies the selection criteria maximally among other tasks.
-For example, if the selection criteria is to choose a highly compute intensive task, than  we calculate the ratio of compute time and communication time for all tasks, and the task with the  maximum ratio is selected (ties are broken randomly).
+For example, if the selection criteria is to choose a highly compute intensive task, then  we calculate the ratio of compute time and communication time for all tasks, and the task with the  maximum ratio is selected (ties are broken randomly).
 As we assume that order on both channels is same, hence order on compute channel will follow the order of communication channel.
@@
 
-	\todo[inline]{Machine information and our model}
+%%	\todo[inline]{Machine information and our model}
 
@@
 We obtain traces by running  two molecular chemistry applications,  double precision version of Hartree-Fock (HF) and Coupled Cluster Single Double (CCSD) of NWChem package with 4 Uracil molecules input on 10 nodes of this machine.
-Each node is composed of 16 Intel Xeon E5-2670 cores, hence we use 160 processes for the execution.
-Each process executes 300-800 tasks.
+Each node is composed of 16 Intel Xeon E5-2670 cores.
 NWChem takes advantages of a Partitioned Global Address Space Programming Model, Global Arrays (GA), to use shared-memory programming APIs  on distributed memory computers.
+GA dedicates one core of each node to handle communication, hence we can view a node as being composed of 15 computational cores.
+We use 150 processes for each application and obtain 150 trace files.
+Each process executes around 300-800 tasks.
 Our data transfer model is quite simple and  we consider that all data transfers between each process's local memory and GA memory take the same route.
@@
  \begin{figure}[htb]
-	\centering
-	\begin{subfigure}{.5\textwidth}
-		\centering
-		\includegraphics[width=.95\linewidth]{../ExperimentalResults/application_properties_hf.pdf}
-		\caption{HF workloads}
-		\label{fig:hfProperties}
-	\end{subfigure}%
-	\begin{subfigure}{.5\textwidth}
-		\centering
-		\includegraphics[width=.95\linewidth]{../ExperimentalResults/application_properties_ccsd.pdf}
-		\caption{CCSD workloads}
-		\label{fig:ccsdProperties}
-	\end{subfigure}
+ 	%\begin{tabular}{c}
+ 	\subfloat[HF workloads\label{fig:hfProperties}]{%
+		\includegraphics[width=.45\linewidth]{../ExperimentalResults/application_properties_hf.pdf}
+ 	}%\\
+ 	\subfloat[CCSD workloads\label{fig:ccsdProperties}]{%
+		\includegraphics[width=.45\linewidth]{../ExperimentalResults/application_properties_ccsd.pdf}
+ 	}%\\
+ 	%\end{tabular}
 	\caption{HF and CCSD tasks characteristics.}
@@
  \end{figure}
+
+%%  
+%%\begin{figure}[htb]
+%%	\centering
+%%	\begin{subfigure}{.5\textwidth}
+%%		\centering
+%%		\includegraphics[width=.95\linewidth]{../ExperimentalResults/application_properties_hf.pdf}
+%%		\caption{HF workloads}
+%%		\label{fig:hfProperties}
+%%	\end{subfigure}%
+%%	\begin{subfigure}{.5\textwidth}
+%%		\centering
+%%		\includegraphics[width=.95\linewidth]{../ExperimentalResults/application_properties_ccsd.pdf}
+%%		\caption{CCSD workloads}
+%%		\label{fig:ccsdProperties}
+%%	\end{subfigure}
+%%	\caption{HF and CCSD tasks characteristics.}
+%%	\label{fig:ApplicationProperties}
+%%\end{figure}
 
@@
 
-\subsection{Scheduling In Batches}
-In most applications, scheduler can only observe a limited batch of independent tasks.
-Therefore we organize tasks of each trace file in the group of 100 and apply each heuristic on them consecutively.
+\subsection{Scheduling in Batches}
+In most applications, scheduler may only observe a limited batch of independent tasks.
+Therefore we organize tasks of each trace file in the batch of 100.
+Last group may have less than 100 tasks.
+We  apply each heuristic on each group consequently.
 Figure~\ref{fig:best_variants_batch} shows performance of the best variants of all categories for both applications.
@@
 \todo[inline]{SKumar:combine both plots}
+
  \begin{figure}[htb]
-	\centering
-	\begin{subfigure}{.5\textwidth}
-		\centering
-		\includegraphics[width=.95\linewidth]{../ExperimentalResults/batch-100/inverse_ratio_to_optimal_hf_batch-best.pdf}
-		\caption{Best variants of HF.}
-		\label{fig:hf_best_variants_batch}
-	\end{subfigure}%
-	\begin{subfigure}{.5\textwidth}
-		\centering
-		\includegraphics[width=.95\linewidth]{../ExperimentalResults/batch-100/inverse_ratio_to_optimal_ccsd_batch-best.pdf}
-		\caption{Best variants of CCSD.}
-		\label{fig:hf_best_variants_batch}
-	\end{subfigure}
+	\subfloat[Best variants of HF.\label{fig:hf_best_variants_batch}]{%
+		\includegraphics[width=.45\linewidth]{../ExperimentalResults/batch-100/inverse_ratio_to_optimal_hf_batch-best.pdf}
+	}%\\
+	\subfloat[Best variants of CCSD.\label{fig:ccsd_best_variants_batch}]{%
+		\includegraphics[width=.45\linewidth]{../ExperimentalResults/batch-100/inverse_ratio_to_optimal_ccsd_batch-best.pdf}
+	}%\\
 	\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
@@
  \end{figure}
+
+%%\begin{figure}[htb]
+%%	\centering
+%%	\begin{subfigure}{.5\textwidth}
+%%		\centering
+%%		\includegraphics[width=.95\linewidth]{../ExperimentalResults/batch-100/inverse_ratio_to_optimal_hf_batch-best.pdf}
+%%		\caption{Best variants of HF.}
+%%		\label{fig:hf_best_variants_batch}
+%%	\end{subfigure}%
+%%	\begin{subfigure}{.5\textwidth}
+%%		\centering
+%%		\includegraphics[width=.95\linewidth]{../ExperimentalResults/batch-100/inverse_ratio_to_optimal_ccsd_batch-best.pdf}
+%%		\caption{Best variants of CCSD.}
+%%		\label{fig:ccsd_best_variants_batch}
+%%	\end{subfigure}
+%%	\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
+%%	\label{fig:best_variants_batch}
+%%\end{figure}
 
@@
 
+%%We also plan to extend our model by taking bandwidth sharing and different possible routes for the same source-destination pair into account.
+
 In this article, we consider the problem of deciding the order of data transfers between two memory nodes such that overlap of communication and  computation is maximized.
@@
 
-%%	\begin{itemize}
-%%		\item Machine description
-%%		\item temporary data requirement
-%%		\item Description of all kernels (Molecular Chemistry Kernels)
-%%		\item Think about results and graphs (Most probably results in $R$ plots)
-%%	\end{itemize}
-
 \bibliographystyle{IEEEtran}

### 2019-04-01 Article/article.tex
tikz diagram for static schedule

@@
 %% 	\subfloat[Optimal schedule]{
-		\begin{tikzpicture}[decoration={brace, amplitude=5},scale=1, every node/.style={scale=1}]
+		\begin{tikzpicture}[decoration={brace, amplitude=5},scale=0.5, every node/.style={scale=0.5}]
+		\tikzstyle{legend}=[below=0.25, anchor=mid] 	
 		\node(t1) at (0,0) {};
-		\node[above right=0cm and 0cm of t1.mid, draw, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b11) {$B$};
 
-		\node[below right=0cm and 0cm of b11.south east, draw, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b12) {$B$};
+	    \node[above right=0.8cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=13cm, draw=white, fill=white](IMC) {$Infinite Memory Capacity$};
 
-		\node[above right=0cm and 0cm of b11.south east, draw, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c11) {$C$};
+		\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b11) {$B$};
 
-		\node[below right=0cm and 0cm of c11.south east, draw, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c12) {$C$};
+		\node[below right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b12) {$B$};
 
-		\node[above right=0cm and 0cm of c11.south east, draw, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a11) {$A$};
+		\node[above right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c11) {$C$};
 
-		\node[below right=0cm and 0cm of c12.north east, draw, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a12) {$A$};
+		\node[below right=0cm and 0cm of c11.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c12) {$C$};
 
-		\node[above right=0cm and 0cm of a11.south east, draw, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d11) {$D$};
+		\node[above right=0cm and 0cm of c11.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a11) {$A$};
 
-		\node[below right=0cm and 0cm of a12.north east, draw, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d12) {$D$};
+		\node[below right=0cm and 0cm of c12.north east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a12) {$A$};
+
+		\node[above right=0cm and 0cm of a11.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d11) {$D$};
+
+		\node[below right=0cm and 0cm of a12.north east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d12) {$D$};
 
@@
 %%		\draw[->] ([xshift=-0.1cm, yshift=-1cm] b11.south west)--([xshift=13cm, yshift=-1cm] b11.south west);
-		\tikzstyle{legend}=[below=0.25, anchor=mid] 	
+
 		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
@@
              -- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5] {$12$}                                      
-              --([shift={(13, -0.65)}] t1.mid) node[right,scale=0.5] {$t$};
+              --([shift={(17, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};
 
@@
 
- 		\node(t1) at ([shift={(0, -2)}] t1.mid) {};       		
-		 \node[above right=0cm and 0cm of t1.mid, draw, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b11) {$B$};
+ 		\node(t1) at ([shift={(0, -3)}] t1.mid) {};   
+	    \node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=13cm, draw=white, fill=white](MC) {$Memory Capacity=6$};
+
+   		\node(t1) at ([shift={(0, -0.8)}] t1.mid) {};                		
+		\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b21) {$B$};
+
+		\node[below right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b22) {$B$};
+
+		\node[above right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c21) {$C$};
+
+		\node[below right=0cm and 0cm of c21.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c22) {$C$};
+
+		\node[above right=0cm and 0cm of c22.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a21) {$A$};
+
+		\node[below right=0cm and 0cm of a21.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a22) {$A$};
+
+		\node[above right=0cm and 0cm of a21.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d11) {$D$};
+
+		\node[below right=0cm and 0cm of d11.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d12) {$D$};
+
+		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
+		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
+		-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.5] {$1$}
+		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
+		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.5] {$5$}
+		-- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.5] {$9$}
+		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5] {$12$}         
+		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.5] {$14$}                                      
+		-- ([shift={(15, -0.65)}] t1.mid)node[legend,scale=0.5]{$15$}
+	  	-- ([shift={(17, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};
+
+		\foreach \x in {0, 1, 4, 5, 9, 12, 14, 15} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
+
+		\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BCAD$};
+
+%% schedule of third heuristic		
+   		\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};                		
+		\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b31) {$B$};
+
+		\node[below right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b32) {$B$};
+
+		\node[above right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d31) {$D$};
+
+		\node[below right=0cm and 0cm of b32.north east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d32) {$D$};
+
+		\node[above right=0cm and 0cm of d31.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a31) {$A$};
+
+		\node[below right=0cm and 0cm of a31.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a32) {$A$};
+
+		\node[above right=0cm and 0cm of a32.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c31) {$C$};
+
+		\node[below right=0cm and 0cm of c31.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c32) {$C$};
+
+		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
+		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
+		-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.5] {$1$}
+		-- ([shift={(3, -0.65)}] t1.mid)node[legend,scale=0.5] {$3$}
+		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
+		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.5] {$5$}
+		-- ([shift={(6, -0.65)}] t1.mid)node[legend,scale=0.5] {$6$}         
+		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}                                      
+		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5]{$12$} 
+		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.5] {$16$}
+		--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};
+
+		\foreach \x in {0, 1, 3, 4, 5, 6, 8, 12, 16} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
+
+		\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BDAC$};
+
+%% schedule of fourth heuristic		
+		\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};                		
+		\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c41) {$C$};
+
+		\node[below right=0cm and 0cm of c41.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c42) {$C$};
+
+		\node[above right=0cm and 0cm of c41.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b41) {$B$};
+
+		\node[below right=0cm and 0cm of c42.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b42) {$B$};
+
+		\node[above right=0cm and 0cm of c42.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a41) {$A$};
+
+		\node[below right=0cm and 0cm of a41.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a42) {$A$};
+
+		\node[above right=0cm and 0cm of b42.north east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d41) {$D$};
+
+		\node[below right=0cm and 0cm of d41.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d42) {$D$};
+
+		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
+		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
+		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
+		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.5] {$5$}
+		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}
+		-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.5] {$11$}
+		-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.5] {$13$}         
+		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.5] {$14$} 
+		--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};
+
+		\foreach \x in {0, 4, 5, 8, 11, 13, 14} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
+
+		\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$CBAD$};
+
+%% schedule of fifth heuristic		
+		\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};                		
+		\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d51) {$D$};
+
+		\node[below right=0cm and 0cm of d51.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d52) {$D$};
+
+		\node[above right=0cm and 0cm of d51.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b51) {$B$};
+
+		\node[below right=0cm and 0cm of b51.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b52) {$B$};
+
+		\node[above right=0cm and 0cm of d52.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a51) {$A$};
+
+		\node[below right=0cm and 0cm of a51.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a52) {$A$};
+
+		\node[above right=0cm and 0cm of a52.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c51) {$C$};
+
+		\node[below right=0cm and 0cm of c51.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c52) {$C$};
+
+		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
+		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
+		-- ([shift={(2, -0.65)}] t1.mid)node[legend,scale=0.5] {$2$}
+		-- ([shift={(3, -0.65)}] t1.mid)node[legend,scale=0.5] {$3$}
+		-- ([shift={(6, -0.65)}] t1.mid)node[legend,scale=0.5] {$6$}
+		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}
+		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5] {$12$}         
+		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.5] {$16$} 
+		--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};
+
+		\foreach \x in {0, 2, 3, 6, 8, 12, 16} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
+
+		\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$DBAC$};
+
+%% schedule of sixth heuristic		
+		\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};                		
+		\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c61) {$C$};
+
+		\node[below right=0cm and 0cm of c61.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c62) {$C$};
+
+		\node[above right=0cm and 0cm of c62.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a61) {$A$};
+
+		\node[below right=0cm and 0cm of a61.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a62) {$A$};
+
+		\node[above right=0cm and 0cm of a61.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b61) {$B$};
+
+		\node[below right=0cm and 0cm of a62.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b62) {$B$};
+
+		\node[above right=0cm and 0cm of b61.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d61) {$D$};
+
+		\node[below right=0cm and 0cm of b62.north east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d62) {$D$};
+
+		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
+		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
+		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
+		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}
+		-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.5] {$11$}
+		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5] {$12$}
+		-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.5] {$13$}         
+		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.5] {$14$}
+		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.5] {$16$} 
+		-- ([shift={(17, -0.65)}] t1.mid)node[legend,scale=0.5] {$17$}  
+		--([shift={(17.1, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};
+
+		\foreach \x in {0, 4, 8, 11, 12, 13, 14, 16, 17} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
+
+		\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$CABD$};
 

### 2019-04-01 Article/article.tex
minor

@@
 		\begin{tikzpicture}[decoration={brace, amplitude=5},scale=0.5, every node/.style={scale=0.5}]
-		\tikzstyle{legend}=[below=0.25, anchor=mid] 	
+		\tikzstyle{legend}=[below=0.1, anchor=mid] 	
 		\node(t1) at (0,0) {};
 
-	    \node[above right=0.8cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=13cm, draw=white, fill=white](IMC) {$Infinite Memory Capacity$};
+	    \node[above right=0.4cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Infinite Memory Capacity$};
 
@@
 		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
-             -- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
-             -- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.5] {$1$}
-             -- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
-             -- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.5] {$5$}
-             -- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}
-             -- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.5] {$9$}
-             -- ([shift={(10, -0.65)}] t1.mid)node[legend,scale=0.5] {$10$}
-             -- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.5] {$11$}
-             -- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5] {$12$}                                      
-              --([shift={(17, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};
+             -- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
+             -- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
+             -- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
+             -- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
+             -- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
+             -- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.65]{$9$}
+             -- ([shift={(10, -0.65)}] t1.mid)node[legend,scale=0.65]{$10$}
+             -- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}
+             -- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}                                      
+              --([shift={(17, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
 
@@
 
- 		\node(t1) at ([shift={(0, -3)}] t1.mid) {};   
-	    \node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=13cm, draw=white, fill=white](MC) {$Memory Capacity=6$};
-
-   		\node(t1) at ([shift={(0, -0.8)}] t1.mid) {};                		
+ 		\node(t1) at ([shift={(0, -3.8)}] t1.mid) {};   
+%%	    \node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](MC) {$Memory Capacity=6$}; 
+	    \node[above right=0.4cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Memory Capacity=6$};
+
+%%   		\node(t1) at ([shift={(0, -1.0)}] t1.mid) {};                		
 		\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b21) {$B$};
@@
 		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
-		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
-		-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.5] {$1$}
-		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
-		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.5] {$5$}
-		-- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.5] {$9$}
-		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5] {$12$}         
-		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.5] {$14$}                                      
-		-- ([shift={(15, -0.65)}] t1.mid)node[legend,scale=0.5]{$15$}
-	  	-- ([shift={(17, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};
+		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
+		-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
+		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
+		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
+		-- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.65]{$9$}
+		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}         
+		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.65]{$14$}                                      
+		-- ([shift={(15, -0.65)}] t1.mid)node[legend,scale=0.65]{$15$}
+	  	-- ([shift={(17, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
 
@@
 		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
-		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
-		-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.5] {$1$}
-		-- ([shift={(3, -0.65)}] t1.mid)node[legend,scale=0.5] {$3$}
-		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
-		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.5] {$5$}
-		-- ([shift={(6, -0.65)}] t1.mid)node[legend,scale=0.5] {$6$}         
-		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}                                      
-		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5]{$12$} 
-		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.5] {$16$}
-		--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};
+		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
+		-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
+		-- ([shift={(3, -0.65)}] t1.mid)node[legend,scale=0.65]{$3$}
+		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
+		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
+		-- ([shift={(6, -0.65)}] t1.mid)node[legend,scale=0.65]{$6$}         
+		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}                                      
+		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$} 
+		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.65]{$16$}
+		--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
 
@@
 		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
-		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
-		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
-		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.5] {$5$}
-		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}
-		-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.5] {$11$}
-		-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.5] {$13$}         
-		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.5] {$14$} 
-		--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};
+		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
+		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
+		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
+		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
+		-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}
+		-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}         
+		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.65]{$14$} 
+		--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
 
@@
 		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
-		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
-		-- ([shift={(2, -0.65)}] t1.mid)node[legend,scale=0.5] {$2$}
-		-- ([shift={(3, -0.65)}] t1.mid)node[legend,scale=0.5] {$3$}
-		-- ([shift={(6, -0.65)}] t1.mid)node[legend,scale=0.5] {$6$}
-		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}
-		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5] {$12$}         
-		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.5] {$16$} 
-		--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};
+		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
+		-- ([shift={(2, -0.65)}] t1.mid)node[legend,scale=0.65]{$2$}
+		-- ([shift={(3, -0.65)}] t1.mid)node[legend,scale=0.65]{$3$}
+		-- ([shift={(6, -0.65)}] t1.mid)node[legend,scale=0.65]{$6$}
+		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
+		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}         
+		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.65]{$16$} 
+		--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
 
@@
 		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
-		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
-		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
-		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}
-		-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.5] {$11$}
-		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5] {$12$}
-		-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.5] {$13$}         
-		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.5] {$14$}
-		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.5] {$16$} 
-		-- ([shift={(17, -0.65)}] t1.mid)node[legend,scale=0.5] {$17$}  
-		--([shift={(17.1, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};
+		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
+		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
+		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
+		-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}
+		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}
+		-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}         
+		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.65]{$14$}
+		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.65]{$16$} 
+		-- ([shift={(17, -0.65)}] t1.mid)node[legend,scale=0.65]{$17$}  
+		--([shift={(17.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
 
@@
 %%		\tikzstyle{legend}=[below=0.35, anchor=mid] 	
-%%		\draw[->] (-0.1, -0.1) -- (0, -0.1)  node[legend,scale=0.5] {$0$} --(1,-0.1) node [legend,scale=0.5] {$1$} --(1.5, -0.1) node[right,scale=0.5] {$t$}; 
+%%		\draw[->] (-0.1, -0.1) -- (0, -0.1)  node[legend,scale=0.65]{$0$} --(1,-0.1) node [legend,scale=0.65]{$1$} --(1.5, -0.1) node[right,scale=0.65]{$t$}; 
 %%		
@@
 %%		\tikzstyle{legend}=[below=0.35, anchor=mid] 	
-%%		\draw[->] (-0.1, -0.1) -- (0, -0.1)  node[legend,scale=0.5] {$0$} --(0.618,-0.1) node [legend,scale=0.5] {$\tfrac{1}{\phi}$} --(1.618,-0.1) node [legend,scale=0.5] {$\phi$} --(2, -0.1) node[right,scale=0.5] {$t$};
+%%		\draw[->] (-0.1, -0.1) -- (0, -0.1)  node[legend,scale=0.65]{$0$} --(0.618,-0.1) node [legend,scale=0.65]{$\tfrac{1}{\phi}$} --(1.618,-0.1) node [legend,scale=0.65]{$\phi$} --(2, -0.1) node[right,scale=0.65]{$t$};
 %%		

### 2019-04-02 Article/article.tex
tikz diagrams

@@
 \usepackage{subfig}
+\usepackage{multirow}
 
@@
 \end{itemize}
-\todo[inline]{SKumar: equivalent tikz figure}
-\begin{tabular}{|l|l|l|}
+\todo[inline]{SKumar: update short name of each strategy in tikz}
+	\begin{table}[htb]
+	\begin{center}
+
+		\begin{tabular}{|c|c|c|}
 		\hline
-Task & Comm Time & Comp Time\\ \hline
+		\multirow{2}{*}{Task} & Comm Time & \multirow{2}{*}{Comp Time}\\ 
+		&=Comm Volume& \\ \hline
 		A & 3 & 2\\ \hline
@@
 		\end{tabular}
+	\caption{\label{tab:staticOrderExample} A task set for static order schedules.}
+	\end{center}
+	\end{table}
+
 	\begin{figure}[htb]
@@
 %% 	\subfloat[Optimal schedule]{
-		\begin{tikzpicture}[decoration={brace, amplitude=5},scale=0.5, every node/.style={scale=0.5}]
+		\begin{tikzpicture}[decoration={brace, amplitude=5},scale=0.6, every node/.style={scale=0.6}]
 		\tikzstyle{legend}=[below=0.1, anchor=mid] 	
@@
 
-	    \node[above right=0.4cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Infinite Memory Capacity$};
+	    \node[above right=0.6cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Infinite Memory Capacity$}; 	    				
+%%	    \node[above right=0.4cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Infinite Memory Capacity$};
 
@@
 %%	    \node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](MC) {$Memory Capacity=6$}; 
-	    \node[above right=0.4cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Memory Capacity=6$};
+%%	    \node[above right=0.4cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Memory Capacity=6$};	   
+	    \node[above right=0.6cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Memory Capacity=6$};
 
@@
 		\end{tikzpicture}
-%%	} %\hspace{0.01\textwidth} %\hfill% or \hspace{5mm} or \hspace{0.3\textwidth}
-%%	\subfloat[HP schedule]{
-%%		\begin{tikzpicture}[decoration={brace, amplitude=5},scale=1.8, every node/.style={scale=1.8}]
-%%		\node(t1) at (0,0) {};      		
+
+	\caption{ \label{fig:staticOrderExample} Different static order heuristic schedules for Table~\ref{tab:staticOrderExample}.}
+\end{figure}
+
+%%\begin{figure}[htb]
 %%	
-%%		\node[above right=0cm and 0cm of t1.mid, draw, minimum height=0.5cm, minimum width=0.618cm,draw,fill=white](t2) {$Y$};
-%%		
-%%		\node[above right=0.5cm and 0cm of t2.north west, draw, minimum height=0.5cm, minimum width=1.618cm,draw,fill=white](t3) {$X$};								
-%%		
-%%		\tikzstyle{legend}=[below=0.35, anchor=mid] 	
-%%		\draw[->] (-0.1, -0.1) -- (0, -0.1)  node[legend,scale=0.65]{$0$} --(0.618,-0.1) node [legend,scale=0.65]{$\tfrac{1}{\phi}$} --(1.618,-0.1) node [legend,scale=0.65]{$\phi$} --(2, -0.1) node[right,scale=0.65]{$t$};
-%%		
-%%		\foreach \x in {0cm, 0.618cm, 1.618cm} \draw (\x, -0.12) -- (\x, -0.08);
-%%		%%			To align both figures of subfloat -- an object without drawing at the same depth
-%%		
-%%		\path (-0.1, -0.5) -- (2, -0.5);
-%%		
-%%		\end{tikzpicture}
-%%	} 
-	\caption{ \label{fig:staticSchedules} Static.}
-\end{figure}
-
-\begin{figure}[htb]
-
-	\includegraphics[scale=0.05]{Figs/staticOrderSchedules}
-			\caption{Task set and schedules where orders are precomputed based on different heuristics.}
-	\label{fig:staticOrderExample}
-\end{figure}
-
-Fig~\ref{fig:staticOrderExample} shows schedules for all proposed heuristics of this class for task set of Table (ref).
+%%	\includegraphics[scale=0.05]{Figs/staticOrderSchedules}
+%%			\caption{Task set and schedules where orders are precomputed based on different heuristics.}
+%%	\label{fig:staticOrderExample}
+%%\end{figure}
+
+Fig~\ref{fig:staticOrderExample} shows schedules for all proposed heuristics of this class for task set of Table~\ref{tab:staticOrderExample}.
 \subsection{Dynamic Selection}
@@
 \end{itemize}
-\todo[inline]{SKumar: equivalent tikz figure}
+%%\todo[inline]{SKumar: equivalent tikz figure}
+	\begin{table}[htb]
+	\begin{center}
+
+		\begin{tabular}{|c|c|c|}
+			\hline
+			\multirow{2}{*}{Task} & Comm Time & \multirow{2}{*}{Comp Time}\\ 
+			&=Comm Volume& \\ \hline
+			A & 3 & 2\\ \hline
+			B & 1 & 6\\ \hline
+			C & 4 & 6\\ \hline
+			D & 5 & 1\\ \hline
+		\end{tabular}
+		\caption{\label{tab:dynamicSelectionExample} A task set for dynamic schedules.}
+	\end{center}
+\end{table}
 
 \begin{figure}[htb]
-
-\includegraphics[scale=0.05]{Figs/dynamiSelectionSchedules}
-\caption{Task set and schedules where orders are precomputed based on different heuristics.}
-\label{fig:dynamicSelectionExample}
+	\centering
+	%% 	\subfloat[Optimal schedule]{
+	\begin{tikzpicture}[decoration={brace, amplitude=5},scale=0.6, every node/.style={scale=0.6}]
+	\tikzstyle{legend}=[below=0.1, anchor=mid] 	
+	\node(t1) at (0,0) {};  
+	\node[above right=0.6cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=15cm, draw=white, fill=white, scale=1.5](IMC) {$Memory Capacity=6$};
+
+	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b11) {$B$};
+
+	\node[below right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](b12) {$B$};
+
+	\node[above right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=5cm,draw,fill=white](d11) {$D$};
+
+	\node[below right=0cm and 0cm of b12.north east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d12) {$D$};
+
+	\node[above right=0cm and 0cm of d12.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a11) {$A$};
+
+	\node[below right=0cm and 0cm of a11.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a12) {$A$};
+
+	\node[above right=0cm and 0cm of a12.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c11) {$C$};
+
+	\node[below right=0cm and 0cm of c11.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](c12) {$C$};
+
+	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
+	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
+	-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
+	-- ([shift={(6, -0.65)}] t1.mid)node[legend,scale=0.65]{$6$}
+	-- ([shift={(7, -0.65)}] t1.mid)node[legend,scale=0.65]{$7$}
+	-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
+	-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}         
+	-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}                                      
+	-- ([shift={(17, -0.65)}] t1.mid)node[legend,scale=0.65]{$17$}
+	-- ([shift={(23, -0.65)}] t1.mid)node[legend,scale=0.65]{$23$}
+	-- ([shift={(25.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
+
+	\foreach \x in {0, 1, 6, 7, 8, 11, 13, 17, 23} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
+
+	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BDAC$};
+
+	%% schedule of third heuristic		
+	\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};                		
+	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b21) {$B$};
+
+	\node[below right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](b22) {$B$};
+
+	\node[above right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a21) {$A$};
+
+	\node[below right=0cm and 0cm of b22.north east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a22) {$A$};
+
+	\node[above right=0cm and 0cm of a22.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c21) {$C$};
+
+	\node[below right=0cm and 0cm of c21.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](c22) {$C$};
+
+	\node[above right=0cm and 0cm of c22.north east, minimum height=0.5cm, minimum width=5cm,draw,fill=white](d21) {$D$};
+
+	\node[below right=0cm and 0cm of d21.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d22) {$D$};
+
+		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
+		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
+		-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
+		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
+		-- ([shift={(7, -0.65)}] t1.mid)node[legend,scale=0.65]{$7$}
+		-- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.65]{$9$}
+		-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}         
+		-- ([shift={(19, -0.65)}] t1.mid)node[legend,scale=0.65]{$19$}                                      
+		-- ([shift={(24, -0.65)}] t1.mid)node[legend,scale=0.65]{$24$}
+		-- ([shift={(25, -0.65)}] t1.mid)node[legend,scale=0.65]{$25$}
+		-- ([shift={(25.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
+
+	\foreach \x in {0, 1, 4, 7, 9, 13, 19, 24, 25} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
+
+	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BACD$};
+
+	%% schedule of third heuristic		
+	\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};    	
+	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b31) {$B$};
+
+	\node[below right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](b32) {$B$};
+
+	\node[above right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c31) {$C$};
+
+	\node[below right=0cm and 0cm of b32.north east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](c32) {$C$};
+
+	\node[above right=0cm and 0cm of c32.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a31) {$A$};
+
+	\node[below right=0cm and 0cm of a31.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a32) {$A$};
+
+	\node[above right=0cm and 0cm of a32.north east, minimum height=0.5cm, minimum width=5cm,draw,fill=white](d31) {$D$};
+
+	\node[below right=0cm and 0cm of d31.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d32) {$D$};
+
+		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
+		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
+		-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
+		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
+		-- ([shift={(7, -0.65)}] t1.mid)node[legend,scale=0.65]{$7$}
+		-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}
+		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.65]{$16$}         
+		-- ([shift={(18, -0.65)}] t1.mid)node[legend,scale=0.65]{$18$}                                      
+		-- ([shift={(23, -0.65)}] t1.mid)node[legend,scale=0.65]{$23$}
+		-- ([shift={(24, -0.65)}] t1.mid)node[legend,scale=0.65]{$24$}
+		-- ([shift={(25.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
+
+	\foreach \x in {0, 1, 5, 7, 13, 16, 18, 23, 24} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
+
+	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BCAD$};
+
+	\end{tikzpicture}
+		\caption{ \label{fig:dynamicSelectionExample} Different dynamic heuristic schedules for a task set of Table~\ref{tab:dynamicSelectionExample}.}
 	\end{figure}
 
-Fig~\ref{fig:dynamicSelectionExample} shows schedules for all proposed heuristics of this class for task set of Table (ref).
+%%\begin{figure}[htb]
+%%
+%%\includegraphics[scale=0.05]{Figs/dynamiSelectionSchedules}
+%%\caption{Task set and schedules where orders are precomputed based on different heuristics.}
+%%\label{fig:dynamicSelectionExample}
+%%\end{figure}
+
+Fig~\ref{fig:dynamicSelectionExample} shows schedules for all proposed heuristics of this class for task set of Table~\ref{tab:dynamicSelectionExample}.
 
@@
 
-\todo[inline]{SKumar: equivalent tikz figure}
+	\begin{table}[htb]
+	\begin{center}
+
+		\begin{tabular}{|c|c|c|}
+			\hline
+			\multirow{2}{*}{Task} & Comm Time & \multirow{2}{*}{Comp Time}\\ 
+			&=Comm Volume& \\ \hline
+			A & 4 & 1\\ \hline
+			B & 2 & 6\\ \hline
+			C & 8 & 8\\ \hline
+			D & 5 & 4\\ \hline
+			E & 3 & 2\\ \hline
+		\end{tabular}
+		\caption{\label{tab:staticOrderDynamicCorrectionsExample} A task set for static order dynamic corrections schedules.}
+	\end{center}
+\end{table}
+
 \begin{figure}[htb]
-\includegraphics[scale=0.05]{Figs/staticOrderDynamicCorrectionsSchedules}
-\caption{Task set and schedules where orders are precomputed based on different heuristics.}
-\label{fig:staticOrderDynamicCorrectionsExample}
+	\centering
+	%% 	\subfloat[Optimal schedule]{
+	\begin{tikzpicture}[decoration={brace, amplitude=5},scale=0.3, every node/.style={scale=0.3}]
+	\tikzstyle{legend}=[below=0.1, anchor=mid] 	
+	\node(t1) at (0,0) {};  
+	\node[above right=1.2cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=20cm, draw=white, fill=white, scale=1.5](MC) {Optimal Order with Infinite Memory = $BCDAE$};
+	\node[above right=0.6cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=20cm, draw=white, fill=white, scale=1.5](MC) {$Memory Capacity=9$};
+
+	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=2cm,draw,fill=white](b11) {$B$};
+
+	\node[below right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](b12) {$B$};
+
+	\node[above right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=5cm,draw,fill=white](d11) {$D$};
+
+	\node[below right=0cm and 0cm of b12.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](d12) {$D$};
+
+	\node[above right=0cm and 0cm of b12.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](a11) {$A$};
+
+	\node[below right=0cm and 0cm of a11.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](a12) {$A$};
+
+	\node[above right=0cm and 0cm of d12.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](e11) {$E$};
+
+	\node[below right=0cm and 0cm of e11.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](e12) {$E$};
+
+	\node[above right=0cm and 0cm of e12.north east, minimum height=0.5cm, minimum width=8cm,draw,fill=white](c11) {$C$};
+
+	\node[below right=0cm and 0cm of c11.south east, minimum height=0.5cm, minimum width=8cm,draw,fill=white](c12) {$C$};
+
+		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
+		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
+		-- ([shift={(2, -0.65)}] t1.mid)node[legend,scale=0.65]{$2$}
+		-- ([shift={(7, -0.65)}] t1.mid)node[legend,scale=0.65]{$7$}
+		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
+		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}
+		-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}         
+		-- ([shift={(15, -0.65)}] t1.mid)node[legend,scale=0.65]{$15$}                                      
+		-- ([shift={(17, -0.65)}] t1.mid)node[legend,scale=0.65]{$17$}
+		-- ([shift={(25, -0.65)}] t1.mid)node[legend,scale=0.65]{$25$}
+		-- ([shift={(33, -0.65)}] t1.mid)node[legend,scale=0.65]{$33$}
+		-- ([shift={(33.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
+
+	\foreach \x in {0, 2, 7, 8, 12, 13, 15, 17, 25, 33} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
+
+	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BDAEC$};
+
+	%% schedule of second heuristic		
+	\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};
+
+	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=2cm,draw,fill=white](b21) {$B$};
+
+	\node[below right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](b22) {$B$};
+
+	\node[above right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](e21) {$E$};
+
+	\node[below right=0cm and 0cm of b22.north east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](e22) {$E$};
+
+	\node[above right=0cm and 0cm of e21.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](a21) {$A$};
+
+	\node[below right=0cm and 0cm of e22.north east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](a22) {$A$};
+
+	\node[above right=0cm and 0cm of a21.south east, minimum height=0.5cm, minimum width=5cm,draw,fill=white](d21) {$D$};
+
+	\node[below right=0cm and 0cm of d21.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](d22) {$D$};
+
+	\node[above right=0cm and 0cm of d22.north east, minimum height=0.5cm, minimum width=8cm,draw,fill=white](c21) {$C$};
+
+	\node[below right=0cm and 0cm of c21.south east, minimum height=0.5cm, minimum width=8cm,draw,fill=white](c22) {$C$};
+
+		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
+		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
+		-- ([shift={(2, -0.65)}] t1.mid)node[legend,scale=0.65]{$2$}
+		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
+		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
+		-- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.65]{$9$}
+		-- ([shift={(10, -0.65)}] t1.mid)node[legend,scale=0.65]{$10$}
+		-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}         
+		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.65]{$14$}                                      
+		-- ([shift={(18, -0.65)}] t1.mid)node[legend,scale=0.65]{$18$}
+		-- ([shift={(26, -0.65)}] t1.mid)node[legend,scale=0.65]{$26$}
+		-- ([shift={(34, -0.65)}] t1.mid)node[legend,scale=0.65]{$34$}
+		-- ([shift={(34.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
+
+	\foreach \x in {0, 2, 5, 8, 9, 10, 11, 14, 18, 26, 34} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
+
+	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BEADC$};
+
+	%% schedule of third heuristic		
+	\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};
+
+	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=2cm,draw,fill=white](b31) {$B$};
+
+	\node[below right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](b32) {$B$};
+
+	\node[above right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=5cm,draw,fill=white](d31) {$D$};
+
+	\node[below right=0cm and 0cm of b32.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](d32) {$D$};
+
+	\node[above right=0cm and 0cm of b32.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](e31) {$E$};
+
+	\node[below right=0cm and 0cm of d32.north east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](e32) {$E$};
+
+	\node[above right=0cm and 0cm of d32.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](a31) {$A$};
+
+	\node[below right=0cm and 0cm of a31.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](a32) {$A$};
+
+	\node[above right=0cm and 0cm of a32.north east, minimum height=0.5cm, minimum width=8cm,draw,fill=white](c31) {$C$};
+
+	\node[below right=0cm and 0cm of c31.south east, minimum height=0.5cm, minimum width=8cm,draw,fill=white](c32) {$C$};
+
+		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
+		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
+		-- ([shift={(2, -0.65)}] t1.mid)node[legend,scale=0.65]{$2$}
+		-- ([shift={(7, -0.65)}] t1.mid)node[legend,scale=0.65]{$7$}
+		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
+		-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}
+		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}         
+		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.65]{$14$}                                      
+		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.65]{$16$}
+		-- ([shift={(17, -0.65)}] t1.mid)node[legend,scale=0.65]{$17$}
+		-- ([shift={(25, -0.65)}] t1.mid)node[legend,scale=0.65]{$25$}
+		-- ([shift={(33, -0.65)}] t1.mid)node[legend,scale=0.65]{$33$}
+		-- ([shift={(33.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
+
+	\foreach \x in {0, 2, 7, 8, 11, 12, 14, 16, 17, 25, 33} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
+
+	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BDEAC$};
+
+	\end{tikzpicture}
+	\caption{ \label{fig:staticOrderDynamicCorrectionsExample} Different static order dynamic corrections heuristic schedules for a task set of Table~\ref{tab:staticOrderDynamicCorrectionsExample}.}
 \end{figure}
+
+%%\begin{figure}[htb]
+%%\includegraphics[scale=0.05]{Figs/staticOrderDynamicCorrectionsSchedules}
+%%\caption{Task set and schedules where orders are precomputed based on different heuristics.}
+%%\label{fig:staticOrderDynamicCorrectionsExample}
+%%\end{figure}
 

### 2019-04-03 Article/article.tex
rewritten infinite memory proof

@@
 
-\newcommand{\hp}{{\sc HeteroPrio}\xspace}
 \SetKw{continue}{continue}
@@
 \usetikzlibrary{fit,calc,positioning,decorations.pathreplacing,matrix}
+
+\definecolor{pdfurlcolor}{rgb}{0,0,0.6}
+\definecolor{pdfcitecolor}{rgb}{0,0.6,0}
+\definecolor{pdflinkcolor}{rgb}{0.6,0,0}
+\usepackage{epsfig,color}
+%\usepackage[colorlinks=true,citecolor=pdfcitecolor,urlcolor=pdfurlcolor,linkcolor=pdflinkcolor,pdfborder={0 0 0}]{hyperref}
+
+\newcommand{\scomm}{\ensuremath{{\cal S}_{\text{COMM}}}}
+\newcommand{\scomp}{\ensuremath{{\cal S}_{\text{COMP}}}}
+
+%%\newtheorem{theorem}{Theorem}
+%%\newtheorem{corollary}{Corollary}[theorem]
+%\newtheorem{lemma}[theorem]{Lemma}
 
@@
 
-	\todo[inline]{SKumar: Modify both proofs }
+%%	\todo[inline]{SKumar: Modify both proofs }
 	\section{Data Transfer problem formulation}
@@
 We prove that order of execution of such tasks with finite memory capacity, is an NP-complete problem.
+We also present an optimal algorithm to determine the order of execution of tasks when there is not any  restriction on memory limit.
 
 	\subsection{Infinite Memory Case}
-	Let $S$ be the set of tasks assigned on processor $P$ with memory unit $M$, and this set of tasks  need input data from another memory unit $M'$.
+	Let $S$ be the set of tasks assigned on a processor with memory unit $M$, and this set of tasks  need input data from another memory unit $M'$.
 We assume that size of $M$ is very large and there will not be any memory capacity restriction for tasks.
 
+	Let \scomm($i$) and  \scomp($i$) represent the start times of task $i$ on communication and computation resources. $CM_i$ and $CP_i$ are communication and computation times of task $i$.
+
 	\begin{algorithm}
-	\caption{\label{alg:OrderOfExecutionInfinteMemory}Algorithm to determine the order of processing for a set of ready tasks (infinite memory case)}
+	\caption{\label{alg:OrderOfExecutionInfinteMemory}Algorithm to determine the order of processing and schedule for a set of ready tasks (infinite memory case)}
 	\begin{algorithmic}[1]
@@
 		\STATE Sort $S_2$ in queue $Q_2$ by non-increasing computation times
-		\WHILE{all tasks did not complete}
-		\IF{$Q_1 \neq \emptyset$}
-		\STATE remove a task $T$ from beginning of $Q_1$ for processing
-		\ELSE 
-		\STATE remove a task $T$ from beginning of $Q_2$ for processing
-		\ENDIF
+		\STATE $Q \gets  Q_1$
+		\STATE Append $Q_2$ to $Q$
+		\STATE $early\_available\_time\_on\_communication\_resource \gets 0$
+		\STATE $early\_available\_time\_on\_computation\_resource \gets 0$
+		\WHILE{$Q \neq \emptyset$}
+		\STATE remove a task $T$ from beginning of $Q$ for processing
+		\STATE $\scomm(T) \gets  early\_available\_time\_on\_communication\_resource$
+		\STATE $\scomp(T) \gets  max(\scomm(T) + CM_T, early\_available\_time\_on\_computation\_resource)$
+		\STATE $early\_available\_time\_on\_communication\_resource \gets  \scomm(T) + CM_T$
+		\STATE $early\_available\_time\_on\_computation\_resource \gets  \scomp(T) + CP_T$
 		\ENDWHILE
@@
 
-	\noindent \textbf{Claim} : Order provided by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} achives the optimal makespan for a set of ready tasks.
-	\todo[inline]{SKumar:rewrite this proof}
+%%	\noindent \textbf{Claim} : Order provided by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} achives the optimal makespan for a set of ready tasks.
+%%	\todo[inline]{SKumar:rewrite this proof}
+In order to prove the optimality of makespan for the schedule obtained by the above algorithm, we need the following lemma.
+
+	\begin{lemma}\label{lemma:swappingOfTasks}
+	Swapping two contiguous tasks $A$ and $B$ in a schedule does not improve the makespan if one of the conditions is true.
+	\begin{enumerate}[label=\roman*)]
+		\item  $CP_A \ge CM_A, CP_B \ge CM_B, CM_A \le CM_B$
+		\item $CP_A < CM_A, CP_B < CM_B, CP_A \ge CP_B$
+		\item $CP_A \ge CM_A, CP_B < CM_B$
+	\end{enumerate}
+\end{lemma}
 \begin{proof}
-		Let us first define some notations which we need for this proof.
-%%		\todo[inline]{SKumar: Specify the destination for all notations}
-		\begin{align*}
-		t : & \text{Time at which data transfer for task A starts in original schedule}\\
-		S_A : & \text{ Start of computation  time of task A in original schedule}\\
-		S_B : & \text{ Start of computation time of task B in original schedule}\\
-		S'_A : & \text{ Start of computation time of task A in swapped schedule}\\
-		S'_B : & \text{ Start of computation time of task B in swapped schedule}\\
-		CM(A) : & \text{ Data transfer time for task A}\\
-		CM(B) : & \text{ Data transfer time for task B}\\
-		CP(A) : & \text{ Computation time of of task A}\\
-		CP(B) : & \text{ Computation time of task B}\\
-		\rho : & \text{ ratio of length of task and data transfer time}
-		\end{align*}
-	\end{proof}
-
-	Let $S$ be the schedule obtained by the above heuristic and $O$ be an optimal schedule.
-We prove the above claim by converting $S$ to $O$ and showing that at each step completing time of intermediate schedule is not less than the completion time of original schedule $S$.
-In order to do so, we make sure order of two tasks in both schedules $S$ and $O$ is same.
-If not, We perform swapping of two tasks.
-
-	\noindent If we prove the swapping strategy for two contiguous tasks holds, then the same strategy transitively hold for any two tasks of Schedule $S$
-
-	Let $A$ and $B$ are two contiguous tasks of schedule $S$, which need to be swapped.
-	\todo[inline]{SKumar: draw an equivalent xfig diagram}
+	Let $t_1$ and $t_2$ be the early start time on communication and computation resources just before the task $A$ starts.
+
 	\begin{figure}[htb]
@@
 
-	We can write the following constraints based on the two schedules of the Fig~\ref{fig:bothSchedule}.
+	We write the following constraints based on the two schedules of the Fig~\ref{fig:bothSchedule}.
 
 	\begin{eqnarray*}
-		S_A & = & max(CM(A), l) \\
-		S_B & = & max(S_A + CP(A), CM(A) + CM(B))
+		\scomp(A) & = & max(t_1 + CM_A, t_2) \\
+		\scomp(B) & = & max(\scomp(A) + CP_A,  t_1 + CM_A + CM_B)
 	\end{eqnarray*}
 
-	Completion time in original Schedule = $S_B + CP(B)$
+	Completion time of $B$ in original Schedule = $\scomm(B) + CP_B$
+
 	\begin{eqnarray*}
-		S'_B & = & max(CM(B), l) \\
-		S'_A & = & max(S'_B + CP(B), CM(A) + CM(B))
+		\text{Completion time of $B$ in swapped Schedule, } \scomp '(B) & = & max(t_1 + CM_B, t_2)\\
+		\text{Completion time of $A$ in swapped Schedule, } \scomp '(A) & = & max(\scomp'(B) + CP_B, t_1 + CM_B + CM_A)
 	\end{eqnarray*}
 
-	Completion time in swapped Schedule = $S'_A + CP(A)$
-
-	Our goal is to prove the following inequality.
+	In both schedules, early available time on communication resource after scheduling $A$ and $B$ is same.
+If we show that early available time on computation resource in swapped schedule after scheduling both tasks is not less than the time of original schedule, then we are done.
+Hence our goal is to prove that,
+	$$\scomp(B) + CP_B \le \scomp'(A) + CP_A $$
+
 	\begin{eqnarray*}
-		S_B + CP(B) & \le & S'_A + CP(A)
+		\scomp(B) + CP_B & = & max(\scomp(A) + CP_A + CP_B,  t_1 + CM_A + CM_B + CP_B)\\
+		& = & max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A + CM_B + CP_B) 
 	\end{eqnarray*}
-	\begin{proof}
+
+	Case I: $CP_A \ge CM_A, CP_B \ge CM_B, CM_A \le CM_B$
 	\begin{eqnarray*}
-			S_B + CP(B) & = & max(S_A + CP(A)+CP(B), CM(A) + CM(B) + CP(B))\\
-			& = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) 
+		\scomp(B) + CP_B & = & max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A + CM_B + CP_B)\\
+		& \le& max(t_1 + CM_A + CP_B, t_2  + CP_B, t_1  + CM_B + CP_B) + CP_A\\
+		& = & max( t_1  + CM_B + CP_B, t_2  + CP_B) + CP_A \\
+		& = & max(max(t_1 + CM_B, t_2) + CP_B, t_1 + CM_A + CM_B) + CP_A\\
+		& = & max(\scomp'(B) + CP_B, t_1 + CM_A + CM_B) + CP_A \\
+		& = & \scomp'(A) + CP_A
 	\end{eqnarray*}
-		Case I: $A, B\in ST_1, CM(A) \le CM(B), CP(A) \ge CM(A), CP(B) \ge CM(B)$
+	Case II: $CP_A < CM_A, CP_B < CM_B, CP_A \ge CP_B$
 	\begin{eqnarray*}
-			S_B + CP(B) & = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) \\
-			& \le & max(CM(A) + CP(B), l+CP(B), CM(B)+CP(B)) + CP(A)\\
-			& = & max(CM(B) + CP(B), l + CP(B)) + CP(A) \\
-			& = & max(max(CM(B), l) + CP(B), CM(A) + CM(B)) + CP(A) \\
-			& = & max(S'_B + CP(B), CM(A) +CM(B)) + CP(A) \\
-			& = & S'_A + CP(A)
+		\scomp(B) + CP_B & = & max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A + CM_B + CP_B)\\
+		& \le & max(t_1 + CM_A + CP_B, t_2+CP_B, t_1 + CM_A + CM_B) + CP_A\\
+		& = & max(t_1 + CM_A + CM_B, t_2+ CP_B) + CP_A \\
+		& = & max(t_1 + CM_B + CP_B, t_2 + CP_B, t_1 + CM(A) + CM_B) + CP_A \\
+		& = & max(max(t_1 + CM_B, t_2) + CP_B, t_1 + CM_A + CM_B) + CP_A \\
+		& = & max(\scomp'(B) + CP_B, t_1 + CM_A +CM_B) + CP_A \\
+		& = & \scomp'(A) + CP_A
 	\end{eqnarray*}
-		Case II: $A, B\in ST_2, CP(A) \ge CP(B), CP(A) < CM(A), CP(B) < CM(B)$
+	Case III: $CP_A \ge CM_A, CP_B < CM_B$
 	\begin{eqnarray*}
-			S_B + CP(B) & = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) \\
-			& \le & max(CM(A) + CP(B), l+CP(B), CM(A)+CM(B)) + CP(A)\\
-			& = & max(CM(A) + CM(B), l + CP(B)) + CP(A) \\
-			& = & max(CM(B) + CP(B), l + CP(B), CM(A) + CM(B)) + CP(A) \\
-			& = & max(max(CM(B), l) + CP(B), CM(A) + CM(B)) + CP(A) \\
-			& = & max(S'_B + CP(B), CM(A) +CM(B)) + CP(A) \\
-			& = & S'_A + CP(A)
-		\end{eqnarray*}
-		Case III: $A \in ST_1, B\in ST_2, CP(A) \ge CM(A), CP(B) < CM(B)$
-		\begin{eqnarray*}
-			S_B + CP(B) & = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) \\
-			& \le & max(CM(A) + CP(B), l + CP(B), CM(B) + CP(B)) + CP(A)\\
-			& \le & max(CM(A) + CM(B), l + CP(B), CM(B) + CP(B)) + CP(A) \\
-			& = & max(max(CM(B), l) + CP(B), CM(A) + CM(B)) + CP(A) \\
-			& = & max(S'_B + CP(B), CM(A) +CM(B)) + CP(A) \\
-			& = & S'_A + CP(A)
+		\scomp(B) + CP_B & = & max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A + CM_B + CP_B)\\
+		& \le & max(t_1 + CM_A + CP_B, t_2 + CP_B, t_1 + CM_B + CP_B) + CP_A\\
+		& \le & max(t_1 + CM_A + CM_B, t_2 + CP_B, t_1 + CM_B + CP_B) + CP_A \\
+		& = & max(max(t_1 + CM_B, t_2) + CP_B, t_1 + CM_A + CM_B) + CP_A \\
+		& = & max(\scomp'(B) + CP_B, t_1 + CM_A +CM_B) + CP_A \\
+		& = & \scomp'(A) + CP_A
 	\end{eqnarray*}
@@
 
-This problem can be expressed as 2-machine flowshop problem with infinite storage, where communication time is the processing time on first machine and computation time is the processing time on second machine and the goal is to minimize the overall makespan.
-In ~\cite{GareyJohnson}, Johnson's algorithm also achieves the optimal makespan but the proof techniques and algorithm are quite different from ours.
+\begin{theorem}
+	Scheduled constructed by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} achieves optimal makespan.
+\end{theorem}
+%%	\begin{proof}
+%%		Let us first define some notations which we need for this proof.
+%%%%		\todo[inline]{SKumar: Specify the destination for all notations}
+%%		\begin{align*}
+%%		t : & \text{Time at which data transfer for task A starts in original schedule}\\
+%%		S_A : & \text{ Start of computation  time of task A in original schedule}\\
+%%		S_B : & \text{ Start of computation time of task B in original schedule}\\
+%%		S'_A : & \text{ Start of computation time of task A in swapped schedule}\\
+%%		S'_B : & \text{ Start of computation time of task B in swapped schedule}\\
+%%		CM(A) : & \text{ Data transfer time for task A}\\
+%%		CM(B) : & \text{ Data transfer time for task B}\\
+%%		CP(A) : & \text{ Computation time of of task A}\\
+%%		CP(B) : & \text{ Computation time of task B}\\
+%%		\rho : & \text{ ratio of length of task and data transfer time}
+%%		\end{align*}
+%%	\end{proof}
+
+	\begin{proof}
+
+	Let $O$ be an optimal schedule.
+We assume that order of communications and computations is same on both resources in $O$.
+If it is not the case, we make the order of computations same as the order of communications without increasing the makespan.
+Suppose two tasks have opposite order on both resources then we position the second task just before the first task on the computation resource.
+It is evident that this change does not alter the optimal  makespan, we repeat this procedure until order of communications and computations is same in $O$.
+
+	Let $S$ be the  schedule obtained from Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}.
+We prove the theorem by converting $S$ to $O$ and showing that at each step makespan of intermediate schedule is not less than the original makespan.
+We rely on Lemma~\ref{lemma:swappingOfTasks} to convert $S$ to $O$.
+
+  We traverse schedule $O$ from left to right and for each $ith$ task in sequence, we apply Lemma~\ref{lemma:swappingOfTasks} repetitively until order of task in the swapped schedule is same.
+It is obvious that after moving the $ith$ task at the beginning remaining schedule (schedule after $ith$ task) still satisfies one of the conditions of Lemma~\ref{lemma:swappingOfTasks}.
+
+  Let the final swapped schedule is $S_{final}$.
+From Lemma~\ref{lemma:swappingOfTasks}, $makespan(S_{final}) \ge makesapn(S)$.
+From the construction, $makespan(S_{final}) \le makesapn(O)$.
+As $O$ is an optimal schedule, hence $makespan(S) = makesapn(O)$.
+This completes our proof.
+
+	\end{proof}
+
+%%	 
+%%	Let $S$ be the schedule obtained by the above heuristic and $O$ be an optimal schedule.
+We prove the above claim by converting $S$ to $O$ and showing that at each step completing time of intermediate schedule is not less than the completion time of original schedule $S$.
+In order to do so, we make sure order of two tasks in both schedules $S$ and $O$ is same.
+If not, We perform swapping of two tasks.
+%%	
+%%	\noindent If we prove the swapping strategy for two contiguous tasks holds, then the same strategy transitively hold for any two tasks of Schedule $S$
+
+%%	Let $A$ and $B$ are two contiguous tasks of schedule $S$, which need to be swapped.
+%%	\todo[inline]{SKumar: draw an equivalent xfig diagram}
+%%	\begin{figure}[htb]
+%%		\centering
+%%		\includegraphics[width=\textwidth, height=0.5\textheight, 
+%%		keepaspectratio]{Figs/swappedSchedule.jpg}
+%%		\caption{ \label{fig:bothSchedule} Original and Swapped Schedule}
+%%	\end{figure}
+%%	
+%%	We can write the following constraints based on the two schedules of the Fig~\ref{fig:bothSchedule}.
+%%	
+%%	\begin{eqnarray*}
+%%		S_A & = & max(CM(A), l) \\
+%%		S_B & = & max(S_A + CP(A), CM(A) + CM(B))
+%%	\end{eqnarray*}
+%%	
+%%	Completion time in original Schedule = $S_B + CP(B)$
+%%	\begin{eqnarray*}
+%%		S'_B & = & max(CM(B), l) \\
+%%		S'_A & = & max(S'_B + CP(B), CM(A) + CM(B))
+%%	\end{eqnarray*}
+%%	
+%%	Completion time in swapped Schedule = $S'_A + CP(A)$
+%%	
+%%	Our goal is to prove the following inequality.
+%%	\begin{eqnarray*}
+%%		S_B + CP(B) & \le & S'_A + CP(A)
+%%	\end{eqnarray*}
+%%	\begin{proof}
+%%		\begin{eqnarray*}
+%%			S_B + CP(B) & = & max(S_A + CP(A)+CP(B), CM(A) + CM(B) + CP(B))\\
+%%			& = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) 
+%%		\end{eqnarray*}
+%%		Case I: $A, B\in ST_1, CM(A) \le CM(B), CP(A) \ge CM(A), CP(B) \ge CM(B)$
+%%		\begin{eqnarray*}
+%%			S_B + CP(B) & = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) \\
+%%			& \le & max(CM(A) + CP(B), l+CP(B), CM(B)+CP(B)) + CP(A)\\
+%%			& = & max(CM(B) + CP(B), l + CP(B)) + CP(A) \\
+%%			& = & max(max(CM(B), l) + CP(B), CM(A) + CM(B)) + CP(A) \\
+%%			& = & max(S'_B + CP(B), CM(A) +CM(B)) + CP(A) \\
+%%			& = & S'_A + CP(A)
+%%		\end{eqnarray*}
+%%		Case II: $A, B\in ST_2, CP(A) \ge CP(B), CP(A) < CM(A), CP(B) < CM(B)$
+%%		\begin{eqnarray*}
+%%			S_B + CP(B) & = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) \\
+%%			& \le & max(CM(A) + CP(B), l+CP(B), CM(A)+CM(B)) + CP(A)\\
+%%			& = & max(CM(A) + CM(B), l + CP(B)) + CP(A) \\
+%%			& = & max(CM(B) + CP(B), l + CP(B), CM(A) + CM(B)) + CP(A) \\
+%%			& = & max(max(CM(B), l) + CP(B), CM(A) + CM(B)) + CP(A) \\
+%%			& = & max(S'_B + CP(B), CM(A) +CM(B)) + CP(A) \\
+%%			& = & S'_A + CP(A)
+%%		\end{eqnarray*}
+%%		Case III: $A \in ST_1, B\in ST_2, CP(A) \ge CM(A), CP(B) < CM(B)$
+%%		\begin{eqnarray*}
+%%			S_B + CP(B) & = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) \\
+%%			& \le & max(CM(A) + CP(B), l + CP(B), CM(B) + CP(B)) + CP(A)\\
+%%			& \le & max(CM(A) + CM(B), l + CP(B), CM(B) + CP(B)) + CP(A) \\
+%%			& = & max(max(CM(B), l) + CP(B), CM(A) + CM(B)) + CP(A) \\
+%%			& = & max(S'_B + CP(B), CM(A) +CM(B)) + CP(A) \\
+%%			& = & S'_A + CP(A)
+%%		\end{eqnarray*}
+%%	\end{proof}
+
+The problem considered here can also be expressed as 2-machine flowshop problem with infinite storage, where communication time is the processing time on first machine and computation time is the processing time on second machine and the goal is to minimize the overall makespan.
+In ~\cite{johnson}, Johnson's algorithm also achieves the optimal makespan but the proof techniques and algorithm are quite different from ours.
 	\subsection{Finite Memory}

### 2019-04-03 Article/article.tex
Proofread : Upto related work

@@
 We propose several heuristics for this problem and provide details about their favorable situations.
-We present analysis of our heuristics on traces obtained by running 2 molecular chemistry kernels, namely, Hartree–Fock (HF)  and Coupled Cluster Single Double (CCSD) on 10 nodes of an HPC system.
+We present analysis of our heuristics on traces, obtained by running 2 molecular chemistry kernels, namely, Hartree–Fock (HF)  and Coupled Cluster Single Double (CCSD) on 10 nodes of an HPC system.
 Our results show that some of our heuristics achieve significant overlap for moderate memory capacities and are very close to the lower bound of makespan.
 
-		\keywords{Communication Scheduling  \and Memory Nodes \and Molecular Chemistry.}
+		\keywords{Communication Scheduling  \and Memory Nodes \and Runtime Systems \and Communication-Computation Overlap \and Molecular Chemistry.}
 	\end{abstract} %
@@
 	\section{Introduction} 
-
-	With the advent of multicore, and the use of accelerators, it is notoriously cumbersome to exploit the full capacity of a machine.
+	\label{sec:intro}
+
+	With the advent of multicore, and the use of accelerators, it is notoriously cumbersome to exploit the full capability of a machine.
 Indeed, there are several challenges come into picture.
@@
 (USA), StarSs~\cite{ompss} from Barcelona Supercomputing Center (Spain), KAPPI~\cite{kaapi} from INRIA Grenoble (France).
-All these runtime systems allow programmers to express their algorithms at the abstract level in the form of direct acyclic graphs, where vertices represent computations and edges represent dependencies among them.
+All these runtime systems allow programmers to express their algorithms at the abstract level in the form of direct acyclic graphs (DAG), where vertices represent computations and edges represent dependencies among them.
 Sometimes some static information such as distance to exit (last) node as a priority or affinity of computation towards resources is also provided along with the DAG.
@@
 	Certain applications such as dense linear algebra kernels have regular structure.
-Therefore it is possible to associate priorities, based on the task graph structure, with computations, which runtime uses to make the execution efficient.
+Therefore, it is possible to associate priorities, based on the task graph structure, with computations, which runtime uses to make the execution efficient.
 In some applications, such as sparse linear algebra kernels, where programmers do not know the precise structure of the tasks graphs in advance,  tasks are added recursively based on certain sentinel constraints.
@@
 		\item Proposed different scheduling strategies with the objective to minimize the makespan
-		\item An optimal strategy and its proof, when there is not any memory capacity constraint on target machine
+		\item An optimal strategy and its proof, when there is not any memory capacity constraint on the target machine
 		\item NP-Completeness proof for the general data-transfer problem  
@@
 
-\todo[inline]{Add outline of this article (in the end)}
+The outline of the article is the following.
+Section~\ref{sec:relatedWork} describes past work on the computations with limited memory and similar problems in the literature.
+In section~\ref{sec:theoreticalProof}, we present an algorithm to obtain the order of data transfers when there is not any memory capacity restriction and prove its optimality.
+Then, we also prove that in general data transfer problem is NP-complete.
+In Section~\ref{sec:heuristics}, we propose several heuristics and describe their favorable scenarios.
+We mainly consider three categories of heuristics: Static heuristics, dynamic heuristics and static heuristics with dynamic corrections.
+We evaluate our proposed strategies on two molecular chemistry kernels in Section~\ref{sec:exp}.
+Our results show that static heuristics with dynamic corrections achieve good performance in most cases.
+We finally  propose conclusions and perspectives in Section~\ref{sec:conclusion}.
+
 \section{Related Work}
+\label{sec:relatedWork}
 
@@
 
-The problem considered in this paper also can be viewed as a flow shop problem.
+The problem considered in this article also can be viewed as a flow shop problem.
 Communication and computation timings of a task can be considered as processing timings on different machines.
@@
 al  worked on the scheduling of graphs of smaller-grain tasks with limited memory, where each task requires homogeneous data size ~\cite{vsarkar-pact}.
-The same work has been extend by Loris et.
+The same work has been extend by Marchal et.
 al for task graphs where memory requirement of each task is highly irregular~\cite{loris-ipdps18}.
 
-\begin{itemize}
-	\item theoretical/performance work on molecular chemistry kernels
-\end{itemize}
+\todo[inline]{theoretical/performance work on molecular chemistry kernels}
 
 %%	\todo[inline]{SKumar: Modify both proofs }
-	\section{Data Transfer problem formulation}
-%%	\section*{Order of data transfers}
+	\section{Data Transfer Problem Formulation}
+	\label{sec:theoreticalProof}
 
@@
 	\section{Order of Data Transfer and Computation heuristics}
-%%	\begin{itemize}
-%%		\item Talk about optimal strategy
-%%		\item Order of computations and communications are same
-%%		\item Static strategy
-%%		\item Dynamic strategies
-%%		\item Combination of Static and dynamic strategies
-%%		\item strategies based on linear program 
-%%	\end{itemize}
+	\label{sec:heuristics}
 
@@
 \section{Conclusion and Perspectives}
+\label{sec:conclusion}
 

### 2019-04-03 Article/article.tex
Proofread at the high level

@@
 It is possible that all output data can be stored in a preallocated separate buffer on a memory node.
-Hence, we do not consider output data separately in our analysis and assume that output data is negligible (zero or stored in a separate buffer) for each task.
-We prove that order of execution of such tasks with finite memory capacity, is an NP-complete problem.
+Hence, we do not consider output data separately in our analysis and assume that output data is negligible  or stored in a separate buffer for each task.
+We prove that order of execution of such tasks with finite memory capacity is an NP-complete problem.
 We also present an optimal algorithm to determine the order of execution of tasks when there is not any  restriction on memory limit.
@@
 		\STATE Divide ready tasks in two sets $S_1$ and $S_2$. If computation time of a task $T$is not less than its communication time, then $T$ is in $S_1$ otherwise $S_2$.
-		\STATE Sort $S_1$ in queue $Q_1$ by non-decreasing communication times
-		\STATE Sort $S_2$ in queue $Q_2$ by non-increasing computation times
-		\STATE $Q \gets  Q_1$
-		\STATE Append $Q_2$ to $Q$
+		\STATE Sort $S_1$ in queue $Q$ by non-decreasing communication times
+		\STATE Sort $S_2$ in queue $Q'$ by non-increasing computation times
+		\STATE Append $Q'$ to $Q$
 		\STATE $early\_available\_time\_on\_communication\_resource \gets 0$
@@
 
-%%	\noindent \textbf{Claim} : Order provided by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} achives the optimal makespan for a set of ready tasks.
-%%	\todo[inline]{SKumar:rewrite this proof}
 In order to prove the optimality of makespan for the schedule obtained by the above algorithm, we need the following lemma.
@@
 	Let $O$ be an optimal schedule.
-We assume that order of communications and computations is same on both resources in $O$.
-If it is not the case, we make the order of computations same as the order of communications without increasing the makespan.
+We assume that $O$ is a permuation schedule, If it is not the case, we make the order of computations same as the order of communications without increasing the makespan.
 Suppose two tasks have opposite order on both resources then we position the second task just before the first task on the computation resource.
@@
 	\subsection{Finite Memory}
-
+	\todo[inline]{Find a citation saying 3-machine flowshop problem is NP-Complete.}
 	In general, order of task execution with input and output data transfers can be 
@@
 	processing time on 3rd machine is output data transfer time  and the objective is 
-	to minimize the total makespan. This is a well known NP-complete problem. 
-	\todo{Skumar: Need a citation}
-	As stated earlier, we do not consider output data separately in our analysis and assume that output data is zero or stored in a separate buffer.
+	to minimize the total makespan.
+This is a well known hard problem~\cite{NPComplete3Machine,johnson}.
+As stated earlier, we do not consider output data separately in our analysis and assume that output data is negligible or stored in a separate buffer.
 Hence, problem considered in this article is simpler than general 3-machine flowshop problem.
@@
 	unit $P$  with memory unit $M$ of capacity $C$. Input data for tasks of $ST$ reside on 
-	another memory unit $M'$. $comm_i$ is the time to transfer input data from $M'$ to $M$ for task 
-	$T_i$,  $e_i$ is the execution time of task $T_i$ on $P$.
+	another memory unit $M'$.  $COMM_i$ is the time to transfer input data from $M'$ to $M$ for task 
+	$i$ and $COMP_i$ is the execution time of task $i$ on $P$.
 We assume that these tasks  do not produce any output data.
@@
 
-   	This problem is known to be NP-complete.
- 	\todo{Skumar: Need a citation}
+   	This problem is known to be NP-complete~\cite{GareyJohnson}.
 
@@
    	problem  has a solution. Notice that sum of transfer times and sum of computation times, both are 
-   	equal to $L$, therefore $\mu(S) \le L$ iff $\mu(S)=L$  and there is no idle time on both channels in 
+   	equal to $L$, therefore $\mu(S) \le L$ iff $\mu(S)=L$  and there is no idle time on both resources in 
    	$S$. It indicates that first task is $K_0$ and last task is $K_m$.
@@
    	This is true because if $a_{i_1}' + a_{i_2}'  + a_{i_3}'  > b'$, total used memory after the data transfer 
-   	for  $K_i$ task finishes is atleast $b'+1$, hence only $A_i$ tasks can be considered, which will lead to a schedule in which at a point only $A_i$ tasks are active on both channels, therefore length of
+   	for  $K_i$ task finishes is atleast $b'+1$, hence only $A_i$ tasks can be considered, which will lead to a schedule in which at a point only $A_i$ tasks are active on both resources, therefore length of
    	schedule would be more than $L$, and if $a_{i_1}' + a_{i_2}'  + a_{i_3}'  < b'$, then we have idle time on computation channel.
@@
 requested input data and memory is acquired before starting the data transfer on communication 
-channel(1st machine).
-
-	\section{Order of Data Transfer and Computation heuristics}
+resource.
+
+	\section{Data Transfer Order heuristics}
 	\label{sec:heuristics}
 
-The heuristic proposed in the Section provides the optimal makespan when there is not any constraint on memory capacity.
+The algorithm proposed in the Section~\ref{sec:theoreticalProof} provides the optimal makespan when there is not any constraint on memory capacity.
 This optimal value indicates a lower bound on the makespan.
-We use $optimal_makespan_infinite_memory$ to represent this value.
-We assess the efficiency of other proposed heuristics in limited memory capacity in Section~\ref{sec:exp} with respect to this lower bound, $optimal_makespan_infinite_memory$.
+We use $optimal\_makespan\_infinite\_memory$ ($OMIM$) to represent this value.
+We assess the efficiency of other proposed heuristics in limited memory capacity in Section~\ref{sec:exp} with respect to this lower bound, $OMIM$.
 
 We classify our heuristics into mainly three categories.
-In the first category, the order of all computations and communications is computed in advanced and the same order is followed on both channels.
+In the first category, the order of all computations and communications is computed in advance and the same order is followed on both resources.
 While in the second category, the best suited next task is chosen based on different criteria.
@@
 In this class of strategies, we compute the order of both computations and communications in advance based on criteria such as communication time, compute time and accelerated tasks.
-After computing the order, we follow the same order on computation and communication channels and make sure that at each point in the schedule memory capacity is respected.
-
-In Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}, compute intensive tasks (step 1) are sorted in increasing order of communication times.
-It allows tasks to utilize the computation channel maximally and make enough space on communication channel to accommodate more communication intensive tasks with maximum overlap.
-Communication intensive tasks are sorted in decreasing order of computation time, which allows tasks to utilize the gap created on communication channel.
+After computing the order, we follow the same order on computation and communication resources and make sure that at each point in the schedule memory capacity is respected.
+
+In Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}, compute intensive tasks  are sorted in increasing order of communication times.
+It allows tasks to utilize the computation channel maximally and make enough margin on communication resource to accommodate more communication intensive tasks with maximum overlap.
+Communication intensive tasks are sorted in decreasing order of computation time, which allows tasks to utilize the margin created on communication resource.
 Hence,  in this section, we obtain the orders by sorting tasks based on different combinations of communication and computation times.
@@
 %%%%string alg_name="decreasing_order_of_communication_plus_computation_strategy";
-%%%%string alg_name="optimal_order_infinite_memory_largest_communication_task_respects_memory_restriction";
-%%%%string alg_name="optimal_order_infinite_memory_smallest_communication_task_respects_memory_restriction";
-%%%%string alg_name="optimal_order_infinite_memory_maximum_accelerated_task_respects_memory_restriction";
+%%%%string alg_name="optimal_order_infinite_memory_largest_communication\_task\_respects\_memory\_restriction";
+%%%%string alg_name="optimal_order_infinite_memory_smallest_communication\_task\_respects\_memory\_restriction";
+%%%%string alg_name="optimal_order_infinite_memory_maximum_accelerated\_task\_respects\_memory\_restriction";
 \begin{itemize}[a)]
-	\item $order_of_optimal_strategy_infinite_memory $: Order of communications and computations is obtained by the infinite memory heuristic.
+	\item $order\_of\_optimal\_strategy\_infinite\_memory $ ($OOSIM$): Order of communications and computations is obtained by the infinite memory heuristic.
 At each point in the schedule memory capacity is respected.
-Hence the makespan of this heuristic may be completely different from $optimal_makespan_infinite_memory$.
-
-	\item $increasing_order_of_communication_strategy$: Order is obtained by sorting all tasks in non-decreasing order of communication time.
-
-	\item $decreasing_order_of_computation_strategy$: Order is obtained by sorting all tasks in non-increasing order of computation time. 
-	\item $increasing_order_of_communication_plus_computation_strategy$: Order is obtained by sorting all tasks in non-decreasing order of sum of communication and computation times.
-	\item $decreasing_order_of_communication_plus_computation_strategy$: Order is obtained by sorting all tasks in non-increasing order of sum of communication and computation times.
+Hence the makespan of this heuristic may be completely different from $OMIM$.
+
+	\item $increasing\_order\_of\_communication\_strategy$ ($IOCMS$): Order is obtained by sorting all tasks in non-decreasing order of communication time.
+
+	\item $decreasing\_order\_of\_computation\_strategy$ ($DOCPS$): Order is obtained by sorting all tasks in non-increasing order of computation time. 
+	\item $increasing\_order\_of\_communication\_plus\_computation\_strategy$ ($IOCCS$): Order is obtained by sorting all tasks in non-decreasing order of sum of communication and computation times.
+	\item $decreasing\_order\_of\_communication\_plus\_computation\_strategy$ ($DOCCS$): Order is obtained by sorting all tasks in non-increasing order of sum of communication and computation times.
 
 \end{itemize}
-\todo[inline]{SKumar: update short name of each strategy in tikz}
+%%\todo[inline]{SKumar: update short name of each strategy in tikz}
 	\begin{table}[htb]
@@
 
-      \node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BCAD$};
+      \node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$OMIM$};
 
@@
 
-		\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BCAD$};
+		\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$OOSIM$};
 
@@
 
-		\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BDAC$};
+		\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$IOCMS$};
 
@@
 
-		\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$CBAD$};
+		\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$DOCPS$};
 
@@
 
-		\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$DBAC$};
+		\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$IOCCS$};
 
@@
 
-		\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$CABD$};
+		\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$DOCCS$};
 
@@
 \subsection{Dynamic Selection}
-%%%%string alg_name="largest_communication_task_respects_memory_restriction";
-%%%%string alg_name="smallest_communication_task_respects_memory_restriction";
-%%%%string alg_name="maximum_accelerated_task_respects_memory_restriction";
+%%%%string alg_name="largest_communication\_task\_respects\_memory\_restriction";
+%%%%string alg_name="smallest_communication\_task\_respects\_memory\_restriction";
+%%%%string alg_name="maximum_accelerated\_task\_respects\_memory\_restriction";
 
@@
 For example, if the selection criteria is to choose a highly compute intensive task, then  we calculate the ratio of compute time and communication time for all tasks, and the task with the  maximum ratio is selected (ties are broken randomly).
-As we assume that order on both channels is same, hence order on compute channel will follow the order of communication channel.
-
+As we assume that order on both channels is same, hence order on compute channel will follow the order of communication resource.
+
+We select a set of tasks which induce minimum idle time on compute channel and satisfy available memory requirement.
+Then a task is chosen for processing from this set based on the following heuristics.
 \begin{itemize}[a)]
-	\item $largest_communication_task_respects_memory_restriction$:  We select a set of tasks which induce minimum idle time on compute channel.
+%%	\item $largest_communication\_task\_respects\_memory\_restriction$:  We select a set of tasks which induce minimum idle time on compute channel.
 A task with the largest communication time is chosen from this set.
 Memory requirement of this task should not be more than presently available memory.
-	\item $smallest_communication_task_respects_memory_restriction$: A task with the smallest communication time is chosen.
+%%	\item $smallest_communication\_task\_respects\_memory\_restriction$: A task with the smallest communication time is chosen.
 Memory requirement of this task should not be more than presently available memory.
-	\item $maximum_accelerated_task_respects_memory_restriction$:  We select a set of tasks which induce minimum idle time on compute channel.
+%%	\item $maximum_accelerated\_task\_respects\_memory\_restriction$:  We select a set of tasks which induce minimum idle time on compute channel.
 A task with the maximum ratio of compute time to communication time  is chosen from this set.
@@
 
+	\item $largest\_communication\_task\_respects\_memory\_restriction$ ($LCMR$):    A task with the largest communication time is chosen. 
+	\item $smallest\_communication\_task\_respects\_memory\_restriction$ ($SCMR$): A task with the smallest communication time is chosen.
+	\item $maximum\_accelerated\_task\_respects\_memory\_restriction$ ($MAMR$):  A task with the maximum ratio of compute time to communication time  is chosen.
+
 \end{itemize}
-%%\todo[inline]{SKumar: equivalent tikz figure}
 	\begin{table}[htb]
@@
 
-	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BDAC$};
+	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$LCMR$};
 
@@
 
-	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BACD$};
+	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$SCMR$};
 
@@
 
-	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BCAD$};
+	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$MAMR$};
 
@@
 
-\subsection{Static Order with dynamic Corrections}
+\subsection{Static Order with Dynamic Corrections}
 
@@
 This class of strategy takes advantage of  static information in the form of precomputed order and dynamic correction to minimize the idle time due to memory constraint.
-%%%%alg_name="optimal_order_infinite_memory_largest_communication_task_respects_memory_restriction";
-%%%%string alg_name="optimal_order_infinite_memory_smallest_communication_task_respects_memory_restriction";
-%%%%string alg_name="optimal_order_infinite_memory_maximum_accelerated_task_respects_memory_restriction";
+%%%%alg_name="optimal_order_infinite_memory_largest_communication\_task\_respects\_memory\_restriction";
+%%%%string alg_name="optimal_order_infinite_memory_smallest_communication\_task\_respects\_memory\_restriction";
+%%%%string alg_name="optimal_order_infinite_memory_maximum_accelerated\_task\_respects\_memory\_restriction";
 
@@
 \begin{itemize}[a)]
-	\item $optimal_order_infinite_memory_largest_communication_task_respects_memory_restriction$: A task with the largest communication time is chosen from the set.
-	\item $optimal_order_infinite_memory_smallest_communication_task_respects_memory_restriction$:  A task with the smallest communication time is chosen from the set.
-	\item $optimal_order_infinite_memory_maximum_accelerated_task_respects_memory_restriction$: A task,  whose ratio of compute time to communication time is maximum, is chosen from the set .
+	\item $optimal\_order\_infinite\_memory\_largest\_communication\_task\_respects\_memory\_restriction$ ($OOLCMR$): A task with the largest communication time is chosen from the set.
+	\item $optimal\_order\_infinite\_memory\_smallest\_communication\_task\_respects\_memory\_restriction$ ($OOSCMR$):  A task with the smallest communication time is chosen from the set.
+	\item $optimal\_order\_infinite\_memory\_maximum\_accelerated\_task\_respects\_memory\_restriction$ ($OOMAMR$): A task,  whose ratio of compute time to communication time is maximum, is chosen from the set .
 \end{itemize}
@@
 
-	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BDAEC$};
+	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$OOLCMR$};
 
@@
 
-	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BEADC$};
+	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$OOSCMR$};
 
@@
 
-	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BDEAC$};
+	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$OOMAMR$};
+%%	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BDEAC$};
 
@@
 
-Fig~\ref{fig:staticOrderDynamicCorrectionsExample} shows schedules for all proposed heuristics of this class for task set of Table (ref).
+Fig~\ref{fig:staticOrderDynamicCorrectionsExample} shows schedules for all proposed heuristics of this class for task set of Table~\ref{tab:staticOrderDynamicCorrectionsExample}.
 
@@
 Hence, we construct and solve the linear program iteratively for a small subset of size $k$ .
-$CP(i)$ and $CM(i)$ represent computation and communication timings of task $T_i$.
-$TM(i)$ denotes intermediate memory requirement of task $T_i$ .
+$COMP_i$ and $COMM_i$ represent computation and communication timings of task $i$.
 Memory capacity of the  target system is $C$.
@@
 $s'_i$ and $e'_i$) represent start and end time of communication (resp.
-computation) for task $T_i$.
-The formulation contains $i)$ n-1 boolean variables, $a_{ij}$, for each task $T_i$ to denote the order of $T_i$ and $T_j$  on communication channel   $ii)$ n-1 boolean variables, $b_{ij}$, for each task $T_i$ to denote the order of $T_i$ and $T_j$  on computation channel $iii)$ n-1 boolean variables, $c_{ij}$, for each task $T_i$ to denote the order of $s_i$ and $e'_j$, and $iv)$ (optional, if we consider temporary buffer requirement for each task) n-1 boolean variables, $d_{ij}$, for each task $T_i$ to denote the order of $e'_i$ and $s_j$.
-
-\noindent Let $L=\sum_i (CP(i) + CM(i))$. It is evident that $e_i =s_i + CM(i)$ and $e'_i =s'_i + CP(i)$. The constraints are following.
+computation) for task $i$.
+The formulation contains $i)$ n-1 boolean variables, $a_{ij}$, for each task $i$ to denote the order of $i$ and $j$  on communication resource   $ii)$ n-1 boolean variables, $b_{ij}$, for each task $T_i$ to denote the order of $i$ and $j$  on computation resource, and $iii)$ n-1 boolean variables, $c_{ij}$, for each task $i$ to denote the order of $s_i$ and $e'_j$.
+
+%% $TM(i)$ denotes intermediate memory requirement of task $T_i$ .
+
+%%, and $iv)$ (optional, if we consider temporary buffer requirement for each task) n-1 boolean variables, $d_{ij}$, for each task $T_i$ to denote the order of $e'_i$ and $s_j$.
+
+\noindent Let $L=\sum_i (COMP_i + COMM_i)$. It is evident that $e_i =s_i + COMM_i$ and $e'_i =s'_i + COMP_i$. The constraints are following.
 
@@
 & \text{minimize } l \text{ such that }\\
-\forall i, \quad & \text{computation of task } T_i \text{ completes:}\\
+\forall i, \quad & \text{computation of task } i \text{ completes:}\\
 & e'_i \leq l\\
@@
 & e_i \leq s'_i\\
-\forall i, \forall j\ne i, \quad & \text{exclusive communication of task }T_i \text{ on communication channel:}\\
+\forall i, \forall j\ne i, \quad & \text{exclusive communication of task } i \text{ on communication channel:}\\
 & e_j \leq s_i +(1-a_{ij})L\\
 & e_i\leq s_j +a_{ij}L\\
-\forall i, \forall j\ne i, \quad & \text{exclusive computation of task }T_i \text{ on computation channel:}\\
+\forall i, \forall j\ne i, \quad & \text{exclusive computation of task } i \text{ on computation channel:}\\
 & e'_j \leq s'_i +(1-b_{ij})L\\
 & e'_i\leq s'_j +b_{ij}L\\
-\forall i, \forall j\ne i, \quad & \text{task }T_i \text{ respects memory capacity on communication channel:}\\
+\forall i, \forall j\ne i, \quad & \text{task } i \text{ respects memory capacity on communication channel:}\\
 & e'_j \leq s_i +(1-c_{ij})L\\
@@
 & \sum_r (a_{ir} - c_{ir})CM(r) + CM(i) \le C\\
-\forall i, \forall j\ne i, \quad & \text{task }T_i \text{ respects memory capacity on computation channel:}\\
-& s_j < e'_i +(1-d_{ij})L\\
-& e'_i\leq s_j +d_{ij}L\\
-& \sum_r (d_{ir} - b_{ir})CM(r) + TM(i) \le C\\
+%%\forall i, \forall j\ne i, \quad & \text{task }T_i \text{ respects memory capacity on computation channel:}\\
+%%& s_j < e'_i +(1-d_{ij})L\\
+%%& e'_i\leq s_j +d_{ij}L\\
+%%& \sum_r (d_{ir} - b_{ir})CM(r) + TM(i) \le C\\
 \end{align*}
 
-\subsection{Favorable Situation for Heuristics}
+\subsection{Favorable Situations for Heuristics}
 \noindent The following table exhibits favorable scenarios for different heuristics.
@@
 	We consider a machine called Cascade, available at PNNL, for our experiments.
-We obtain traces by running  two molecular chemistry applications,  double precision version of Hartree-Fock (HF) and Coupled Cluster Single Double (CCSD) of NWChem package with 4 Uracil molecules input on 10 nodes of this machine.
+We obtain traces by running  two molecular chemistry applications,  double precision version of Hartree-Fock (HF) and Coupled Cluster Single Double (CCSD) of NWChem package  on 10 nodes of this machine.
 Each node is composed of 16 Intel Xeon E5-2670 cores.
 NWChem takes advantages of a Partitioned Global Address Space Programming Model, Global Arrays (GA), to use shared-memory programming APIs  on distributed memory computers.
-GA dedicates one core of each node to handle communication, hence we can view a node as being composed of 15 computational cores.
+GA dedicates one core of each node to handle other cores, hence we can view a node as being composed of 15 computational cores.
 We use 150 processes for each application and obtain 150 trace files.
+We run CCSD with Uracil molecules input and HF with SiOSi molecules (for Uracil molecules, HF has very less workload, each processor executes only around 20 tasks, that is why we chose SiOSi input for HF execution).
 Each process executes around 300-800 tasks.
@@
 Modeling of different routes of data transfers for the same source-destination pair, bandwidth sharing for different source-destination pairs and network congestion is more challenging and part of our future work.
-Our model is simple yet it provides insight to the application developers (or runtime system) that  in what-order all data transfer  are issued for the same source-destination pair to maximise communication-computation overlap.
-Our model is easily adaptable to any source-destination where there is one fixed route between source and destination (such as between CPU and GPU, one copy engine to transfer data from CPU (resp.
+Our model is simple yet it provides insight to the application developers (or runtime system) that  in what-order all data transfers  are issued for the same source-destination pair to maximise communication-computation overlap.
+Our model is easily adaptable to any source-destination pair when there is one fixed route between source and destination (such as between CPU and GPU, one copy engine to transfer data from CPU (resp.
 GPU) to GPU (resp.
@@
 HF expects to specify a tile size and we set it to 100, so that each core can be efficiently utilize.
-CCSD automatically determines tile sizes at different program points based on the input (molecule?).
+CCSD automatically determines tile sizes at different program points based on the input molecules.
 Hence, HF operates on almost homogeneous tiles while CCSD on heterogeneous tiles.
@@
 In this algorithm, each job has a start and end state and a cost is associated to change the state.
-In our context, this cost can be seen as non-overlap time of computation for two adjacent jobs.
+In our context, this cost can be seen as non-overlap time of computation for two adjacent tasks.
 Here is the main idea of this algorithm.
@@
 
-	IWe evaluate different data transfer heuristics for the several memory capacities.
+	We evaluate different data transfer heuristics for the several memory capacities.
 From the obtained traces, first we determine the minimum requirement of the memory capacity $m_c$ to execute all tasks.
@@
 Our performance metric is $ratio\_to\_optimal$, which is defined as the following.
-Let the makespan of a heuristic $H$ is $M_H$ and the makespan of the $optimal  case$ with infinite memory is $M_O$, then  $ratio\_to\_optimal (H)$ is $\frac{M_H}{M_O}$ (lower value is better).
+Let the makespan of a heuristic $H$ is $M_H$ and the makespan of the optimal  case with infinite memory is $OMIM$, then  $ratio\_to\_optimal (H)$ is $\frac{M_H}{OMIM}$ (lower value is better).
 This value would be  greater or equal to $1$.
@@
 All heuristics depict similar behavior for minimum memory capacity $m_c$  and  increasing the memory capacity slightly does not change the performance of all heuristics.
-As memory capacity increased further, dynamic variants of heuristics starts performing better and for the moderate memory capacities (close to $2m_c$ ), staticOrderDynamicCorrection variants outperforms others.
+As memory capacity increased further, dynamic variants of heuristics starts performing better and for the moderate memory capacities (close to $2m_c$ ), static order with dynamic correction variants outperform others.
 \textit{Gilmore-Gomory} heuristic does not achieve good performance.
-it can be understand from the fact that task sequence is obtained considering no extra memory is available, but here we apply the same sequence for a different scenario,  overall memory consumed at each point is limited to memory capacity.
+it can be understand from the fact that the task sequence is obtained considering no extra memory is available, but here we apply the same sequence for a different scenario,  overall memory consumed at each point is limited to memory capacity.
 
@@
 
-Figure~\ref{fig:ratio_to_optimal_best_hf} shows the performance comparison of best variants of all categories with the $order_of_submission$ strategy.
+Figure~\ref{fig:ratio_to_optimal_best_hf} shows the performance comparison of best variants of all categories with the $order\_of\_submission$ ($OS$)strategy.
 Static strategies are expected to perform better when there is not any memory capacity restriction, hence this plot indicates that static strategies face capacity bottleneck and underperform.
-Dynamic strategies achieve better performance with limited memory capacity and staticOrderDynamicCorrection  strategies suit in moderate memory capacity scenarios.
+Dynamic strategies achieve better performance with limited memory capacity and static order with dynamic correction strategies suit in moderate memory capacity scenarios.
 
@@
 CCSD application operates on tasks of different sizes, hence different heuristics depict distinct behaviors even at minimum memory capacity $m_c$ .
-Heterogeneity favors to dynamic strategies, therefore both dynamic and static+dynamic correction based strategies perform good than  static based strategies.
-Similar to HF,  static+dynamic correction based strategies outperform others as memory capacity becomes moderate.
+Heterogeneity favors to dynamic strategies, therefore both dynamic and static order with dynamic correction based strategies perform good than  static based strategies.
+Similar to HF,  static order with dynamic correction based strategies outperform others as memory capacity becomes moderate.
 
@@
 
-Figure~\ref{fig:ratio_to_optimal_best_ccsd} shows that best variants of dynamic and static+dynamic strategies achieve similar performance at minimum memory capacity $m_c$.
-But as memory capacity increases hterogeneity allows static+dynamic strategies to take advantage of static knowledge to get maximum overlap and dynamic correction to select another task in case of memory capacity limitation.
+Figure~\ref{fig:ratio_to_optimal_best_ccsd} shows that best variants of dynamic and static order with dynamic correction  strategies achieve similar performance at minimum memory capacity $m_c$.
+But as memory capacity increases heterogeneity allows static+dynamic strategies to take advantage of static knowledge to get maximum overlap and dynamic correction to select another task in case of memory capacity limitation.
 Static strategies also start performing better at the end, which indicates that this application has potential for significant communication-computation overlap and pure dynamic strategies are unable to take scheduling decision based on this information.
@@
 To get more insights into the considered applications, we also look in to their workloads.
-Figure~\ref{fig:ApplicationProperties} exhibits that HF is a communication intensive application and maximum 20\%  can be expected in the best scenario.
+Figure~\ref{fig:ApplicationProperties} exhibits that HF is a communication intensive application and maximum 20\%  overlap can be expected in the best scenario.
 While in CCSD , communications and computations are almost evenly distributed and  40-75\% communication-computation overlap is possible.
@@
 Figure~\ref{fig:best_variants_batch} shows performance of the best variants of all categories for both applications.
-The plots exhibit behavior similar to Figures~\ref{fig:ratio_to_optimal_best_hf} and ~\ref{fig:ratio_to_optimal_best_CCSD}, static+dynamic variants attain maximum communication-computation overlap and outperform other heuristics.
+The plots exhibit behavior similar to Figures~\ref{fig:ratio_to_optimal_best_hf} and ~\ref{fig:ratio_to_optimal_best_CCSD}, static order with dynamic correction variants attain maximum communication-computation overlap and outperform other heuristics.
 \todo[inline]{SKumar:combine both plots}
@@
 \subsection{Impact of heterogeneity on different heuristics}
-
+\todo[inline]{SKumar: remove this subsection or replace with an experiment which shows the performance difference with all classes of heuristics for randomly generated inputs.}
 	\begin{figure}[htb]
@@
 To know the affect of heterogeneity, we set the memory requirement of each task in CCSD trace randomly between 100 to 900 and observe the behavior of different heuristics in  Figure~\ref{fig:ratio_to_optimal_ccsd_random}.
-This plot also exhibits that static+dynamic variants make good use of static information to maximize communication-computation overlap and dynamic mechanism to minimize the penalty caused by memory capacity limitation.
+This plot also exhibits that static order with dynamic correction variants make good use of static information to maximize communication-computation overlap and dynamic mechanism to minimize the penalty caused by memory capacity limitation.
 Pure static strategies suffer from memory capacity imitation and pure dynamic strategies are unable to maximize communication-computation overlap.

### 2019-04-04 Article/article.tex
minor

@@
 Sometimes some static information such as distance to exit (last) node as a priority or affinity of computation towards resources is also provided along with the DAG.
-Then runtime manages scheduling of computations and communications, data transfer among different memories, computation-communication overlap, load balance in the best possible way.
+Then runtime manages scheduling of computations and communications, data transfers among different memories, computation-communication overlap, load balance in the best possible way.
 
@@
 It is extremely important for runtimes to decide the order of data transfers for these scheduled computations such that overlap between computations and communications can be maximised.
-This is the main topic of this paper.
+This is the main topic of this article.
 We propose different strategies for runtimes such that it can maximize the overlap of computation and communication for kernels running on two different memory nodes.
 We prove that one of our proposed strategies is an optimal one when we do not have any restriction on the capacity of memory node.
-We also prove that order of communication on two memory nodes  with the objective of minimizing the makespan is  NP-Complete.
+We also prove that order of communications on two memory nodes  with the objective of minimizing the makespan is  NP-Complete.
 We evaluate our strategies on a cluster of homogeneous nodes.
@@
 In Section~\ref{sec:heuristics}, we propose several heuristics and describe their favorable scenarios.
-We mainly consider three categories of heuristics: Static heuristics, dynamic heuristics and static heuristics with dynamic corrections.
+We mainly consider three categories of heuristics: static heuristics, dynamic heuristics and static heuristics with dynamic corrections.
 We evaluate our proposed strategies on two molecular chemistry kernels in Section~\ref{sec:exp}.

### 2019-04-04 ICPP-19/communications.tex
A new directoy with modified plots

--- 2019-04-04 Article/article.tex
@@
 
-	\todo[inline]{may convert 10 subplots to 8 in all performance diagrams}
+%%	\todo[inline]{may convert 10 subplots to 8 in all performance diagrams}
 	\todo[inline]{increase font size in all plots, may be free scale-y}
@@
 From the obtained traces, first we determine the minimum requirement of the memory capacity $m_c$ to execute all tasks.
-Then we observe the behavior of all heuristics with memory capacity  $m_c$ to $2m_c$, in the gap of $0.1m_c$.
+Then we observe the behavior of all heuristics with memory capacity  $m_c$ to $2m_c$, in the gap of $0.125m_c$.
 Our performance metric is $ratio\_to\_optimal$, which is defined as the following.
@@
 	\begin{figure}[htb]
-		\includegraphics[scale=0.3]{../ExperimentalResults/ratio_to_optimal_hf.pdf}
+		\includegraphics[scale=0.225]{./results/plots/ratio_to_optimal_selected_hf.pdf}
 		\caption{Comparison of different heuristics for HF.}
@@
 	\begin{figure}[htb]
-	\includegraphics[scale=0.25]{../ExperimentalResults/inverse_ratio_to_optimal_hf-best.pdf}
+	\includegraphics[scale=0.225]{./results/plots/inverse_ratio_to_optimal_hf-best.pdf}
 	\caption{Comparision of best variants of all categories for HF.}
@@
 	\begin{figure}[htb]
-	\includegraphics[scale=0.3]{../ExperimentalResults/ratio_to_optimal_ccsd.pdf}
+	\includegraphics[scale=0.225]{./results/plots/ratio_to_optimal_selected_ccsd.pdf}
 	\caption{Comparison of different heuristics for CCSD.}
@@
 	\begin{figure}[htb]
-	\includegraphics[scale=0.25]{../ExperimentalResults/inverse_ratio_to_optimal_ccsd-best.pdf}
+	\includegraphics[scale=0.225]{./results/plots/inverse_ratio_to_optimal_ccsd-best.pdf}
 	\caption{Comparision of best variants of all categories for CCSD.}
@@
  	\subfloat[HF workloads\label{fig:hfProperties}]{%
-		\includegraphics[width=.45\linewidth]{../ExperimentalResults/application_properties_hf.pdf}
+		\includegraphics[width=.45\linewidth]{./results/plots/application_properties_hf.pdf}
  	}%\\
  	\subfloat[CCSD workloads\label{fig:ccsdProperties}]{%
-		\includegraphics[width=.45\linewidth]{../ExperimentalResults/application_properties_ccsd.pdf}
+		\includegraphics[width=.45\linewidth]{./results/plots/application_properties_ccsd.pdf}
  	}%\\
@@
 	\begin{figure}[htb]
-	\includegraphics[scale=0.25]{../ExperimentalResults/makespan_with_lp.pdf}
+	\includegraphics[scale=0.5]{./results/makespan_with_lp.pdf}
 	\caption{Comparision of different heuristics with MILP solution based heuristic.}
@@
 	\subfloat[Best variants of HF.\label{fig:hf_best_variants_batch}]{%
-		\includegraphics[width=.45\linewidth]{../ExperimentalResults/batch-100/inverse_ratio_to_optimal_hf_batch-best.pdf}
+		\includegraphics[width=.45\linewidth]{./results/plots/inverse_ratio_to_optimal_hf_batch-best.pdf}
 	}%\\
 	\subfloat[Best variants of CCSD.\label{fig:ccsd_best_variants_batch}]{%
-		\includegraphics[width=.45\linewidth]{../ExperimentalResults/batch-100/inverse_ratio_to_optimal_ccsd_batch-best.pdf}
+		\includegraphics[width=.45\linewidth]{./results/plots/inverse_ratio_to_optimal_ccsd_batch-best.pdf}
 	}%\\
@@
 	\begin{figure}[htb]
-	\includegraphics[scale=0.3]{../ExperimentalResults/ccsd-random/ratio_to_optimal_ccsd_random.pdf}
+	\includegraphics[scale=0.225]{./results/plots/ratio_to_optimal_random_selected_ccsd.pdf}
 	\caption{Comparison of different heuristics for CCSD with highly heterogeneous tasks.}
@@
 % argument is your BibTeX string definitions and bibliography database(s)
-\bibliography{article}
+\bibliography{communications}
 

### 2019-04-04 ICPP-19/results/scripts/ratio_to_optimal.R

@@ -1,0 +1,31 @@
+#!/usr/bin/env Rscript
+ratio_to_optimal_func <-function(file_name)
+{
+library(ggplot2)
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
+dftest[,2:6]<-NULL
+dftestMelted<-melt(dftest, "capacity")
+names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
+p<-ggplot(dftestMelted, aes(x=Heuristic, y=ratio_to_optimal, color=Heuristic)) + geom_boxplot(outlier.color="black") + facet_wrap(~capacity, ncol=4)  + theme(axis.ticks = element_blank(), axis.text.x = element_blank()) + xlab("")
+p <- p + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Ratio to Optimal")
+return (p)
+}
+p<-ratio_to_optimal_func('all_results_hf.txt')
+ggsave(file="ratio_to_optimal_hf.pdf", p, width=23.6, height=13.4)
+
+p<-ratio_to_optimal_func('all_results_ccsd.txt')
+ggsave(file="ratio_to_optimal_ccsd.pdf", p, width=23.6, height=13.4)
+
+p<-ratio_to_optimal_func('selected_results_hf.txt')
+ggsave(file="ratio_to_optimal_selected_hf.pdf", p, width=23.6, height=13.4)
+
+p<-ratio_to_optimal_func('selected_results_ccsd.txt')
+ggsave(file="ratio_to_optimal_selected_ccsd.pdf", p, width=23.6, height=13.4)
+
+p<-ratio_to_optimal_func('all_results_random_ccsd.txt')
+ggsave(file="ratio_to_optimal_random_ccsd.pdf", p, width=23.6, height=13.4)
+
+p<-ratio_to_optimal_func('selected_results_random_ccsd.txt')
+ggsave(file="ratio_to_optimal_random_selected_ccsd.pdf", p, width=23.6, height=13.4)

### 2019-04-05 ICPP-19/results/scripts/insights.R
remove old files

@@ -1,25 +1,0 @@
-#!/usr/bin/env Rscript
-insights_func <-function(file_name)
-{
-library(ggplot2)
-library(reshape2)
-dftest<-read.table(file_name, header=T)
-
-
-dftest[,1:ncol(dftest)]<-dftest[,1:ncol(dftest)]/dftest[,5]
-dftest[,5]<-NULL
-dftestMelted<-melt(dftest)
-names(dftestMelted)<-c( "Parameter", "ratio_to_optimal")
-p<-ggplot(dftestMelted, aes(x=Parameter, y=ratio_to_optimal, color=Parameter))  + geom_boxplot(outlier.color="black") + geom_hline(yintercept=1, linetype="dashed", color = "red")
-p <- p + theme(plot.title = element_text(hjust = 0.5), legend.position='none') +  ggtitle("Application Properties") + scale_y_continuous(breaks=seq(0.0, 2.0, 0.5), limits=c(0, 2))
-#p <- p + theme(plot.title = element_text(hjust = 0.5), legend.position='none') +  ggtitle("Application Properties") 
-
-return (p)
-}
-p<-insights_func('insight_hf.txt')
-ggsave(file="application_properties_hf.pdf", p, width=23.6, height=13.4)
-
-p<-insights_func('insight_ccsd.txt')
-ggsave(file="application_properties_ccsd.pdf", p, width=23.6, height=13.4)
-
-

### 2019-04-05 ICPP-19/results/scripts/inverse_ratio_to_optimal-best.R

@@ -1,28 +1,0 @@
-#!/usr/bin/env Rscript
-inverse_ratio_to_optimal_best_func <-function(file_name)
-{
-library(ggplot2)
-library(reshape2)
-dftest<-read.table(file_name, header=T)
-dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
-
-dftest[,8]<-NULL
-dftest[,c(2:6)]<-NULL
-dftest$static_best<-do.call('pmin', c(dftest[,3:7]))
-dftest$dynamic_best<-do.call('pmin', c(dftest[,8:10]))
-dftest$static_dynamic_best<-do.call('pmin', c(dftest[,11:13]))
-dftest<-dftest[,c(1,2,14:16)]
-dftestMelted<-melt(dftest, "capacity")
-names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
-#p<-ggplot(dftestMelted, aes(x=jitter(capacity), y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth()
-p<-ggplot(dftestMelted, aes(x=capacity, y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth(method="loess")
-p<-p + ylab("inverse(ratio_to_optimal)") + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Performance With Best of all categories")
-return (p)
-}
-
-p<-inverse_ratio_to_optimal_best_func('all_results_hf.txt')
-ggsave(file="inverse_ratio_to_optimal_hf-best.pdf", p, width=23.6, height=13.4)
-
-p<-inverse_ratio_to_optimal_best_func('all_results_ccsd.txt')
-ggsave(file="inverse_ratio_to_optimal_ccsd-best.pdf", p, width=23.6, height=13.4)
-

### 2019-04-05 ICPP-19/communications.tex
ICPP-19 format

@@
-%
-\documentclass[runningheads]{llncs} %
+\documentclass[sigconf]{acmart}
+
+%%%
+%%% \BibTeX command to typeset BibTeX logo in the docs
+%%\AtBeginDocument{%
+%%  \providecommand\BibTeX{{%
+%%    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
+
+\copyrightyear{2019}
+\acmYear{2019}
+\setcopyright{acmlicensed}
+\acmConference[ICPP '19]{ICPP 2019: 48th International Conference on Parallel Processing}{August 05--08, 2019}{Kyoto, Japan}
+%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
+%%\acmPrice{15.00}
+%%\acmDOI{10.1145/1122445.1122456}
+%%\acmISBN{978-1-4503-9999-9/18/06}
+
 \usepackage{graphicx}
@@
 \usepackage[ruled,vlined]{algorithm2e}
-\usepackage[cmex10,fleqn]{amsmath}
+%%\usepackage[cmex10,fleqn]{amsmath}
 \usepackage{amsfonts}
@@
 
-\newcommand{\scomm}{\ensuremath{{\cal S}_{\text{COMM}}}}
-\newcommand{\scomp}{\ensuremath{{\cal S}_{\text{COMP}}}}
+%%\newcommand{\scomm}{\ensuremath{{\cal S}_{\text{COMM}}}}
+%%\newcommand{\scomp}{\ensuremath{{\cal S}_{\text{COMP}}}}
+
+\newcommand{\scomm}{\ensuremath{{S}_{\text{COMM}}}}
+\newcommand{\scomp}{\ensuremath{{S}_{\text{COMP}}}}
 
@@
 
-\begin{document} %
-	%	\title{Contribution Title\thanks{Supported by organization x.}}
+\begin{document}
+
 \title{Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels}
-	%\titlerunning{Abbreviated paper title}
-	% If the paper title is too long for the running head, you can set
-	% an abbreviated paper title here
+
+\author{Valerie B\'eranger}
+\affiliation{%
+  \institution{Inria Paris-Rocquencourt}
+  \city{Rocquencourt}
+  \country{France}
+}
+\author{John Smith}
+\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
+\email{jsmith@affiliation.org}
+
+\author{Julius P. Kumquat}
+\affiliation{\institution{The Kumquat Consortium}}
+\email{jpkumquat@consortium.net}
+
+\renewcommand{\shortauthors}{Trovato and Tobin, et al.}
+
 %
-	\author{}
-%%%%	\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and Second
-%%%%		Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and Third
-%%%%		Author\inst{3}\orcidID{2222--3333-4444-5555}} %
-%%%%	\authorrunning{F. Author et al.} % First names are abbreviated in the running
-	% head.
-	% If there are more than two authors, 'et al.' is used.
-	%
-	\institute{Princeton University, Princeton NJ 08544, USA \and Springer
-		Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
-		\email{lncs@springer.com}\\
-		\url{http://www.springer.com/gp/computer-science/lncs} \and ABC Institute,
-		Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
-		\email{\{abc,lncs\}@uni-heidelberg.de}} %
-	\maketitle              % typeset the header of the contribution
-	%
+% The abstract is a short summary of the work to be presented in the article.
 \begin{abstract}
-%%		
-%%		The abstract should briefly summarize the contents of the
-%%		paper in 150--250 words.
-
 With increasing complexity of hardwares, systems with different memory nodes are ubiquitous in high performance computing (HPC).
@@
 Our results show that some of our heuristics achieve significant overlap for moderate memory capacities and are very close to the lower bound of makespan.
-
-		\keywords{Communication Scheduling  \and Memory Nodes \and Runtime Systems \and Communication-Computation Overlap \and Molecular Chemistry.}
-	\end{abstract} %
+\end{abstract}
+
+%%\begin{CCSXML}
+%%	<ccs2012>
+%%	<concept>
+%%	<concept_id>10010520.10010553.10010562</concept_id>
+%%	<concept_desc>Computer systems organization~Embedded systems</concept_desc>
+%%	<concept_significance>500</concept_significance>
+%%	</concept>
+%%	<concept>
+%%	<concept_id>10010520.10010575.10010755</concept_id>
+%%	<concept_desc>Computer systems organization~Redundancy</concept_desc>
+%%	<concept_significance>300</concept_significance>
+%%	</concept>
+%%	<concept>
+%%	<concept_id>10010520.10010553.10010554</concept_id>
+%%	<concept_desc>Computer systems organization~Robotics</concept_desc>
+%%	<concept_significance>100</concept_significance>
+%%	</concept>
+%%	<concept>
+%%	<concept_id>10003033.10003083.10003095</concept_id>
+%%	<concept_desc>Networks~Network reliability</concept_desc>
+%%	<concept_significance>100</concept_significance>
+%%	</concept>
+%%	</ccs2012>
+%%\end{CCSXML}
+\ccsdesc[100]{Computer systems organization~Embedded systems1}
+\ccsdesc[100]{Computer systems organization~Redundancy}
+\ccsdesc{Computer systems organization~Robotics}
+\ccsdesc[100]{Networks~Network reliability}
+
+\keywords{Communication Scheduling, Memory Nodes, Runtime Systems, Communication-Computation Overlap, Molecular Chemistry}
+
+\maketitle
 
@@
 		\centering
-		\includegraphics[width=\textwidth, height=0.5\textheight, 
-		keepaspectratio]{Figs/swappedSchedule.jpg}
-		\caption{ \label{fig:bothSchedule} Original and Swapped Schedule}
+		\includegraphics[scale=0.35]{Figs/original_swapped_schedules}
+		\caption{ \label{fig:bothSchedule} Original and Swapped Schedules.}
 	\end{figure}
-
+	\todo[inline]{SKumar: decrease space between both schedules of Figure~\ref{fig:bothSchedule}}
 	We write the following constraints based on the two schedules of the Fig~\ref{fig:bothSchedule}.
@@
 
-   		\begin{table*}[htb]
+%%	\begin{table*}[htb]
 		\begin{tabular}{ |c|c|c| }
@@
 		\end{tabular}
-   		\end{table*}
+%%	\end{table*}
 	Where $x= 2 max\{a_i:1\le i\le 3m\}$\\ 
@@
 	problem reduces to $DT$, and hence problem $DT$ is NP-complete.
+	\todo[inline]{Skumar: Increase width of both channels of Figure~\ref{fig:firstSegment}.}
 
@@
 		\centering
-   		\includegraphics[scale=0.07]{Figs/3PARToSched.jpg}
-   		\caption{ \label{fig:firstSegment} First segment of Schedule $S$}
+		\includegraphics[scale=0.5]{Figs/first_segment}
+		\caption{ \label{fig:firstSegment} First segment of Schedule $S$.}
 	\end{figure}
@@
 
-\begin{table}[htb]
+\begin{table*}[htb]
 	\scriptsize
@@
 	\end{tabular}\caption{~\label{tab:heuristicsAndFavorableScenarios}Heuristics and their favorable scenarios}
-\end{table}
+\end{table*}
 
@@
 \subsection{HF Performance}	
-	\begin{figure}[htb]
-		\includegraphics[scale=0.225]{./results/plots/ratio_to_optimal_selected_hf.pdf}
+\begin{figure*}[htb]
+	\includegraphics[scale=0.25]{./results/plots/ratio_to_optimal_selected_hf.pdf}
 	\caption{Comparison of different heuristics for HF.}
 	\label{fig:ratio_to_optimal_hf}
-	\end{figure}
+\end{figure*}
 As indicated above, HF tasks are highly homogeneous, this is also noticeable in Figure~\ref{fig:ratio_to_optimal_hf}.
@@
 \begin{figure}[htb]
-	\includegraphics[scale=0.225]{./results/plots/inverse_ratio_to_optimal_hf-best.pdf}
+	\includegraphics[scale=0.15]{./results/plots/inverse_ratio_to_optimal_hf-best.pdf}
 	\caption{Comparision of best variants of all categories for HF.}
@@
 
-	\begin{figure}[htb]
-	\includegraphics[scale=0.225]{./results/plots/ratio_to_optimal_selected_ccsd.pdf}
+\begin{figure*}[htb]
+	\includegraphics[scale=0.25]{./results/plots/ratio_to_optimal_selected_ccsd.pdf}
 	\caption{Comparison of different heuristics for CCSD.}
 	\label{fig:ratio_to_optimal_ccsd}
-	\end{figure}
+\end{figure*}
 
@@
 \begin{figure}[htb]
-	\includegraphics[scale=0.225]{./results/plots/inverse_ratio_to_optimal_ccsd-best.pdf}
+	\includegraphics[scale=0.15]{./results/plots/inverse_ratio_to_optimal_ccsd-best.pdf}
 	\caption{Comparision of best variants of all categories for CCSD.}
@@
 \subsection{MILP Based Strategy}
- We use GLPK solver v4.65 to solve the MILP problem described in Section~\ref{subsec:linearprogrammingformulation}.
+We use GLPK solver v4.65 to solve the MILP formulation described in Section~\ref{subsec:linearprogrammingformulation}.
 The solver was unable to handle number of variables required to solve MILP at the scale of our interest.
@@
 Figure~\ref{fig:iterativeLpSolution} shows the comparison of different heuristics with MILP based heuristic for various memory capacities of a single trace file.
-
+\todo[inline]{SKumar: Obtain MILP based makespans for new memory capacities}
 \begin{figure}[htb]
@@
 
- \begin{figure}[htb]
+\begin{figure*}[htb]
 	\subfloat[Best variants of HF.\label{fig:hf_best_variants_batch}]{%
@@
 	\label{fig:best_variants_batch}
- \end{figure}
+\end{figure*}
 
@@
 \todo[inline]{SKumar: remove this subsection or replace with an experiment which shows the performance difference with all classes of heuristics for randomly generated inputs.}
-	\begin{figure}[htb]
-	\includegraphics[scale=0.225]{./results/plots/ratio_to_optimal_random_selected_ccsd.pdf}
+\begin{figure*}[htb]
+	\includegraphics[scale=0.25]{./results/plots/ratio_to_optimal_random_selected_ccsd.pdf}
 	\caption{Comparison of different heuristics for CCSD with highly heterogeneous tasks.}
 	\label{fig:ratio_to_optimal_ccsd_random}
-	\end{figure}
+\end{figure*}
 
@@
 
-\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
+\begin{acks}
+Identification of funding sources and other support, and thanks to individuals and groups that assisted in the research and the preparation of the work should be included in an acknowledgment section, which is placed just before the reference section in your document.
+
+\end{acks}
+
+\section{Acknowledgments}
+
+%
+% The next two lines define the bibliography style to be used, and the bibliography file.
+\bibliographystyle{ACM-Reference-Format}
 \bibliography{communications}

### 2019-04-05 ICPP-19/scripts/inverse_ratio_to_optimal-best.R

@@ -1,0 +1,28 @@
+#!/usr/bin/env Rscript
+inverse_ratio_to_optimal_best_func <-function(file_name)
+{
+library(ggplot2)
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
+
+dftest[,8]<-NULL
+dftest[,c(2:6)]<-NULL
+dftest$static_best<-do.call('pmin', c(dftest[,3:7]))
+dftest$dynamic_best<-do.call('pmin', c(dftest[,8:10]))
+dftest$static_dynamic_best<-do.call('pmin', c(dftest[,11:13]))
+dftest<-dftest[,c(1,2,14:16)]
+dftestMelted<-melt(dftest, "capacity")
+names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
+#p<-ggplot(dftestMelted, aes(x=jitter(capacity), y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth()
+p<-ggplot(dftestMelted, aes(x=capacity, y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth(method="loess")
+p<-p + ylab("inverse(ratio_to_optimal)") + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Performance With Best of all categories")
+return (p)
+}
+
+p<-inverse_ratio_to_optimal_best_func('all_results_hf.txt')
+ggsave(file="inverse_ratio_to_optimal_hf-best.pdf", p, width=23.6, height=13.4)
+
+p<-inverse_ratio_to_optimal_best_func('all_results_ccsd.txt')
+ggsave(file="inverse_ratio_to_optimal_ccsd-best.pdf", p, width=23.6, height=13.4)
+

### 2019-04-05 ICPP-19/scripts/inverse_ratio_to_optimal_batch-best.R

@@ -1,0 +1,25 @@
+#!/usr/bin/env Rscript
+inverse_ratio_to_optimal_best_func <-function(file_name)
+{
+library(ggplot2)
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
+
+dftest[,c(2:6)]<-NULL
+dftest$static_best<-do.call('pmin', c(dftest[,3:7]))
+dftest$dynamic_best<-do.call('pmin', c(dftest[,8:10]))
+dftest$static_dynamic_best<-do.call('pmin', c(dftest[,11:13]))
+dftest<-dftest[,c(1,2,14:16)]
+dftestMelted<-melt(dftest, "capacity")
+names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
+p<-ggplot(dftestMelted, aes(x=capacity, y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth(method="loess")
+p<-p + ylab("inverse(ratio_to_optimal)") + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Performance With Best of all categories")
+return (p)
+}
+p<-inverse_ratio_to_optimal_best_func('results_batch_hf.txt')
+ggsave(file="inverse_ratio_to_optimal_hf_batch-best.pdf", p, width=23.6, height=13.4)
+
+p<-inverse_ratio_to_optimal_best_func('results_batch_ccsd.txt')
+ggsave(file="inverse_ratio_to_optimal_ccsd_batch-best.pdf", p, width=23.6, height=13.4)
+

### 2019-04-05 ICPP-19/scripts/inverse_ratio_to_optimal_batch-best.R
removing duplicate files

@@ -1,25 +1,0 @@
-#!/usr/bin/env Rscript
-inverse_ratio_to_optimal_best_func <-function(file_name)
-{
-library(ggplot2)
-library(reshape2)
-dftest<-read.table(file_name, header=T)
-dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
-
-dftest[,c(2:6)]<-NULL
-dftest$static_best<-do.call('pmin', c(dftest[,3:7]))
-dftest$dynamic_best<-do.call('pmin', c(dftest[,8:10]))
-dftest$static_dynamic_best<-do.call('pmin', c(dftest[,11:13]))
-dftest<-dftest[,c(1,2,14:16)]
-dftestMelted<-melt(dftest, "capacity")
-names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
-p<-ggplot(dftestMelted, aes(x=capacity, y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth(method="loess")
-p<-p + ylab("inverse(ratio_to_optimal)") + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Performance With Best of all categories")
-return (p)
-}
-p<-inverse_ratio_to_optimal_best_func('results_batch_hf.txt')
-ggsave(file="inverse_ratio_to_optimal_hf_batch-best.pdf", p, width=23.6, height=13.4)
-
-p<-inverse_ratio_to_optimal_best_func('results_batch_ccsd.txt')
-ggsave(file="inverse_ratio_to_optimal_ccsd_batch-best.pdf", p, width=23.6, height=13.4)
-

### 2019-04-07 ICPP-19/communications.tex
minor
Changes after Lionel tikz diagrams:

@@
 		\begin{algorithmic}[1]
-		\STATE Divide ready tasks in two sets $S_1$ and $S_2$. If computation time of a task $T$is not less than its communication time, then $T$ is in $S_1$ otherwise $S_2$.
+			\STATE Divide ready tasks in two sets $S_1$ and $S_2$. If computation time of a task $T$is not less than its communication time, then $T$ is in $S_1$ otherwise in $S_2$.
 			\STATE Sort $S_1$ in queue $Q$ by non-decreasing communication times
@@
 		\begin{figure}[htb]
+			\tikzset{xtick/.style={inner xsep=0pt, inner ysep=3pt, minimum
+					size=0pt, draw},%
+				task/.style args={#1start#2length#3res#4color#5}{rounded corners, draw, inner
+					sep=0pt, fill=#5, label=center:#1, fit={(#2,#4*0.75)
+						(#2+#3,#4*0.75+0.75)}},%
+				vert/.style={inner sep=1pt, fill=black, circle, draw, label=#1}
+			}
+			\newcommand{\schedule}[1]{
+				\draw[->] (-0.4, 0) -- (#1, 0) node[below] {$t$};
+				\draw     (0, 0)    -- (0, 1.5) node[pos=0.25, left] {Compute}
+				node[pos=0.75, left] {Comm.};
+				\draw[dashed,gray] (0, 0.75) -- (#1, 0.75);
+			}
 			\centering
-		\includegraphics[scale=0.5]{Figs/first_segment}
+			\begin{tikzpicture}[scale=0.7, thick]
+			\schedule{9.5}
+			\node[task=$A_{i1}$ start 0 length 1 res 1 color cyan]{};
+			\node[task=$A_{i2}$ start 1 length 1 res 1 color blue!70!white]{};
+			\node[task=$A_{i3}$ start 2 length 1 res 1 color blue]{};
+			\node[task=$K_0$   start 0 length 3 res 0 color gray!40!white]{};
+			\node[task=$K_1$  start 3 length 6 res 1 color green]{}; 
+			\node[task=$A_{i1}$ start 3 length 1.8 res 0 color cyan]{};
+			\node[task=$A_{i2}$ start 4.8 length 2.3 res 0 color blue!70!white]{};
+			\node[task=$A_{i3}$ start 7.1 length 1.9 res 0 color blue]{};
+			\draw[<->,thin] (0, -0.2) -- node[below]{$3$} (3, -0.2) ;
+			\draw[<->,thin] (3, -0.2) -- node[below]{$b'$} (9, -0.2) ;
+			\end{tikzpicture}
 			\caption{ \label{fig:firstSegment} First segment of Schedule $S$.}
@@
 
+	\tikzset{xtick/.style={inner xsep=0pt, inner ysep=3pt, minimum
+			size=0pt, draw, label=below:#1},%
+		comm/.style args={#1start#2length#3color#4}{rounded corners=1mm, draw, inner
+			sep=0pt, fill=#4, label=center:#1, fit={(#2,0.75)
+				(#2+#3,1.5)}},%
+		comp/.style args={#1start#2length#3color#4}{rounded corners=1mm, draw, inner
+			sep=0pt, fill=#4, label=center:#1, fit={(#2,0)
+				(#2+#3,0.75)}},%
+	}
+	\newcommand{\schedule}[3]{
+		\draw[->] (-0.2, 0) -- (#1, 0) node[below] {$t$};
+		\draw     (0, 0)    -- (0, 1.5);
+		\node at (-0.8, 0.75)[rotate=90] {#2};
+		\draw[dashed,gray] (0, 0.75) -- (#1, 0.75);
+		\foreach \t in {0,#3} {
+			\node[xtick=\t] at (\t, 0){};
+		}
+	}
+	\newcommand{\task}[6][0]{
+		\node[comm=#2 start #3 length #4 color #6]{};
+		\node[comp=#2 start #3+#4+#1 length #5 color #6]{}; 
+	}
+
 	\begin{figure}[htb]
+		\newcommand{\taskA}[2][0]{\task[#1]{$A$}{#2}{3}{2}{cyan}}
+		\newcommand{\taskB}[2][0]{\task[#1]{$B$}{#2}{1}{3}{blue!40!white}}
+		\newcommand{\taskC}[2][0]{\task[#1]{$C$}{#2}{4}{4}{blue!70!white}}
+		\newcommand{\taskD}[2][0]{\task[#1]{$D$}{#2}{2}{1}{blue}}
+
 		\centering
-	%% 	\subfloat[Optimal schedule]{
-	\begin{tikzpicture}[decoration={brace, amplitude=5},scale=0.6, every node/.style={scale=0.6}]
-	\tikzstyle{legend}=[below=0.1, anchor=mid] 	
-	\node(t1) at (0,0) {};
-
-	\node[above right=0.6cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Infinite Memory Capacity$}; 	    				
-	%%	    \node[above right=0.4cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Infinite Memory Capacity$};
-
-	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b11) {$B$};
-
-	\node[below right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b12) {$B$};
-
-	\node[above right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c11) {$C$};
-
-	\node[below right=0cm and 0cm of c11.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c12) {$C$};
-
-	\node[above right=0cm and 0cm of c11.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a11) {$A$};
-
-	\node[below right=0cm and 0cm of c12.north east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a12) {$A$};
-
-	\node[above right=0cm and 0cm of a11.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d11) {$D$};
-
-	\node[below right=0cm and 0cm of a12.north east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d12) {$D$};
-
-	%%		\draw[->]	(5,-1)-- (b11.west, b11.south)	;
-
-	%%		\draw[->] ([xshift=-0.1cm, yshift=-1cm] b11.south west)--([xshift=13cm, yshift=-1cm] b11.south west);
-
-	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
-	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
-	-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
-	-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
-	-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
-	-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
-	-- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.65]{$9$}
-	-- ([shift={(10, -0.65)}] t1.mid)node[legend,scale=0.65]{$10$}
-	-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}
-	-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}                                      
-	--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
-
-	\foreach \x in {0, 1, 4, 5, 8, 9, 10, 11, 12} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
-
-	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$OMIM$};
-
-	%%      \node[above right=-1.15cm and -2cm of t1.mid, scale=1, rotate=0] {$Hello BCAD$};
-
-	\node(t1) at ([shift={(0, -3.8)}] t1.mid) {};   
-	%%	    \node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](MC) {$Memory Capacity=6$}; 
-	%%	    \node[above right=0.4cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Memory Capacity=6$};	   
-	\node[above right=0.6cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Memory Capacity=6$};
-
-	%%   		\node(t1) at ([shift={(0, -1.0)}] t1.mid) {};                		
-	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b21) {$B$};
-
-	\node[below right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b22) {$B$};
-
-	\node[above right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c21) {$C$};
-
-	\node[below right=0cm and 0cm of c21.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c22) {$C$};
-
-	\node[above right=0cm and 0cm of c22.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a21) {$A$};
-
-	\node[below right=0cm and 0cm of a21.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a22) {$A$};
-
-	\node[above right=0cm and 0cm of a21.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d11) {$D$};
-
-	\node[below right=0cm and 0cm of d11.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d12) {$D$};
-
-	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
-	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
-	-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
-	-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
-	-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
-	-- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.65]{$9$}
-	-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}         
-	-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.65]{$14$}                                      
-	-- ([shift={(15, -0.65)}] t1.mid)node[legend,scale=0.65]{$15$}
-	-- ([shift={(17, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
-
-	\foreach \x in {0, 1, 4, 5, 9, 12, 14, 15} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
-
-	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$OOSIM$};
-
-	%% schedule of third heuristic		
-	\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};                		
-	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b31) {$B$};
-
-	\node[below right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b32) {$B$};
-
-	\node[above right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d31) {$D$};
-
-	\node[below right=0cm and 0cm of b32.north east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d32) {$D$};
-
-	\node[above right=0cm and 0cm of d31.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a31) {$A$};
-
-	\node[below right=0cm and 0cm of a31.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a32) {$A$};
-
-	\node[above right=0cm and 0cm of a32.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c31) {$C$};
-
-	\node[below right=0cm and 0cm of c31.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c32) {$C$};
-
-	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
-	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
-	-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
-	-- ([shift={(3, -0.65)}] t1.mid)node[legend,scale=0.65]{$3$}
-	-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
-	-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
-	-- ([shift={(6, -0.65)}] t1.mid)node[legend,scale=0.65]{$6$}         
-	-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}                                      
-	-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$} 
-	-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.65]{$16$}
-	--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
-
-	\foreach \x in {0, 1, 3, 4, 5, 6, 8, 12, 16} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
-
-	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$IOCMS$};
-
-	%% schedule of fourth heuristic		
-	\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};                		
-	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c41) {$C$};
-
-	\node[below right=0cm and 0cm of c41.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c42) {$C$};
-
-	\node[above right=0cm and 0cm of c41.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b41) {$B$};
-
-	\node[below right=0cm and 0cm of c42.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b42) {$B$};
-
-	\node[above right=0cm and 0cm of c42.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a41) {$A$};
-
-	\node[below right=0cm and 0cm of a41.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a42) {$A$};
-
-	\node[above right=0cm and 0cm of b42.north east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d41) {$D$};
-
-	\node[below right=0cm and 0cm of d41.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d42) {$D$};
-
-	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
-	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
-	-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
-	-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
-	-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
-	-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}
-	-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}         
-	-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.65]{$14$} 
-	--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
-
-	\foreach \x in {0, 4, 5, 8, 11, 13, 14} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
-
-	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$DOCPS$};
-
-	%% schedule of fifth heuristic		
-	\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};                		
-	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d51) {$D$};
-
-	\node[below right=0cm and 0cm of d51.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d52) {$D$};
-
-	\node[above right=0cm and 0cm of d51.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b51) {$B$};
-
-	\node[below right=0cm and 0cm of b51.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b52) {$B$};
-
-	\node[above right=0cm and 0cm of d52.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a51) {$A$};
-
-	\node[below right=0cm and 0cm of a51.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a52) {$A$};
-
-	\node[above right=0cm and 0cm of a52.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c51) {$C$};
-
-	\node[below right=0cm and 0cm of c51.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c52) {$C$};
-
-	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
-	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
-	-- ([shift={(2, -0.65)}] t1.mid)node[legend,scale=0.65]{$2$}
-	-- ([shift={(3, -0.65)}] t1.mid)node[legend,scale=0.65]{$3$}
-	-- ([shift={(6, -0.65)}] t1.mid)node[legend,scale=0.65]{$6$}
-	-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
-	-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}         
-	-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.65]{$16$} 
-	--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
-
-	\foreach \x in {0, 2, 3, 6, 8, 12, 16} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
-
-	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$IOCCS$};
-
-	%% schedule of sixth heuristic		
-	\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};                		
-	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c61) {$C$};
-
-	\node[below right=0cm and 0cm of c61.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c62) {$C$};
-
-	\node[above right=0cm and 0cm of c62.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a61) {$A$};
-
-	\node[below right=0cm and 0cm of a61.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a62) {$A$};
-
-	\node[above right=0cm and 0cm of a61.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b61) {$B$};
-
-	\node[below right=0cm and 0cm of a62.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b62) {$B$};
-
-	\node[above right=0cm and 0cm of b61.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d61) {$D$};
-
-	\node[below right=0cm and 0cm of b62.north east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d62) {$D$};
-
-	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
-	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
-	-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
-	-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
-	-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}
-	-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}
-	-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}         
-	-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.65]{$14$}
-	-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.65]{$16$} 
-	-- ([shift={(17, -0.65)}] t1.mid)node[legend,scale=0.65]{$17$}  
-	--([shift={(17.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
-
-	\foreach \x in {0, 4, 8, 11, 12, 13, 14, 16, 17} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
-
-	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$DOCCS$};
-
-	%%  \draw ([yshift=-0.5mm] second0.north)
-	%%		-- ([yshift=-0.5mm, xshift=0.5mm] second0.north)
-	%%		-- ([xshift=0.5mm] second0.north);
-
-	%%		\node[above left=0.15cm and 0cm of t2.south west, scale=0.5, rotate=0] {$GPU$};
-	%%		\node[above left=0.15cm and 0cm of t3.south west, scale=0.5, rotate=0] {$CPU$};		
-	%%		
-	%%		\tikzstyle{legend}=[below=0.35, anchor=mid] 	
-	%%		\draw[->] (-0.1, -0.1) -- (0, -0.1)  node[legend,scale=0.65]{$0$} --(1,-0.1) node [legend,scale=0.65]{$1$} --(1.5, -0.1) node[right,scale=0.65]{$t$}; 
-	%%		
-	%%		\foreach \x in {0cm, 1cm} \draw (\x, -0.12) -- (\x, -0.08);
-	%%		%%			To align both figures of subfloat-- an object without drawing at the same depth
-	%%		\path (-0.1, -0.5) -- (1.5, -0.5);
-
+		\subfloat[][Infinite Memory Capacity]{
+			\begin{tikzpicture}[scale=0.6]
+			\schedule{12.5}{OMIM}{1,4,5,8,9,10,11,12}
+			\taskB{0}
+			\taskC{1}
+			\taskA[1]{5}
+			\taskD[1]{8}
 			\end{tikzpicture}
-
-	\caption{ \label{fig:staticOrderExample} Different static order heuristic schedules for Table~\ref{tab:staticOrderExample}.}
+		}
+
+		\subfloat[][Memory Capacity: 6]{
+			\begin{tikzpicture}[yscale=0.6, xscale=0.45]
+			\begin{scope}
+			\schedule{15.5}{OOSIM}{1,4,5,9,12,14,15}
+			\taskB{0}
+			\taskC{1}
+			\taskA{9}
+			\taskD{12}
+			\end{scope}
+			\begin{scope}[yshift=-2.75cm]
+			\schedule{16.5}{IOCMS}{1,3,4,5,6,8,12,16}
+			\taskB{0}
+			\taskD[1]{1}
+			\taskA{3}
+			\taskC{8}
+			\end{scope}
+			\begin{scope}[yshift=-5.5cm]
+			\schedule{14.5}{DOCPS}{4,5,8,11,13,14}
+			\taskC{0}
+			\taskB[3]{4}
+			\taskA{8}
+			\taskD{11}
+			\end{scope}
+			\begin{scope}[yshift=-8.25cm]
+			\schedule{16.5}{IOCCS}{2,3,6,8,12,16}
+			\taskD{0}
+			\taskB{2}
+			\taskA{3}
+			\taskC{8}
+			\end{scope}
+			\begin{scope}[yshift=-11cm]
+			\schedule{17.5}{DOCCS}{4,8,11,12,13,14,16,17}
+			\taskC{0}
+			\taskA{8}
+			\taskB[1]{11}
+			\taskD[2]{12}
+			\end{scope}
+			\end{tikzpicture}
+		}
+
+		\caption{ \label{fig:staticOrderExample} Different static
+			order heuristic schedules for
+			Table~\ref{tab:staticOrderExample}. Optimal schedule length
+			is 14. }
 	\end{figure}
@@
 		\centering
-	%% 	\subfloat[Optimal schedule]{
-	\begin{tikzpicture}[decoration={brace, amplitude=5},scale=0.6, every node/.style={scale=0.6}]
-	\tikzstyle{legend}=[below=0.1, anchor=mid] 	
-	\node(t1) at (0,0) {};  
-	\node[above right=0.6cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=15cm, draw=white, fill=white, scale=1.5](IMC) {$Memory Capacity=6$};
-
-	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b11) {$B$};
-
-	\node[below right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](b12) {$B$};
-
-	\node[above right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=5cm,draw,fill=white](d11) {$D$};
-
-	\node[below right=0cm and 0cm of b12.north east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d12) {$D$};
-
-	\node[above right=0cm and 0cm of d12.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a11) {$A$};
-
-	\node[below right=0cm and 0cm of a11.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a12) {$A$};
-
-	\node[above right=0cm and 0cm of a12.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c11) {$C$};
-
-	\node[below right=0cm and 0cm of c11.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](c12) {$C$};
-
-	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
-	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
-	-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
-	-- ([shift={(6, -0.65)}] t1.mid)node[legend,scale=0.65]{$6$}
-	-- ([shift={(7, -0.65)}] t1.mid)node[legend,scale=0.65]{$7$}
-	-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
-	-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}         
-	-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}                                      
-	-- ([shift={(17, -0.65)}] t1.mid)node[legend,scale=0.65]{$17$}
-	-- ([shift={(23, -0.65)}] t1.mid)node[legend,scale=0.65]{$23$}
-	-- ([shift={(25.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
-
-	\foreach \x in {0, 1, 6, 7, 8, 11, 13, 17, 23} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
-
-	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$LCMR$};
-
-	%% schedule of third heuristic		
-	\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};                		
-	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b21) {$B$};
-
-	\node[below right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](b22) {$B$};
-
-	\node[above right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a21) {$A$};
-
-	\node[below right=0cm and 0cm of b22.north east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a22) {$A$};
-
-	\node[above right=0cm and 0cm of a22.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c21) {$C$};
-
-	\node[below right=0cm and 0cm of c21.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](c22) {$C$};
-
-	\node[above right=0cm and 0cm of c22.north east, minimum height=0.5cm, minimum width=5cm,draw,fill=white](d21) {$D$};
-
-	\node[below right=0cm and 0cm of d21.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d22) {$D$};
-
-	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
-	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
-	-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
-	-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
-	-- ([shift={(7, -0.65)}] t1.mid)node[legend,scale=0.65]{$7$}
-	-- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.65]{$9$}
-	-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}         
-	-- ([shift={(19, -0.65)}] t1.mid)node[legend,scale=0.65]{$19$}                                      
-	-- ([shift={(24, -0.65)}] t1.mid)node[legend,scale=0.65]{$24$}
-	-- ([shift={(25, -0.65)}] t1.mid)node[legend,scale=0.65]{$25$}
-	-- ([shift={(25.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
-
-	\foreach \x in {0, 1, 4, 7, 9, 13, 19, 24, 25} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
-
-	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$SCMR$};
-
-	%% schedule of third heuristic		
-	\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};    	
-	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b31) {$B$};
-
-	\node[below right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](b32) {$B$};
-
-	\node[above right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c31) {$C$};
-
-	\node[below right=0cm and 0cm of b32.north east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](c32) {$C$};
-
-	\node[above right=0cm and 0cm of c32.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a31) {$A$};
-
-	\node[below right=0cm and 0cm of a31.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a32) {$A$};
-
-	\node[above right=0cm and 0cm of a32.north east, minimum height=0.5cm, minimum width=5cm,draw,fill=white](d31) {$D$};
-
-	\node[below right=0cm and 0cm of d31.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d32) {$D$};
-
-	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
-	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
-	-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
-	-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
-	-- ([shift={(7, -0.65)}] t1.mid)node[legend,scale=0.65]{$7$}
-	-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}
-	-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.65]{$16$}         
-	-- ([shift={(18, -0.65)}] t1.mid)node[legend,scale=0.65]{$18$}                                      
-	-- ([shift={(23, -0.65)}] t1.mid)node[legend,scale=0.65]{$23$}
-	-- ([shift={(24, -0.65)}] t1.mid)node[legend,scale=0.65]{$24$}
-	-- ([shift={(25.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
-
-	\foreach \x in {0, 1, 5, 7, 13, 16, 18, 23, 24} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
-
-	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$MAMR$};
-
+
+		\newcommand{\taskA}[2][0]{\task[#1]{$A$}{#2}{3}{2}{cyan}}
+		\newcommand{\taskB}[2][0]{\task[#1]{$B$}{#2}{1}{6}{blue!40!white}}
+		\newcommand{\taskC}[2][0]{\task[#1]{$C$}{#2}{4}{6}{blue!70!white}}
+		\newcommand{\taskD}[2][0]{\task[#1]{$D$}{#2}{5}{1}{blue}}
+
+		\centering
+		\begin{tikzpicture}[yscale=0.6,xscale=0.3]
+		\begin{scope}
+		\schedule{24}{LCMR}{1,6,7,8,11,13,17,23}
+		\taskB{0}
+		\taskD[1]{1}
+		\taskA{8}
+		\taskC{13}
+		\end{scope}
+		\begin{scope}[yshift=-2.75cm]
+		\schedule{26}{SCMR}{1,4,7,9,13,19,24,25}
+		\taskB{0}
+		\taskA[3]{1}
+		\taskC{9}
+		\taskD{19}
+		\end{scope}
+		\begin{scope}[yshift=-5.5cm]
+		\schedule{25}{MAMR}{1,5,7,13,16,18,23,24}
+		\taskB{0}
+		\taskC[2]{1}
+		\taskA{13}
+		\taskD{18}
+		\end{scope}
 		\end{tikzpicture}
-	\caption{ \label{fig:dynamicSelectionExample} Different dynamic heuristic schedules for a task set of Table~\ref{tab:dynamicSelectionExample}.}
+		\caption{ \label{fig:dynamicSelectionExample} Different dynamic heuristic schedules for a task set of Table~\ref{tab:dynamicSelectionExample} for a memory capacity of 6.
+Optimal schedule length is 23.}
 	\end{figure}
@@
 	\begin{figure}[htb]
-	\centering
-	%% 	\subfloat[Optimal schedule]{
-	\begin{tikzpicture}[decoration={brace, amplitude=5},scale=0.3, every node/.style={scale=0.3}]
-	\tikzstyle{legend}=[below=0.1, anchor=mid] 	
-	\node(t1) at (0,0) {};  
-	\node[above right=1.2cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=20cm, draw=white, fill=white, scale=1.5](MC) {Optimal Order with Infinite Memory = $BCDAE$};
-	\node[above right=0.6cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=20cm, draw=white, fill=white, scale=1.5](MC) {$Memory Capacity=9$};
-
-	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=2cm,draw,fill=white](b11) {$B$};
-
-	\node[below right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](b12) {$B$};
-
-	\node[above right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=5cm,draw,fill=white](d11) {$D$};
-
-	\node[below right=0cm and 0cm of b12.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](d12) {$D$};
-
-	\node[above right=0cm and 0cm of b12.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](a11) {$A$};
-
-	\node[below right=0cm and 0cm of a11.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](a12) {$A$};
-
-	\node[above right=0cm and 0cm of d12.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](e11) {$E$};
-
-	\node[below right=0cm and 0cm of e11.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](e12) {$E$};
-
-	\node[above right=0cm and 0cm of e12.north east, minimum height=0.5cm, minimum width=8cm,draw,fill=white](c11) {$C$};
-
-	\node[below right=0cm and 0cm of c11.south east, minimum height=0.5cm, minimum width=8cm,draw,fill=white](c12) {$C$};
-
-	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
-	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
-	-- ([shift={(2, -0.65)}] t1.mid)node[legend,scale=0.65]{$2$}
-	-- ([shift={(7, -0.65)}] t1.mid)node[legend,scale=0.65]{$7$}
-	-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
-	-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}
-	-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}         
-	-- ([shift={(15, -0.65)}] t1.mid)node[legend,scale=0.65]{$15$}                                      
-	-- ([shift={(17, -0.65)}] t1.mid)node[legend,scale=0.65]{$17$}
-	-- ([shift={(25, -0.65)}] t1.mid)node[legend,scale=0.65]{$25$}
-	-- ([shift={(33, -0.65)}] t1.mid)node[legend,scale=0.65]{$33$}
-	-- ([shift={(33.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
-
-	\foreach \x in {0, 2, 7, 8, 12, 13, 15, 17, 25, 33} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
-
-	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$OOLCMR$};
-
-	%% schedule of second heuristic		
-	\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};
-
-	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=2cm,draw,fill=white](b21) {$B$};
-
-	\node[below right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](b22) {$B$};
-
-	\node[above right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](e21) {$E$};
-
-	\node[below right=0cm and 0cm of b22.north east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](e22) {$E$};
-
-	\node[above right=0cm and 0cm of e21.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](a21) {$A$};
-
-	\node[below right=0cm and 0cm of e22.north east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](a22) {$A$};
-
-	\node[above right=0cm and 0cm of a21.south east, minimum height=0.5cm, minimum width=5cm,draw,fill=white](d21) {$D$};
-
-	\node[below right=0cm and 0cm of d21.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](d22) {$D$};
-
-	\node[above right=0cm and 0cm of d22.north east, minimum height=0.5cm, minimum width=8cm,draw,fill=white](c21) {$C$};
-
-	\node[below right=0cm and 0cm of c21.south east, minimum height=0.5cm, minimum width=8cm,draw,fill=white](c22) {$C$};
-
-	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
-	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
-	-- ([shift={(2, -0.65)}] t1.mid)node[legend,scale=0.65]{$2$}
-	-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
-	-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
-	-- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.65]{$9$}
-	-- ([shift={(10, -0.65)}] t1.mid)node[legend,scale=0.65]{$10$}
-	-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}         
-	-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.65]{$14$}                                      
-	-- ([shift={(18, -0.65)}] t1.mid)node[legend,scale=0.65]{$18$}
-	-- ([shift={(26, -0.65)}] t1.mid)node[legend,scale=0.65]{$26$}
-	-- ([shift={(34, -0.65)}] t1.mid)node[legend,scale=0.65]{$34$}
-	-- ([shift={(34.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
-
-	\foreach \x in {0, 2, 5, 8, 9, 10, 11, 14, 18, 26, 34} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
-
-	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$OOSCMR$};
-
-	%% schedule of third heuristic		
-	\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};
-
-	\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=2cm,draw,fill=white](b31) {$B$};
-
-	\node[below right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=6cm,draw,fill=white](b32) {$B$};
-
-	\node[above right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=5cm,draw,fill=white](d31) {$D$};
-
-	\node[below right=0cm and 0cm of b32.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](d32) {$D$};
-
-	\node[above right=0cm and 0cm of b32.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](e31) {$E$};
-
-	\node[below right=0cm and 0cm of d32.north east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](e32) {$E$};
-
-	\node[above right=0cm and 0cm of d32.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](a31) {$A$};
-
-	\node[below right=0cm and 0cm of a31.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](a32) {$A$};
-
-	\node[above right=0cm and 0cm of a32.north east, minimum height=0.5cm, minimum width=8cm,draw,fill=white](c31) {$C$};
-
-	\node[below right=0cm and 0cm of c31.south east, minimum height=0.5cm, minimum width=8cm,draw,fill=white](c32) {$C$};
-
-	\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
-	-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
-	-- ([shift={(2, -0.65)}] t1.mid)node[legend,scale=0.65]{$2$}
-	-- ([shift={(7, -0.65)}] t1.mid)node[legend,scale=0.65]{$7$}
-	-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
-	-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}
-	-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}         
-	-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.65]{$14$}                                      
-	-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.65]{$16$}
-	-- ([shift={(17, -0.65)}] t1.mid)node[legend,scale=0.65]{$17$}
-	-- ([shift={(25, -0.65)}] t1.mid)node[legend,scale=0.65]{$25$}
-	-- ([shift={(33, -0.65)}] t1.mid)node[legend,scale=0.65]{$33$}
-	-- ([shift={(33.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};
-
-	\foreach \x in {0, 2, 7, 8, 11, 12, 14, 16, 17, 25, 33} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);
-
-	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$OOMAMR$};
-	%%	\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BDEAC$};
+		\newcommand{\taskA}[2][0]{\task[#1]{$A$}{#2}{4}{1}{cyan}}
+		\newcommand{\taskB}[2][0]{\task[#1]{$B$}{#2}{2}{6}{cyan!50!black}}
+		\newcommand{\taskC}[2][0]{\task[#1]{$C$}{#2}{8}{8}{blue!40!white}}
+		\newcommand{\taskD}[2][0]{\task[#1]{$D$}{#2}{5}{4}{blue!70!white}}
+		\newcommand{\taskE}[2][0]{\task[#1]{$E$}{#2}{3}{2}{blue}}
+		\begin{tikzpicture}[yscale=0.6,xscale=0.2]
+		\begin{scope}
+		\schedule{35}{OOLCMR}{2,8,12,15,17,25,33}
+		\taskB{0}
+		\taskD[1]{2}
+		\taskA{8}
+		\taskE{12}
+		\taskC{17}
+		\end{scope}
+		\begin{scope}[yshift=-2.75cm]
+		\schedule{36}{OOSCMR}{2,5,8,11,14,18,26,34}
+		\taskB{0}
+		\taskE[3]{2}
+		\taskA[1]{5}
+		\taskD{9}
+		\taskC{18}
+		\end{scope}
+		\begin{scope}[yshift=-5.5cm]
+		\schedule{36}{OOMAMR}{2,8,11,14,17,25,33}
+		\taskB{0}
+		\taskD[1]{2}
+		\taskE[1]{8}
+		\taskA{12}
+		\taskC{17}
+		\end{scope}
+		\begin{scope}[yshift=+2.75cm]
+		\schedule{40}{OMIM}{2,8,16,24,29,33,38}
+		\taskB{0}
+		\taskC{8}
+		\taskD{24}
+		\taskA{29}
+		\taskE{33}
+		\end{scope}
 
 		\end{tikzpicture}
-	\caption{ \label{fig:staticOrderDynamicCorrectionsExample} Different static order dynamic corrections heuristic schedules for a task set of Table~\ref{tab:staticOrderDynamicCorrectionsExample}.}
+		\caption{ \label{fig:staticOrderDynamicCorrectionsExample} Different static order dynamic corrections heuristic schedules for a task set of Table~\ref{tab:staticOrderDynamicCorrectionsExample} and a memory capacity of 9.
+Optimal schedule length is 33.}
 	\end{figure}
@@
 \textit{Gilmore-Gomory} heuristic does not achieve good performance.
-it can be understand from the fact that the task sequence is obtained considering no extra memory is available, but here we apply the same sequence for a different scenario,  overall memory consumed at each point is limited to memory capacity.
+It can be understood from the fact that the task sequence is obtained considering no extra memory is available, but here we apply the same sequence for a different scenario,  overall memory consumed at each point is limited to memory capacity.
 
@@
 
-\section{Acknowledgments}
-
 	%

### 2019-04-07 ICPP-19/communications.tex
rearranging stuff

@@
 	%%\end{CCSXML}
-	\ccsdesc[100]{Computer systems organization~Embedded systems1}
+	\ccsdesc[100]{Computer systems organization~Embedded systems}
 	\ccsdesc[100]{Computer systems organization~Redundancy}
@@
 Sometimes some static information such as distance to exit (last) node as a priority or affinity of computation towards resources is also provided along with the DAG.
-Then runtime manages scheduling of computations and communications, data transfers among different memories, computation-communication overlap, load balance in the best possible way.
+Then runtime is responsible for managing scheduling of computations and communications, data transfers among different memories, computation-communication overlap, and load balance.
 
@@
 Therefore, it is possible to associate priorities, based on the task graph structure, with computations, which runtime uses to make the execution efficient.
-In some applications, such as sparse linear algebra kernels, where programmers do not know the precise structure of the tasks graphs in advance,  tasks are added recursively based on certain sentinel constraints.
+In irregular applications, programmers do not know the precise structure of the tasks graphs in advance, tasks are added recursively based on certain sentinel constraints.
 For such applications, runtime sees a set of independent ready tasks and schedule them on different processing units.
@@
 This is the main topic of this article.
+We prove that order of communications on two memory nodes  with the objective of minimizing the makespan is  NP-Complete.
+Our proof is inspired from work by ~\cite{Papadimitriou:1980:FSL:322203.322213}, which applies a similar technique for 2-machine flowshop problem.
+The main difference with their and our approach is that they consider unit buffer requirement on 1st machine after job completion.
+On the contrary, our approach is designed where there is not any restriction on requested input data and memory is acquired before starting the data transfer on communication resource.
 We propose different strategies for runtimes such that it can maximize the overlap of computation and communication for kernels running on two different memory nodes.
-We prove that one of our proposed strategies is an optimal one when we do not have any restriction on the capacity of memory node.
-We also prove that order of communications on two memory nodes  with the objective of minimizing the makespan is  NP-Complete.
+We also prove that one of our proposed strategies is an optimal one when we do not have any restriction on the capacity of memory node.
 We evaluate our strategies on a cluster of homogeneous nodes.
@@
 
-	There is also a numerous study pertaining to the scheduling with limited memory and storage, since the work of Sethi and Ulman, register allocation for arithmetic expressions~\cite{Sethi:1970:GOC:321607.321620}.
+	There is also a numerous study pertaining to the scheduling with limited memory and storage, since the work of register allocation for arithmetic expressions by Sethi and Ulman~\cite{Sethi:1970:GOC:321607.321620}.
 Sarkar et.
@@
 
-	In order to prove the optimality of makespan for the schedule obtained by the above algorithm, we need the following lemma.
+\noindent In order to prove the optimality of makespan for the schedule obtained by the  Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}, we need the following lemma.
 
@@
 
-		\begin{eqnarray*}
-			\scomp(A) & = & max(t_1 + CM_A, t_2) \\
-			\scomp(B) & = & max(\scomp(A) + CP_A,  t_1 + CM_A + CM_B)
-		\end{eqnarray*}
-
-		Completion time of $B$ in original Schedule = $\scomm(B) + CP_B$
-
-		\begin{eqnarray*}
-			\text{Completion time of $B$ in swapped Schedule, } \scomp '(B) & = & max(t_1 + CM_B, t_2)\\
-			\text{Completion time of $A$ in swapped Schedule, } \scomp '(A) & = & max(\scomp'(B) + CP_B, t_1 + CM_B + CM_A)
-		\end{eqnarray*}
+			\noindent $\scomp(A) = max(t_1 + CM_A, t_2)$ \\
+			\noindent $\scomp(B) = max(\scomp(A) + CP_A,  t_1 + CM_A + CM_B)$\\
+
+%%		\begin{eqnarray*}
+%%			\scomp(A) & = & max(t_1 + CM_A, t_2) \\
+%%			\scomp(B) & = & max(\scomp(A) + CP_A,  t_1 + CM_A + CM_B)
+%%		\end{eqnarray*}
+
+		\noindent Completion time of $B$ in original Schedule = $\scomm(B) + CP_B$\\
+		\noindent Completion time of $B$ in swapped Schedule,  $\scomp '(B)  =  max(t_1 + CM_B, t_2)$\\
+		\noindent Completion time of $A$ in swapped Schedule, $ \scomp '(A) = max(\scomp'(B) + CP_B, t_1 + CM_B + CM_A)$
+
+%%		\begin{eqnarray*}
+%%			\text{Completion time of $B$ in swapped Schedule, } \scomp '(B) & = & max(t_1 + CM_B, t_2)\\
+%%			\text{Completion time of $A$ in swapped Schedule, } \scomp '(A) & = & max(\scomp'(B) + CP_B, t_1 + CM_B + CM_A)
+%%		\end{eqnarray*}
 
@@
 		\end{eqnarray*}
-
 		Case I: $CP_A \ge CM_A, CP_B \ge CM_B, CM_A \le CM_B$
@@
 		Let the final swapped schedule is $S_{final}$.
-From Lemma~\ref{lemma:swappingOfTasks}, $makespan(S_{final}) \ge makesapn(S)$.
-From the construction, $makespan(S_{final}) \le makesapn(O)$.
+From Lemma~\ref{lemma:swappingOfTasks}, $makespan(S_{final})$ $ \ge $ $makesapn(S)$.
+From the construction, $makespan(S_{final})$ $ \le$ $ makesapn(O)$.
 As $O$ is an optimal schedule, hence $makespan(S) = makesapn(O)$.
 This completes our proof.
-
 	\end{proof}
@@
 		problem reduces to $DT$, and hence problem $DT$ is NP-complete.
-		\todo[inline]{Skumar: Increase width of both channels of Figure~\ref{fig:firstSegment}.}
 
@@
 	requirement). Hence, problem $DT$ with intermediate memory requirement is also NP-complete.
-
-	The proof of the above theorem is inspired from work by [Papadimitriou et. al], which applies a similar 
-	technique for 2-machine flowshop problem, where each machine can hold fixed amount of jobs. The 
-	main difference with the our approach is that they consider unit buffer requirement on 1st machine 
-	after job completion. On the contrary, our approach is designed where there is not any restriction on 
-	requested input data and memory is acquired before starting the data transfer on communication 
-	resource.
 
@@
 
-	Fig~\ref{fig:staticOrderExample} shows schedules for all proposed heuristics of this class for task set of Table~\ref{tab:staticOrderExample}.
+	Fig~\ref{fig:staticOrderExample} shows schedules for all proposed heuristics of this class for the task set of Table~\ref{tab:staticOrderExample}.
 	\subsection{Dynamic Selection}
@@
 
-	Fig~\ref{fig:dynamicSelectionExample} shows schedules for all proposed heuristics of this class for task set of Table~\ref{tab:dynamicSelectionExample}.
+	Fig~\ref{fig:dynamicSelectionExample} shows schedules for all proposed heuristics of this class for the task set of Table~\ref{tab:dynamicSelectionExample}.
 
@@
 
-	Fig~\ref{fig:staticOrderDynamicCorrectionsExample} shows schedules for all proposed heuristics of this class for task set of Table~\ref{tab:staticOrderDynamicCorrectionsExample}.
+	Fig~\ref{fig:staticOrderDynamicCorrectionsExample} shows schedules for all proposed heuristics of this class for the task set of Table~\ref{tab:staticOrderDynamicCorrectionsExample}.
 
@@
 
+We use GLPK solver v4.65 to solve the above formulation.
+The solver was unable to handle number of variables required to solve MILP at the scale of our interest.
+Hence, we solve the linear program iteratively for a small subset of size $k=3,4,5$ (solver was unable to handle number of variables required for $k\ge6$ ) and represent the makespan calculated by this heuristic as $lp.k$.
+At the boundary of two iterations we fixed the event (communication or computation) of an unfinished task who has  started before the boundary point and consider other events flexible.
+We compute various  $lp.k$ values for different memory capacities and observe that most of the other heuristics perform better than this heuristic.
+Hence, we do not include  this heuristic for the comparison in Section~{\ref{sec:exp}.
+Figure~\ref{fig:iterativeLpSolution} shows the performance of different heuristics with MILP based heuristics for various memory capacities of a single trace file.
+%%	\subsection{MILP Based Strategy}
+%%We use GLPK solver v4.65 to solve the MILP formulation described in Section~\ref{subsec:linearprogrammingformulation}.
+The solver was unable to handle number of variables required to solve MILP at the scale of our interest.
+Hence, we solve the linear program iteratively for a small subset of size $k=3,4,5$ (solver was unable to handle number of variables required for $k\ge6$ ) and represent the makespan calculated by this heuristic as $lp.k$.
+At the boundary of two iterations we fixed the event (communication or computation) of an unfinished task who has  started before the boundary point and consider other events flexible.
+We compute various  $lp.k$ values for different memory capacities and observe that most of the other heuristics perform better than this heuristic.
+Figure~\ref{fig:iterativeLpSolution} shows the comparison of different heuristics with MILP based heuristic for various memory capacities of a single trace file.
+\todo[inline]{SKumar: Obtain MILP based makespans for new memory capacities}
+\begin{figure}[htb]
+	\includegraphics[scale=0.5]{./results/makespan_with_lp.pdf}
+	\caption{Comparision of different heuristics with MILP solution based heuristic.}
+	\label{fig:iterativeLpSolution}
+\end{figure}
+
 	\subsection{Favorable Situations for Heuristics}
@@
 This algorithm does not take memory capacity into consideration and only provides the sequence of processing.
-We applied the same sequence with different memory capacity restrictions for our experiments and call this heuristic as \textit{Gilmore-Gomory}.
+We applied the same sequence with different memory capacity restrictions for our experiments and call this heuristic as \textit{Gilmore-Gomory} ($GG$).
 
@@
 	\todo[inline]{increase font size in all plots, may be free scale-y}
-	\todo[inline]{SKumar: decide metrics: ratio to optimal, percentage overlap, 100 - percentage non overlap}
+%%	\todo[inline]{SKumar: decide metrics: ratio to optimal, percentage overlap, 100 - percentage non overlap}
 
@@
 \textit{Gilmore-Gomory} heuristic does not achieve good performance.
-It can be understood from the fact that the task sequence is obtained considering no extra memory is available, but here we apply the same sequence for a different scenario,  overall memory consumed at each point is limited to memory capacity.
+It can be explained from the fact that the task sequence is obtained considering no extra memory is available, but here we apply the same sequence for a different scenario,  overall memory consumed at each point is limited to memory capacity.
 
@@
 	CCSD application operates on tasks of different sizes, hence different heuristics depict distinct behaviors even at minimum memory capacity $m_c$ .
-Heterogeneity favors to dynamic strategies, therefore both dynamic and static order with dynamic correction based strategies perform good than  static based strategies.
-Similar to HF,  static order with dynamic correction based strategies outperform others as memory capacity becomes moderate.
+Heterogeneity favors to dynamic strategies, therefore both dynamic and static order with dynamic correction based strategies perform better than  static based strategies.
+Similar to HF,  static order with dynamic corrections based strategies outperform others as memory capacity becomes moderate.
 
@@
 	Figure~\ref{fig:ratio_to_optimal_best_ccsd} shows that best variants of dynamic and static order with dynamic correction  strategies achieve similar performance at minimum memory capacity $m_c$.
-But as memory capacity increases heterogeneity allows static+dynamic strategies to take advantage of static knowledge to get maximum overlap and dynamic correction to select another task in case of memory capacity limitation.
-Static strategies also start performing better at the end, which indicates that this application has potential for significant communication-computation overlap and pure dynamic strategies are unable to take scheduling decision based on this information.
+But as memory capacity increases, heterogeneity allows static order with dynamic corrections based strategies to take advantage of static knowledge to get maximum overlap and dynamic correction to select another task in case of memory capacity limitation.
+Static strategies also start performing better at the end, which indicates that this application has potential for significant communication-computation overlap and pure dynamic strategies are unable to take this information into account while making scheduling decisions.
 
@@
 
-	\subsection{MILP Based Strategy}
-	We use GLPK solver v4.65 to solve the MILP formulation described in Section~\ref{subsec:linearprogrammingformulation}.
-The solver was unable to handle number of variables required to solve MILP at the scale of our interest.
-Hence, we solve the linear program iteratively for a small subset of size $k=3,4,5$ (solver was unable to handle number of variables required for $k\ge6$ ) and represent the makespan calculated by this heuristic as $lp.k$.
-At the boundary of two iterations we fixed the event (communication or computation) of an unfinished task who has  started before the boundary point and consider other events flexible.
-We compute various  $lp.k$ values for different memory capacities and observe that most of the other heuristics perform better than this heuristic.
-Figure~\ref{fig:iterativeLpSolution} shows the comparison of different heuristics with MILP based heuristic for various memory capacities of a single trace file.
-	\todo[inline]{SKumar: Obtain MILP based makespans for new memory capacities}
-	\begin{figure}[htb]
-		\includegraphics[scale=0.5]{./results/makespan_with_lp.pdf}
-		\caption{Comparision of different heuristics with MILP solution based heuristic.}
-		\label{fig:iterativeLpSolution}
-	\end{figure}
-
 	\subsection{Scheduling in Batches}
@@
 We show that determining the order of data transfers is an NP complete problem.
-We proposed multiple data transfer heuristics and evaluated them on two molecular chemistry kernels, HF and CCSD.
+We proposed several data transfer heuristics and evaluated them on two molecular chemistry kernels, HF and CCSD.
 Our results show that some of our heuristics achieve significant overlap and perform very close to the lower bound of makespan.
 We plan to evaluate our strategies on different applications coming from multiple domains.
-We also plan to study the behavior of our strategies in the context of overlapping CPU-GPU communications with computation.
+We also plan to study the behavior of our strategies in the context of overlapping CPU-GPU communications with computations.
 A runtime system aims at exposing different heuristics, to maximize the communication-computation overlap, at developer level and automatically selecting the best one is currently underway.

### 2019-04-07 ICPP-19/communications.tex
removing subsection relying on random communication volumes

@@
 
-	\subsection{Impact of heterogeneity on different heuristics}
-	\todo[inline]{SKumar: remove this subsection or replace with an experiment which shows the performance difference with all classes of heuristics for randomly generated inputs.}
-	\begin{figure*}[htb]
-		\includegraphics[scale=0.25]{./results/plots/ratio_to_optimal_random_selected_ccsd.pdf}
-		\caption{Comparison of different heuristics for CCSD with highly heterogeneous tasks.}
-		\label{fig:ratio_to_optimal_ccsd_random}
-	\end{figure*}
-
-	To know the affect of heterogeneity, we set the memory requirement of each task in CCSD trace randomly between 100 to 900 and observe the behavior of different heuristics in  Figure~\ref{fig:ratio_to_optimal_ccsd_random}.
+%%	\subsection{Impact of heterogeneity on different heuristics}
+%%	\todo[inline]{SKumar: remove this subsection or replace with an experiment which shows the performance difference with all classes of heuristics for randomly generated inputs.}
+%%	\begin{figure*}[htb]
+%%		\includegraphics[scale=0.25]{./results/plots/ratio_to_optimal_random_selected_ccsd.pdf}
+%%		\caption{Comparison of different heuristics for CCSD with highly heterogeneous tasks.}
+%%		\label{fig:ratio_to_optimal_ccsd_random}
+%%	\end{figure*}	
+%%	
+%%	
+%%	To know the affect of heterogeneity, we set the memory requirement of each task in CCSD trace randomly between 100 to 900 and observe the behavior of different heuristics in  Figure~\ref{fig:ratio_to_optimal_ccsd_random}.
 This plot also exhibits that static order with dynamic correction variants make good use of static information to maximize communication-computation overlap and dynamic mechanism to minimize the penalty caused by memory capacity limitation.

### 2019-04-07 ICPP-19/communications.tex
minor

@@
 	\begin{algorithm}
-		\caption{\label{alg:OrderOfExecutionInfinteMemory}Algorithm to determine the order of processing and schedule for a set of ready tasks (infinite memory case)}
+		\caption{\label{alg:OrderOfExecutionInfinteMemory}Algorithm to determine the order of processing and schedule for a set of ready tasks (infinite memory case).}
 		\begin{algorithmic}[1]
@@
 			optimal\_order\_infinite\_memory\_maximum\_accelerated\_task\_respects\_memory\_restriction & Moderate   memory capacity and number of communication and compute intensive tasks are approximately equal \\ \hline
-		\end{tabular}\caption{~\label{tab:heuristicsAndFavorableScenarios}Heuristics and their favorable scenarios}
+		\end{tabular}\caption{~\label{tab:heuristicsAndFavorableScenarios}Heuristics and their favorable scenarios.}
 	\end{table*}

### 2019-04-07 ExperimentalData/Gilmore_Gomory.cpp
C++ code for different heuristics

@@ -386,8 +386,8 @@ int main(int argc, char* argv[])
     string alg_name="order_of_Gilmore_Gomory";
 
     long unsigned int capacity = CAPACITY;
-    long unsigned int inc = CAPACITY/10;
-    for(i=0; i<10; i++)
+    long unsigned int inc = CAPACITY/8;
+    for(i=0; i<9; i++)
     {
 
         compute_schedule_for_specified_order(tasks, ntasks, capacity);

### 2019-04-07 ExperimentalData/binpack.cpp

@@ -1,0 +1,228 @@
+#include <iostream>
+#include <string>
+#include <algorithm>
+#include <vector>
+#include <queue>
+#include <utility>
+#include <cassert>
+
+#include <limits>
+#include <iomanip>
+#include <fstream>
+#include <sstream>
+
+#include <numeric>
+#include <random>
+
+#define MAXNUMBEROFTASKS 10000
+
+
+#ifndef CAPACITY
+#define CAPACITY 0
+#endif
+
+#ifndef PRINTCOMPLETESCHEDULE
+#define PRINTCOMPLETESCHEDULE 0
+#endif
+using namespace std;
+
+class Task
+{
+    public:
+        unsigned int task_id;
+
+        double input_comm_time, comp_time, output_comm_time;
+        long unsigned int input_volume, output_volume;
+
+        double start_comm_time, end_comm_time;
+        double start_comp_time, end_comp_time;
+
+        long unsigned int internal_memory_requirement;
+        long unsigned int memory_requirement;
+
+        long unsigned int available_memory_after_comm_scheduling = CAPACITY;
+        long unsigned int available_memory_after_comp_scheduling = CAPACITY;
+        std::string task_name;
+        //private:
+        long unsigned int getMemoryRequirement() { return input_volume + internal_memory_requirement; }
+
+        unsigned int sequence_id;
+};
+
+void obtainSequence(Task* tasks, int ntasks, unsigned int capacity)
+{
+    std::vector<int> initial_sequence(ntasks);
+    std::iota(initial_sequence.begin(), initial_sequence.end(), 0);
+    std::vector<std::vector<int>>bins;
+    std::vector<int> bin_size;
+
+    for(auto i=ntasks; i>0; i--)
+    {
+        unsigned int id = rand()%i;
+        unsigned int task_id = initial_sequence[id];
+        assert(task_id == tasks[task_id].task_id);
+        initial_sequence.erase(initial_sequence.begin() +id);
+        bool found =false;
+        for(auto j=0; j<bin_size.size(); j++)
+        {
+            if(bin_size[j] <= tasks[task_id].memory_requirement);
+            {
+                bin_size[j]-=tasks[task_id].memory_requirement;
+                bins[j].push_back(task_id);
+                found = true;
+            }
+        }
+
+        if(!found)
+        {
+            std::vector<int> new_bin;
+            new_bin.push_back(task_id);
+            bin_size.push_back(capacity - tasks[task_id].memory_requirement);
[…]

### 2019-04-07 ExperimentalData/heuristics_batch.cpp

@@ -15,6 +15,9 @@
 #define PRINTCOMPLETESCHEDULE 0
 #endif
 
+#define BATCHSIZE 100
+
+
 using namespace std;
 
 class Task
@@ -248,63 +251,70 @@ void compute_schedule_next_task_heuristic(Task tasks[], long unsigned int ntasks
         //k denotes the index of next task in computation channel 
         long unsigned int k=0;
         //While all tasks complete on computation channel
+        long unsigned int end = min(i+BATCHSIZE, ntasks);
+
         while(k<ntasks)
         {
-            if(!computation_queue.empty())
+            //std::cout << "start = " << i <<" end = " <<end <<std::endl;
+            while((i < end)|| ((i == ntasks) && (k<ntasks)))
             {
-                if(computation_queue.front().end_comp_time <= early_available_comm_time)
+                if(!computation_queue.empty())
                 {
-                    available_memory_for_present_task += computation_queue.front().memory_requirement;
-                    computation_queue.pop();
+                    if(computation_queue.front().end_comp_time <= early_available_comm_time)
+                    {
+                        available_memory_for_present_task += computation_queue.front().memory_requirement;
+                        computation_queue.pop();
+                    }
                 }
-            }
-            if(k<i && early_available_comp_time <= early_available_comm_time)
-            {
-                tasks[k].start_comp_time = max(early_available_comp_time, tasks[k].end_comm_time);
-                early_available_comp_time = tasks[k].start_comp_time + tasks[k].comp_time;
-                tasks[k].end_comp_time = early_available_comp_time;
-                computation_queue.push(tasks[k]);
-                tasks[k].available_memory_after_comp_scheduling = available_memory_for_present_task;
-                k++;
-
-            }
-            else if((initial_order == true )&&(i<ntasks) && (tasks[i].memory_requirement <= available_memory_for_present_task ))
-            {
-                tasks[i].start_comm_time = early_available_comm_time;
-                early_available_comm_time += tasks[i].input_comm_time;
-                tasks[i].end_comm_time = early_available_comm_time;
-                available_memory_for_present_task -= tasks[i].memory_requirement;
-                tasks[i].available_memory_after_comm_scheduling = available_memory_for_present_task;
-                i++;
-            }
[…]

### 2019-04-08 ICPP-19/all-binpack/ratio_to_optimal.R
results with bin packing heuristic

@@ -1,0 +1,31 @@
+#!/usr/bin/env Rscript
+ratio_to_optimal_func <-function(file_name)
+{
+library(ggplot2)
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
+dftest[,2:6]<-NULL
+dftestMelted<-melt(dftest, "capacity")
+names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
+p<-ggplot(dftestMelted, aes(x=Heuristic, y=ratio_to_optimal, color=Heuristic)) + geom_boxplot(outlier.color="black") + facet_wrap(~capacity, ncol=4)  + theme(axis.ticks = element_blank(), axis.text.x = element_blank()) + xlab("")
+p <- p + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Ratio to Optimal")
+return (p)
+}
+p<-ratio_to_optimal_func('all_results_hf.txt')
+ggsave(file="ratio_to_optimal_hf.pdf", p, width=23.6, height=13.4)
+
+p<-ratio_to_optimal_func('all_results_ccsd.txt')
+ggsave(file="ratio_to_optimal_ccsd.pdf", p, width=23.6, height=13.4)
+
+p<-ratio_to_optimal_func('selected_results_hf.txt')
+ggsave(file="ratio_to_optimal_selected_hf.pdf", p, width=23.6, height=13.4)
+
+p<-ratio_to_optimal_func('selected_results_ccsd.txt')
+ggsave(file="ratio_to_optimal_selected_ccsd.pdf", p, width=23.6, height=13.4)
+
+#p<-ratio_to_optimal_func('all_results_random_ccsd.txt')
+#ggsave(file="ratio_to_optimal_random_ccsd.pdf", p, width=23.6, height=13.4)
+#
+#p<-ratio_to_optimal_func('selected_results_random_ccsd.txt')
+#ggsave(file="ratio_to_optimal_random_selected_ccsd.pdf", p, width=23.6, height=13.4)

### 2019-04-08 ICPP-19/communications.tex
added a heuristic based on first fit algorithm of bin packing problem

@@
 
-	Let \scomm($i$) and  \scomp($i$) represent the start times of task $i$ on communication and computation resources. $CM_i$ and $CP_i$ are communication and computation times of task $i$.
+	Let \scomm($i$) and  \scomp($i$) represent the start times of task $i$ on communication and computation resources.
+$CM_i$ and $CP_i$ are communication and computation times of task $i$.
+We call a task $i$ is compute (resp.
+communication) intensive if $CP_i $$\ge$ (resp.
+$<$) $CM_i$ ).
 
@@
 	%%%%string alg_name="optimal_order_infinite_memory_maximum_accelerated\_task\_respects\_memory\_restriction";
-	\begin{itemize}[a)]
+
+	\begin{enumerate}[label=\roman*)]
+		\item 
+	\end{enumerate}
+	\begin{enumerate}[label=\roman*)]
 		\item $order\_of\_optimal\_strategy\_infinite\_memory $ ($OOSIM$): Order of communications and computations is obtained by the infinite memory heuristic.
@@
 
-	\end{itemize}
-	%%\todo[inline]{SKumar: update short name of each strategy in tikz}
+	\end{enumerate}
 	\begin{table}[htb]
@@
 Then a task is chosen for processing from this set based on the following heuristics.
-	\begin{itemize}[a)]
+	\begin{enumerate}[label=\roman*)]
 		%%	\item $largest_communication\_task\_respects\_memory\_restriction$:  We select a set of tasks which induce minimum idle time on compute channel.
@@
 		\item $maximum\_accelerated\_task\_respects\_memory\_restriction$ ($MAMR$):  A task with the maximum ratio of compute time to communication time  is chosen.
-
-	\end{itemize}
+	\end{enumerate}
 	\begin{table}[htb]
@@
 
-	\begin{itemize}[a)]
+	\begin{enumerate}[label=\roman*)]
 		\item $optimal\_order\_infinite\_memory\_largest\_communication\_task\_respects\_memory\_restriction$ ($OOLCMR$): A task with the largest communication time is chosen from the set.
@@
 		\item $optimal\_order\_infinite\_memory\_maximum\_accelerated\_task\_respects\_memory\_restriction$ ($OOMAMR$): A task,  whose ratio of compute time to communication time is maximum, is chosen from the set .
-	\end{itemize}
+	\end{enumerate}
 
@@
 	%%	\todo[inline]{Scheduled based on Gilmore-Gomory algorithm and its performance }
-	We also consider an algorithm, proposed by Gilmore and Gomory, to obtain the minimal cost sequence for a set of jobs.
+	We also consider two other heuristics for evaluation.
+The first heuristic is based on an algorithm, proposed by Gilmore and Gomory, to obtain the minimal cost sequence for a set of jobs.
 In this algorithm, each job has a start and end state and a cost is associated to change the state.
@@
 When all nodes of this graph is connected then an edge interchange mechanism is taken into account to determine the sequence of jobs, which ensures that the sequence has minimal cost.
-
 We refer ~\cite{Gilmore-Gomory:1964} for the detailed algorithm and ~\cite{gitworkrepo} for our implementation.
@@
 
-	%%	\todo[inline]{may convert 10 subplots to 8 in all performance diagrams}
+	The second heuristic is based on first fit algorithm of bin packing problem.
+In this heuristic, tasks are considered in random order and added to the first bin which satisfies memory capacity restriction.
+If no bin is found then a new bin is created and this task is added to it.
+When all tasks are added to some bin then we decide the order of processing in the following way.
+If a task is added to the $jth$ location in the $ith$ bin, then it is placed at the $pth$ position for processing, where $p=\sum_{k<i}(\text{number of tasks in $kth$ bin}) + j$.
+We call this heuristic as \textit{Bin Packing} ($BP$).
+
 	\todo[inline]{increase font size in all plots, may be free scale-y}
@@
 	\subsection{HF Performance}	
+%%	\begin{figure*}[htb]
+%%		\includegraphics[scale=0.25]{./results/plots/ratio_to_optimal_selected_hf.pdf}
+%%		\caption{Comparison of different heuristics for HF.}
+%%		\label{fig:ratio_to_optimal_hf}
+%%	\end{figure*}
 	\begin{figure*}[htb]
-		\includegraphics[scale=0.25]{./results/plots/ratio_to_optimal_selected_hf.pdf}
+	\includegraphics[scale=0.25]{./all-binpack/ratio_to_optimal_selected_hf.pdf}
 	\caption{Comparison of different heuristics for HF.}
@@
 As memory capacity increased further, dynamic variants of heuristics starts performing better and for the moderate memory capacities (close to $2m_c$ ), static order with dynamic correction variants outperform others.
-\textit{Gilmore-Gomory} heuristic does not achieve good performance.
+$GG$ heuristic does not achieve good performance.
 It can be explained from the fact that the task sequence is obtained considering no extra memory is available, but here we apply the same sequence for a different scenario,  overall memory consumed at each point is limited to memory capacity.
+$BP$ heuristic does not take the advantage of task types, hence it performs poorly in most cases.
 
@@
 
+%%	\begin{figure*}[htb]
+%%		\includegraphics[scale=0.25]{./results/plots/ratio_to_optimal_selected_ccsd.pdf}
+%%		\caption{Comparison of different heuristics for CCSD.}
+%%		\label{fig:ratio_to_optimal_ccsd}
+%%	\end{figure*}
+
 	\begin{figure*}[htb]
-		\includegraphics[scale=0.25]{./results/plots/ratio_to_optimal_selected_ccsd.pdf}
+	\includegraphics[scale=0.25]{./all-binpack/ratio_to_optimal_selected_ccsd.pdf}
 	\caption{Comparison of different heuristics for CCSD.}

### 2019-04-08 ICPP-19/communications.tex
linking table with results

@@
 \subsection{Favorable Situations for Heuristics}
-	\noindent The following table exhibits favorable scenarios for different heuristics.
-This table allows programmers to use the appropriate strategies to maximize communication-computation overlap for their applications.
-
-	\begin{table*}[htb]
-		\scriptsize
-		\begin{tabular}{|c|p{3cm}|}
+Based on the definition of proposed strategies and the  optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}, we present favorable scenarios for different heuristics in Table~\ref{tab:heuristicsAndFavorableScenarios}.
+This  allows programmers to use appropriate strategies to maximize communication-computation overlap for their applications.
+
+%%\begin{table*}[htb]
+%%	\scriptsize
+%%	\begin{tabular}{|c|p{3cm}|}
+%%		\hline
+%%		\textbf{Heuristic} & \textbf{Favorable Situation} \\ \hline
+%%		order\_of\_optimal\_strategy\_infinite\_memory & Unlimited memory capacity (\textcolor{green}{Optimal}) \\ \hline
+%%		increasing\_order\_of\_communication\_strategy & Unlimited memory capacity and tasks are compute intensive (\textcolor{green}{Optimal}) \\ \hline
+%%		decreasing\_order\_of\_computation\_strategy & Unlimited memory capacity and tasks are communication intensive (\textcolor{green}{Optimal}) \\ \hline
+%%		increasing\_order\_of\_communication\_plus\_computation\_strategy & Moderate memory capacity and most tasks are compute intensive \\ \hline
+%%		decreasing\_order\_of\_communication\_plus\_computation\_strategy & Moderate memory capacity and most tasks are communication intensive \\ \hline
+%%		largest\_communication\_task\_respects\_memory\_restriction &  Limited memory capacity and significant percentage of tasks are communication intensive \\ \hline
+%%		smallest\_communication\_task\_respects\_memory\_restriction & Limited memory capacity and most tasks are compute intensive \\ \hline
+%%		maximum\_accelerated\_task\_respects\_memory\_restriction &  Limited memory capacity and number of communication and compute intensive tasks are approximately equal \\ \hline
+%%		optimal\_order\_infinite\_memory\_largest\_communication\_task\_respects\_memory\_restriction & Moderate memory capacity and significant percentage of tasks are communication intensive\\ \hline
+%%		optimal\_order\_infinite\_memory\_smallest\_communication\_task\_respects\_memory\_restriction & Moderate memory capacity and most tasks are compute intensive \\ \hline
+%%		optimal\_order\_infinite\_memory\_maximum\_accelerated\_task\_respects\_memory\_restriction & Moderate   memory capacity and number of communication and compute intensive tasks are approximately equal \\ \hline
+%%	\end{tabular}\caption{~\label{tab:heuristicsAndFavorableScenarios}Heuristics and their favorable scenarios.}
+%%\end{table*}
+
+\begin{table}[htb]
+	%%	\scriptsize
+	\begin{tabular}{|c|p{6.5cm}|}
 		\hline
-			\textbf{Heuristic} & \textbf{Favorable Situation} \\ \hline
-			order\_of\_optimal\_strategy\_infinite\_memory & Unlimited memory capacity (\textcolor{green}{Optimal}) \\ \hline
-			increasing\_order\_of\_communication\_strategy & Unlimited memory capacity and tasks are compute intensive (\textcolor{green}{Optimal}) \\ \hline
-			decreasing\_order\_of\_computation\_strategy & Unlimited memory capacity and tasks are communication intensive (\textcolor{green}{Optimal}) \\ \hline
-			increasing\_order\_of\_communication\_plus\_computation\_strategy & Moderate memory capacity and most tasks are compute intensive \\ \hline
-			decreasing\_order\_of\_communication\_plus\_computation\_strategy & Moderate memory capacity and most tasks are communication intensive \\ \hline
-			largest\_communication\_task\_respects\_memory\_restriction &  Limited memory capacity and significant percentage of tasks are communication intensive \\ \hline
-			smallest\_communication\_task\_respects\_memory\_restriction & Limited memory capacity and most tasks are compute intensive \\ \hline
-			maximum\_accelerated\_task\_respects\_memory\_restriction &  Limited memory capacity and number of communication and compute intensive tasks are approximately equal \\ \hline
-			optimal\_order\_infinite\_memory\_largest\_communication\_task\_respects\_memory\_restriction & Moderate memory capacity and significant percentage of tasks are communication intensive\\ \hline
-			optimal\_order\_infinite\_memory\_smallest\_communication\_task\_respects\_memory\_restriction & Moderate memory capacity and most tasks are compute intensive \\ \hline
-			optimal\_order\_infinite\_memory\_maximum\_accelerated\_task\_respects\_memory\_restriction & Moderate   memory capacity and number of communication and compute intensive tasks are approximately equal \\ \hline
+		\textbf{Heuristic} & \textbf{\hspace{2cm}Favorable Situation} \\ \hline
+		$OOSIM$ & Memory capacity is not a restriction (\textcolor{green}{Optimal}) \\ \hline
+		$IOCMS$ & Memory capacity is not a restriction and tasks are compute intensive (\textcolor{green}{Optimal}) \\ \hline
+		$DOCPS$ & Memory capacity is not a restriction and tasks are communication intensive (\textcolor{green}{Optimal}) \\ \hline
+		$IOCCS$ & Moderate memory capacity and most tasks are highly compute intensive \\ \hline
+		$DOCCS$ & Moderate memory capacity and most tasks are highly communication intensive \\ \hline
+		$LCMR$ & Limited memory capacity and significant percentage of tasks with large communication timings are compute intensive\\ \hline
+		$SCMR$ & Limited memory capacity and significant percentage of tasks with small communication timings are compute intensive\\ \hline
+		$MAMR$ & Limited memory capacity and significant percentage of tasks of both types\\ \hline
+		$OOLCMR$ & Moderate memory capacity and significant percentage of tasks are communication intensive\\ \hline
+		$OOSCMR$ & Moderate memory capacity and significant percentage of tasks are compute intensive \\ \hline
+		$OOMAMR$ & Moderate memory capacity and significant percentage of highly compute and  communication intensive tasks \\ \hline
 	\end{tabular}\caption{~\label{tab:heuristicsAndFavorableScenarios}Heuristics and their favorable scenarios.}
-	\end{table*}
+\end{table}
 
 Here moderate memory capacity refers to limited capacity but close to the maximum memory  requirement of the considered application.
+We can clearly observe the favorable scenarios for a few heuristics in Figures~\ref{fig:ratio_to_optimal_hf} and ~\ref{fig:ratio_to_optimal_ccsd}.
+For example, HF compute intensive tasks have small communication timings, hence $SCMR$ heuristic exhibits very good performance in limited memory cases.
+CCSD has significant percentage of both types of tasks, therefore $OOLCMR$ and $OOSCMR$ heuristics performance is very close to optimal in moderate memory cases.
 
@@
 	%%	\todo[inline]{Scheduled based on Gilmore-Gomory algorithm and its performance }
-	We also consider two other heuristics for evaluation.
+	We also consider two other static heuristics for evaluation.
 The first heuristic is based on an algorithm, proposed by Gilmore and Gomory, to obtain the minimal cost sequence for a set of jobs.

### 2019-04-09 ICPP-19/communications.tex
rearranging stuff after Lionel's modification

@@
 %%to comment all todos
-%\renewcommand{\todo}{}
+%%\renewcommand{\todo}{}
 
@@
 \newcommand{\scomp}{\ensuremath{{S}_{\text{COMP}}}}
+\newcommand{\threepart}{\textsc{3Par}\xspace}
 
@@
 		With increasing complexity of hardwares, systems with different memory nodes are ubiquitous in high performance computing (HPC).
-It is paramount to develop strategies to overlap the data transfers between memory nodes with the computation in order to exploit the full potential of these systems.
+It is paramount to develop strategies to overlap the data transfers between memory nodes with computations in order to exploit the full potential of these systems.
 In this article, we consider the problem of deciding the order of data transfers between two memory nodes for a set of independent tasks with the objective to minimize the makespan.
-We propose an optimal heuristic to obtain the order of data transfers when there is not any restriction on memory limit.
-We also show that with finite memory capacity obtaining the optimal order of data transfers is an NP-complete problem.
+We prove that with finite memory capacity obtaining the optimal order of data transfers is an NP-complete problem.
 We propose several heuristics for this problem and provide details about their favorable situations.
@@
 	%%\end{CCSXML}
-	\ccsdesc[100]{Computer systems organization~Embedded systems}
-	\ccsdesc[100]{Computer systems organization~Redundancy}
-	\ccsdesc{Computer systems organization~Robotics}
-	\ccsdesc[100]{Networks~Network reliability}
+	\ccsdesc[100]{Computer systems organization~ High Performance Computing }
+	\ccsdesc[100]{Computing Methodologies~Modeling and Simulation}
+	\ccsdesc[100]{General ~ Performance}
 
@@
 Therefore, it is possible to associate priorities, based on the task graph structure, with computations, which runtime uses to make the execution efficient.
-In irregular applications, programmers do not know the precise structure of the tasks graphs in advance, tasks are added recursively based on certain sentinel constraints.
+In irregular applications, programmers do not know the precise structure of the task graphs in advance, tasks are added recursively based on certain sentinel constraints.
 For such applications, runtime sees a set of independent ready tasks and schedule them on different processing units.
@@
 Our proof is inspired from work by ~\cite{Papadimitriou:1980:FSL:322203.322213}, which applies a similar technique for 2-machine flowshop problem.
-The main difference with their and our approach is that they consider unit buffer requirement on 1st machine after job completion.
-On the contrary, our approach is designed where there is not any restriction on requested input data and memory is acquired before starting the data transfer on communication resource.
+The main difference with their and our approach is that they consider a bounded number of tasks can await execution on second machine.
+On the contrary, our approach is designed for tasks appearing in scientific workloads whose memory requirements are highly irregular and memory is acquired before starting the data transfer on communication resource.
 We propose different strategies for runtimes such that it can maximize the overlap of computation and communication for kernels running on two different memory nodes.
-We also prove that one of our proposed strategies is an optimal one when we do not have any restriction on the capacity of memory node.
 We evaluate our strategies on a cluster of homogeneous nodes.
@@
 		\item Proposed different scheduling strategies with the objective to minimize the makespan
-		\item An optimal strategy and its proof, when there is not any memory capacity constraint on the target machine
+%%		\item An optimal strategy and its proof, when there is not any memory capacity constraint on the target machine
 		\item NP-Completeness proof for the general data-transfer problem 
@@
 Section~\ref{sec:relatedWork} describes past work on the computations with limited memory and similar problems in the literature.
-In section~\ref{sec:theoreticalProof}, we present an algorithm to obtain the order of data transfers when there is not any memory capacity restriction and prove its optimality.
+In section~\ref{sec:theoreticalProof}, we present an algorithm to obtain the order of data transfers when there is not any memory capacity restriction.
 Then, we also prove that in general data transfer problem is NP-complete.
@@
 Johnson has provided scheduling strategies for 2 and 3-machine flow shop problems with infinite memory capacity~\cite{johnson}.
-2-machine flow shop problem with finite memory capacity has been proven NP-Complete by Papadimitriou et.
+2-machine flow shop problem with finite buffer has been proven NP-Complete by Papadimitriou et.
 al~\cite{Papadimitriou:1980:FSL:322203.322213}.
-The main difference with the our approach is that they consider unit buffer requirement on 1st machine after job completion.
-On the contrary, our approach is designed for tasks appearing in scientific workloads whose sizes are highly irregular and memory is acquired before starting the communication.
+They consider a bounded number of tasks can await execution on second machine.
 
@@
 	memory node. Order of data transfers for such tasks is very crucial for the
-	communication-computation overlap, thus for the overall performance. Tasks may
-	also produce some output data, which, in general, is very less.
+	communication-computation overlap, thus for the overall performance. In general, order of task execution with input and output data transfers can be 
+	viewed as 3-machine flowshop problem, where processing time on first machine is 
+	input data transfer time, processing time on second machine is task execution time, 
+	processing time on third machine is output data transfer time and the objective is 
+	to minimize the total makespan. This is a well known hard problem~\cite{NPComplete3Machine,johnson}.
+
+	In general, output data produced by a task is very less.
 It is often the case that future tasks running on the same memory node require output data of the past tasks.
@@
 Hence, we do not consider output data separately in our analysis and assume that output data is negligible or stored in a separate buffer for each task.
+Thus problem considered here is simpler than general 3-machine flowshop problem.
 We prove that order of execution of such tasks with finite memory capacity is an NP-complete problem.
@@
 
-	\subsection{Infinite Memory Case}
-	Let $S$ be the set of tasks assigned on a processor with memory unit $M$, and this set of tasks  need input data from another memory unit $M'$.
-We assume that size of $M$ is very large and there will not be any memory capacity restriction for tasks.
+	\todo[inline]{Find a citation saying 3-machine flowshop problem is NP-Complete.}
+%%%%	done:\todo[inline]{Rewrite both paragraphs together.}
+%%	In general, order of task execution with input and output data transfers can be 
+%%	viewed as 3-machine flowshop problem, where processing time on 1st machine is 
+%%	input data transfer time, processing time on 2nd machine is task execution time, 
+%%	processing time on 3rd machine is output data transfer time and the objective is 
+%%	to minimize the total makespan.
+This is a well known hard problem~\cite{NPComplete3Machine,johnson}.
+As stated earlier, we do not consider output data separately in our analysis and assume that output data is negligible or stored in a separate buffer.
+Hence, problem considered in this article is simpler than general 3-machine flowshop problem.
+
+	\noindent\textbf{Problem $DT$} : A set of tasks $ST=\{T_1,
+	\cdots, T_n\}$ is scheduled on a processing unit $P$ with
+	memory unit $M$ of capacity $C$. Input data for tasks of $ST$
+	reside on another memory unit $M'$. $COMM_i$ is the time to
+	transfer input data from $M'$ to $M$ for task $i$ and $COMP_i$
+	is the execution time of task $i$ on $P$. We assume that these
+	tasks do not produce any output data. There can be only one
+	communication at a time, and $P$ can only process one task at
+	a time. A task uses an amount of memory in memory $M$ from the
+	start of its communication to the end of its computation.
+
+	\noindent Given $L$, is there a feasible schedule $S$ for $ST$ such that
+	makespan of $S$, $\mu(S) \le L$?
+
+%%	\todo[inline]{Mention that memory occupation of a task is the same as its communication time. Skumar: it is not required at all, but we use this for simplicity in Theorem~\ref{th:npComplete}}
+%%	\todo[inline]{Mention that it is always best to use the same order on both machines.}
 
 Let \scomm($i$) and  \scomp($i$) represent the start times of task $i$ on communication and computation resources.
-$CM_i$ and $CP_i$ are communication and computation times of task $i$.
 We call a task $i$ is compute (resp.
@@
 
+	\subsection{Special case: Infinite Memory}
+
+	When the computing resource has a very large memory, our problem
+	becomes a classic 2-machine flowshop problem: communication time is
+	the processing time on the first machine and computation time is the
+	processing time on the second machine. Johnson's
+	algorithm~\cite{johnson} is known to provide an ordering for the tasks
+	which results in an optimal makespan. This algorithm is rewritten in
+	Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}.
+
 	\begin{algorithm}
-		\caption{\label{alg:OrderOfExecutionInfinteMemory}Algorithm to determine the order of processing and schedule for a set of ready tasks (infinite memory case).}
+		\caption{\label{alg:OrderOfExecutionInfinteMemory}Johnson's~\cite{johnson} algorithm (infinite memory case).}
 		\begin{algorithmic}[1]
-			\STATE Divide ready tasks in two sets $S_1$ and $S_2$. If computation time of a task $T$is not less than its communication time, then $T$ is in $S_1$ otherwise in $S_2$.
+			\STATE Divide ready tasks in two sets $S_1$ and $S_2$. If computation time of a task $T$ is not less than its communication time, then $T$ is in $S_1$ otherwise in $S_2$.
 			\STATE Sort $S_1$ in queue $Q$ by non-decreasing communication times
@@
 			\STATE Append $Q'$ to $Q$
-			\STATE $early\_available\_time\_on\_communication\_resource \gets 0$
-			\STATE $early\_available\_time\_on\_computation\_resource \gets 0$
+			\STATE $\tau_{\text{COMM}} \gets 0$ \hfill\COMMENT{Available time of communication resource}
+			\STATE $\tau_{\text{COMP}} \gets 0$\hfill \COMMENT{Available time of computation resource}
 			\WHILE{$Q \neq \emptyset$}
-			\STATE remove a task $T$ from beginning of $Q$ for processing
-			\STATE $\scomm(T) \gets  early\_available\_time\_on\_communication\_resource$
-			\STATE $\scomp(T) \gets  max(\scomm(T) + CM_T, early\_available\_time\_on\_computation\_resource)$
-			\STATE $early\_available\_time\_on\_communication\_resource \gets  \scomm(T) + CM_T$
-			\STATE $early\_available\_time\_on\_computation\_resource \gets  \scomp(T) + CP_T$
+			\STATE Remove a task $T$ from beginning of $Q$ for processing
+			\STATE $\scomm(T) \gets \tau_{\text{COMM}}$
+			\STATE $\scomp(T) \gets max(\scomm(T) + CM_T, \tau_{\text{COMP}})$
+			\STATE $\tau_{\text{COMM}} \gets \scomm(T) + CM_T$
+			\STATE $\tau_{\text{COMP}} \gets \scomp(T) + CP_T$
 			\ENDWHILE
@@
 
-\noindent In order to prove the optimality of makespan for the schedule obtained by the  Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}, we need the following lemma.
-
-	\begin{lemma}\label{lemma:swappingOfTasks}
-		Swapping two contiguous tasks $A$ and $B$ in a schedule does not improve the makespan if one of the conditions is true.
-		\begin{enumerate}[label=\roman*)]
-			\item  $CP_A \ge CM_A, CP_B \ge CM_B, CM_A \le CM_B$
-			\item $CP_A < CM_A, CP_B < CM_B, CP_A \ge CP_B$
-			\item $CP_A \ge CM_A, CP_B < CM_B$
-		\end{enumerate}
-	\end{lemma}
-	\begin{proof}
-		Let $t_1$ and $t_2$ be the early start time on communication and computation resources just before the task $A$ starts.
-
-		\begin{figure}[htb]
-			\centering
-			\includegraphics[scale=0.35]{Figs/original_swapped_schedules}
-			\caption{ \label{fig:bothSchedule} Original and Swapped Schedules.}
-		\end{figure}
-		\todo[inline]{SKumar: decrease space between both schedules of Figure~\ref{fig:bothSchedule}}
-		We write the following constraints based on the two schedules of the Fig~\ref{fig:bothSchedule}.
-
-			\noindent $\scomp(A) = max(t_1 + CM_A, t_2)$ \\
-			\noindent $\scomp(B) = max(\scomp(A) + CP_A,  t_1 + CM_A + CM_B)$\\
-
-%%		\begin{eqnarray*}
-%%			\scomp(A) & = & max(t_1 + CM_A, t_2) \\
-%%			\scomp(B) & = & max(\scomp(A) + CP_A,  t_1 + CM_A + CM_B)
-%%		\end{eqnarray*}
-
-		\noindent Completion time of $B$ in original Schedule = $\scomm(B) + CP_B$\\
-		\noindent Completion time of $B$ in swapped Schedule,  $\scomp '(B)  =  max(t_1 + CM_B, t_2)$\\
-		\noindent Completion time of $A$ in swapped Schedule, $ \scomp '(A) = max(\scomp'(B) + CP_B, t_1 + CM_B + CM_A)$
-
-%%		\begin{eqnarray*}
-%%			\text{Completion time of $B$ in swapped Schedule, } \scomp '(B) & = & max(t_1 + CM_B, t_2)\\
-%%			\text{Completion time of $A$ in swapped Schedule, } \scomp '(A) & = & max(\scomp'(B) + CP_B, t_1 + CM_B + CM_A)
-%%		\end{eqnarray*}
-
-		In both schedules, early available time on communication resource after scheduling $A$ and $B$ is same.
-If we show that early available time on computation resource in swapped schedule after scheduling both tasks is not less than the time of original schedule, then we are done.
-Hence our goal is to prove that,
-		$$\scomp(B) + CP_B \le \scomp'(A) + CP_A $$
-
-		\begin{eqnarray*}
-			\scomp(B) + CP_B & = & max(\scomp(A) + CP_A + CP_B,  t_1 + CM_A + CM_B + CP_B)\\
-			& = & max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A + CM_B + CP_B) 
-		\end{eqnarray*}
-		Case I: $CP_A \ge CM_A, CP_B \ge CM_B, CM_A \le CM_B$
-		\begin{eqnarray*}
-			\scomp(B) + CP_B & = & max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A + CM_B + CP_B)\\
-			& \le& max(t_1 + CM_A + CP_B, t_2  + CP_B, t_1  + CM_B + CP_B) + CP_A\\
-			& = & max( t_1  + CM_B + CP_B, t_2  + CP_B) + CP_A \\
-			& = & max(max(t_1 + CM_B, t_2) + CP_B, t_1 + CM_A + CM_B) + CP_A\\
-			& = & max(\scomp'(B) + CP_B, t_1 + CM_A + CM_B) + CP_A \\
-			& = & \scomp'(A) + CP_A
-		\end{eqnarray*}
-		Case II: $CP_A < CM_A, CP_B < CM_B, CP_A \ge CP_B$
-		\begin{eqnarray*}
-			\scomp(B) + CP_B & = & max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A + CM_B + CP_B)\\
-			& \le & max(t_1 + CM_A + CP_B, t_2+CP_B, t_1 + CM_A + CM_B) + CP_A\\
-			& = & max(t_1 + CM_A + CM_B, t_2+ CP_B) + CP_A \\
-			& = & max(t_1 + CM_B + CP_B, t_2 + CP_B, t_1 + CM(A) + CM_B) + CP_A \\
-			& = & max(max(t_1 + CM_B, t_2) + CP_B, t_1 + CM_A + CM_B) + CP_A \\
-			& = & max(\scomp'(B) + CP_B, t_1 + CM_A +CM_B) + CP_A \\
-			& = & \scomp'(A) + CP_A
-		\end{eqnarray*}
-		Case III: $CP_A \ge CM_A, CP_B < CM_B$
-		\begin{eqnarray*}
-			\scomp(B) + CP_B & = & max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A + CM_B + CP_B)\\
-			& \le & max(t_1 + CM_A + CP_B, t_2 + CP_B, t_1 + CM_B + CP_B) + CP_A\\
-			& \le & max(t_1 + CM_A + CM_B, t_2 + CP_B, t_1 + CM_B + CP_B) + CP_A \\
-			& = & max(max(t_1 + CM_B, t_2) + CP_B, t_1 + CM_A + CM_B) + CP_A \\
-			& = & max(\scomp'(B) + CP_B, t_1 + CM_A +CM_B) + CP_A \\
-			& = & \scomp'(A) + CP_A
-		\end{eqnarray*}
-	\end{proof}
-
-	\begin{theorem}
-		Scheduled constructed by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} achieves optimal makespan.
-	\end{theorem}
-	%%	\begin{proof}
-	%%		Let us first define some notations which we need for this proof.
-	%%%%		\todo[inline]{SKumar: Specify the destination for all notations}
-	%%		\begin{align*}
-	%%		t : & \text{Time at which data transfer for task A starts in original schedule}\\
-	%%		S_A : & \text{ Start of computation  time of task A in original schedule}\\
-	%%		S_B : & \text{ Start of computation time of task B in original schedule}\\
-	%%		S'_A : & \text{ Start of computation time of task A in swapped schedule}\\
-	%%		S'_B : & \text{ Start of computation time of task B in swapped schedule}\\
-	%%		CM(A) : & \text{ Data transfer time for task A}\\
-	%%		CM(B) : & \text{ Data transfer time for task B}\\
-	%%		CP(A) : & \text{ Computation time of of task A}\\
-	%%		CP(B) : & \text{ Computation time of task B}\\
-	%%		\rho : & \text{ ratio of length of task and data transfer time}
-	%%		\end{align*}
-	%%	\end{proof}
-
-	\begin{proof}
-
-		Let $O$ be an optimal schedule.
-We assume that $O$ is a permuation schedule, If it is not the case, we make the order of computations same as the order of communications without increasing the makespan.
-Suppose two tasks have opposite order on both resources then we position the second task just before the first task on the computation resource.
-It is evident that this change does not alter the optimal  makespan, we repeat this procedure until order of communications and computations is same in $O$.
-
-		Let $S$ be the  schedule obtained from Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}.
-We prove the theorem by converting $S$ to $O$ and showing that at each step makespan of intermediate schedule is not less than the original makespan.
-We rely on Lemma~\ref{lemma:swappingOfTasks} to convert $S$ to $O$.
-
-		We traverse schedule $O$ from left to right and for each $ith$ task in sequence, we apply Lemma~\ref{lemma:swappingOfTasks} repetitively until order of task in the swapped schedule is same.
-It is obvious that after moving the $ith$ task at the beginning remaining schedule (schedule after $ith$ task) still satisfies one of the conditions of Lemma~\ref{lemma:swappingOfTasks}.
-
-		Let the final swapped schedule is $S_{final}$.
-From Lemma~\ref{lemma:swappingOfTasks}, $makespan(S_{final})$ $ \ge $ $makesapn(S)$.
-From the construction, $makespan(S_{final})$ $ \le$ $ makesapn(O)$.
-As $O$ is an optimal schedule, hence $makespan(S) = makesapn(O)$.
-This completes our proof.
-	\end{proof}
-
-	%%	 
-	%%	Let $S$ be the schedule obtained by the above heuristic and $O$ be an optimal schedule.
-We prove the above claim by converting $S$ to $O$ and showing that at each step completing time of intermediate schedule is not less than the completion time of original schedule $S$.
-In order to do so, we make sure order of two tasks in both schedules $S$ and $O$ is same.
-If not, We perform swapping of two tasks.
-	%%	
-	%%	\noindent If we prove the swapping strategy for two contiguous tasks holds, then the same strategy transitively hold for any two tasks of Schedule $S$
-
-	%%	Let $A$ and $B$ are two contiguous tasks of schedule $S$, which need to be swapped.
-	%%	\todo[inline]{SKumar: draw an equivalent xfig diagram}
-	%%	\begin{figure}[htb]
-	%%		\centering
-	%%		\includegraphics[width=\textwidth, height=0.5\textheight, 
-	%%		keepaspectratio]{Figs/swappedSchedule.jpg}
-	%%		\caption{ \label{fig:bothSchedule} Original and Swapped Schedule}
-	%%	\end{figure}
-	%%	
-	%%	We can write the following constraints based on the two schedules of the Fig~\ref{fig:bothSchedule}.
-	%%	
-	%%	\begin{eqnarray*}
-	%%		S_A & = & max(CM(A), l) \\
-	%%		S_B & = & max(S_A + CP(A), CM(A) + CM(B))
-	%%	\end{eqnarray*}
-	%%	
-	%%	Completion time in original Schedule = $S_B + CP(B)$
-	%%	\begin{eqnarray*}
-	%%		S'_B & = & max(CM(B), l) \\
-	%%		S'_A & = & max(S'_B + CP(B), CM(A) + CM(B))
-	%%	\end{eqnarray*}
-	%%	
-	%%	Completion time in swapped Schedule = $S'_A + CP(A)$
-	%%	
-	%%	Our goal is to prove the following inequality.
-	%%	\begin{eqnarray*}
-	%%		S_B + CP(B) & \le & S'_A + CP(A)
-	%%	\end{eqnarray*}
-	%%	\begin{proof}
-	%%		\begin{eqnarray*}
-	%%			S_B + CP(B) & = & max(S_A + CP(A)+CP(B), CM(A) + CM(B) + CP(B))\\
-	%%			& = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) 
-	%%		\end{eqnarray*}
-	%%		Case I: $A, B\in ST_1, CM(A) \le CM(B), CP(A) \ge CM(A), CP(B) \ge CM(B)$
-	%%		\begin{eqnarray*}
-	%%			S_B + CP(B) & = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) \\
-	%%			& \le & max(CM(A) + CP(B), l+CP(B), CM(B)+CP(B)) + CP(A)\\
-	%%			& = & max(CM(B) + CP(B), l + CP(B)) + CP(A) \\
-	%%			& = & max(max(CM(B), l) + CP(B), CM(A) + CM(B)) + CP(A) \\
-	%%			& = & max(S'_B + CP(B), CM(A) +CM(B)) + CP(A) \\
-	%%			& = & S'_A + CP(A)
-	%%		\end{eqnarray*}
-	%%		Case II: $A, B\in ST_2, CP(A) \ge CP(B), CP(A) < CM(A), CP(B) < CM(B)$
-	%%		\begin{eqnarray*}
-	%%			S_B + CP(B) & = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) \\
-	%%			& \le & max(CM(A) + CP(B), l+CP(B), CM(A)+CM(B)) + CP(A)\\
-	%%			& = & max(CM(A) + CM(B), l + CP(B)) + CP(A) \\
-	%%			& = & max(CM(B) + CP(B), l + CP(B), CM(A) + CM(B)) + CP(A) \\
-	%%			& = & max(max(CM(B), l) + CP(B), CM(A) + CM(B)) + CP(A) \\
-	%%			& = & max(S'_B + CP(B), CM(A) +CM(B)) + CP(A) \\
-	%%			& = & S'_A + CP(A)
-	%%		\end{eqnarray*}
-	%%		Case III: $A \in ST_1, B\in ST_2, CP(A) \ge CM(A), CP(B) < CM(B)$
-	%%		\begin{eqnarray*}
-	%%			S_B + CP(B) & = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) \\
-	%%			& \le & max(CM(A) + CP(B), l + CP(B), CM(B) + CP(B)) + CP(A)\\
-	%%			& \le & max(CM(A) + CM(B), l + CP(B), CM(B) + CP(B)) + CP(A) \\
-	%%			& = & max(max(CM(B), l) + CP(B), CM(A) + CM(B)) + CP(A) \\
-	%%			& = & max(S'_B + CP(B), CM(A) +CM(B)) + CP(A) \\
-	%%			& = & S'_A + CP(A)
-	%%		\end{eqnarray*}
-	%%	\end{proof}
-
-	The problem considered here can also be expressed as 2-machine flowshop problem with infinite storage, where communication time is the processing time on first machine and computation time is the processing time on second machine and the goal is to minimize the overall makespan.
-In ~\cite{johnson}, Johnson's algorithm also achieves the optimal makespan but the proof techniques and algorithm are quite different from ours.
+	We also prove optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} in a different way, which is available in an extended version(cite).
 	\subsection{Finite Memory}
-	\todo[inline]{Find a citation saying 3-machine flowshop problem is NP-Complete.}
-	In general, order of task execution with input and output data transfers can be 
-	viewed as  3-machine flowshop problem, where processing time on 1st machine is 
-	input data transfer time,  processing time on 2nd machine is task execution time, 
-	processing time on 3rd machine is output data transfer time  and the objective is 
-	to minimize the total makespan.
-This is a well known hard problem~\cite{NPComplete3Machine,johnson}.
-As stated earlier, we do not consider output data separately in our analysis and assume that output data is negligible or stored in a separate buffer.
-Hence, problem considered in this article is simpler than general 3-machine flowshop problem.
-
-	\noindent\textbf{Probelm  $DT$} : A set of tasks $ST=\{T_1, \cdots, T_n\}$ is scheduled on a processing 
-	unit $P$  with memory unit $M$ of capacity $C$. Input data for tasks of $ST$ reside on 
-	another memory unit $M'$.  $COMM_i$ is the time to transfer input data from $M'$ to $M$ for task 
-	$i$ and $COMP_i$ is the execution time of task $i$ on $P$.
-We assume that these tasks  do not produce any output data.
-Given $L$, is there a feasible schedule $S$ for $ST$ such that makespan of $S$, $\mu(S) \le L$?
-	%%	What is the order of execution of $ST$ on $P$ such that 
-	%%	makespan of	$ST$ is minimal? 
-	%%	
-	\begin{theorem}
+
+	We now consider the general case, in which the memory limit is a
+	constraint for the schedule. This is related to previous work by
+	Papadimitriou et. al~\cite{Papadimitriou:1980:FSL:322203.322213}, in which the second machine
+	can only handle a bounded number of tasks. Our problem generalizes this
+	work to heterogeneous memory consumption among tasks, with an
+	additional difference: memory usage starts at the beginning of the
+	first part of a task (instead of at the end of the first part). This
+	requires to provide a slightly different NP-completeness proof, as
+	given below.
+
+	\begin{theorem}\label{th:npComplete}
 		Problem $DT$ is NP-complete.
@@
 
-		Proving $DT$ is NP-complete requires first to show that decision version of this problem can be 
-		verified by a polynomial time nondeterministic algorithm, and then showing that a known 
-		NP-complete problem is polynomially reducible to this problem. As usual first job is simple and can 
-		be 
-		done in linear time, given a schedule we can check that at each change point memory capacity is 
-		restricted and a task starts execution only after its input data is transferred to $M$. In our case, the 
-		known NP-complete problem that can be reduced to problem $DT$ is the following.
-
-		\noindent \textbf{Three Partition Problem (3PAR)} : Given a set of $3m$ integers $A = \{ a_1,  
-		\cdots, a_{3m }\}$, is there a partition of $A$ into $m$ triplets $TR_i = \{a_{i_1}, a_{i_2}, a_{i_3}\}$, 
-		such that $\forall i, a_{i_1} + a_{i_2}  + a_{i_3}  = b$, where $b=(1/m) \sum a_i $?
-
-		This problem is known to be NP-complete~\cite{GareyJohnson}.
-
-		\noindent Let us first show that $3PAR$ problem reduces in polynomial time to problem $DT$.  
-		Suppose that we 
-		are given an instance  $A = \{ a_1,  \cdots, a_{3m }\}$ of $3PAR$ problem. It is immediately obvious 
-		that $a_i>1$, since we can always add sufficiently large integers to $a_i$'s and scale the problem 
-		accordingly.
-This scaling will not affect in any way the existence of a solution for the instance of $3PAR$ problem.
-Consequently, given any instance of the $3PAR$ problem, we construct an instance $I$ of the problem $DT$ such that $I$ has a schedule with makespan bounded by $L$ iff the instance
-		$I$ of $3PAR$ problem has a solution. The instance of problem $DT$ will have $4m+1$ tasks.
-
-		%%	\begin{table*}[htb]
+		It is easy to see that the $DT$ belongs in NP: given a schedule, one
+		can check in linear time that at each start of a communication, the
+		memory constraint is satisfied, and that task starts execution only
+		after its input data is transferred to $M$.
+
+		In order to prove NP-hardness, we use a reduction from the
+		well-known NP-complete problem 3 Partition~\cite{GareyJohnson}:
+
+		\noindent \textbf{Three Partition Problem} (\threepart): Given a set of
+		$3m$ integers $A = \{ a_1, \cdots, a_{3m }\}$ with $a_i > 1$, is there a partition
+		of $A$ into $m$ triplets $TR_i = \{a_{i_1}, a_{i_2}, a_{i_3}\}$,
+		such that $\forall i, a_{i_1} + a_{i_2} + a_{i_3} = b$, where
+		$b=(1/m) \sum a_i $?
+
+		Let us first show that \threepart problem reduces in polynomial time to
+		problem $DT$. Suppose that we are given an instance $A = \{ a_1,
+		\cdots, a_{3m }\}$ of \threepart. It is immediately obvious that
+		$a_i>1$, since we can always add sufficiently large integers to
+		the $a_i$ values and scale the problem accordingly. This scaling will not
+		affect in any way the existence of a solution for the instance of
+		\threepart problem.
+
+		From such an instance, we define $x = max\{a_i:1\le i\le 3m\}$,
+		and we construct an instance $I$ of the problem $DT$ with $4m+1$
+		tasks, whose characteristics are given in
+		Table~\ref{table:np.completeness.tasks}.
+
+		\begin{table}[htb]
 			\begin{tabular}{ |c|c|c| }
 				\hline
-			Task & Input Transfer time ($comm_i$)& Computation time ($e_i$)\\ \hline
+				Task & Transfer time ($comm_i$)& Computation time ($e_i$)\\ \hline
 				$K_0$ & $0$ & $3$ \\ \hline
-			$K_1, \cdots, K_{m-1}$ & $b'=b+3x$ & $3$\\ \hline
-			$K_m$ & $b'=b+3x$ & $0$ \\ \hline
-			$1\le i \le 3m, A_i$ & $1$ & $a_i' = a_i +x$\\ \hline
+				$K_1, \cdots, K_{m-1}$ & $b'=b+6x$ & $3$\\ \hline
+				$K_m$ & $b'=b+6x$ & $0$ \\ \hline
+				$1\le i \le 3m, A_i$ & $1$ & $a_i' = a_i + 2x$\\ \hline
 			\end{tabular}
-		%%	\end{table*}
-		Where $x= 2 max\{a_i:1\le i\le 3m\}$\\ 
-		Memory capacity $C=b'+3$ and $L=m(b'+3)$, this completes the construction of instance $I$ of the 
-		problem $DT$.
-
-		$Transfer time = Latency + \frac{Data Volume}{Bandwidth}$, for simplicity we consider Latency=0 
-		and Bandwidth=1, (implies Input data volume = Input transfer time), otherwise we can adjust $C$ in 
-		a way such that at any point in a schedule at max one $K_i$ and three $A_i$ tasks can be active.
-
-		We show that $I$ has a schedule $S$ with $\mu(S) \le L$ iff the original instance of $3PAR$ 
-		problem  has a solution. Notice that sum of transfer times and sum of computation times, both are 
-		equal to $L$, therefore $\mu(S) \le L$ iff $\mu(S)=L$  and there is no idle time on both resources in 
-		$S$. It indicates that first task is $K_0$ and last task is $K_m$.
-		%%   	
-		%%   	\todo[inline]{SK: Unable to argue why only $A_i$ tasks will run on communication channel when 
-		%%   	$K_0$ is running on computation channel.}
-
-		Now we prove that any feasible schedule of $I$ corresponds to a decomposition of $A$ into m 
-		triplets $TR_i = \{a_{i_1}, a_{i_2}, a_{i_3}\}$ such that $\forall i, a_{i_1} + a_{i_2}  + a_{i_3}  = b$. Every 
-		feasible schedule has to consist of $m$ segments like the one shown in Fig~\ref{fig:firstSegment}.
-Each segment provides a triplet  $\{a_{i_1}, a_{i_2}, a_{i_3}\} $such that  $a_{i_1} + a_{i_2}  + a_{i_3}  = b$.
-
-		Any schedule $S$ of $I$ having no idle time must start with $K_0$.
-No other $K_i$ tasks can be active with $K_0$, otherwise we would get idle time on computation channel ($b'>3, b'-2>max\{a_i':1\le i\le 3m\},  \text{and } b'-1 > 2 max\{a_i':1\le i\le 3m\}$).
-Hence three $A_i$ tasks must follow $K_0$.
-		Memory requirement of other $K_i$ tasks is $b'$ and $2b'>C$, therefore at any point in schedule at max one $K_i$ task can be active.
-Sum of duration of all $K_i$ tasks = $3 + (m-1)(b'+3) + b' = m (b'+3)=L$, hence at each point in $S$ exactly one $K_i$ task is active.
-When $K_i$ task is in computation phase, no other $K_i$ tasks can be active in that duration, therefore  $3A_i$ tasks must complete data transfers in that duration.
-After that next task must be a
-		$K_i$ task, otherwise total makespan would be more than $\sum(transfertime(k_i))  + 
-		\sum(computetime(k_i)) =L$. When communication for  $K_i$ task starts we exactly have $3A_i$ 
-		tasks whose data is available in local memory. Hence three $A_i$ tasks are scheduled for computation. Now we must prove that $a_{i_1}' + a_{i_2}'  + a_{i_3}'  = b'$.
-
-		This is true because if $a_{i_1}' + a_{i_2}'  + a_{i_3}'  > b'$, total used memory after the data transfer 
-		for  $K_i$ task finishes is atleast $b'+1$, hence only $A_i$ tasks can be considered, which will lead to a schedule in which at a point only $A_i$ tasks are active on both resources, therefore length of
-		schedule would be more than $L$, and if $a_{i_1}' + a_{i_2}'  + a_{i_3}'  < b'$, then we have idle time on computation channel.
-
-		Conversely, if such a partition of $A$ is achievable, then we can construct a feasible schedule $S$ 
-		without idle times by the pattern depicted in Fig~\ref{fig:firstSegment}. We have shown that $3PAR$ 
-		problem reduces to $DT$, and hence problem $DT$ is NP-complete.
+			\noindent Memory capacity: $C=b'+3$\\
+			\noindent Target makespan: $L=m(b'+3)$
+			\caption{Definition of tasks in the reduction from \threepart.}
+			\label{table:np.completeness.tasks}
+		\end{table}
+
+		$Transfer time = Latency + \frac{Data Volume}{Bandwidth}$.
+For simplicity we consider $Latency=0$ and $Bandwidth=1$, (implies Input data volume = Input transfer time).
+Otherwise, we can adjust $C$ in a way such that at any point in a schedule at max one $K_i$ and three $A_i$ tasks can be active.
+
+		We show that $I$ has a schedule $S$ with makespan at most $L$ if and
+		only if the original \threepart instance has a solution. Notice that
+		the sum of transfer times and the sum of computation times are both
+		equal to $L$, therefore a valid schedule of makespan at most $L$ has
+		makespan exactly $L$, with no idle time on both resources. It
+		indicates that the first task is $K_0$ and the last task is $K_m$.
 
 		\begin{figure}[htb]
-			\tikzset{xtick/.style={inner xsep=0pt, inner ysep=3pt, minimum
-					size=0pt, draw},%
+			\tikzset{xtick/.style={inner xsep=0pt, inner ysep=3pt, minimum size=0pt, draw},%
 				task/.style args={#1start#2length#3res#4color#5}{rounded corners, draw, inner
-					sep=0pt, fill=#5, label=center:#1, fit={(#2,#4*0.75)
-						(#2+#3,#4*0.75+0.75)}},%
+					sep=0pt, fill=#5, label=center:#1, fit={(#2,#4*0.75) (#2+#3,#4*0.75+0.75)}},%
 				vert/.style={inner sep=1pt, fill=black, circle, draw, label=#1}
@@
 				\draw[->] (-0.4, 0) -- (#1, 0) node[below] {$t$};
-				\draw     (0, 0)    -- (0, 1.5) node[pos=0.25, left] {Compute}
+				\draw (0, 0) -- (0, 1.5) node[pos=0.25, left] {Comp.}
 				node[pos=0.75, left] {Comm.};
@@
 			\centering
-			\begin{tikzpicture}[scale=0.7, thick]
-			\schedule{9.5}
-			\node[task=$A_{i1}$ start 0 length 1 res 1 color cyan]{};
-			\node[task=$A_{i2}$ start 1 length 1 res 1 color blue!70!white]{};
-			\node[task=$A_{i3}$ start 2 length 1 res 1 color blue]{};
+			\begin{tikzpicture}[yscale=0.7, thick, xscale=0.6]
+			\schedule{12.5}
+			\node[task=$A_{1,1}$ start 0 length 1 res 1 color cyan]{};
+			\node[task=$A_{1,2}$ start 1 length 1 res 1 color blue!40!white]{};
+			\node[task=$A_{1,3}$ start 2 length 1 res 1 color blue!70!white]{};
 			\node[task=$K_0$ start 0 length 3 res 0 color gray!40!white]{};
 			\node[task=$K_1$ start 3 length 6 res 1 color green]{}; 
-			\node[task=$A_{i1}$ start 3 length 1.8 res 0 color cyan]{};
-			\node[task=$A_{i2}$ start 4.8 length 2.3 res 0 color blue!70!white]{};
-			\node[task=$A_{i3}$ start 7.1 length 1.9 res 0 color blue]{};
+			\node[task=$A_{1,1}$ start 3 length 1.8 res 0 color cyan]{};
+			\node[task=$A_{1,2}$ start 4.8 length 2.3 res 0 color blue!40!white]{};
+			\node[task=$A_{1,3}$ start 7.1 length 1.9 res 0 color blue!70!white]{};
+			\node[task=$A_{2,1}$ start 9 length 1 res 1 color cyan]{};
+			\node[task=$A_{2,2}$ start 10 length 1 res 1 color blue!40!white]{};
+			\node[task=$A_{2,3}$ start 11 length 1 res 1 color blue!70!white]{};
+			\node[task=$K_1$ start 9 length 3 res 0 color green]{};
 			\draw[<->,thin] (0, -0.2) -- node[below]{$3$} (3, -0.2) ;
+			\draw[<->,thin] (9, -0.2) -- node[below]{$3$} (12, -0.2) ;
 			\draw[<->,thin] (3, -0.2) -- node[below]{$b'$} (9, -0.2) ;
 			\end{tikzpicture}
-			\caption{ \label{fig:firstSegment} First segment of Schedule $S$.}
+			\caption{ \label{fig:firstSegment} Pattern of feasible schedule $S$.}
 		\end{figure}
 
+		If the \threepart instance has a solution, $A$ can be partitioned into
+		$m$ triplets $TR_i = \{a_{i_1}, a_{i_2}, a_{i_3}\}$ such that $\forall
+		i, a_{i_1} + a_{i_2} + a_{i_3} = b$, then we can construct a feasible
+		schedule $S$ without idle times by the pattern depicted in
+		Figure~\ref{fig:firstSegment}. The communications of tasks in $TR_i$ take
+		place during the computation of task $K_{i-1}$, and the computations
+		of tasks in $TR_i$ take place during the communication of task
+		$K_i$. Since the memory capacity is $C=b'+3$, all tasks from a triplet
+		can fit in memory with a task $K_i$, and their duration are exactly
+		equal to the communication time of $K_i$. This schedule is thus
+		feasible, and has length exactly $L$.
+
+		\medskip
+
+		We now prove that any feasible schedule of $I$ corresponds to a valid
+		decomposition of $A$ for \threepart. Indeed, we argue that every
+		feasible schedule has to consist of $m$ segments like the one shown in
+		Figure~\ref{fig:firstSegment}. Each segment provides a triplet
+		$\{a_{i_1}, a_{i_2}, a_{i_3}\}$ such that $a_{i_1} + a_{i_2} + a_{i_3}
+		= b$.
+
+		Any schedule $S$ of $I$ having no idle time must start with $K_0$. We
+		first show that no other $K_i$ task can be active with $K_0$,
+		otherwise we would get idle time on computation channel. Indeed, the
+		communication of such a task $K_i$ would end at time at least $b'>3 +
+		6x$, but at most two $A_i$ tasks can be computed, and they end at time
+		at most $3+2max\{a_i':1\le i\le 3m\} = 3 + 6x$
+
+		Hence three $A_i$ tasks must follow $K_0$. The memory requirement of
+		other $K_i$ tasks is $b'$ and $2b'>C$, therefore at any point in the
+		schedule at most one $K_i$ task can be active. Since the total
+		duration of all $K_i$ tasks is $3 + (m-1)(b'+3) + b' = m (b'+3)=L$, at
+		each point in $S$ exactly one $K_i$ task is active.
+
+		With these $K_i$ tasks in place, the schedule on the computation
+		resource contains $m$ slots of length exactly $b'$, in which all $A_i$
+		tasks must fit without preemption. We can thus define triplet $TR_i$
+		as the setof tasks which execute during the communication phase of
+		task $K_i$. Since at each point in $S$, exactly one $K_i$ task is
+		active, and since $S$ has no idle time on the computation resource,
+		the total execution time of tasks in $TR_i$ is exactly $b'$, and thus
+		$a_{i_1} + a_{i_2} + a_{i_3} = b$. This partition is thus a valid
+		solution for the \threepart instance $A$.
+
+		%% We have shown that $3PAR$ problem reduces
+		%% to $DT$, and hence problem $DT$ is NP-complete.
 	\end{proof}
 
-	Each task may require some intermediate buffer. As problem $DT$ is NP-complete and intermediate 
-	memory requirement of each task is zero (which is a special case of problem with intermediate memory 
-	requirement). Hence, problem $DT$ with intermediate memory requirement is also NP-complete.
+	%% Each task may require some intermediate buffer. As problem $DT$ is NP-complete and intermediate 
+	%% memory requirement of each task is zero (which is a special case of problem with intermediate memory 
+	%% requirement). Hence, problem $DT$ with intermediate memory requirement is also NP-complete.
 
@@
 
-	The algorithm proposed in the Section~\ref{sec:theoreticalProof} provides the optimal makespan when there is not any constraint on memory capacity.
+	The algorithm presented in the Section~\ref{sec:theoreticalProof} achieves optimal makespan when there is not any memory capacity constraint.
 This optimal value indicates a lower bound on the makespan.
@@
 	\subsection{Static Ordering}
-	In this class of strategies, we compute the order of both computations and communications in advance based on criteria such as communication time, compute time and accelerated tasks.
+	In this class of strategies, we compute the order of processing in advance based on criteria such as communication time, compute time and accelerated tasks.
 After computing the order, we follow the same order on computation and communication resources and make sure that at each point in the schedule memory capacity is respected.
@@
 	In Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}, compute intensive tasks are sorted in increasing order of communication times.
-It allows tasks to utilize the computation channel maximally and make enough margin on communication resource to accommodate more communication intensive tasks with maximum overlap.
+It allows tasks to utilize the computation resource maximally and make enough margin on the communication resource to accommodate more communication intensive tasks with maximum overlap.
 Communication intensive tasks are sorted in decreasing order of computation time, which allows tasks to utilize the margin created on communication resource.
@@
 	\begin{enumerate}[label=\roman*)]
-		\item 
-	\end{enumerate}
-	\begin{enumerate}[label=\roman*)]
-		\item $order\_of\_optimal\_strategy\_infinite\_memory $ ($OOSIM$): Order of communications and computations is obtained by the infinite memory heuristic.
+		\item $order\_of\_optimal\_strategy\_infinite\_memory $ ($OOSIM$): Order of processing is obtained by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}.
 At each point in the schedule memory capacity is respected.
@@
 
-		\caption{ \label{fig:staticOrderExample} Different static
-			order heuristic schedules for
-			Table~\ref{tab:staticOrderExample}. Optimal schedule length
-			is 14. }
+		\caption{ \label{fig:staticOrderExample} Different static order heuristic schedules for Table~\ref{tab:staticOrderExample}}. 
+%%			Optimal schedule length	is 14. 
 	\end{figure}
@@
 		\end{tikzpicture}
-		\caption{ \label{fig:dynamicSelectionExample} Different dynamic heuristic schedules for a task set of Table~\ref{tab:dynamicSelectionExample} for a memory capacity of 6.
-Optimal schedule length is 23.}
+		\caption{ \label{fig:dynamicSelectionExample} Different dynamic heuristic schedules for a task set of Table~\ref{tab:dynamicSelectionExample} for a memory capacity of 6.}
+%%		 Optimal schedule length is 23.
 	\end{figure}
@@
 	In this class of strategy, we precompute the order of tasks based on different criteria and then try to follow the same order as much as possible.
-But when communication channel is idle due to memory requirement of the next task in the obtained order, then we select a task similar to previous strategy.
+But when communication resource is idle due to memory requirement of the next task in the obtained order, then we select a task similar to previous strategy.
 After a task is selected then we update the remaining order without this task.
@@
 
-	Initial order is obtained by infinity memory heuristic.
-When communication channel is idle due to memory requirement of the next task in the order, then we select a set of tasks which induce minimum idle time on compute channel and satisfy memory requirement.
+	Initial order is obtained by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}.
+When communication resource is idle due to memory requirement of the next task in the order, then we select a set of tasks which induce minimum idle time on compute channel and satisfy memory requirement.
 We define the following heuristics based on how we select a task from this set.
@@
 		\end{scope}
-		\begin{scope}[yshift=+2.75cm]
-		\schedule{40}{OMIM}{2,8,16,24,29,33,38}
-		\taskB{0}
-		\taskC{8}
-		\taskD{24}
-		\taskA{29}
-		\taskE{33}
-		\end{scope}
+%%		\begin{scope}[yshift=+2.75cm]
+%%		\schedule{40}{OMIM}{2,8,16,24,29,33,38}
+%%		\taskB{0}
+%%		\taskC{8}
+%%		\taskD{24}
+%%		\taskA{29}
+%%		\taskE{33}
+%%		\end{scope}
 
 		\end{tikzpicture}
-		\caption{ \label{fig:staticOrderDynamicCorrectionsExample} Different static order dynamic corrections heuristic schedules for a task set of Table~\ref{tab:staticOrderDynamicCorrectionsExample} and a memory capacity of 9.
-Optimal schedule length is 33.}
+		\caption{ \label{fig:staticOrderDynamicCorrectionsExample} Different static order dynamic corrections heuristic schedules for a task set of Table~\ref{tab:staticOrderDynamicCorrectionsExample} .
+The $OMIM$ order is $BCDAE$..}
 	\end{figure}
@@
 	We use a mixed integer linear program to obtain the order of data transfers and computations.
-We are unable to mange the optimal solution for the complete set $S$ in limited amount of time.
-Hence, we construct and solve the linear program iteratively for a small subset of size $k$ .
 $COMP_i$ and $COMM_i$ represent computation and communication timings of task $i$.
@@
 		\todo[inline]{More about tiling}
-	Both applications mainly perform two types of computations, tensor transpose and tensor contractions.
+		Both applications mainly perform two types of computations, tensor transpose and tensor contraction.
 HF expects to specify a tile size and we set it to 100, so that each core can be efficiently utilize.
@@
 This algorithm does not take memory capacity into consideration and only provides the sequence of processing.
-We applied the same sequence with different memory capacity restrictions for our experiments and call this heuristic as \textit{Gilmore-Gomory} ($GG$).
+We applied the same sequence with different memory capacity restrictions for our experiments and call this heuristic \textit{Gilmore-Gomory} ($GG$).
 
@@
 If a task is added to the $jth$ location in the $ith$ bin, then it is placed at the $pth$ position for processing, where $p=\sum_{k<i}(\text{number of tasks in $kth$ bin}) + j$.
-We call this heuristic as \textit{Bin Packing} ($BP$).
+We call this heuristic \textit{Bin Packing} ($BP$).
 
@@
 Figure~\ref{fig:best_variants_batch} shows performance of the best variants of all categories for both applications.
-The plots exhibit behavior similar to Figures~\ref{fig:ratio_to_optimal_best_hf} and ~\ref{fig:ratio_to_optimal_best_CCSD}, static order with dynamic correction variants attain maximum communication-computation overlap and outperform other heuristics.
+The plots exhibit behavior similar to Figures~\ref{fig:ratio_to_optimal_best_hf} and ~\ref{fig:ratio_to_optimal_best_ccsd}, static order with dynamic correction variants attain maximum communication-computation overlap and outperform other heuristics.
 		\todo[inline]{SKumar:combine both plots}

### 2019-04-09 ICPP-19/communications.tex
minor

@@
 Our proof is inspired from work by ~\cite{Papadimitriou:1980:FSL:322203.322213}, which applies a similar technique for 2-machine flowshop problem.
-The main difference with their and our approach is that they consider a bounded number of tasks can await execution on second machine.
+The main difference with their and our approach is that they consider a bounded number of tasks can await execution on second machine and buffer is acquired after completing the task on first machine.
 On the contrary, our approach is designed for tasks appearing in scientific workloads whose memory requirements are highly irregular and memory is acquired before starting the data transfer on communication resource.
@@
 
-	We also prove optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} in a different way, which is available in an extended version(cite).
+	We also prove optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} differently in an extended version(cite).
 	\subsection{Finite Memory}
@@
 
-		$Transfer time = Latency + \frac{Data Volume}{Bandwidth}$.
-For simplicity we consider $Latency=0$ and $Bandwidth=1$, (implies Input data volume = Input transfer time).
-Otherwise, we can adjust $C$ in a way such that at any point in a schedule at max one $K_i$ and three $A_i$ tasks can be active.
+		As \textit{Transfer time = Latency + (Data Volume)/Bandwidth}.
+For simplicity, we consider input transfer time is same as input data volume (i.e., \textit{Latency=0} and \textit{Bandwidth=1}).
+Otherwise, we can adjust $C$ such that at any point in a schedule at max one $K_i$ and three $A_i$ tasks can be active.
 
@@
 
-	The algorithm presented in the Section~\ref{sec:theoreticalProof} achieves optimal makespan when there is not any memory capacity constraint.
+	The algorithm presented in Section~\ref{sec:theoreticalProof} achieves optimal makespan when there is not any memory capacity constraint.
 This optimal value indicates a lower bound on the makespan.
-We use $optimal\_makespan\_infinite\_memory$ ($OMIM$) to represent this value.
+We use $optimal\_ \allowbreak makespan\_  \allowbreak infinite\_  \allowbreak memory$ ($OMIM$) to represent this value.
 We assess the efficiency of other proposed heuristics in limited memory capacity in Section~\ref{sec:exp} with respect to this lower bound, $OMIM$.
@@
 	\begin{enumerate}[label=\roman*)]
-		\item $order\_of\_optimal\_strategy\_infinite\_memory $ ($OOSIM$): Order of processing is obtained by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}.
+		\item $order  \_ \allowbreak  \allowbreak of  \_ \allowbreak  \allowbreak optimal \_ \allowbreak strategy \_ \allowbreak infinite \_ \allowbreak memory $ ($OOSIM$): Order of processing is obtained by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}.
 At each point in the schedule memory capacity is respected.
@@
 
-		\item $increasing\_order\_of\_communication\_strategy$ ($IOCMS$): Order is obtained by sorting all tasks in non-decreasing order of communication time.
-
-		\item $decreasing\_order\_of\_computation\_strategy$ ($DOCPS$): Order is obtained by sorting all tasks in non-increasing order of computation time. 
-		\item $increasing\_order\_of\_communication\_plus\_computation\_strategy$ ($IOCCS$): Order is obtained by sorting all tasks in non-decreasing order of sum of communication and computation times.
-		\item $decreasing\_order\_of\_communication\_plus\_computation\_strategy$ ($DOCCS$): Order is obtained by sorting all tasks in non-increasing order of sum of communication and computation times.
+		\item $increasing \_ \allowbreak order \_ \allowbreak of \_ \allowbreak communication \_ \allowbreak strategy$ ($IOCMS$): Order is obtained by sorting all tasks in non-decreasing order of communication time.
+
+		\item $decreasing \_ \allowbreak order \_ \allowbreak of \_ \allowbreak computation \_ \allowbreak strategy$ ($DOCPS$): Order is obtained by sorting all tasks in non-increasing order of computation time.
+		\item $increasing \_ \allowbreak order \_ \allowbreak of \_ \allowbreak communication \_ \allowbreak plus \_ \allowbreak computation \_ \allowbreak strategy$ ($IOCCS$): Order is obtained by sorting all tasks in non-decreasing order of sum of communication and computation times.
+		\item $decreasing \_ \allowbreak order \_ \allowbreak of \_ \allowbreak communication \_ \allowbreak plus \_ \allowbreak computation \_ \allowbreak strategy$ ($DOCCS$): Order is obtained by sorting all tasks in non-increasing order of sum of communication and computation times.
 
@@
 
-			\begin{tabular}{|c|c|c|}
+			\begin{tabular}{|c|c|c|c|}
 				\hline
-				\multirow{2}{*}{Task} & Comm Time & \multirow{2}{*}{Comp Time}\\ 
-				&=Comm Volume& \\ \hline
-				A & 3 & 2\\ \hline
-				B & 1 & 3\\ \hline
-				C & 4 & 4\\ \hline
-				D & 2 & 1\\ \hline
+%%				\multirow{2}{*}{Task} & Comm Time & \multirow{2}{*}{Comp Time}\\ 
+%%				&=Comm Volume& \\ \hline
+				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
+				A & 3 & 3 &  2\\ \hline
+				B & 1 & 1 & 3\\ \hline
+				C & 4 & 4 & 4\\ \hline
+				D & 2 & 2 & 1\\ \hline
 			\end{tabular}
@@
 	\subsection{Dynamic Selection}
-	%%%%string alg_name="largest_communication\_task\_respects\_memory\_restriction";
-	%%%%string alg_name="smallest_communication\_task\_respects\_memory\_restriction";
-	%%%%string alg_name="maximum_accelerated\_task\_respects\_memory\_restriction";
+	%%%%string alg_name="largest_communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction";
+	%%%%string alg_name="smallest_communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction";
+	%%%%string alg_name="maximum_accelerated \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction";
 
@@
 	\begin{enumerate}[label=\roman*)]
-		%%	\item $largest_communication\_task\_respects\_memory\_restriction$: We select a set of tasks which induce minimum idle time on compute channel.
+		%%	\item $largest_communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$: We select a set of tasks which induce minimum idle time on compute channel.
 A task with the largest communication time is chosen from this set.
 Memory requirement of this task should not be more than presently available memory.
-		%%	\item $smallest_communication\_task\_respects\_memory\_restriction$: A task with the smallest communication time is chosen.
+		%%	\item $smallest_communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$: A task with the smallest communication time is chosen.
 Memory requirement of this task should not be more than presently available memory.
-		%%	\item $maximum_accelerated\_task\_respects\_memory\_restriction$: We select a set of tasks which induce minimum idle time on compute channel.
+		%%	\item $maximum_accelerated \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$: We select a set of tasks which induce minimum idle time on compute channel.
 A task with the maximum ratio of compute time to communication time is chosen from this set.
@@
 
-		\item $largest\_communication\_task\_respects\_memory\_restriction$ ($LCMR$): A task with the largest communication time is chosen. 
-		\item $smallest\_communication\_task\_respects\_memory\_restriction$ ($SCMR$): A task with the smallest communication time is chosen.
-		\item $maximum\_accelerated\_task\_respects\_memory\_restriction$ ($MAMR$): A task with the maximum ratio of compute time to communication time is chosen.
+		\item $largest \_ \allowbreak communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$ ($LCMR$): A task with the largest communication time is chosen.
+		\item $smallest \_ \allowbreak communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$ ($SCMR$): A task with the smallest communication time is chosen.
+		\item $maximum \_ \allowbreak accelerated \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$ ($MAMR$): A task with the maximum ratio of compute time to communication time is chosen.
 	\end{enumerate}
@@
 
-			\begin{tabular}{|c|c|c|}
+			\begin{tabular}{|c|c|c|c|}
 				\hline
-				\multirow{2}{*}{Task} & Comm Time & \multirow{2}{*}{Comp Time}\\ 
-				&=Comm Volume& \\ \hline
-				A & 3 & 2\\ \hline
-				B & 1 & 6\\ \hline
-				C & 4 & 6\\ \hline
-				D & 5 & 1\\ \hline
+%%				\multirow{2}{*}{Task} & Comm Time & \multirow{2}{*}{Comp Time}\\ 
+%%				&=Comm Volume& \\ \hline
+				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
+				A & 3 & 3 & 2\\ \hline
+				B & 1 & 1 &  6\\ \hline
+				C & 4 & 4 & 6\\ \hline
+				D & 5 & 5 & 1\\ \hline
 			\end{tabular}
@@
 This class of strategy takes advantage of static information in the form of precomputed order and dynamic correction to minimize the idle time due to memory constraint.
-	%%%%alg_name="optimal_order_infinite_memory_largest_communication\_task\_respects\_memory\_restriction";
-	%%%%string alg_name="optimal_order_infinite_memory_smallest_communication\_task\_respects\_memory\_restriction";
-	%%%%string alg_name="optimal_order_infinite_memory_maximum_accelerated\_task\_respects\_memory\_restriction";
+	%%%%alg_name="optimal_order_infinite_memory_largest_communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction";
+	%%%%string alg_name="optimal_order_infinite_memory_smallest_communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction";
+	%%%%string alg_name="optimal_order_infinite_memory_maximum_accelerated \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction";
 
@@
 	\begin{enumerate}[label=\roman*)]
-		\item $optimal\_order\_infinite\_memory\_largest\_communication\_task\_respects\_memory\_restriction$ ($OOLCMR$): A task with the largest communication time is chosen from the set.
-		\item $optimal\_order\_infinite\_memory\_smallest\_communication\_task\_respects\_memory\_restriction$ ($OOSCMR$): A task with the smallest communication time is chosen from the set.
-		\item $optimal\_order\_infinite\_memory\_maximum\_accelerated\_task\_respects\_memory\_restriction$ ($OOMAMR$): A task, whose ratio of compute time to communication time is maximum, is chosen from the set .
+		\item $optimal \_ \allowbreak order \_ \allowbreak infinite \_ \allowbreak memory \_ \allowbreak largest \_ \allowbreak communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$ ($OOLCMR$): A task with the largest communication time is chosen from the set.
+		\item $optimal \_ \allowbreak order \_ \allowbreak infinite \_ \allowbreak memory \_ \allowbreak smallest \_ \allowbreak communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$ ($OOSCMR$): A task with the smallest communication time is chosen from the set.
+		\item $optimal \_ \allowbreak order \_ \allowbreak infinite \_ \allowbreak memory \_ \allowbreak maximum \_ \allowbreak accelerated \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$ ($OOMAMR$): A task, whose ratio of compute time to communication time is maximum, is chosen from the set .
 	\end{enumerate}
@@
 
-			\begin{tabular}{|c|c|c|}
+			\begin{tabular}{|c|c|c|c|}
 				\hline
-				\multirow{2}{*}{Task} & Comm Time & \multirow{2}{*}{Comp Time}\\ 
-				&=Comm Volume& \\ \hline
-				A & 4 & 1\\ \hline
-				B & 2 & 6\\ \hline
-				C & 8 & 8\\ \hline
-				D & 5 & 4\\ \hline
-				E & 3 & 2\\ \hline
+%%				\multirow{2}{*}{Task} & Comm Time & \multirow{2}{*}{Comp Time}\\ 
+%%				&=Comm Volume& \\ \hline
+				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
+				A & 4 & 4 &  1\\ \hline
+				B & 2 & 2 & 6\\ \hline
+				C & 8 & 8 & 8\\ \hline
+				D & 5 & 5 & 4\\ \hline
+				E & 3 & 3 & 2\\ \hline
 			\end{tabular}

### 2019-04-09 ICPP-19/communications.tex
Adjusting plots

@@
 		As \textit{Transfer time = Latency + (Data Volume)/Bandwidth}.
-For simplicity, we consider input transfer time is same as input data volume (i.e., \textit{Latency=0} and \textit{Bandwidth=1}).
+For simplicity, we consider input transfer time is same as input data volume (i.e., \textit{Latency = 0} and \textit{Bandwidth = 1}).
 Otherwise, we can adjust $C$ such that at any point in a schedule at max one $K_i$ and three $A_i$ tasks can be active.
@@
 		\begin{figure*}[htb]
-			\includegraphics[scale=0.25]{./all-binpack/ratio_to_optimal_selected_hf.pdf}
+		  \includegraphics[scale=0.5]{./all-binpack/ratio_to_optimal_selected_hf.pdf}
 			\caption{Comparison of different heuristics for HF.}
@@
 		\begin{figure}[htb]
-			\includegraphics[scale=0.15]{./results/plots/inverse_ratio_to_optimal_hf-best.pdf}
+			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_hf-best.pdf}
 			\caption{Comparision of best variants of all categories for HF.}
@@
 		\begin{figure*}[htb]
-			\includegraphics[scale=0.25]{./all-binpack/ratio_to_optimal_selected_ccsd.pdf}
+			\includegraphics[scale=0.5]{./all-binpack/ratio_to_optimal_selected_ccsd.pdf}
 			\caption{Comparison of different heuristics for CCSD.}
@@
 		\begin{figure}[htb]
-			\includegraphics[scale=0.15]{./results/plots/inverse_ratio_to_optimal_ccsd-best.pdf}
+			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_ccsd-best.pdf}
 			\caption{Comparision of best variants of all categories for CCSD.}
@@
 
+%%		\begin{figure}[htb]
+%%			%\begin{tabular}{c}
+%%			\subfloat[HF workloads\label{fig:hfProperties}]{%
+%%				\includegraphics[width=.45\linewidth]{./results/plots/application_properties_hf.pdf}
+%%			}%\\
+%%			\subfloat[CCSD workloads\label{fig:ccsdProperties}]{%
+%%				\includegraphics[width=.45\linewidth]{./results/plots/application_properties_ccsd.pdf}
+%%			}%\\
+%%			%\end{tabular}
+%%			\caption{HF and CCSD tasks characteristics.}
+%%			\label{fig:ApplicationProperties}
+%%		\end{figure}
+
 		\begin{figure}[htb]
 	%\begin{tabular}{c}
-			\subfloat[HF workloads\label{fig:hfProperties}]{%
-				\includegraphics[width=.45\linewidth]{./results/plots/application_properties_hf.pdf}
-			}%\\
-			\subfloat[CCSD workloads\label{fig:ccsdProperties}]{%
-				\includegraphics[width=.45\linewidth]{./results/plots/application_properties_ccsd.pdf}
-			}%\\
-			%\end{tabular}
+		\includegraphics[scale=0.5]{./results/plots/application_properties.pdf}
 	\caption{HF and CCSD tasks characteristics.}
@@
 
+%%		
+%%		\begin{figure*}[htb]
+%%			\subfloat[Best variants of HF.\label{fig:hf_best_variants_batch}]{%
+%%				\includegraphics[width=.45\linewidth]{./results/plots/inverse_ratio_to_optimal_hf_batch-best.pdf}
+%%			}%\\
+%%			\subfloat[Best variants of CCSD.\label{fig:ccsd_best_variants_batch}]{%
+%%				\includegraphics[width=.45\linewidth]{./results/plots/inverse_ratio_to_optimal_ccsd_batch-best.pdf}
+%%			}%\\
+%%			\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
+%%			\label{fig:best_variants_batch}
+%%		\end{figure*}
+
 \begin{figure*}[htb]
-			\subfloat[Best variants of HF.\label{fig:hf_best_variants_batch}]{%
-				\includegraphics[width=.45\linewidth]{./results/plots/inverse_ratio_to_optimal_hf_batch-best.pdf}
-			}%\\
-			\subfloat[Best variants of CCSD.\label{fig:ccsd_best_variants_batch}]{%
-				\includegraphics[width=.45\linewidth]{./results/plots/inverse_ratio_to_optimal_ccsd_batch-best.pdf}
-			}%\\
+		\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_batch-best.pdf}
 	\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}

### 2019-04-09 ICPP-19/all-binpack/ratio_to_optimal.R

@@ -13,19 +13,19 @@ p <- p + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Ratio to Opti
 return (p)
 }
 p<-ratio_to_optimal_func('all_results_hf.txt')
-ggsave(file="ratio_to_optimal_hf.pdf", p, width=23.6, height=13.4)
+ggsave(file="ratio_to_optimal_hf.pdf", p, width=14.25, height=6.5)
 
 p<-ratio_to_optimal_func('all_results_ccsd.txt')
-ggsave(file="ratio_to_optimal_ccsd.pdf", p, width=23.6, height=13.4)
+ggsave(file="ratio_to_optimal_ccsd.pdf", p, width=14.25, height=6.5)
 
 p<-ratio_to_optimal_func('selected_results_hf.txt')
-ggsave(file="ratio_to_optimal_selected_hf.pdf", p, width=23.6, height=13.4)
+ggsave(file="ratio_to_optimal_selected_hf.pdf", p, width=14.25, height=6.5)
 
 p<-ratio_to_optimal_func('selected_results_ccsd.txt')
-ggsave(file="ratio_to_optimal_selected_ccsd.pdf", p, width=23.6, height=13.4)
+ggsave(file="ratio_to_optimal_selected_ccsd.pdf", p, width=14.25, height=6.5)
 
 #p<-ratio_to_optimal_func('all_results_random_ccsd.txt')
-#ggsave(file="ratio_to_optimal_random_ccsd.pdf", p, width=23.6, height=13.4)
+#ggsave(file="ratio_to_optimal_random_ccsd.pdf", p, width=14.25, height=6.5)
 #
 #p<-ratio_to_optimal_func('selected_results_random_ccsd.txt')
-#ggsave(file="ratio_to_optimal_random_selected_ccsd.pdf", p, width=23.6, height=13.4)
+#ggsave(file="ratio_to_optimal_random_selected_ccsd.pdf", p, width=14.25, height=6.5)

### 2019-04-09 ICPP-19/results/scripts/insights.R

@@ -1,7 +1,6 @@
 #!/usr/bin/env Rscript
 insights_func <-function(file_name)
 {
-library(ggplot2)
 library(reshape2)
 dftest<-read.table(file_name, header=T)
 
@@ -16,10 +15,32 @@ p <- p + theme(plot.title = element_text(hjust = 0.5), legend.position='none') +
 
 return (p)
 }
-p<-insights_func('insight_hf.txt')
-ggsave(file="application_properties_hf.pdf", p, width=23.6, height=13.4)
+#p<-insights_func('insight_hf.txt')
+#w=20
+#h=10
+#ggsave(file="application_properties_hf.pdf", p, width=w, height=h)
+#
+#p<-insights_func('insight_ccsd.txt')
+#ggsave(file="application_properties_ccsd.pdf", p, width=w, height=h)
 
-p<-insights_func('insight_ccsd.txt')
-ggsave(file="application_properties_ccsd.pdf", p, width=23.6, height=13.4)
-
+get_melted_data_frame<-function(file_name)
+{
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+dftest[,1:ncol(dftest)]<-dftest[,1:ncol(dftest)]/dftest[,5]
+dftest[,5]<-NULL
+dftestMelted<-melt(dftest)
+names(dftestMelted)<-c( "Parameter", "ratio_to_optimal")
+return (dftestMelted)
+}
+dfMelted1<-get_melted_data_frame('insight_hf.txt');
+dfMelted1$application <- "HF Workload"
+dfMelted2<-get_melted_data_frame('insight_ccsd.txt');
+dfMelted2$application <- "CCSD Workload"
+dfMelted <- rbind(dfMelted1, dfMelted2)
+library(ggplot2)
+p<-ggplot(dfMelted, aes(x=Parameter, y=ratio_to_optimal, color=Parameter))  + geom_boxplot(outlier.color="black") + geom_hline(yintercept=1, linetype="dashed", color = "red") +
+          facet_wrap(~application) + scale_y_continuous(breaks=seq(0.0, 2.0, 0.5), limits=c(0, 2)) +
+          theme(legend.position='none', axis.text.x = element_text(angle = 40, hjust=1, vjust = 1));
+ggsave(file="application_properties.pdf", p, width=7, height=4)
 

### 2019-04-09 ICPP-19/results/scripts/inverse_ratio_to_optimal-best.R

@@ -16,13 +16,13 @@ dftestMelted<-melt(dftest, "capacity")
 names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
 #p<-ggplot(dftestMelted, aes(x=jitter(capacity), y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth()
 p<-ggplot(dftestMelted, aes(x=capacity, y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth(method="loess")
-p<-p + ylab("inverse(ratio_to_optimal)") + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Performance With Best of all categories")
+p<-p + ylab("inverse(ratio_to_optimal)") + theme(plot.title = element_text(hjust = 0.5), legend.position="bottom") +  ggtitle("Performance With Best of all categories")
 return (p)
 }
 
 p<-inverse_ratio_to_optimal_best_func('all_results_hf.txt')
-ggsave(file="inverse_ratio_to_optimal_hf-best.pdf", p, width=23.6, height=13.4)
+ggsave(file="inverse_ratio_to_optimal_hf-best.pdf", p + xlim(NA, 340000), width=6.5, height=5)
 
 p<-inverse_ratio_to_optimal_best_func('all_results_ccsd.txt')
-ggsave(file="inverse_ratio_to_optimal_ccsd-best.pdf", p, width=23.6, height=13.4)
+ggsave(file="inverse_ratio_to_optimal_ccsd-best.pdf", p, width=6.5, height=5)
 

### 2019-04-09 ICPP-19/results/scripts/inverse_ratio_to_optimal_batch-best.R

@@ -17,9 +17,39 @@ p<-ggplot(dftestMelted, aes(x=capacity, y=1/ratio_to_optimal, color=Heuristic)) 
 p<-p + ylab("inverse(ratio_to_optimal)") + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Performance With Best of all categories")
 return (p)
 }
-p<-inverse_ratio_to_optimal_best_func('results_batch_hf.txt')
-ggsave(file="inverse_ratio_to_optimal_hf_batch-best.pdf", p, width=23.6, height=13.4)
+#p<-inverse_ratio_to_optimal_best_func('results_batch_hf.txt')
+#ggsave(file="inverse_ratio_to_optimal_hf_batch-best.pdf", p, width=23.6, height=13.4)
+#
+#p<-inverse_ratio_to_optimal_best_func('results_batch_ccsd.txt')
+#ggsave(file="inverse_ratio_to_optimal_ccsd_batch-best.pdf", p, width=23.6, height=13.4)
 
-p<-inverse_ratio_to_optimal_best_func('results_batch_ccsd.txt')
-ggsave(file="inverse_ratio_to_optimal_ccsd_batch-best.pdf", p, width=23.6, height=13.4)
+get_melted_data_frame <-function(file_name)
+{
+library(ggplot2)
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
 
+dftest[,c(2:6)]<-NULL
+dftest$static_best<-do.call('pmin', c(dftest[,3:7]))
+dftest$dynamic_best<-do.call('pmin', c(dftest[,8:10]))
+dftest$static_dynamic_best<-do.call('pmin', c(dftest[,11:13]))
+dftest<-dftest[,c(1,2,14:16)]
+dftestMelted<-melt(dftest, "capacity")
+names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
+return (dftestMelted)
+}
+
+dfMelted1 <- get_melted_data_frame('results_batch_hf.txt')
+dfMelted1$aname <- "Best Variants of HF";
+
+dfMelted2 <- get_melted_data_frame('results_batch_ccsd.txt')
+dfMelted2$aname <- "Best Variants of CCSD";
+
+dfMelted <- rbind(dfMelted1, dfMelted2)
+library(ggplot2)
+
[…]

### 2019-04-09 ICPP-19/communications.tex
minor
THe optimal schedule  does not have same order on both resources

@@
 \newcommand{\threepart}{\textsc{3Par}\xspace}
+
+% Command for figures
+
+\tikzset{xtick/.style={inner xsep=0pt, inner ysep=3pt, minimum
+		size=0pt, draw, label=below:#1},%
+	comm/.style args={#1start#2length#3color#4}{rounded corners=1mm, draw, inner
+		sep=0pt, fill=#4, label=center:#1, fit={(#2,0.75)
+			(#2+#3,1.5)}},%
+	comp/.style args={#1start#2length#3color#4}{rounded corners=1mm, draw, inner
+		sep=0pt, fill=#4, label=center:#1, fit={(#2,0)
+			(#2+#3,0.75)}},%
+}
+
+\newcommand{\schedule}[3]{
+	\draw[->] (-0.2, 0) -- (#1, 0) node[below] {$t$};
+	\draw (0, 0) -- (0, 1.5);
+	\node at (-0.8, 0.75)[rotate=90] {#2};
+	\draw[dashed,gray] (0, 0.75) -- (#1, 0.75);
+	\foreach \t in {0,#3} {
+		\node[xtick=\t] at (\t, 0){};
+	}
+}
+\newcommand{\task}[6][0]{
+	\node[comm=#2 start #3 length #4 color #6]{};
+	\node[comp=#2 start #3+#4+#1 length #5 color #6]{}; 
+}
 
@@
 			}
-			\newcommand{\schedule}[1]{
+			\newcommand{\scheduleNoName}[1]{
 				\draw[->] (-0.4, 0) -- (#1, 0) node[below] {$t$};
@@
 			\begin{tikzpicture}[yscale=0.7, thick, xscale=0.6]
-			\schedule{12.5}
+			\scheduleNoName{12.5}
 			\node[task=$A_{1,1}$ start 0 length 1 res 1 color cyan]{};
@@
 
+	This Theorem shows that adding a memory constraint to our
+	problem makes it more difficult. One additional difficulty
+	compared to limited capacity 2-machine
+	flowshop~\cite{Papadimitriou:1980:FSL:322203.322213} is that
+	it may not be optimal to consider the same ordering on both
+	machines:
+
+	\begin{proposition}
+		There exists an instance of $DT$ for which in all optimal
+		schedules, the communication order of tasks is different
+		from their computation order.
+	\end{proposition}
+
+	\begin{table}
+		\begin{center}
+			\begin{tabular}{|c|c|c|c|}
+				\hline
+				%%				\multirow{2}{*}{Task} & Comm Time & \multirow{2}{*}{Comp Time}\\ 
+				%%				&=Comm Volume& \\ \hline
+				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
+				A & 0 & 0 & 5\\ \hline
+				B & 4 & 4 & 3\\ \hline
+				C & 1 & 1 & 6\\ \hline
+				D & 3 & 3 & 7\\ \hline
+				E & 6 & 6 & 0.5\\ \hline
+				F & 7 & 7 & 0.5\\ \hline
+			\end{tabular}
+		\end{center}
+		\caption{Example instance where ordering on both resources
+			has to be different.}
+		\label{table:different.order}
+	\end{table}
+
+	\begin{figure}
+		\centering
+		\newcommand{\taskA}[1]{\node[comp=$A$ start #1 length 5 color cyan] {};}
+		\newcommand{\taskB}[2][0]{\task[#1]{$B$}{#2}{4}{3}{blue!25!white}}
+		\newcommand{\taskC}[2][0]{\task[#1]{$C$}{#2}{1}{6}{blue!50!white}}
+		\newcommand{\taskD}[2][0]{\task[#1]{$D$}{#2}{3}{7}{blue!75!white}}
+		\newcommand{\taskE}[2][0]{\node[comm=$E$ start #2 length 6 color green!25!white]{};%
+			\node[comp={} start #2+6+#1 length 0.5 color green!25!white]{};}
+		\newcommand{\taskF}[2][0]{\node[comm=$F$ start #2 length 7 color green!50!white]{};%
+			\node[comp={} start #2+7+#1 length 0.5 color green!50!white]{};}
+
+		\subfloat[][Optimal schedule with common ordering on both
+		resources]{
+			\begin{tikzpicture}[yscale=0.7, thick, xscale=0.3]
+			\schedule{24}{}{5,8,15,21.5,23}
+			\taskA{0}
+			\taskB[1]{0}
+			\taskD[1]{4}
+			\taskE[1]{8}
+			\taskC[0.5]{14}
+			\taskF{15.5}
+			\end{tikzpicture}
+			\label{fig:different.order.same}
+		}
+
+		\subfloat[][Schedule with different ordering on both
+		resources]{
+			\begin{tikzpicture}[yscale=0.7, thick, xscale=0.3]
+			\schedule{24}{}{5,8,14,22}
+			\taskA{0}
+			\taskB[1]{0}
+			\taskC[3]{4}
+			\taskD[6.5]{5}
+			\taskE{8}
+			\taskF{14.5}
+			\end{tikzpicture}
+			\label{fig:different.order.opt}
+		}
+		\caption{Schedules for the instance of
+			Table~\ref{table:different.order}}
+		\label{fig:different.order}
+	\end{figure}
+
+	\begin{proof}
+		Consider the instance described on
+		Table~\ref{table:different.order}, in which memory capacity
+		is $C=10$. Figure~\ref{fig:different.order.same} shows the
+		best possible schedule when tasks are scheduled in the same
+		order on both resources (obtained by exhaustive search). On
+		the other hand, Figure~\ref{fig:different.order.opt} shows
+		another schedule with lower makespan, in which the order is
+		different.
+
+		In the infinite memory case, the standard proof that an
+		optimal schedule exists with the same order on both
+		resources claims that it is possible to swap two tasks which
+		do not satisfy this property. On
+		Figure~\ref{fig:different.order}, this would mean swapping
+		tasks $D$ and $E$. But the communication of task $E$ can not
+		start earlier because it would not fit in memory with tasks
+		$B$ and $C$, and delaying the computation of task $E$ after
+		task $D$ would delay task $F$ because $E$ and $F$ do not fit
+		in memory together. We can see that this claim does not hold
+		in the constrained memory case. 
+	\end{proof}
+
 	\section{Data Transfer Order heuristics}
@@
 	\end{table}
-
-	\tikzset{xtick/.style={inner xsep=0pt, inner ysep=3pt, minimum
-			size=0pt, draw, label=below:#1},%
-		comm/.style args={#1start#2length#3color#4}{rounded corners=1mm, draw, inner
-			sep=0pt, fill=#4, label=center:#1, fit={(#2,0.75)
-				(#2+#3,1.5)}},%
-		comp/.style args={#1start#2length#3color#4}{rounded corners=1mm, draw, inner
-			sep=0pt, fill=#4, label=center:#1, fit={(#2,0)
-				(#2+#3,0.75)}},%
-	}
-	\newcommand{\schedule}[3]{
-		\draw[->] (-0.2, 0) -- (#1, 0) node[below] {$t$};
-		\draw (0, 0) -- (0, 1.5);
-		\node at (-0.8, 0.75)[rotate=90] {#2};
-		\draw[dashed,gray] (0, 0.75) -- (#1, 0.75);
-		\foreach \t in {0,#3} {
-			\node[xtick=\t] at (\t, 0){};
-		}
-	}
-	\newcommand{\task}[6][0]{
-		\node[comm=#2 start #3 length #4 color #6]{};
-		\node[comp=#2 start #3+#4+#1 length #5 color #6]{}; 
-	}
 
@@
 
-		\todo[inline]{increase font size in all plots, may be free scale-y}
+		%%		\todo[inline]{increase font size in all plots, may be free scale-y}
 		%%	\todo[inline]{SKumar: decide metrics: ratio to optimal, percentage overlap, 100 - percentage non overlap}
@@
 The plots exhibit behavior similar to Figures~\ref{fig:ratio_to_optimal_best_hf} and ~\ref{fig:ratio_to_optimal_best_ccsd}, static order with dynamic correction variants attain maximum communication-computation overlap and outperform other heuristics.
-		\todo[inline]{SKumar:combine both plots}
+		%%		\todo[inline]{SKumar:combine both plots}
 

### 2019-04-10 ICPP-19/communications.tex
minor modifications

@@
 It is paramount to develop strategies to overlap the data transfers between memory nodes with computations in order to exploit the full potential of these systems.
-In this article, we consider the problem of deciding the order of data transfers between two memory nodes for a set of independent tasks with the objective to minimize the makespan.
+In this paper, we consider the problem of deciding the order of data transfers between two memory nodes for a set of independent tasks with the objective to minimize the makespan.
 We prove that with finite memory capacity obtaining the optimal order of data transfers is an NP-complete problem.
@@
 It is extremely important for runtimes to decide the order of data transfers for these scheduled computations such that overlap between computations and communications can be maximised.
-This is the main topic of this article.
+This is the main topic of this paper.
 We prove that order of communications on two memory nodes with the objective of minimizing the makespan is NP-Complete.
@@
 On the contrary, our approach is designed for tasks appearing in scientific workloads whose memory requirements are highly irregular and memory is acquired before starting the data transfer on communication resource.
-We propose different strategies for runtimes such that it can maximize the overlap of computation and communication for kernels running on two different memory nodes.
+We propose different strategies for runtimes such that it can maximize the overlap of computations and communications.
 We evaluate our strategies on a cluster of homogeneous nodes.
@@
 
-	The outline of the article is the following.
+	The outline of the paper is the following.
 Section~\ref{sec:relatedWork} describes past work on the computations with limited memory and similar problems in the literature.
@@
 
-	The problem considered in this article also can be viewed as a flow shop problem.
+	The problem considered in this paper also can be viewed as a flow shop problem.
 Communication and computation timings of a task can be considered as processing timings on different machines.
@@
 		first show that no other $K_i$ task can be active with $K_0$,
-		otherwise we would get idle time on computation channel. Indeed, the
+		otherwise we would get idle time on computation resource. Indeed, the
 		communication of such a task $K_i$ would end at time at least $b'>3 +
@@
 In the last category, which is based on combination of strategies of the other two categories, we precompute the order and try to follow it as much as possible, but when the precomputed schedule induces idle time then we look for the best suited next task.
-In all of our strategies (except linear programming based strategy) order of communications and computations, are same.
+In all of our strategies (except linear programming based strategy) order of communications and computations is same.
 
@@
 		\item $decreasing \_ \allowbreak order \_ \allowbreak of \_ \allowbreak computation \_ \allowbreak strategy$ ($DOCPS$): Order is obtained by sorting all tasks in non-increasing order of computation time.
-		\item $increasing \_ \allowbreak order \_ \allowbreak of \_ \allowbreak communication \_ \allowbreak plus \_ \allowbreak computation \_ \allowbreak strategy$ ($IOCCS$): Order is obtained by sorting all tasks in non-decreasing order of sum of communication and computation times.
-		\item $decreasing \_ \allowbreak order \_ \allowbreak of \_ \allowbreak communication \_ \allowbreak plus \_ \allowbreak computation \_ \allowbreak strategy$ ($DOCCS$): Order is obtained by sorting all tasks in non-increasing order of sum of communication and computation times.
+		\item $increasing \_ \allowbreak order \_ \allowbreak of \_ \allowbreak communication \_ \allowbreak plus \_ \allowbreak computation \_ \linebreak[4] \allowbreak strategy$ ($IOCCS$): Order is obtained by sorting all tasks in non-decreasing order of sum of communication and computation times.
+		\item $decreasing \_ \allowbreak order \_ \allowbreak of \_ \allowbreak communication \_ \allowbreak plus \_ \allowbreak computation \_ \linebreak[4] \allowbreak strategy$ ($DOCCS$): Order is obtained by sorting all tasks in non-increasing order of sum of communication and computation times.
 
@@
 
-	In this class of strategy, when communication channel is idle, a task is chosen which satisfies the selection criteria maximally among other tasks.
+	In this class of strategy, when communication resource is idle, a task is chosen which satisfies the selection criteria maximally among other tasks.
 For example, if the selection criteria is to choose a highly compute intensive task, then we calculate the ratio of compute time and communication time for all tasks, and the task with the maximum ratio is selected (ties are broken randomly).
-As we assume that order on both channels is same, hence order on compute channel will follow the order of communication resource.
-
-	We select a set of tasks which induce minimum idle time on compute channel and satisfy available memory requirement.
+As we assume that order on both resources is same, hence order on compute resource follows the order of communication resource.
+
+	We select a set of tasks which induce minimum idle time on compute resource and satisfy available memory requirement.
 Then a task is chosen for processing from this set based on the following heuristics.
@@
 		\item $smallest \_ \allowbreak communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$ ($SCMR$): A task with the smallest communication time is chosen.
-		\item $maximum \_ \allowbreak accelerated \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$ ($MAMR$): A task with the maximum ratio of compute time to communication time is chosen.
+		\item $maximum \_ \allowbreak accelerated \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$ \linebreak[4]($MAMR$): A task with the maximum ratio of compute time to communication time is chosen.
 	\end{enumerate}
@@
 After a task is selected then we update the remaining order without this task.
-This class of strategy takes advantage of static information in the form of precomputed order and dynamic correction to minimize the idle time due to memory constraint.
+This class of strategy takes advantage of static information in the form of precomputed order and dynamic corrections to minimize the idle time due to memory constraint.
 	%%%%alg_name="optimal_order_infinite_memory_largest_communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction";
@@
 	Initial order is obtained by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}.
-When communication resource is idle due to memory requirement of the next task in the order, then we select a set of tasks which induce minimum idle time on compute channel and satisfy memory requirement.
+When communication resource is idle due to memory requirement of the next task in the order, then we select a set of tasks which induce minimum idle time on compute resource and satisfy memory requirement.
 We define the following heuristics based on how we select a task from this set.
@@
 	\begin{enumerate}[label=\roman*)]
-		\item $optimal \_ \allowbreak order \_ \allowbreak infinite \_ \allowbreak memory \_ \allowbreak largest \_ \allowbreak communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$ ($OOLCMR$): A task with the largest communication time is chosen from the set.
+		\item $optimal \_ \allowbreak order \_ \allowbreak infinite \_ \allowbreak memory \_ \allowbreak largest \_ \allowbreak communication \_ \linebreak[4]\allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$ ($OOLCMR$): A task with the largest communication time is chosen from the set.
 		\item $optimal \_ \allowbreak order \_ \allowbreak infinite \_ \allowbreak memory \_ \allowbreak smallest \_ \allowbreak communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$ ($OOSCMR$): A task with the smallest communication time is chosen from the set.
-		\item $optimal \_ \allowbreak order \_ \allowbreak infinite \_ \allowbreak memory \_ \allowbreak maximum \_ \allowbreak accelerated \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$ ($OOMAMR$): A task, whose ratio of compute time to communication time is maximum, is chosen from the set .
+		\item $optimal \_ \allowbreak order \_ \allowbreak infinite \_ \allowbreak memory \_ \allowbreak maximum \_ \allowbreak accelerated \_ \linebreak[4]\allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$ ($OOMAMR$): A task, whose ratio of compute time to communication time is maximum, is chosen from the set .
 	\end{enumerate}
@@
 		\caption{ \label{fig:staticOrderDynamicCorrectionsExample} Different static order dynamic corrections heuristic schedules for a task set of Table~\ref{tab:staticOrderDynamicCorrectionsExample} .
-The $OMIM$ order is $BCDAE$..}
+The $OMIM$ order is $BCDAE$.}
 	\end{figure}
@@
 	\label{subsec:linearprogrammingformulation}
-	We use a mixed integer linear program to obtain the order of data transfers and computations.
+	We use a mixed integer linear program to obtain the order of communications and computations.
 $COMP_i$ and $COMM_i$ represent computation and communication timings of task $i$.
@@
 		& e_i \leq s'_i\\
-		\forall i, \forall j\ne i, \quad & \text{exclusive communication of task } i \text{ on communication channel:}\\
+		\forall i, \forall j\ne i, \quad & \text{exclusive communication of task } i \text{ on communication resource:}\\
 		& e_j \leq s_i +(1-a_{ij})L\\
 		& e_i\leq s_j +a_{ij}L\\
-		\forall i, \forall j\ne i, \quad & \text{exclusive computation of task } i \text{ on computation channel:}\\
+		\forall i, \forall j\ne i, \quad & \text{exclusive computation of task } i \text{ on computation resource:}\\
 		& e'_j \leq s'_i +(1-b_{ij})L\\
@@
 		& \sum_r (a_{ir} - c_{ir})CM(r) + CM(i) \le C\\
-		%%\forall i, \forall j\ne i, \quad & \text{task }T_i \text{ respects memory capacity on computation channel:}\\
+		%%\forall i, \forall j\ne i, \quad & \text{task }T_i \text{ respects memory capacity on computation resource:}\\
 		%%& s_j < e'_i +(1-d_{ij})L\\
@@
 Hence, we do not include this heuristic for the comparison in Section~{\ref{sec:exp}.
+Performance comparison of different heuristics with MILP based heuristics is available in an extended version(cite).
+
+		\todo[inline]{SKumar: Move to an extended version, Obtain MILP based makespans for new memory capacities}
  Figure~\ref{fig:iterativeLpSolution} shows the performance of different heuristics with MILP based heuristics for various memory capacities of a single trace file.
@@
 Figure~\ref{fig:iterativeLpSolution} shows the comparison of different heuristics with MILP based heuristic for various memory capacities of a single trace file.
-		\todo[inline]{SKumar: Obtain MILP based makespans for new memory capacities}
 		\begin{figure}[htb]
@@
 		%%	\todo[inline]{Machine information and our model}
+		\subsection{Experimental Settings}
 
@@
 CCSD automatically determines tile sizes at different program points based on the input molecules.
-Hence, HF operates on almost homogeneous tiles while CCSD on heterogeneous tiles.
+Hence, HF operates on almost less heterogeneous tiles while CCSD on more heterogeneous tiles.
 
@@
 		We also consider two other static heuristics for evaluation.
-The first heuristic is based on an algorithm, proposed by Gilmore and Gomory, to obtain the minimal cost sequence for a set of jobs.
+The first heuristic is based on an algorithm, proposed by Gilmore and Gomory, to obtain the minimal cost sequence for a set of jobs~\cite{Gilmore-Gomory:1964}.
+This is classic in 2-machine no-wait flow shop.
 In this algorithm, each job has a start and end state and a cost is associated to change the state.
@@
 		\end{figure*}
-		As indicated above, HF tasks are highly homogeneous, this is also noticeable in Figure~\ref{fig:ratio_to_optimal_hf}.
+		As indicated above, HF tasks operate on less heterogeneous tiles, this is also noticeable in Figure~\ref{fig:ratio_to_optimal_hf}.
 All heuristics depict similar behavior for minimum memory capacity $m_c$ and increasing the memory capacity slightly does not change the performance of all heuristics.
@@
 It can be explained from the fact that the task sequence is obtained considering no extra memory is available, but here we apply the same sequence for a different scenario, overall memory consumed at each point is limited to memory capacity.
-$BP$ heuristic does not take the advantage of task types, hence it performs poorly in most cases.
+Surprisingly $BP$ performs good among static heuristics.
+As it does not take the advantage of task types,  heuristics of other categories outperform it.
 
@@
 
-		Figure~\ref{fig:ratio_to_optimal_best_ccsd} shows that best variants of dynamic and static order with dynamic correction strategies achieve similar performance at minimum memory capacity $m_c$.
+		Figure~\ref{fig:ratio_to_optimal_best_ccsd} shows that best variants of dynamic and static order with dynamic corrections strategies achieve similar performance at minimum memory capacity $m_c$.
 But as memory capacity increases, heterogeneity allows static order with dynamic corrections based strategies to take advantage of static knowledge to get maximum overlap and dynamic correction to select another task in case of memory capacity limitation.
@@
 
-		To get more insights into the considered applications, we also look in to their workloads.
-Figure~\ref{fig:ApplicationProperties} exhibits that HF is a communication intensive application and maximum 20\% overlap can be expected in the best scenario.
+		To get more insights into the considered applications, we also look in to their sum of communication timings ($sum_comm$)  and sum of computation timings  ($sum_comp$) with respect to $OMIM$ in Figure~\ref{fig:ApplicationProperties}.
+It exhibits that HF is a communication intensive application and maximum 20\% overlap can be expected in the best scenario.
 While in CCSD , communications and computations are almost evenly distributed and 40-75\% communication-computation overlap is possible.
@@
 
-		In this article, we consider the problem of deciding the order of data transfers between two memory nodes such that overlap of communication and computation is maximized.
+		In this paper, we consider the problem of deciding the order of data transfers between two memory nodes such that overlap of communication and computation is maximized.
 With Exascale computing, applications face bottlenecks due to communications.
@@
 		\begin{acks}
+
+			We are grateful to Ajay Panyala for his help to run NWChem on Cascade machine.
 			Identification of funding sources and other support, and thanks to individuals and groups that assisted in the research and the preparation of the work should be included in an acknowledgment section, which is placed just before the reference section in your document.

### 2019-04-10 ICPP-19/all-binpack/ratio_to_optimal.R
plots modification

@@ -9,7 +9,7 @@ dftest[,2:6]<-NULL
 dftestMelted<-melt(dftest, "capacity")
 names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
 p<-ggplot(dftestMelted, aes(x=Heuristic, y=ratio_to_optimal, color=Heuristic)) + geom_boxplot(outlier.color="black") + facet_wrap(~capacity, ncol=4)  + theme(axis.ticks = element_blank(), axis.text.x = element_blank()) + xlab("")
-p <- p + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Ratio to Optimal")
+#p <- p + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Ratio to Optimal")
 return (p)
 }
 p<-ratio_to_optimal_func('all_results_hf.txt')

### 2019-04-10 ICPP-19/results/scripts/insights.R

@@ -27,6 +27,8 @@ get_melted_data_frame<-function(file_name)
 {
 library(reshape2)
 dftest<-read.table(file_name, header=T)
+colnames(dftest)[colnames(dftest) == "sum_comm_comp" ] <- "sum_comm+sum_comp"
+colnames(dftest)[colnames(dftest) == "max.sum_comm.sum_comp." ] <- "max(sum_comm,sum_comp)"
 dftest[,1:ncol(dftest)]<-dftest[,1:ncol(dftest)]/dftest[,5]
 dftest[,5]<-NULL
 dftestMelted<-melt(dftest)
@@ -41,6 +43,6 @@ dfMelted <- rbind(dfMelted1, dfMelted2)
 library(ggplot2)
 p<-ggplot(dfMelted, aes(x=Parameter, y=ratio_to_optimal, color=Parameter))  + geom_boxplot(outlier.color="black") + geom_hline(yintercept=1, linetype="dashed", color = "red") +
           facet_wrap(~application) + scale_y_continuous(breaks=seq(0.0, 2.0, 0.5), limits=c(0, 2)) +
-          theme(legend.position='none', axis.text.x = element_text(angle = 40, hjust=1, vjust = 1));
+          theme(legend.position='none', axis.text.x = element_text(angle = 45, hjust=1, vjust = 1)) + xlab(" ")
 ggsave(file="application_properties.pdf", p, width=7, height=4)
 

### 2019-04-10 ICPP-19/results/scripts/inverse_ratio_to_optimal-best.R

@@ -13,10 +13,11 @@ dftest$dynamic_best<-do.call('pmin', c(dftest[,8:10]))
 dftest$static_dynamic_best<-do.call('pmin', c(dftest[,11:13]))
 dftest<-dftest[,c(1,2,14:16)]
 dftestMelted<-melt(dftest, "capacity")
-names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
+names(dftestMelted)<-c("Capacity", "Heuristic", "ratio_to_optimal")
 #p<-ggplot(dftestMelted, aes(x=jitter(capacity), y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth()
-p<-ggplot(dftestMelted, aes(x=capacity, y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth(method="loess")
-p<-p + ylab("inverse(ratio_to_optimal)") + theme(plot.title = element_text(hjust = 0.5), legend.position="bottom") +  ggtitle("Performance With Best of all categories")
+p<-ggplot(dftestMelted, aes(x=Capacity, y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth(method="loess")
+#p<-p + ylab("inverse(ratio_to_optimal)") + theme(plot.title = element_text(hjust = 0.5), legend.position="bottom") +  ggtitle("Performance With Best of all categories")
+p<-p + ylab("inverse(ratio_to_optimal)") + xlab ("Memory Capacity") + theme(legend.position="bottom")
 return (p)
 }
 

### 2019-04-10 ICPP-19/results/scripts/inverse_ratio_to_optimal_batch-best.R

@@ -50,6 +50,6 @@ dfMelted <- rbind(dfMelted1, dfMelted2)
 library(ggplot2)
 
 p<-ggplot(dfMelted, aes(x=capacity, y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth(method="loess") +
-facet_wrap(~aname, scale="free") + ylab("inverse(ratio_to_optimal)") + theme (legend.position="bottom")
+facet_wrap(~aname, scale="free") + ylab("inverse(ratio_to_optimal)") + xlab("Memory Capacity") + theme (legend.position="bottom")
 #ggsave(file="test.pdf", p, width=7, height=4)
 ggsave(file="inverse_ratio_to_optimal_batch-best.pdf",p, width=13, height=5)

### 2019-04-10 ICPP-19/communications.tex
Edit after Lionel's proofread

@@
 
-	\author{Valerie B\'eranger}
+	\author{Suraj Kumar}
 	\affiliation{%
-		\institution{Inria Paris-Rocquencourt}
-		\city{Rocquencourt}
-		\country{France}
-	}
-	\author{John Smith}
-	\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
-	\email{jsmith@affiliation.org}
-
-	\author{Julius P. Kumquat}
-	\affiliation{\institution{The Kumquat Consortium}}
-	\email{jpkumquat@consortium.net}
+		\institution{Pacific Northwest National Laboratory}
+		\city{Richland, Washington, USA}}
+	\email{suraj.kumar@pnnl.gov}
+
+	\author{Lionel Eyraud-Dubois}
+	\affiliation{\institution{Inria Bordeaux -- Sud-Ouest}\institution{Université de Bordeaux, France}}
+	\email{lionel.eyraud-dubois@inria.fr}
+
+	\author{Sriram Krishnamoorthy}
+	\affiliation{
+	\institution{Pacific Northwest National Laboratory}
+	\city{Richland, Washington, USA}}
+	\email{sriram@pnnl.gov}
 
@@
 In this paper, we consider the problem of deciding the order of data transfers between two memory nodes for a set of independent tasks with the objective to minimize the makespan.
-We prove that with finite memory capacity obtaining the optimal order of data transfers is an NP-complete problem.
+We prove that with finite memory capacity, obtaining the optimal order of data transfers is an NP-complete problem.
 We propose several heuristics for this problem and provide details about their favorable situations.
@@
 	With the advent of multicore, and the use of accelerators, it is notoriously cumbersome to exploit the full capability of a machine.
-Indeed, there are several challenges come into picture.
-First, every architecture provides its own efficacy and interface.
+Indeed, there are several challenges that come into picture.
+First, every architecture provides its own efficiency and interface.
 Therefore, a steep learning curve is required for programmers to take good utilization of all resources.
 Second, scheduling is a well known NP-Complete optimization problem, and hybrid and distributed resources make this problem harder (we refer ~\cite{webpagescheduling} for a survey on the complexity of scheduling problems and ~\cite{bleuse2015scheduling} for a recent survey in the case of hybrid nodes).
-Third, due to shared buses, parallel resources, it is hard to obtain a precise model based on prediction of computation and communication timings.
-Fourth, number of architectures has increased drastically in recent years, therefore it is almost impossible to develop hand tune optimized code for all these architectures.
+Third, due to shared buses and parallel resources, it is challenging to obtain a precise model based on prediction of computation and communication timings.
+Fourth, then number of architectures has increased drastically in recent years, therefore it is almost impossible to develop hand tuned optimized code for all these architectures.
 All these observations led to the development of different task based runtime systems.
 Among several runtimes, we may cite QUARK~\cite{YarKhan:2011:Quark:Manual} and PaRSEC~\cite{parsec} from from ICL, Univ.
-of Tennessee Knoxville (USA), StarPU~\cite{starpu} form INRIA Bordeaux (France), Legion~\cite{legion12} from Stanford Univ.
-(USA), StarSs~\cite{ompss} from Barcelona Supercomputing Center (Spain), KAPPI~\cite{kaapi} from INRIA Grenoble (France).
+of Tennessee Knoxville (USA), StarPU~\cite{starpu} form Inria Bordeaux (France), Legion~\cite{legion12} from Stanford Univ.
+(USA), StarSs~\cite{ompss} from Barcelona Supercomputing Center (Spain), KAAPI~\cite{kaapi} from Inria Grenoble (France).
 All these runtime systems allow programmers to express their algorithms at the abstract level in the form of direct acyclic graphs (DAG), where vertices represent computations and edges represent dependencies among them.
-Sometimes some static information such as distance to exit (last) node as a priority or affinity of computation towards resources is also provided along with the DAG.
-Then runtime is responsible for managing scheduling of computations and communications, data transfers among different memories, computation-communication overlap, and load balance.
+Sometimes some static information is also provided along with the DAG, such as distance to exit (last) node as a priority or affinity of computation towards resources.
+The runtime is then responsible for managing scheduling of computations and communications, data transfers among different memories, computation-communication overlap, and load balance.
 
@@
 
-	In the last few decades, there is a drastic improvement in the hardware to provide perminent rate of computation, but little improvement has been achieved for the rate of data movement.
+	In the last few decades, we have witnessed a drastic improvement in the hardware to provide higher rate of computation, but comparatively smaller improvement has been achieved for the rate of data movement.
 With extreme scale computing, supercomputers face bottlenecks due to the need of large amount of data~\cite{ascaccommitteereport2014,yelick2016}.
-Therefore focus of HPC community is now changing towards avoiding, hiding and minimizing communication costs.
+Therefore, the HPC community is now focusing on avoiding, hiding and minimizing communication costs.
 
 	Certain applications such as dense linear algebra kernels have regular structure.
-Therefore, it is possible to associate priorities, based on the task graph structure, with computations, which runtime uses to make the execution efficient.
-In irregular applications, programmers do not know the precise structure of the task graphs in advance, tasks are added recursively based on certain sentinel constraints.
-For such applications, runtime sees a set of independent ready tasks and schedule them on different processing units.
-It is extremely important for runtimes to decide the order of data transfers for these scheduled computations such that overlap between computations and communications can be maximised.
+Therefore, it is possible to associate priorities to computations, based on the task graph structure, and to use them at runtime to make the execution efficient.
+In irregular applications, programmers do not know the precise structure of the task graphs in advance: tasks are added recursively based on certain sentinel constraints.
+For such applications, the runtime system sees a set of independent ready tasks and schedules them on different processing units.
+It is extremely important for runtimes to decide the order of data transfers for these scheduled computations so as to maximize the overlap between computations and communications.
 This is the main topic of this paper.
-We prove that order of communications on two memory nodes with the objective of minimizing the makespan is NP-Complete.
-Our proof is inspired from work by ~\cite{Papadimitriou:1980:FSL:322203.322213}, which applies a similar technique for 2-machine flowshop problem.
-The main difference with their and our approach is that they consider a bounded number of tasks can await execution on second machine and buffer is acquired after completing the task on first machine.
-On the contrary, our approach is designed for tasks appearing in scientific workloads whose memory requirements are highly irregular and memory is acquired before starting the data transfer on communication resource.
-We propose different strategies for runtimes such that it can maximize the overlap of computations and communications.
-We evaluate our strategies on a cluster of homogeneous nodes.
-But our approach is generic and easily adaptable to any system which operates on different memory spaces.
-Here are the important contributions of this paper.
+We prove that the order of communications on two memory nodes with the objective of minimizing the makespan is a NP-Complete problem if the memory of the target node is limited.
+Our proof is inspired from work by~\cite{Papadimitriou:1980:FSL:322203.322213}, which applies a similar technique for 2-machine flowshop problem with bounded capacity.
+The main difference between both approaches is that they consider that all tasks have the same occupation on the second machine) and that the memory occupation starts when the second machine starts working.
+On the contrary, our approach is designed for tasks appearing in scientific workloads whose memory requirements are highly irregular and we consider that memory is acquired before starting the data transfer on communication resource.
+We propose different runtime strategies in order to maximize the overlap of computations and communications.
+We evaluate our strategies on the context of a cluster of homogeneous nodes.
+However, our approach is generic and easily adaptable to any system which operates on different memory spaces.
+Here are the important contributions of this paper:
 
@@
 	\begin{itemize}
+		\item NP-Completeness proof for the general data-transfer problem 
 		\item Proposed different scheduling strategies with the objective to minimize the makespan
 		%%		\item An optimal strategy and its proof, when there is not any memory capacity constraint on the target machine
-		\item NP-Completeness proof for the general data-transfer problem 
 		\item Linear programming formulation of the problem
@@
 
-	The problem of scheduling tasks has been highly studied in literature and this problem is known to be NP-Complete~\cite{GareyJohnson}.
-Many static and dynamic strategies have been proposed and analyzed for this problem~\cite{heft-Topcuoglu,hipc16multiresource,ipdps16starpu}.
-There ia also a number of studies in the direction of task scheduling with the emphasis of improving locality and minimizing the communication cost~\cite{starpu,heft-Topcuoglu}.
+	The problem of scheduling tasks has been highly studied in the literature and many formulations are known to be NP-Complete~\cite{GareyJohnson}.
+Many static and dynamic strategies have been proposed and analyzed for scheduling tasks on heterogeneous resources~\cite{heft-Topcuoglu,hipc16multiresource,ipdps16starpu}.
+There is also a number of studies in the direction of task scheduling with the emphasis of improving locality and minimizing the communication cost~\cite{starpu,heft-Topcuoglu}.
 Stanisic et.
-al proposed a heuristic to schedule tasks on a computing resource where most of its data is available~\cite{luka-dmdar}.
-Similar approach has been adopted by Agullo et.
+al~\cite{luka-dmdar} proposed a heuristic to schedule tasks on a computing resource where most of its data is available.
+A similar approach has been adopted by Agullo et.
 al for the scheduling of sparse linear algebra kernels~\cite{agullo_fmm}.
-Predari et.al proposed heuristics to partition the task graph across a number of processors such that inter processor communication can be minimized ~\cite{predari:tel-01518956}.
-
-	The problem considered in this paper also can be viewed as a flow shop problem.
-Communication and computation timings of a task can be considered as processing timings on different machines.
+Predari et.
+al proposed heuristics to partition the task graph across a number of processors such that inter-processor communication can be minimized~\cite{predari:tel-01518956}.
+
+	The problem considered in this paper also can be viewed as a flow shop problem: the communication link can be seen as a processing resource, and each task needs to first be handled by the communication link and then by the computational resource.
+Communication and computation timings of a task can thus be considered as processing times on different machines.
 Johnson has provided scheduling strategies for 2 and 3-machine flow shop problems with infinite memory capacity~\cite{johnson}.
 2-machine flow shop problem with finite buffer has been proven NP-Complete by Papadimitriou et.
-al~\cite{Papadimitriou:1980:FSL:322203.322213}.
-They consider a bounded number of tasks can await execution on second machine.
-
-	There is also a numerous study pertaining to the scheduling with limited memory and storage, since the work of register allocation for arithmetic expressions by Sethi and Ulman~\cite{Sethi:1970:GOC:321607.321620}.
+al~\cite{Papadimitriou:1980:FSL:322203.322213}, in which a constraint is imposed on the number of tasks that can await execution on the second machine.
+
+	A number of other studies have focused on scheduling with limited memory and storage, starting with the work of register allocation for arithmetic expressions by Sethi and Ulman~\cite{Sethi:1970:GOC:321607.321620}.
 Sarkar et.
-al worked on the scheduling of graphs of smaller-grain tasks with limited memory, where each task requires homogeneous data size ~\cite{vsarkar-pact}.
+al worked on the scheduling of graphs of smaller-grain tasks with limited memory, where each task requires homogeneous data size~\cite{vsarkar-pact}.
 The same work has been extend by Marchal et.
@@
 
-	To exploit the full potential of a system tasks may get scheduled on processing
-	units where all of their data does not reside. A task may require all of its data
+	To exploit the full potential of a system it may be necessary to execute tasks on processing
+	units where all of their data does not reside. A task may require all of its input data
 	in local memory before starting the execution. There may be multiple tasks
 	scheduled on a processing unit, which require to transfer data from the same
-	memory node. Order of data transfers for such tasks is very crucial for the
-	communication-computation overlap, thus for the overall performance. In general, order of task execution with input and output data transfers can be 
-	viewed as 3-machine flowshop problem, where processing time on first machine is 
-	input data transfer time, processing time on second machine is task execution time, 
-	processing time on third machine is output data transfer time and the objective is 
+	memory node. Ordering data transfers for such tasks is very crucial for the
+	communication-computation overlap, thus for the overall
+	performance. In general, order of task execution with input
+	and output data transfers can be  
+	viewed as a 3-machine flowshop problem, where processing time on the first machine is 
+	input data transfer time, processing time on the second machine is task execution time, 
+	and processing time on the third machine is output data transfer time; and the objective is 
 	to minimize the total makespan. This is a well known hard problem~\cite{NPComplete3Machine,johnson}.
 
-	In general, output data produced by a task is very less.
+	In many cases, output data that needs to be retrieved after task execution is much smaller than the input data.
 It is often the case that future tasks running on the same memory node require output data of the past tasks.
-Therefore, most runtime systems transfer data to other memory nodes based on the demand -- not immediately.
-It is possible that all output data can be stored in a preallocated separate buffer on a memory node.
-Hence, we do not consider output data separately in our analysis and assume that output data is negligible or stored in a separate buffer for each task.
-Thus problem considered here is simpler than general 3-machine flowshop problem.
-We prove that order of execution of such tasks with finite memory capacity is an NP-complete problem.
-We also present an optimal algorithm to determine the order of execution of tasks when there is not any restriction on memory limit.
+Therefore, most runtime systems transfer data to other memory nodes based on the demand -- not immediately after they were produced.
+It is also possible that all output data can be stored in a preallocated separate buffer on a memory node.
+Hence, we do not consider output data explicitely in our analysis and assume that output data is negligible or stored in a separate buffer for each task.
+Thus problem considered here is thus more similar to a 2-machine flowshop problem.
+We prove that ordering the execution of such tasks with finite memory capacity is an NP-complete problem: %%We also present an optimal algorithm to determine the order of execution of tasks when there is not any restriction on memory limit.
 
@@
 
-	Let \scomm($i$) and  \scomp($i$) represent the start times of task $i$ on communication and computation resources.
-We call a task $i$ is compute (resp.
-communication) intensive if $CP_i $$\ge$ (resp.
-$<$) $CM_i$ ).
+	Given a schedule, \scomm($i$) and \scomp($i$) represent the
+	start times of task $i$ on communication and computation
+	resources. A schedule is feasible if for every time $t$, the
+	amount of memory required by tasks such that $\scomm(i) \leq t
+	\leq \scomp(i) + COMP_i$ is not more than the memory capacity
+	$C$. For simplicity, we assume in all of this paper that the
+	amount of memory required by a task is proportional to its
+	communication time, and without loss of generality we consider
+	that memory size of a task is equal to its communication time.
+
+	We call a task $i$ compute intensive if $COMP_i \ge CM_i$, and
+	communication intensive otherwise.
 
@@
 
-	The algorithm presented in Section~\ref{sec:theoreticalProof} achieves optimal makespan when there is not any memory capacity constraint.
-This optimal value indicates a lower bound on the makespan.
-We use $optimal\_ \allowbreak makespan\_  \allowbreak infinite\_  \allowbreak memory$ ($OMIM$) to represent this value.
-We assess the efficiency of other proposed heuristics in limited memory capacity in Section~\ref{sec:exp} with respect to this lower bound, $OMIM$.
+	Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} presented in Section~\ref{sec:theoreticalProof} achieves an optimal makespan when there is no memory constraint.
+This optimal value indicates a lower bound on the makespan of the constrained case.
+We use denote this value with $optimal\_ \allowbreak makespan\_  \allowbreak infinite\_  \allowbreak memory$ ($OMIM$).
+In the present Section, we propose different heuristics for the limited memory case, and we assess their efficiency with respect to this lower bound in Section~\ref{sec:exp}.
 
@@
 In the first category, the order of all computations and communications is computed in advance and the same order is followed on both resources.
-While in the second category, the best suited next task is chosen based on different criteria.
-In the last category, which is based on combination of strategies of the other two categories, we precompute the order and try to follow it as much as possible, but when the precomputed schedule induces idle time then we look for the best suited next task.
-In all of our strategies (except linear programming based strategy) order of communications and computations is same.
+In the second category, the next task to schedule is dyanmically chosen based on different criteria.
+The final category is based on combining strategies from the first two categories: a static ordering is precomputed and corrected dynamically to avoid idle time caused by memory limitations.
+In all of our strategies (except linear programming based strategy), communication and computations take place in the same order.
 
@@
 	In this class of strategies, we compute the order of processing in advance based on criteria such as communication time, compute time and accelerated tasks.
-After computing the order, we follow the same order on computation and communication resources and make sure that at each point in the schedule memory capacity is respected.
+After computing the order, we follow the same order on computation and communication resources and make sure that the memory constraint is respected at each point in the schedule.
 
@@
 	\begin{enumerate}[label=\roman*)]
-		\item $order  \_ \allowbreak  \allowbreak of  \_ \allowbreak  \allowbreak optimal \_ \allowbreak strategy \_ \allowbreak infinite \_ \allowbreak memory $ ($OOSIM$): Order of processing is obtained by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}.
-At each point in the schedule memory capacity is respected.
+		\item \textit{Order  of  optimal strategy infinite memory} ($OOSIM$): This heuristic uses the order given by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}, but respects the memory constraint at each point in the schedule.
 Hence the makespan of this heuristic may be completely different from $OMIM$.
 
-		\item $increasing \_ \allowbreak order \_ \allowbreak of \_ \allowbreak communication \_ \allowbreak strategy$ ($IOCMS$): Order is obtained by sorting all tasks in non-decreasing order of communication time.
-
-		\item $decreasing \_ \allowbreak order \_ \allowbreak of \_ \allowbreak computation \_ \allowbreak strategy$ ($DOCPS$): Order is obtained by sorting all tasks in non-increasing order of computation time.
-		\item $increasing \_ \allowbreak order \_ \allowbreak of \_ \allowbreak communication \_ \allowbreak plus \_ \allowbreak computation \_ \linebreak[4] \allowbreak strategy$ ($IOCCS$): Order is obtained by sorting all tasks in non-decreasing order of sum of communication and computation times.
-		\item $decreasing \_ \allowbreak order \_ \allowbreak of \_ \allowbreak communication \_ \allowbreak plus \_ \allowbreak computation \_ \linebreak[4] \allowbreak strategy$ ($DOCCS$): Order is obtained by sorting all tasks in non-increasing order of sum of communication and computation times.
+		\item \textit{increasing order of communication strategy} ($IOCMS$): tasks are ordered  in non-decreasing order of communication time.
+
+		\item \textit{decreasing order of computation strategy} ($DOCPS$): tasks are ordered in non-increasing order of computation time. 
+		\item \textit{increasing order of communication plus computation strategy} ($IOCCS$): tasks are ordered in non-decreasing order of the sum of their communication and computation times.
+		\item \textit{decreasing order of communication plus computation strategy} ($DOCCS$): tasks are ordered in non-increasing order of the sum of their communication and computation times.
 
@@
 
-	Fig~\ref{fig:staticOrderExample} shows schedules for all proposed heuristics of this class for the task set of Table~\ref{tab:staticOrderExample}.
+	In order to highlight the different behavior of these static strategies, we propose on Table~\ref{tab:staticOrderExample} an example instance, and on Figure~\ref{fig:staticOrderExample} the corresponding schedules for all these heuristics.
+
 	\subsection{Dynamic Selection}
@@
 
-	In this class of strategy, when communication resource is idle, a task is chosen which satisfies the selection criteria maximally among other tasks.
-For example, if the selection criteria is to choose a highly compute intensive task, then we calculate the ratio of compute time and communication time for all tasks, and the task with the maximum ratio is selected (ties are broken randomly).
-As we assume that order on both resources is same, hence order on compute resource follows the order of communication resource.
-
-	We select a set of tasks which induce minimum idle time on compute resource and satisfy available memory requirement.
+	Dynamic strategies are based on the following principle: when the communication resource is idle, a task is chosen based on a ranking criterion which differ depending on the heuristic, among those which fit in memory.
+For example, if the selection criteria is to choose a highly compute intensive task, then we compute the ratio of compute time and communication time for all tasks, and we select the task which fit in the currently available memory and whose ratio is maximum (ties are broken arbitrarily).
+We also ensure that the order on both resources is the same, by ordering tasks on the computing resource accordingly.
+
+	\todo[inline]{LED: I added this part ``among those which fit in memory'', is it correct?}
+	\todo[inline]{LED: What happens if no task fit in memory?}
+
+	%% We select a set of tasks which induce minimum idle time on compute resource and satisfy available memory requirement.
 Then a task is chosen for processing from this set based on the following heuristics.
@@
 
-		\item $largest \_ \allowbreak communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$ ($LCMR$): A task with the largest communication time is chosen.
-		\item $smallest \_ \allowbreak communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$ ($SCMR$): A task with the smallest communication time is chosen.
-		\item $maximum \_ \allowbreak accelerated \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$ \linebreak[4]($MAMR$): A task with the maximum ratio of compute time to communication time is chosen.
+		\item \textit{largest communication task respects memory restriction} ($LCMR$): a task with the largest communication time is chosen. 
+		\item \textit{smallest communication task respects memory restriction} ($SCMR$): a task with the smallest communication time is chosen.
+		\item \textit{maximum accelerated task respects memory restriction} ($MAMR$): a task with the maximum ratio of compute time to communication time is chosen.
 	\end{enumerate}
@@
 
-	Fig~\ref{fig:dynamicSelectionExample} shows schedules for all proposed heuristics of this class for the task set of Table~\ref{tab:dynamicSelectionExample}.
+	We highlight the different dynamic heuristics with the instance described on Table~\ref{tab:dynamicSelectionExample} (these heuristics are too similar on the instance from the previous class), and Figure~\ref{fig:dynamicSelectionExample} shows the corresponding schedules.
 
@@
 
-	In this class of strategy, we precompute the order of tasks based on different criteria and then try to follow the same order as much as possible.
-But when communication resource is idle due to memory requirement of the next task in the obtained order, then we select a task similar to previous strategy.
-After a task is selected then we update the remaining order without this task.
+	In this class of strategy, we precompute the order of tasks based on some criterion and then follow this ordering as much as possible.
+But when the communication resource is idle because the memory requirement of the next task is too high, then we select a task  with a dynamic strategy.
+After a task is dynamically selected, we update the remaining order without this task.
 This class of strategy takes advantage of static information in the form of precomputed order and dynamic corrections to minimize the idle time due to memory constraint.
@@
 
-	Initial order is obtained by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}.
-When communication resource is idle due to memory requirement of the next task in the order, then we select a set of tasks which induce minimum idle time on compute resource and satisfy memory requirement.
-We define the following heuristics based on how we select a task from this set.
-After that order of remaining tasks is updated without this task.
+	In all strategies, the initial order is obtained by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}.
+.
+We define the following heuristics based on how we select a task from the set of tasks which fit in memory.
+	\todo[inline]{LED: What happens if no task fit in memory?}
 
 	\begin{enumerate}[label=\roman*)]
-		\item $optimal \_ \allowbreak order \_ \allowbreak infinite \_ \allowbreak memory \_ \allowbreak largest \_ \allowbreak communication \_ \linebreak[4]\allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$ ($OOLCMR$): A task with the largest communication time is chosen from the set.
-		\item $optimal \_ \allowbreak order \_ \allowbreak infinite \_ \allowbreak memory \_ \allowbreak smallest \_ \allowbreak communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$ ($OOSCMR$): A task with the smallest communication time is chosen from the set.
-		\item $optimal \_ \allowbreak order \_ \allowbreak infinite \_ \allowbreak memory \_ \allowbreak maximum \_ \allowbreak accelerated \_ \linebreak[4]\allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$ ($OOMAMR$): A task, whose ratio of compute time to communication time is maximum, is chosen from the set .
+		\item \textit{optimal order infinite memory largest communication task respects memory restriction} ($OOLCMR$): a task with the largest communication time is chosen from the set.
+		\item \textit{optimal order infinite memory smallest communication task respects memory restriction} ($OOSCMR$): a task with the smallest communication time is chosen from the set.
+		\item \textit{optimal order infinite memory maximum accelerated task respects memory restriction} ($OOMAMR$): a task  with the highest ratio of compute time to communication time is chosen from the set.
 	\end{enumerate}
@@
 
-	Fig~\ref{fig:staticOrderDynamicCorrectionsExample} shows schedules for all proposed heuristics of this class for the task set of Table~\ref{tab:staticOrderDynamicCorrectionsExample}.
+	As previously, we propose on Table~\ref{tab:staticOrderDynamicCorrectionsExample} an example instance for this class of strategies, and provide on Figure~\ref{fig:staticOrderDynamicCorrectionsExample} the corresponding schedules.
 
@@
 	We use a mixed integer linear program to obtain the order of communications and computations.
-$COMP_i$ and $COMM_i$ represent computation and communication timings of task $i$.
-Memory capacity of the target system is $C$.
+Recall that $COMP_i$ and $COMM_i$ represent computation and communication timings of task $i$, and that the memory capacity of the target system is $C$.
 In the linear program formulation, $s_i$ and $e_i$ (resp.
-$s'_i$ and $e'_i$) represent start and end time of communication (resp.
+$s'_i$ and $e'_i$) represent the start and end times of communication (resp.
 computation) for task $i$.
-The formulation contains $i)$ n-1 boolean variables, $a_{ij}$, for each task $i$ to denote the order of $i$ and $j$ on communication resource $ii)$ n-1 boolean variables, $b_{ij}$, for each task $T_i$ to denote the order of $i$ and $j$ on computation resource, and $iii)$ n-1 boolean variables, $c_{ij}$, for each task $i$ to denote the order of $s_i$ and $e'_j$.
+The formulation also contains for each pair of tasks $i$ and $j$ \textit{i)} a boolean variable $a_{ij}$ to denote the order of $i$ and $j$ on the communication resource \textit{ii)} a boolean variables $b_{ij}$ to denote the order of $i$ and $j$ on the computation resource, and \textit{iii)} a boolean variables $c_{ij}$ to denote the order of $s_i$ and $e'_j$.
 
@@
 
-	\noindent Let $L=\sum_i (COMP_i + COMM_i)$. It is evident that $e_i =s_i + COMM_i$ and $e'_i =s'_i + COMP_i$. The constraints are following.
+	\noindent Let $L=\sum_i (COMP_i + COMM_i)$. It is evident that $e_i =s_i + COMM_i$ and $e'_i =s'_i + COMP_i$. The linear program is given below.
 
@@
 	\begin{align*}
-		& \text{minimize } l \text{ such that }\\
-		\forall i, \quad & \text{computation of task } i \text{ completes:}\\
-		& e'_i \leq l\\
-		\forall i, \quad & \text{computation stars after communication ends:}\\
-		& e_i \leq s'_i\\
-		\forall i, \forall j\ne i, \quad & \text{exclusive communication of task } i \text{ on communication resource:}\\
-		& e_j \leq s_i +(1-a_{ij})L\\
-		& e_i\leq s_j +a_{ij}L\\
-		\forall i, \forall j\ne i, \quad & \text{exclusive computation of task } i \text{ on computation resource:}\\
-		& e'_j \leq s'_i +(1-b_{ij})L\\
-		& e'_i\leq s'_j +b_{ij}L\\
-		\forall i, \forall j\ne i, \quad & \text{task } i \text{ respects memory capacity on communication channel:}\\
-		& e'_j \leq s_i +(1-c_{ij})L\\
-		& s_i< e'_j +c_{ij}L\\
-		& \sum_r (a_{ir} - c_{ir})CM(r) + CM(i) \le C\\
-		%%\forall i, \forall j\ne i, \quad & \text{task }T_i \text{ respects memory capacity on computation resource:}\\
-		%%& s_j < e'_i +(1-d_{ij})L\\
-		%%& e'_i\leq s_j +d_{ij}L\\
-		%%& \sum_r (d_{ir} - b_{ir})CM(r) + TM(i) \le C\\
+		& \text{Minimize $l$ subject to:}\\
+		\forall i, \quad & e'_i \leq l && \text{(task $i$ completes)}\\
+		\forall i, \quad & e_i \leq s'_i&& \text{(valid ordering for task $i$)}\\
+		\forall i, \forall j\ne i, \quad & \left\{\begin{aligned}
+			e_j & \leq s_i +(1-a_{ij})L\\
+			e_i & \leq s_j +a_{ij}L 
+		\end{aligned} \right. &&
+		\begin{aligned}
+			&\text{(exclusive use of}\\
+			&\text{  communication link)}
+		\end{aligned}\\
+		\forall i, \forall j\ne i, \quad & \left\{
+		\begin{aligned}
+			e'_j &\leq s'_i +(1-b_{ij})L\\
+			e'_i &\leq s'_j +b_{ij}L
+		\end{aligned}\right. && 
+		\begin{aligned}
+			&\text{(exclusive use of}\\
+			&\text{  computation resource)}
+		\end{aligned}\\
+		\forall i, \forall j\ne i, \quad &\left\{
+		\begin{aligned}
+			e'_j &\leq s_i +(1-c_{ij})L\\
+			s_i  &< e'_j +c_{ij}L\\
+		\end{aligned}\right.&&
+		\begin{aligned}
+			&\text{(respect ordering}\\
+			&\text{ of variables $c_{ij}$)}
+		\end{aligned}\\
+		\forall i, \quad & \sum_{r\ne i} (a_{ir} - c_{ir})CM(r) + CM(i) \le C && \text{(memory constraint)}\\
+		%% %%\forall i, \forall j\ne i, \quad & \text{task }T_i \text{ respects memory capacity on computation resource:}\\
+		%% %%& s_j < e'_i +(1-d_{ij})L\\
+		%% %%& e'_i\leq s_j +d_{ij}L\\
+		%% %%& \sum_r (d_{ir} - b_{ir})CM(r) + TM(i) \le C\\
 	\end{align*}
@@
 	We use GLPK solver v4.65 to solve the above formulation.
-The solver was unable to handle number of variables required to solve MILP at the scale of our interest.
-Hence, we solve the linear program iteratively for a small subset of size $k=3,4,5$ (solver was unable to handle number of variables required for $k\ge6$ ) and represent the makespan calculated by this heuristic as $lp.k$.
-At the boundary of two iterations we fixed the event (communication or computation) of an unfinished task who has started before the boundary point and consider other events flexible.
+We also add the following constraints to help the solver: $\forall i, \forall j\ne i$, $a_{ij} + a_{ji}=1$, $b_{ij} + b_{ji} = 1$, $c_{ij} \le a_{ij}$, $c_{ij} \le b_{ij}$, and  $c_{ij} + c_{ji} \le 1$.
+The solver was unable to handle the number of variables required to solve this MILP at the scale of our interest.
+Hence, we solve the linear program iteratively for a small subset of size $k=3,4,5$: at the boundary of two iterations we fix the events (communication and computation) of an unfinished task started before the boundary point and consider other events flexible.
+The subsets are formed in the order in which tasks are submitted, which is arbitrary.
+For a given size $k$, we represent the makespan calculated by this heuristic as $lp.k$.
 	We compute various $lp.k$ values for different memory capacities and observe that most of the other heuristics perform better than this heuristic.
@@
 
-		\todo[inline]{SKumar: Move to an extended version, Obtain MILP based makespans for new memory capacities}
+		\todo[inline]{SKumar: Move to an extended version and more clear about results and implementation}
 		Figure~\ref{fig:iterativeLpSolution} shows the performance of different heuristics with MILP based heuristics for various memory capacities of a single trace file.
@@
 			\includegraphics[scale=0.5]{./results/makespan_with_lp.pdf}
-			\caption{Comparision of different heuristics with MILP solution based heuristic.}
+			\caption{Comparision of different heuristics with MILP solution based heuristic.\todo[inline]{LED: I understand that this figure will be removed?
+Otherwise, use aes(fill=) instead of aes(color=) to have color filled bars.}}
 			\label{fig:iterativeLpSolution}
@@
 This allows programmers to use appropriate strategies to maximize communication-computation overlap for their applications.
-
-		%%\begin{table*}[htb]
-		%%	\scriptsize
-		%%	\begin{tabular}{|c|p{3cm}|}
-		%%		\hline
-		%%		\textbf{Heuristic} & \textbf{Favorable Situation} \\ \hline
-		%%		order\_of\_optimal\_strategy\_infinite\_memory & Unlimited memory capacity (\textcolor{green}{Optimal}) \\ \hline
-		%%		increasing\_order\_of\_communication\_strategy & Unlimited memory capacity and tasks are compute intensive (\textcolor{green}{Optimal}) \\ \hline
-		%%		decreasing\_order\_of\_computation\_strategy & Unlimited memory capacity and tasks are communication intensive (\textcolor{green}{Optimal}) \\ \hline
-		%%		increasing\_order\_of\_communication\_plus\_computation\_strategy & Moderate memory capacity and most tasks are compute intensive \\ \hline
-		%%		decreasing\_order\_of\_communication\_plus\_computation\_strategy & Moderate memory capacity and most tasks are communication intensive \\ \hline
-		%%		largest\_communication\_task\_respects\_memory\_restriction & Limited memory capacity and significant percentage of tasks are communication intensive \\ \hline
-		%%		smallest\_communication\_task\_respects\_memory\_restriction & Limited memory capacity and most tasks are compute intensive \\ \hline
-		%%		maximum\_accelerated\_task\_respects\_memory\_restriction & Limited memory capacity and number of communication and compute intensive tasks are approximately equal \\ \hline
-		%%		optimal\_order\_infinite\_memory\_largest\_communication\_task\_respects\_memory\_restriction & Moderate memory capacity and significant percentage of tasks are communication intensive\\ \hline
-		%%		optimal\_order\_infinite\_memory\_smallest\_communication\_task\_respects\_memory\_restriction & Moderate memory capacity and most tasks are compute intensive \\ \hline
-		%%		optimal\_order\_infinite\_memory\_maximum\_accelerated\_task\_respects\_memory\_restriction & Moderate memory capacity and number of communication and compute intensive tasks are approximately equal \\ \hline
-		%%	\end{tabular}\caption{~\label{tab:heuristicsAndFavorableScenarios}Heuristics and their favorable scenarios.}
-		%%\end{table*}
 
@@
 
-		Here moderate memory capacity refers to limited capacity but close to the maximum memory requirement of the considered application.
+		Here moderate memory capacity refers to the case where memory is limited but close to the maximum memory requirement of the considered application\todo[inline]{total memory requirement of all tasks?}.
 We can clearly observe the favorable scenarios for a few heuristics in Figures~\ref{fig:ratio_to_optimal_hf} and ~\ref{fig:ratio_to_optimal_ccsd}.
@@
 CCSD has significant percentage of both types of tasks, therefore $OOLCMR$ and $OOSCMR$ heuristics performance is very close to optimal in moderate memory cases.
+		\todo[inline]{LED: Since this is based on experimental results, should this go to a Section 5.5 or 5.6?}
 
@@
 
-		We consider a machine called Cascade, available at PNNL, for our experiments.
-We obtain traces by running two molecular chemistry applications, double precision version of Hartree-Fock (HF) and Coupled Cluster Single Double (CCSD) of NWChem package on 10 nodes of this machine.
+		We consider a machine called Cascade\todo{cite or url?}, available at PNNL, for our experiments.
+We obtain traces by running two molecular chemistry applications, double precision version of Hartree-Fock (HF) and Coupled Cluster Single Double (CCSD) of NWChem\todo{cite or url} package on 10 nodes of this machine.
 Each node is composed of 16 Intel Xeon E5-2670 cores.
-NWChem takes advantages of a Partitioned Global Address Space Programming Model, Global Arrays (GA), to use shared-memory programming APIs on distributed memory computers.
+NWChem takes advantages of a Partitioned Global Address Space Programming Model called Global Arrays (GA)\todo{cite or url?} to use shared-memory programming APIs on distributed memory computers.
 GA dedicates one core of each node to handle other cores, hence we can view a node as being composed of 15 computational cores.
 We use 150 processes for each application and obtain 150 trace files.
-We run CCSD with Uracil molecules input and HF with SiOSi molecules (for Uracil molecules, HF has very less workload, each processor executes only around 20 tasks, that is why we chose SiOSi input for HF execution).
+We run CCSD with Uracil molecules input and HF with SiOSi molecules (for Uracil molecules, HF has a much smaller workload, each processor executes only around 20 tasks, that is why we chose SiOSi input for HF execution).
 Each process executes around 300-800 tasks.
-Our data transfer model is quite simple and we consider that all data transfers between each process's local memory and GA memory take the same route.
+Our data transfer model is quite simple and we consider that all data transfers between the local memory of each process and the GA memory take the same route.
 Modeling of different routes of data transfers for the same source-destination pair, bandwidth sharing for different source-destination pairs and network congestion is more challenging and part of our future work.
-Our model is simple yet it provides insight to the application developers (or runtime system) that in what-order all data transfers are issued for the same source-destination pair to maximise communication-computation overlap.
+This simple model is enough to provide insight to the application developers (or runtime system) about the ordering of data transfers for the same source-destination pair so as to maximize communication-computation overlap.
 Our model is easily adaptable to any source-destination pair when there is one fixed route between source and destination (such as between CPU and GPU, one copy engine to transfer data from CPU (resp.
@@
 		Both applications mainly perform two types of computations, tensor transpose and tensor contraction.
-HF expects to specify a tile size and we set it to 100, so that each core can be efficiently utilize.
+HF expects to specify a tile size and we set it to 100, so that each core can be used efficiently.
 CCSD automatically determines tile sizes at different program points based on the input molecules.
-Hence, HF operates on almost less heterogeneous tiles while CCSD on more heterogeneous tiles.
-
-		%%	\todo[inline]{Scheduled based on Gilmore-Gomory algorithm and its performance }
-		We also consider two other static heuristics for evaluation.
-The first heuristic is based on an algorithm, proposed by Gilmore and Gomory, to obtain the minimal cost sequence for a set of jobs~\cite{Gilmore-Gomory:1964}.
-This is classic in 2-machine no-wait flow shop.
-In this algorithm, each job has a start and end state and a cost is associated to change the state.
-In our context, this cost can be seen as non-overlap time of computation for two adjacent tasks.
-Here is the main idea of this algorithm.
-Initially partial sequence of jobs is represented by a graph such that their overlap is maximum.
-Subsequently edges are added to this graph which minimized the total non-overlap cost and connects two components.
-When all nodes of this graph is connected then an edge interchange mechanism is taken into account to determine the sequence of jobs, which ensures that the sequence has minimal cost.
-We refer ~\cite{Gilmore-Gomory:1964} for the detailed algorithm and ~\cite{gitworkrepo} for our implementation.
-This algorithm does not take memory capacity into consideration and only provides the sequence of processing.
-We applied the same sequence with different memory capacity restrictions for our experiments and call this heuristic \textit{Gilmore-Gomory} ($GG$).
-
-		The second heuristic is based on first fit algorithm of bin packing problem.
-In this heuristic, tasks are considered in random order and added to the first bin which satisfies memory capacity restriction.
-If no bin is found then a new bin is created and this task is added to it.
-When all tasks are added to some bin then we decide the order of processing in the following way.
-If a task is added to the $jth$ location in the $ith$ bin, then it is placed at the $pth$ position for processing, where $p=\sum_{k<i}(\text{number of tasks in $kth$ bin}) + j$.
-We call this heuristic \textit{Bin Packing} ($BP$).
-
-		%%		\todo[inline]{increase font size in all plots, may be free scale-y}
-		%%	\todo[inline]{SKumar: decide metrics: ratio to optimal, percentage overlap, 100 - percentage non overlap}
-
-		We evaluate different data transfer heuristics for the several memory capacities.
-From the obtained traces, first we determine the minimum requirement of the memory capacity $m_c$ to execute all tasks.
-Then we observe the behavior of all heuristics with memory capacity $m_c$ to $2m_c$, in the gap of $0.125m_c$.
-Our performance metric is $ratio\_to\_optimal$, which is defined as the following.
-Let the makespan of a heuristic $H$ is $M_H$ and the makespan of the optimal case with infinite memory is $OMIM$, then $ratio\_to\_optimal (H)$ is $\frac{M_H}{OMIM}$ (lower value is better).
-This value would be greater or equal to $1$.
-A value closer to $1$ indicates that suitability of a particular heuristic and maximum possible communication-computation overlap has been achieved for that heuristic.
-
-		Figures ~\ref{fig:ratio_to_optimal_hf} and ~\ref{fig:ratio_to_optimal_ccsd} depict the distribution of the performance of each heuristic for all considered memory capacities, where plots are categorized by memory capacities.
-For each memory capacity and each heuristic, the box on the plot displays the median, first and last quartile, and the whiskers indicate minimum and maximum values, with outliers are shown by black dots.
-		\subsection{HF Performance}	
-		%%	\begin{figure*}[htb]
-		%%		\includegraphics[scale=0.25]{./results/plots/ratio_to_optimal_selected_hf.pdf}
-		%%		\caption{Comparison of different heuristics for HF.}
-		%%		\label{fig:ratio_to_optimal_hf}
-		%%	\end{figure*}
-		\begin{figure*}[htb]
-			\includegraphics[scale=0.5]{./all-binpack/ratio_to_optimal_selected_hf.pdf}
-			\caption{Comparison of different heuristics for HF.}
-			\label{fig:ratio_to_optimal_hf}
-		\end{figure*}
-		As indicated above, HF tasks operate on less heterogeneous tiles, this is also noticeable in Figure~\ref{fig:ratio_to_optimal_hf}.
-All heuristics depict similar behavior for minimum memory capacity $m_c$ and increasing the memory capacity slightly does not change the performance of all heuristics.
-As memory capacity increased further, dynamic variants of heuristics starts performing better and for the moderate memory capacities (close to $2m_c$ ), static order with dynamic correction variants outperform others.
-$GG$ heuristic does not achieve good performance.
-It can be explained from the fact that the task sequence is obtained considering no extra memory is available, but here we apply the same sequence for a different scenario, overall memory consumed at each point is limited to memory capacity.
-Surprisingly $BP$ performs good among static heuristics.
-As it does not take the advantage of task types,  heuristics of other categories outperform it.
-
-		\begin{figure}[htb]
-			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_hf-best.pdf}
-			\caption{Comparision of best variants of all categories for HF.}
-			\label{fig:ratio_to_optimal_best_hf}
-		\end{figure}
-
-		Figure~\ref{fig:ratio_to_optimal_best_hf} shows the performance comparison of best variants of all categories with the $order\_of\_submission$ ($OS$)strategy.
-Static strategies are expected to perform better when there is not any memory capacity restriction, hence this plot indicates that static strategies face capacity bottleneck and underperform.
-Dynamic strategies achieve better performance with limited memory capacity and static order with dynamic correction strategies suit in moderate memory capacity scenarios.
-
-		\subsection{CCSD Performance}
-
-		%%	\begin{figure*}[htb]
-		%%		\includegraphics[scale=0.25]{./results/plots/ratio_to_optimal_selected_ccsd.pdf}
-		%%		\caption{Comparison of different heuristics for CCSD.}
-		%%		\label{fig:ratio_to_optimal_ccsd}
-		%%	\end{figure*}
-
-		\begin{figure*}[htb]
-			\includegraphics[scale=0.5]{./all-binpack/ratio_to_optimal_selected_ccsd.pdf}
-			\caption{Comparison of different heuristics for CCSD.}
-			\label{fig:ratio_to_optimal_ccsd}
-		\end{figure*}
-
-		CCSD application operates on tasks of different sizes, hence different heuristics depict distinct behaviors even at minimum memory capacity $m_c$ .
-Heterogeneity favors to dynamic strategies, therefore both dynamic and static order with dynamic correction based strategies perform better than static based strategies.
-Similar to HF, static order with dynamic corrections based strategies outperform others as memory capacity becomes moderate.
-
-		\begin{figure}[htb]
-			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_ccsd-best.pdf}
-			\caption{Comparision of best variants of all categories for CCSD.}
-			\label{fig:ratio_to_optimal_best_ccsd}
-		\end{figure}
-
-		Figure~\ref{fig:ratio_to_optimal_best_ccsd} shows that best variants of dynamic and static order with dynamic corrections strategies achieve similar performance at minimum memory capacity $m_c$.
-But as memory capacity increases, heterogeneity allows static order with dynamic corrections based strategies to take advantage of static knowledge to get maximum overlap and dynamic correction to select another task in case of memory capacity limitation.
-Static strategies also start performing better at the end, which indicates that this application has potential for significant communication-computation overlap and pure dynamic strategies are unable to take this information into account while making scheduling decisions.
-
-		\subsection{HF and CCSD Characteristics}
+Hence, HF operates on almost homogeneous tiles while CCSD uses more heterogeneous tiles.
+
+		\subsection{Workload Characteristics}
 
@@
 			\includegraphics[scale=0.5]{./results/plots/application_properties.pdf}
-			\caption{HF and CCSD tasks characteristics.}
+			\caption{HF and CCSD tasks characteristics.\todo[inline]{ylab(``Ratio to optimal'') (or to OSIM). Ideally remove underscores from the X axis.}}
 			\label{fig:ApplicationProperties}
@@
 
-		To get more insights into the considered applications, we also look in to their sum of communication timings ($sum_comm$)  and sum of computation timings  ($sum_comp$) with respect to $OMIM$ in Figure~\ref{fig:ApplicationProperties}.
-It exhibits that HF is a communication intensive application and maximum 20\% overlap can be expected in the best scenario.
-While in CCSD , communications and computations are almost evenly distributed and 40-75\% communication-computation overlap is possible.
+		To get more insights into the considered workloads, we provide in Figure~\ref{fig:ApplicationProperties} information about
+		the instances we consider.
+For each instance, we compute the sum of communication times (\textit{sum comm}) and sum of computation times  (\textit{sum comp}), and normalize it relatively to the $OMIM$ value.
+Figure~\ref{fig:ApplicationProperties} also shows the maximum of both values, which is a lower bound on the possible makespan of a schedule for this instance, and their sum, which is an upper bound: this represents the makespan of the sequential schedule, obtained with zero overlap between computation and communication).
+We can see that HF is a communication intensive application and at most 20\% overlap can be expected in the best scenario.
+On the other hand, in the CCSD workload, communications and computations are almost evenly distributed and a more significant overlap is possible.
+
+		\subsection{Additional heuristics from previous work}
+
+		%%	\todo[inline]{Scheduled based on Gilmore-Gomory algorithm and its performance }
+		We also consider two other static heuristics for evaluation.
+The first heuristic is based on an algorithm, proposed by Gilmore and Gomory, to obtain the minimal cost sequence for a set of jobs~\cite{Gilmore-Gomory:1964}.
+This is a classic algorithm for 2-machine no-wait flow shop.
+In this algorithm, each job has a start and end state and a cost is associated to change the state.
+In our context, this cost can be seen as non-overlap time of computation for two adjacent tasks.
+Here is the main idea of this algorithm.
+Initially, a partial sequence of jobs is represented by a graph such that their overlap is maximum.
+Subsequently edges are greedily added to this graph to connect two components while minimizing the total non-overlap cost.
+When the graph  connected, an edge interchange mechanism is used to determine the sequence of jobs, which ensures that the sequence has minimal cost.
+More details can be found in the original paper~\cite{Gilmore-Gomory:1964} and our implementation is publicly availabl~\cite{gitworkrepo}.
+This algorithm does not take memory constraints into account and only provides the sequence of processing.
+We use this sequence with a memory capacity restriction just like for other static heuristcs, and we call this heuristic \textit{Gilmore-Gomory} ($GG$).
+
+		The second heuristic is based on the first fit algorithm for the bin packing problem.
+The idea of this heuristic is to identify groups of tasks which can fit in memory together, called \emph{bins}.
+In First-Fit, tasks are considered in an arbitrary order and added to the first bin in which they can fit.
+If no suitable bin is found then a new bin is created and this task is added to it.
+When all tasks have been assigned to bins, we consider the sequence made of all tasks from the first bin, then tasks for the second bin, and so on.
+We call this heuristic \textit{Bin Packing} ($BP$).
+
+		%%		\todo[inline]{increase font size in all plots, may be free scale-y}
+		%%	\todo[inline]{SKumar: decide metrics: ratio to optimal, percentage overlap, 100 - percentage non overlap}
+
+		\subsection{Experimental results}
+		We evaluate our scheduling heuristics for several memory capacities.
+From the obtained traces, we first determine the minimum requirement of the memory capacity $m_c$ to execute all tasks.
+Then we observe the behavior of all heuristics with memory capacity $m_c$ to $2m_c$, in increments of $0.125m_c$.
+Our performance metric is the ratio to optimal $r$: if heuristic $H$ has makespan $M_H$ on an instance, and the optimal makespan for the infinite memory case is $OMIM$, then $r(H)=\frac{M_H}{OMIM}$ (lower values are better).
+This ratio is at least $1$, and values close to $1$ indicate a well-suited  heuristic which achives maximum possible communication-computation.
+
+		Figures ~\ref{fig:ratio_to_optimal_hf} and ~\ref{fig:ratio_to_optimal_ccsd} show the distribution of the performance of each heuristic for all considered memory capacities, where plots are categorized by memory capacities.
+For each memory capacity and each heuristic, the box on the plot displays the median, first and last quartile, and the whiskers indicate minimum and maximum values, with outliers are shown by black dots.
+		\subsection{HF Performance}	
+		%%	\begin{figure*}[htb]
+		%%		\includegraphics[scale=0.25]{./results/plots/ratio_to_optimal_selected_hf.pdf}
+		%%		\caption{Comparison of different heuristics for HF.}
+		%%		\label{fig:ratio_to_optimal_hf}
+		%%	\end{figure*}
+		\begin{figure*}[htb]
+			\includegraphics[scale=0.5]{./all-binpack/ratio_to_optimal_selected_hf.pdf}
+			\caption{Comparison of different heuristics for HF.\todo[inline]{LED: Wouldn't it be easier to read if facet labels were expressed as ratios of $m_c$ ($1$, $1.125$, $1.25$, ...) instead of absolute values?.
+Here also, ylab(``Ratio to optimal'')}}
+			\label{fig:ratio_to_optimal_hf}
+		\end{figure*}
+
+		As indicated above, HF tasks operate on less heterogeneous tiles, this is also noticeable in Figure~\ref{fig:ratio_to_optimal_hf}.
+All heuristics depict similar behavior for minimum memory capacity $m_c$ and increasing the memory capacity slightly does not change the performance of all heuristics.
+As memory capacity is increased further, dynamic variants of heuristics start performing better.
+For the moderate memory capacities (close to $2m_c$), static order with dynamic correction variants outperform others.
+$GG$ heuristic does not achieve good performance, because its task sequence is obtained considering no extra memory is available\todo{you mean infinite memory?}, but is then applied in a different scenario where memory is limited.
+Suprisingly, the $BP$ heuristic which considers only memory constraint obtains good performance for a static heuristic, but is outperformed by more dynamic approaches.
+
+		\begin{figure}[htb]
+			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_hf-best.pdf}
+			\caption{Comparision of best variants of all categories for HF.\todo[inline]{LED: I still believe you should plot the actual ratio $r$ and not $1/r$.
+Since I am not sure how to redo the plots I will let you do it.
+Also ylab(``Ratio to optimal'') please (or more explicitley, to OSIM?).
+And make sure to write ``Best static'' and remove underscores.
+You can use plyr::revalue for that.} }
+			\label{fig:ratio_to_optimal_best_hf}
+		\end{figure}
+
+		Figure~\ref{fig:ratio_to_optimal_best_hf} shows the performance comparison of the best variant in each category, in addition to the \textit{order of submission} ($OS$) strategy which orders tasks in the (arbitrary) order in which they are given.
+Static strategies are expected to perform better when there is not any memory capacity restriction, and indeed this plot shows that static strategies face capacity bottleneck and underperform with limited memory.
+Dynamic strategies achieve better performance with limited memory capacity, and static order with dynamic correction strategies are suitable for scenarios with moderate memory capacity.\todo[inline]{LED: I do not understand, on Figure~\ref{fig:ratio_to_optimal_best_hf} it seems that \textit{static dynamic best} is always the best option.}
+
+		\subsection{CCSD Performance}
+
+		%%	\begin{figure*}[htb]
+		%%		\includegraphics[scale=0.25]{./results/plots/ratio_to_optimal_selected_ccsd.pdf}
+		%%		\caption{Comparison of different heuristics for CCSD.}
+		%%		\label{fig:ratio_to_optimal_ccsd}
+		%%	\end{figure*}
+
+		\begin{figure*}[htb]
+			\includegraphics[scale=0.5]{./all-binpack/ratio_to_optimal_selected_ccsd.pdf}
+			\caption{Comparison of different heuristics for CCSD.}
+			\label{fig:ratio_to_optimal_ccsd}
+		\end{figure*}
+
+		The CCSD application operates on tasks of different sizes, hence different heuristics exhibit distinct behaviors even at minimum memory capacity $m_c$.
+Heterogeneity favors dynamic strategies, as can be seen by the fact that both dynamic and static order with dynamic correction based strategies perform better than static based strategies.
+Similar to HF, static order with dynamic corrections based strategies outperform others as memory capacity becomes moderate.
+
+		\begin{figure}[htb]
+			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_ccsd-best.pdf}
+			\caption{Comparision of best variants of all categories for CCSD.}
+			\label{fig:ratio_to_optimal_best_ccsd}
+		\end{figure}
+
+		Figure~\ref{fig:ratio_to_optimal_best_ccsd} shows that best variants of dynamic and static order with dynamic corrections strategies achieve similar performance at minimum memory capacity $m_c$.
+But as memory capacity increases, heterogeneity allows static order with dynamic corrections based strategies to take advantage of static knowledge to get maximum overlap and dynamic correction to select another task in case of memory capacity limitation.
+Static strategies also start performing better at the end, which indicates that this application has potential for significant communication-computation overlap and pure dynamic strategies are unable to take this information into account while making scheduling decisions.
 
 		\subsection{Scheduling in Batches}
-		In most applications, scheduler may only observe a limited batch of independent tasks.
-Therefore we organize tasks of each trace file in the batch of 100.
-Last group may have less than 100 tasks.
-We apply each heuristic on each group consequently.
-Figure~\ref{fig:best_variants_batch} shows performance of the best variants of all categories for both applications.
-The plots exhibit behavior similar to Figures~\ref{fig:ratio_to_optimal_best_hf} and ~\ref{fig:ratio_to_optimal_best_ccsd}, static order with dynamic correction variants attain maximum communication-computation overlap and outperform other heuristics.
+		In most applications, the runtime scheduler may only observe a limited batch of independent tasks.
+Therefore we organize tasks of each trace file in batches of 100 (the last batch may have less than 100 tasks).
+We apply each heuristic on each group independently.
+Figure~\ref{fig:best_variants_batch} shows the performance of the best variants of each category for both applications.
+The plots exhibit behavior similar to Figures~\ref{fig:ratio_to_optimal_best_hf} and~\ref{fig:ratio_to_optimal_best_ccsd}: static order with dynamic correction variants attain maximum communication-computation overlap and outperform other heuristics.
 		%%		\todo[inline]{SKumar:combine both plots}
@@
 			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_batch-best.pdf}
-			\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
+			\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.\todo[inline]{LED: Here also I believe you should plot the actual ratio $r$ and not $1/r$.}}
 			\label{fig:best_variants_batch}
@@
 We show that determining the order of data transfers is an NP complete problem.
-We proposed several data transfer heuristics and evaluated them on two molecular chemistry kernels, HF and CCSD.
-Our results show that some of our heuristics achieve significant overlap and perform very close to the lower bound of makespan.
+We propose several data transfer heuristics and evaluate them on two molecular chemistry kernels, HF and CCSD.
+Our results show that some of our heuristics achieve significant overlap and perform very close to the makespan lower bound.
 We plan to evaluate our strategies on different applications coming from multiple domains.
 We also plan to study the behavior of our strategies in the context of overlapping CPU-GPU communications with computations.
-A runtime system aims at exposing different heuristics, to maximize the communication-computation overlap, at developer level and automatically selecting the best one is currently underway.
+A runtime system aiming at exposing different heuristics to maximize the communication-computation overlap at the developer level and automatically selecting the best one is currently underway.
 
@@
 			We are grateful to Ajay Panyala for his help to run NWChem on Cascade machine.
-			Identification of funding sources and other support, and thanks to individuals and groups that assisted in the research and the preparation of the work should be included in an acknowledgment section, which is placed just before the reference section in your document.
+This material is based upon work supported by the U.S.
+Department of Energy, Office of Science, Office of Advanced Scientific Computing Research .......
+			%% 			Identification of funding sources and other support, and thanks to individuals and groups that assisted in the research and the preparation of the work should be included in an acknowledgment section, which is placed just before the reference section in your document.
 

### 2019-04-11 ICPP-19/communications.tex
minor changes

@@
 
-	\renewcommand{\shortauthors}{Trovato and Tobin, et al.}
+	\renewcommand{\shortauthors}{Kumar and Eyraud-Dubois, et al.}
 
@@
 In this paper, we consider the problem of deciding the order of data transfers between two memory nodes for a set of independent tasks with the objective to minimize the makespan.
-We prove that with finite memory capacity, obtaining the optimal order of data transfers is an NP-complete problem.
+We prove that with limited memory capacity, obtaining the optimal order of data transfers is an NP-complete problem.
 We propose several heuristics for this problem and provide details about their favorable situations.
@@
 Indeed, there are several challenges that come into picture.
-First, every architecture provides its own efficiency and interface.
+First, every architecture provides its own efficacy and interface.
 Therefore, a steep learning curve is required for programmers to take good utilization of all resources.
@@
 Our proof is inspired from work by~\cite{Papadimitriou:1980:FSL:322203.322213}, which applies a similar technique for 2-machine flowshop problem with bounded capacity.
-The main difference between both approaches is that they consider that all tasks have the same occupation on the second machine) and that the memory occupation starts when the second machine starts working.
+The main difference between both approaches is that they consider all tasks have the same occupation on the second machine and the memory occupation starts when the processing finishes on the first machine.
 On the contrary, our approach is designed for tasks appearing in scientific workloads whose memory requirements are highly irregular and we consider that memory is acquired before starting the data transfer on communication resource.
@@
 Many static and dynamic strategies have been proposed and analyzed for scheduling tasks on heterogeneous resources~\cite{heft-Topcuoglu,hipc16multiresource,ipdps16starpu}.
-There is also a number of studies in the direction of task scheduling with the emphasis of improving locality and minimizing the communication cost~\cite{starpu,heft-Topcuoglu}.
+There is also a number of studies in the direction of task scheduling with the emphasis on improving locality and minimizing the communication cost~\cite{starpu,heft-Topcuoglu}.
 Stanisic et.
@@
 	communication at a time, and $P$ can only process one task at
-	a time. A task uses an amount of memory in memory $M$ from the
+	a time. A task uses an amount of memory in  $M$ from the
 	start of its communication to the end of its computation.
@@
 	resources. A schedule is feasible if for every time $t$, the
-	amount of memory required by tasks such that $\scomm(i) \leq t
+	amount of memory required by all tasks such that $\scomm(i) \leq t
 	\leq \scomp(i) + COMP_i$ is not more than the memory capacity
-	$C$. For simplicity, we assume in all of this paper that the
+	$C$. 
+	\todo[inline]{SKumar: We do not need this assumption everywhere. CommVolume=CommTime is not true for experimental section. We used this assumption only in NP-hard proof.}
+	For simplicity, we assume in all of this paper that the
 	amount of memory required by a task is proportional to its
@@
 This optimal value indicates a lower bound on the makespan of the constrained case.
-We use denote this value with $optimal\_ \allowbreak makespan\_  \allowbreak infinite\_  \allowbreak memory$ ($OMIM$).
+We denote this value with $optimal\_ \allowbreak makespan\_  \allowbreak infinite\_  \allowbreak memory$ ($OMIM$).
 In the present Section, we propose different heuristics for the limited memory case, and we assess their efficiency with respect to this lower bound in Section~\ref{sec:exp}.
@@
 	\subsection{Static Ordering}
-	In this class of strategies, we compute the order of processing in advance based on criteria such as communication time, compute time and accelerated tasks.
+	In this class of strategies, we compute the order of processing in advance based on criteria such as communication time and compute time.
 After computing the order, we follow the same order on computation and communication resources and make sure that the memory constraint is respected at each point in the schedule.
@@
 
-	In order to highlight the different behavior of these static strategies, we propose on Table~\ref{tab:staticOrderExample} an example instance, and on Figure~\ref{fig:staticOrderExample} the corresponding schedules for all these heuristics.
+	In order to highlight the different behaviors of these static strategies, we propose on Table~\ref{tab:staticOrderExample} an example instance, and on Figure~\ref{fig:staticOrderExample} the corresponding schedules for all these heuristics.
 
@@
 For example, if the selection criteria is to choose a highly compute intensive task, then we compute the ratio of compute time and communication time for all tasks, and we select the task which fit in the currently available memory and whose ratio is maximum (ties are broken arbitrarily).
+If no task satisfies the selection criteria thee we leave the resource idle at that point and proceed to the next event point.
 We also ensure that the order on both resources is the same, by ordering tasks on the computing resource accordingly.
 
-	\todo[inline]{LED: I added this part ``among those which fit in memory'', is it correct?}
-	\todo[inline]{LED: What happens if no task fit in memory?}
+%%	\todo[inline]{LED: I added this part ``among those which fit in memory'', is it correct? SKumar: Yes, you are correct.}
+%%	\todo[inline]{LED: What happens if no task fit in memory? Skumar: look at the next event point :)}
 
@@
 	In all strategies, the initial order is obtained by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}.
-.
 We define the following heuristics based on how we select a task from the set of tasks which fit in memory.
-	\todo[inline]{LED: What happens if no task fit in memory?}
+If not any task fits in the memory then we leave the resource idle and forward to the next event point.
+%%	\todo[inline]{LED: What happens if no task fit in memory?}
 
@@
 Figure~\ref{fig:iterativeLpSolution} shows the comparison of different heuristics with MILP based heuristic for various memory capacities of a single trace file.
+		\todo[inline]{SKumar: Figure~\ref{fig:iterativeLpSolution} would be removed and I will redraw this or similar figure for extended version}
 		\begin{figure}[htb]
@@
 
-		Here moderate memory capacity refers to the case where memory is limited but close to the maximum memory requirement of the considered application\todo[inline]{total memory requirement of all tasks?}.
+		Here moderate memory capacity refers to the case where memory is limited but close to the total memory requirement of all tasks in $OMIM$.
 We can clearly observe the favorable scenarios for a few heuristics in Figures~\ref{fig:ratio_to_optimal_hf} and ~\ref{fig:ratio_to_optimal_ccsd}.
@@
 CCSD has significant percentage of both types of tasks, therefore $OOLCMR$ and $OOSCMR$ heuristics performance is very close to optimal in moderate memory cases.
+		\todo[inline]{Skumar: Initially I placed this table after results.
+Then I realized that this is our hypothesis not conclusion.
+Only few favorable scenarios are matched with results.
+We do not have enough results to show favorable scenarios for all of them.}
 		\todo[inline]{LED: Since this is based on experimental results, should this go to a Section 5.5 or 5.6?}
@@
 
-		We consider a machine called Cascade\todo{cite or url?}, available at PNNL, for our experiments.
+		We consider a machine called Cascade~\cite{Cascade}, available at PNNL, for our experiments.
 We obtain traces by running two molecular chemistry applications, double precision version of Hartree-Fock (HF) and Coupled Cluster Single Double (CCSD) of NWChem\todo{cite or url} package on 10 nodes of this machine.
 Each node is composed of 16 Intel Xeon E5-2670 cores.
-NWChem takes advantages of a Partitioned Global Address Space Programming Model called Global Arrays (GA)\todo{cite or url?} to use shared-memory programming APIs on distributed memory computers.
+NWChem takes advantages of a Partitioned Global Address Space Programming Model called Global Arrays (GA)~\cite{GlobalArray} to use shared-memory programming APIs on distributed memory computers.
 GA dedicates one core of each node to handle other cores, hence we can view a node as being composed of 15 computational cores.
@@
 
+		\todo[inline]{SKumar: will do}
 		\begin{figure}[htb]
@@
 For each instance, we compute the sum of communication times (\textit{sum comm}) and sum of computation times  (\textit{sum comp}), and normalize it relatively to the $OMIM$ value.
-Figure~\ref{fig:ApplicationProperties} also shows the maximum of both values, which is a lower bound on the possible makespan of a schedule for this instance, and their sum, which is an upper bound: this represents the makespan of the sequential schedule, obtained with zero overlap between computation and communication).
+Figure~\ref{fig:ApplicationProperties} also shows the maximum of both values, which is a lower bound on the possible makespan of a schedule for this instance, and their sum, which is an upper bound: this represents the makespan of the sequential schedule, obtained with zero overlap between computation and communication.
 We can see that HF is a communication intensive application and at most 20\% overlap can be expected in the best scenario.
@@
 Subsequently edges are greedily added to this graph to connect two components while minimizing the total non-overlap cost.
-When the graph  connected, an edge interchange mechanism is used to determine the sequence of jobs, which ensures that the sequence has minimal cost.
-More details can be found in the original paper~\cite{Gilmore-Gomory:1964} and our implementation is publicly availabl~\cite{gitworkrepo}.
+When the graph is  connected, an edge interchange mechanism is used to determine the sequence of jobs, which ensures that the sequence has minimal cost.
+More details can be found in the original paper~\cite{Gilmore-Gomory:1964} and our implementation is publicly available~\cite{gitworkrepo}.
 This algorithm does not take memory constraints into account and only provides the sequence of processing.
@@
 Our performance metric is the ratio to optimal $r$: if heuristic $H$ has makespan $M_H$ on an instance, and the optimal makespan for the infinite memory case is $OMIM$, then $r(H)=\frac{M_H}{OMIM}$ (lower values are better).
-This ratio is at least $1$, and values close to $1$ indicate a well-suited  heuristic which achives maximum possible communication-computation.
+This ratio is at least $1$, and a value close to $1$ indicates a well-suited  heuristic which achives maximum possible communication-computation overlap.
 
@@
 For the moderate memory capacities (close to $2m_c$), static order with dynamic correction variants outperform others.
-$GG$ heuristic does not achieve good performance, because its task sequence is obtained considering no extra memory is available\todo{you mean infinite memory?}, but is then applied in a different scenario where memory is limited.
-Suprisingly, the $BP$ heuristic which considers only memory constraint obtains good performance for a static heuristic, but is outperformed by more dynamic approaches.
+$GG$ heuristic does not achieve good performance, because its task sequence is obtained considering no extra memory is available, but is then applied in a different scenario where memory is limited.
+Surprisingly, the $BP$ heuristic which considers only memory constraint obtains good performance for a static heuristic, but is outperformed by more dynamic approaches.
+%%		\todo{you mean infinite memory? SKumar: GG is classic in no-wait (or no buffer) 2-macine flowshop}
 
@@
 Static strategies are expected to perform better when there is not any memory capacity restriction, and indeed this plot shows that static strategies face capacity bottleneck and underperform with limited memory.
-Dynamic strategies achieve better performance with limited memory capacity, and static order with dynamic correction strategies are suitable for scenarios with moderate memory capacity.\todo[inline]{LED: I do not understand, on Figure~\ref{fig:ratio_to_optimal_best_hf} it seems that \textit{static dynamic best} is always the best option.}
+Dynamic strategies achieve better performance with limited memory capacity, and static order with dynamic correction strategies are suitable for scenarios with moderate memory capacity.
+
+		\todo[inline]{LED: I do not understand, on Figure~\ref{fig:ratio_to_optimal_best_hf} it seems that \textit{static dynamic best} is always the best option.}
+		\todo[inline]{SKumar: If you look at Figure~\ref{fig:ratio_to_optimal_best_hf} carefully,  in the beginning dynamics variants outperform others.
+This behavior is easily noticeable in Figure~\ref{fig:ratio_to_optimal_hf}.
+}
 
@@
 
-		Figure~\ref{fig:ratio_to_optimal_best_ccsd} shows that best variants of dynamic and static order with dynamic corrections strategies achieve similar performance at minimum memory capacity $m_c$.
+		Figure~\ref{fig:ratio_to_optimal_best_ccsd} shows that best variants of dynamic and static order with dynamic correction strategies achieve similar performance at minimum memory capacity $m_c$.
 But as memory capacity increases, heterogeneity allows static order with dynamic corrections based strategies to take advantage of static knowledge to get maximum overlap and dynamic correction to select another task in case of memory capacity limitation.
@@
 We propose several data transfer heuristics and evaluate them on two molecular chemistry kernels, HF and CCSD.
-Our results show that some of our heuristics achieve significant overlap and perform very close to the makespan lower bound.
+Our results show that some of our heuristics achieve significant overlap and perform very close to the lower bound.
 We plan to evaluate our strategies on different applications coming from multiple domains.
@@
 
-			We are grateful to Ajay Panyala for his help to run NWChem on Cascade machine.
+			We are grateful to Ajay Panyala for his help in installation of  NWChem on Cascade machine and providing internal details about the package and its inputs.
 This material is based upon work supported by the U.S.

### 2019-04-11 ICPP-19/communications.tex
redrawing plots

@@
 	$C$. 
-	\todo[inline]{SKumar: We do not need this assumption everywhere. CommVolume=CommTime is not true for experimental section. We used this assumption only in NP-hard proof.}
+	\todo[inline]{SKumar: We do not need this assumption throughout the paper. CommVolume=CommTime is not true for experimental section. We used this assumption only in NP-hard proof for simplicity.}
 	For simplicity, we assume in all of this paper that the
@@
 
-		\todo[inline]{SKumar: will do}
 		\begin{figure}[htb]
@@
 			\includegraphics[scale=0.5]{./results/plots/application_properties.pdf}
-			\caption{HF and CCSD tasks characteristics.\todo[inline]{ylab(``Ratio to optimal'') (or to OSIM). Ideally remove underscores from the X axis.}}
+			\caption{HF and CCSD tasks characteristics.}
+%%				\todo[inline]{ylab(``Ratio to optimal'') (or to OSIM). Ideally remove underscores from the X axis.}
 			\label{fig:ApplicationProperties}
@@
 			\includegraphics[scale=0.5]{./all-binpack/ratio_to_optimal_selected_hf.pdf}
-			\caption{Comparison of different heuristics for HF.\todo[inline]{LED: Wouldn't it be easier to read if facet labels were expressed as ratios of $m_c$ ($1$, $1.125$, $1.25$, ...) instead of absolute values?.
-Here also, ylab(``Ratio to optimal'')}}
+			\caption{Comparison of different heuristics for HF.\todo[inline]{LED: Wouldn't it be easier to read if facet labels were expressed as ratios of $m_c$ ($1$, $1.125$, $1.25$, ...) instead of absolute values?
+Skumar: It'll provide a nice view but $m_c$ values of both experiments are quite different.
+In that case, we have to explicitly mention $m_c$ values.}}
 			\label{fig:ratio_to_optimal_hf}
@@
 		\begin{figure}[htb]
-			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_hf-best.pdf}
-			\caption{Comparision of best variants of all categories for HF.\todo[inline]{LED: I still believe you should plot the actual ratio $r$ and not $1/r$.
+%%			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_hf-best.pdf}
+			\includegraphics[scale=0.5]{./results/plots/ratio_to_optimal_hf-best.pdf}
+			\caption{Comparision of best variants of all categories for HF.}
+%%			\todo[inline]{LED: I still believe you should plot the actual ratio $r$ and not $1/r$.
 Since I am not sure how to redo the plots I will let you do it.
@@
 And make sure to write ``Best static'' and remove underscores.
-You can use plyr::revalue for that.} }
+You can use plyr::revalue for that.}
 			\label{fig:ratio_to_optimal_best_hf}
@@
 		\begin{figure}[htb]
-			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_ccsd-best.pdf}
+%%			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_ccsd-best.pdf}
+			\includegraphics[scale=0.5]{./results/plots/ratio_to_optimal_ccsd-best.pdf}
 			\caption{Comparision of best variants of all categories for CCSD.}
@@
 		\begin{figure*}[htb]
-			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_batch-best.pdf}
-			\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.\todo[inline]{LED: Here also I believe you should plot the actual ratio $r$ and not $1/r$.}}
+%%			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_batch-best.pdf}
+			\includegraphics[scale=0.5]{./results/plots/ratio_to_optimal_batch-best.pdf}
+			\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
+%%			\todo[inline]{LED: Here also I believe you should plot the actual ratio $r$ and not $1/r$.}
 			\label{fig:best_variants_batch}

### 2019-04-11 ICPP-19/all-binpack/ratio_to_optimal.R

@@ -8,7 +8,9 @@ dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
 dftest[,2:6]<-NULL
 dftestMelted<-melt(dftest, "capacity")
 names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
-p<-ggplot(dftestMelted, aes(x=Heuristic, y=ratio_to_optimal, color=Heuristic)) + geom_boxplot(outlier.color="black") + facet_wrap(~capacity, ncol=4)  + theme(axis.ticks = element_blank(), axis.text.x = element_blank()) + xlab("")
+p<-ggplot(dftestMelted, aes(x=Heuristic, y=ratio_to_optimal, color=Heuristic)) + geom_boxplot(outlier.color="black") +
+facet_wrap(~capacity, ncol=4)  + theme(axis.ticks = element_blank(), axis.text.x = element_blank()) + xlab("") +
+ylab("Ratio to Optimal")
 #p <- p + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Ratio to Optimal")
 return (p)
 }

### 2019-04-11 ICPP-19/results/scripts/insights.R

@@ -27,8 +27,10 @@ get_melted_data_frame<-function(file_name)
 {
 library(reshape2)
 dftest<-read.table(file_name, header=T)
-colnames(dftest)[colnames(dftest) == "sum_comm_comp" ] <- "sum_comm+sum_comp"
-colnames(dftest)[colnames(dftest) == "max.sum_comm.sum_comp." ] <- "max(sum_comm,sum_comp)"
+colnames(dftest)[colnames(dftest) == "sum_comm" ] <- "sum comm"
+colnames(dftest)[colnames(dftest) == "sum_comp" ] <- "sum comp"
+colnames(dftest)[colnames(dftest) == "sum_comm_comp" ] <- "sum comm + sum comp"
+colnames(dftest)[colnames(dftest) == "max.sum_comm.sum_comp." ] <- "max(sum comm, sum comp)"
 dftest[,1:ncol(dftest)]<-dftest[,1:ncol(dftest)]/dftest[,5]
 dftest[,5]<-NULL
 dftestMelted<-melt(dftest)
@@ -43,6 +45,7 @@ dfMelted <- rbind(dfMelted1, dfMelted2)
 library(ggplot2)
 p<-ggplot(dfMelted, aes(x=Parameter, y=ratio_to_optimal, color=Parameter))  + geom_boxplot(outlier.color="black") + geom_hline(yintercept=1, linetype="dashed", color = "red") +
           facet_wrap(~application) + scale_y_continuous(breaks=seq(0.0, 2.0, 0.5), limits=c(0, 2)) +
-          theme(legend.position='none', axis.text.x = element_text(angle = 45, hjust=1, vjust = 1)) + xlab(" ")
+          theme(legend.position='none', axis.text.x = element_text(angle = 45, hjust=1, vjust = 1)) + xlab(" ") +
+          ylab("Ratio to Optimal")
 ggsave(file="application_properties.pdf", p, width=7, height=4)
 

### 2019-04-11 ICPP-19/results/scripts/ratio_to_optimal-best.R

@@ -1,0 +1,30 @@
+#!/usr/bin/env Rscript
+ratio_to_optimal_best_func <-function(file_name)
+{
+library(ggplot2)
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
+
+dftest[,8]<-NULL
+dftest[,c(2:6)]<-NULL
+dftest$"Best Static"<-do.call('pmin', c(dftest[,3:7]))
+dftest$"Best Dynamic" <-do.call('pmin', c(dftest[,8:10]))
+dftest$"Best Static Dynamic"<-do.call('pmin', c(dftest[,11:13]))
+dftest<-dftest[,c(1,2,14:16)]
+dftestMelted<-melt(dftest, "capacity")
+names(dftestMelted)<-c("Capacity", "Heuristic", "ratio_to_optimal")
+#p<-ggplot(dftestMelted, aes(x=jitter(capacity), y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth()
+#p<-ggplot(dftestMelted, aes(x=Capacity, y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth(method="loess")
+p<-ggplot(dftestMelted, aes(x=Capacity, y=ratio_to_optimal, color=Heuristic))  + geom_smooth(method="loess")
+#p<-p + ylab("inverse(ratio_to_optimal)") + theme(plot.title = element_text(hjust = 0.5), legend.position="bottom") +  ggtitle("Performance With Best of all categories")
+p<-p + ylab("Ratio to Optimal") + xlab ("Memory Capacity") + theme(legend.position="bottom")
+return (p)
+}
+
+p<-ratio_to_optimal_best_func('all_results_hf.txt')
+ggsave(file="ratio_to_optimal_hf-best.pdf", p + xlim(NA, 340000), width=6.5, height=5)
+
+p<-ratio_to_optimal_best_func('all_results_ccsd.txt')
+ggsave(file="ratio_to_optimal_ccsd-best.pdf", p, width=6.5, height=5)
+

### 2019-04-11 ICPP-19/results/scripts/ratio_to_optimal_batch-best.R

@@ -1,0 +1,55 @@
+#!/usr/bin/env Rscript
+ratio_to_optimal_best_func <-function(file_name)
+{
+library(ggplot2)
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
+
+dftest[,c(2:6)]<-NULL
+dftest$static_best<-do.call('pmin', c(dftest[,3:7]))
+dftest$dynamic_best<-do.call('pmin', c(dftest[,8:10]))
+dftest$static_dynamic_best<-do.call('pmin', c(dftest[,11:13]))
+dftest<-dftest[,c(1,2,14:16)]
+dftestMelted<-melt(dftest, "capacity")
+names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
+p<-ggplot(dftestMelted, aes(x=capacity, y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth(method="loess")
+p<-p + ylab("inverse(ratio_to_optimal)") + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Performance With Best of all categories")
+return (p)
+}
+#p<-ratio_to_optimal_best_func('results_batch_hf.txt')
+#ggsave(file="ratio_to_optimal_hf_batch-best.pdf", p, width=23.6, height=13.4)
+#
+#p<-ratio_to_optimal_best_func('results_batch_ccsd.txt')
+#ggsave(file="ratio_to_optimal_ccsd_batch-best.pdf", p, width=23.6, height=13.4)
+
+get_melted_data_frame <-function(file_name)
+{
+library(ggplot2)
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
+
+dftest[,c(2:6)]<-NULL
+dftest$"Best Static"<-do.call('pmin', c(dftest[,3:7]))
+dftest$"Best Dynamic"<-do.call('pmin', c(dftest[,8:10]))
+dftest$"Best Static Dynamic"<-do.call('pmin', c(dftest[,11:13]))
+dftest<-dftest[,c(1,2,14:16)]
+dftestMelted<-melt(dftest, "capacity")
+names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
+return (dftestMelted)
+}
+
[…]

### 2019-04-11 ICPP-19/communications.tex
fixing MILP section

@@
 We also add the following constraints to help the solver: $\forall i, \forall j\ne i$, $a_{ij} + a_{ji}=1$, $b_{ij} + b_{ji} = 1$, $c_{ij} \le a_{ij}$, $c_{ij} \le b_{ij}$, and  $c_{ij} + c_{ji} \le 1$.
-The solver was unable to handle the number of variables required to solve this MILP at the scale of our interest.
-Hence, we solve the linear program iteratively for a small subset of size $k=3,4,5$: at the boundary of two iterations we fix the events (communication and computation) of an unfinished task started before the boundary point and consider other events flexible.
+The solver was unable to  solve this MILP at the scale of our interest in limited time.
+Hence, we solve the linear program iteratively for a small subset of size $k=3,4,5$: at the boundary of two iterations we fix the event (communication or computation) of an unfinished task started before the boundary point and consider other events flexible.
 The subsets are formed in the order in which tasks are submitted, which is arbitrary.
@@
 
-		\todo[inline]{SKumar: Move to an extended version and more clear about results and implementation}
-		Figure~\ref{fig:iterativeLpSolution} shows the performance of different heuristics with MILP based heuristics for various memory capacities of a single trace file.
-		%%	\subsection{MILP Based Strategy}
-		%%We use GLPK solver v4.65 to solve the MILP formulation described in Section~\ref{subsec:linearprogrammingformulation}.
+%%		\todo[inline]{SKumar: Move to an extended version and more clear about results and implementation}
+%%		Figure~\ref{fig:iterativeLpSolution} shows the performance of different heuristics with MILP based heuristics for various memory capacities of a single trace file.
+%%		%%	\subsection{MILP Based Strategy}
+%%		%%We use GLPK solver v4.65 to solve the MILP formulation described in Section~\ref{subsec:linearprogrammingformulation}.
 The solver was unable to handle number of variables required to solve MILP at the scale of our interest.
@@
 Figure~\ref{fig:iterativeLpSolution} shows the comparison of different heuristics with MILP based heuristic for various memory capacities of a single trace file.
-		\todo[inline]{SKumar: Figure~\ref{fig:iterativeLpSolution} would be removed and I will redraw this or similar figure for extended version}
-		\begin{figure}[htb]
-			\includegraphics[scale=0.5]{./results/makespan_with_lp.pdf}
-			\caption{Comparision of different heuristics with MILP solution based heuristic.\todo[inline]{LED: I understand that this figure will be removed?
+%%		\todo[inline]{SKumar: Figure~\ref{fig:iterativeLpSolution} would be removed and I will redraw this or similar figure for extended version}
+%%		\begin{figure}[htb]
+%%			\includegraphics[scale=0.5]{./results/makespan_with_lp.pdf}
+%%			\caption{Comparision of different heuristics with MILP solution based heuristic.\todo[inline]{LED: I understand that this figure will be removed?
 Otherwise, use aes(fill=) instead of aes(color=) to have color filled bars.}}
-			\label{fig:iterativeLpSolution}
-		\end{figure}
+%%			\label{fig:iterativeLpSolution}
+%%		\end{figure}
 

### 2019-04-11 ICPP-19/communications.tex
clean-up

@@
 
-	%%	\todo[inline]{SKumar: Modify both proofs }
 	\section{Data Transfer Problem Formulation}
@@
 	makespan of $S$, $\mu(S) \le L$?
-
-	%%	\todo[inline]{Mention that memory occupation of a task is the same as its communication time. Skumar: it is not required at all, but we use this for simplicity in Theorem~\ref{th:npComplete}}
-	%%	\todo[inline]{Mention that it is always best to use the same order on both machines.}
 
@@
 				\hline
-				%%				\multirow{2}{*}{Task} & Comm Time & \multirow{2}{*}{Comp Time}\\ 
-				%%				&=Comm Volume& \\ \hline
 				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
@@
 Hence, in this section, we obtain the orders by sorting tasks based on different combinations of communication and computation times.
-
-	%%%%name = "optimal_time_infinite_case";
-	%%%%string alg_name="order_of_optimal_strategy_infinite_memory";
-	%%%%string alg_name="increasing_order_of_communication_strategy";
-	%%%%string alg_name="decreasing_order_of_computation_strategy";
-	%%%%string alg_name="increasing_order_of_communication_plus_computation_strategy";
-	%%%%string alg_name="decreasing_order_of_communication_plus_computation_strategy";
-	%%%%string alg_name="optimal_order_infinite_memory_largest_communication\_task\_respects\_memory\_restriction";
-	%%%%string alg_name="optimal_order_infinite_memory_smallest_communication\_task\_respects\_memory\_restriction";
-	%%%%string alg_name="optimal_order_infinite_memory_maximum_accelerated\_task\_respects\_memory\_restriction";
 
@@
 	\subsection{Dynamic Selection}
-	%%%%string alg_name="largest_communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction";
-	%%%%string alg_name="smallest_communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction";
-	%%%%string alg_name="maximum_accelerated \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction";
-
 	Dynamic strategies are based on the following principle: when the communication resource is idle, a task is chosen based on a ranking criterion which differ depending on the heuristic, among those which fit in memory.
@@
 	\begin{enumerate}[label=\roman*)]
-		%%	\item $largest_communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$: We select a set of tasks which induce minimum idle time on compute channel.
-A task with the largest communication time is chosen from this set.
-Memory requirement of this task should not be more than presently available memory.
-		%%	\item $smallest_communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$: A task with the smallest communication time is chosen.
-Memory requirement of this task should not be more than presently available memory.
-		%%	\item $maximum_accelerated \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction$: We select a set of tasks which induce minimum idle time on compute channel.
-A task with the maximum ratio of compute time to communication time is chosen from this set.
-Memory requirement of this task should not be more than presently available memory.
-
 		\item \textit{largest communication task respects memory restriction} ($LCMR$): a task with the largest communication time is chosen. 
@@
 
-	%%\begin{figure}[htb]
-	%%
-	%%\includegraphics[scale=0.05]{Figs/dynamiSelectionSchedules}
-	%%\caption{Task set and schedules where orders are precomputed based on different heuristics.}
-	%%\label{fig:dynamicSelectionExample}
-	%%\end{figure}
-
 	We highlight the different dynamic heuristics with the instance described on Table~\ref{tab:dynamicSelectionExample} (these heuristics are too similar on the instance from the previous class), and Figure~\ref{fig:dynamicSelectionExample} shows the corresponding schedules.
@@
 This class of strategy takes advantage of static information in the form of precomputed order and dynamic corrections to minimize the idle time due to memory constraint.
-	%%%%alg_name="optimal_order_infinite_memory_largest_communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction";
-	%%%%string alg_name="optimal_order_infinite_memory_smallest_communication \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction";
-	%%%%string alg_name="optimal_order_infinite_memory_maximum_accelerated \_ \allowbreak task \_ \allowbreak respects \_ \allowbreak memory \_ \allowbreak restriction";
 
@@
 		\begin{table}[htb]
-			%%	\scriptsize
 			\begin{tabular}{|c|p{6.5cm}|}
@@
 		\label{sec:exp}
-
-		%%	\todo[inline]{Machine information and our model}
 		\subsection{Experimental Settings}
@@
 		We consider a machine called Cascade~\cite{Cascade}, available at PNNL, for our experiments.
-We obtain traces by running two molecular chemistry applications, double precision version of Hartree-Fock (HF) and Coupled Cluster Single Double (CCSD) of NWChem\todo{cite or url} package on 10 nodes of this machine.
+We obtain traces by running two molecular chemistry applications, double precision version of Hartree-Fock (HF) and Coupled Cluster Single Double (CCSD) of NWChem~\cite{NWChem} package on 10 nodes of this machine.
 Each node is composed of 16 Intel Xeon E5-2670 cores.
@@
 
-		%%		\begin{figure}[htb]
-		%%			%\begin{tabular}{c}
-		%%			\subfloat[HF workloads\label{fig:hfProperties}]{%
-		%%				\includegraphics[width=.45\linewidth]{./results/plots/application_properties_hf.pdf}
-		%%			}%\\
-		%%			\subfloat[CCSD workloads\label{fig:ccsdProperties}]{%
-		%%				\includegraphics[width=.45\linewidth]{./results/plots/application_properties_ccsd.pdf}
-		%%			}%\\
-		%%			%\end{tabular}
-		%%			\caption{HF and CCSD tasks characteristics.}
-		%%			\label{fig:ApplicationProperties}
-		%%		\end{figure}
-
 		\begin{figure}[htb]
@@
 		\end{figure}
-
-		%% 
-		%%\begin{figure}[htb]
-		%%	\centering
-		%%	\begin{subfigure}{.5\textwidth}
-		%%		\centering
-		%%		\includegraphics[width=.95\linewidth]{../ExperimentalResults/application_properties_hf.pdf}
-		%%		\caption{HF workloads}
-		%%		\label{fig:hfProperties}
-		%%	\end{subfigure}%
-		%%	\begin{subfigure}{.5\textwidth}
-		%%		\centering
-		%%		\includegraphics[width=.95\linewidth]{../ExperimentalResults/application_properties_ccsd.pdf}
-		%%		\caption{CCSD workloads}
-		%%		\label{fig:ccsdProperties}
-		%%	\end{subfigure}
-		%%	\caption{HF and CCSD tasks characteristics.}
-		%%	\label{fig:ApplicationProperties}
-		%%\end{figure}
 
@@
 
-		%%		\todo[inline]{increase font size in all plots, may be free scale-y}
-		%%	\todo[inline]{SKumar: decide metrics: ratio to optimal, percentage overlap, 100 - percentage non overlap}
-
 		\subsection{Experimental results}
@@
 		\subsection{HF Performance}	
-		%%	\begin{figure*}[htb]
-		%%		\includegraphics[scale=0.25]{./results/plots/ratio_to_optimal_selected_hf.pdf}
-		%%		\caption{Comparison of different heuristics for HF.}
-		%%		\label{fig:ratio_to_optimal_hf}
-		%%	\end{figure*}
 		\begin{figure*}[htb]
@@
 		\subsection{CCSD Performance}
-
-		%%	\begin{figure*}[htb]
-		%%		\includegraphics[scale=0.25]{./results/plots/ratio_to_optimal_selected_ccsd.pdf}
-		%%		\caption{Comparison of different heuristics for CCSD.}
-		%%		\label{fig:ratio_to_optimal_ccsd}
-		%%	\end{figure*}
-
 		\begin{figure*}[htb]
@@
 The plots exhibit behavior similar to Figures~\ref{fig:ratio_to_optimal_best_hf} and~\ref{fig:ratio_to_optimal_best_ccsd}: static order with dynamic correction variants attain maximum communication-computation overlap and outperform other heuristics.
-		%%		\todo[inline]{SKumar:combine both plots}
-
-		%%		
-		%%		\begin{figure*}[htb]
-		%%			\subfloat[Best variants of HF.\label{fig:hf_best_variants_batch}]{%
-		%%				\includegraphics[width=.45\linewidth]{./results/plots/inverse_ratio_to_optimal_hf_batch-best.pdf}
-		%%			}%\\
-		%%			\subfloat[Best variants of CCSD.\label{fig:ccsd_best_variants_batch}]{%
-		%%				\includegraphics[width=.45\linewidth]{./results/plots/inverse_ratio_to_optimal_ccsd_batch-best.pdf}
-		%%			}%\\
-		%%			\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
-		%%			\label{fig:best_variants_batch}
-		%%		\end{figure*}
 

### 2019-04-11 ICPP-19/communications.tex
rearranging few sections

@@
 	\begin{abstract}
+		\todo[inline]{Initial submission deadline: April 15}
 		With increasing complexity of hardwares, systems with different memory nodes are ubiquitous in high performance computing (HPC).
@@
 In this paper, we consider the problem of deciding the order of data transfers between two memory nodes for a set of independent tasks with the objective to minimize the makespan.
-We prove that with limited memory capacity, obtaining the optimal order of data transfers is an NP-complete problem.
+We prove that with limited memory capacity, obtaining the optimal order of data transfers is a NP-complete problem.
 We propose several heuristics for this problem and provide details about their favorable situations.
@@
 Second, scheduling is a well known NP-Complete optimization problem, and hybrid and distributed resources make this problem harder (we refer ~\cite{webpagescheduling} for a survey on the complexity of scheduling problems and ~\cite{bleuse2015scheduling} for a recent survey in the case of hybrid nodes).
-Third, due to shared buses and parallel resources, it is challenging to obtain a precise model based on prediction of computation and communication timings.
+Third, due to shared buses and parallel resources, it is challenging to obtain a precise model based on prediction of computation and communication times.
 Fourth, then number of architectures has increased drastically in recent years, therefore it is almost impossible to develop hand tuned optimized code for all these architectures.
@@
 In irregular applications, programmers do not know the precise structure of the task graphs in advance: tasks are added recursively based on certain sentinel constraints.
-For such applications, the runtime system sees a set of independent ready tasks and schedules them on different processing units.
+For such applications, the runtime system sees a set of independent tasks and schedules them on different processing units.
 It is extremely important for runtimes to decide the order of data transfers for these scheduled computations so as to maximize the overlap between computations and communications.
@@
 We mainly consider three categories of heuristics: static heuristics, dynamic heuristics and static heuristics with dynamic corrections.
-We evaluate our proposed strategies on two molecular chemistry kernels in Section~\ref{sec:exp}.
+Sections~\ref{sec:expSetting} describes our experimental setup and we evaluate our proposed strategies on two molecular chemistry kernels in Section~\ref{sec:expResults}.
 Our results show that static heuristics with dynamic corrections achieve good performance in most cases.
@@
 	The problem considered in this paper also can be viewed as a flow shop problem: the communication link can be seen as a processing resource, and each task needs to first be handled by the communication link and then by the computational resource.
-Communication and computation timings of a task can thus be considered as processing times on different machines.
+Communication and computation times of a task can thus be considered as processing times on different machines.
 Johnson has provided scheduling strategies for 2 and 3-machine flow shop problems with infinite memory capacity~\cite{johnson}.
@@
 
-	\todo[inline]{theoretical/performance work on molecular chemistry kernels}
+%	\todo[inline]{theoretical/performance work on molecular chemistry kernels}
 
@@
 	$C$. 
-	\todo[inline]{SKumar: We do not need this assumption throughout the paper. CommVolume=CommTime is not true for experimental section. We used this assumption only in NP-hard proof for simplicity.}
-	For simplicity, we assume in all of this paper that the
-	amount of memory required by a task is proportional to its
-	communication time, and without loss of generality we consider
-	that memory size of a task is equal to its communication time.
-
-	We call a task $i$ compute intensive if $COMP_i \ge CM_i$, and
+%%	\todo[inline]{SKumar: We do not need this assumption throughout the paper. CommVolume=CommTime is not true for experimental section. We used this assumption only in NP-hard proof for simplicity.}
+%%	For simplicity, we assume in all of this paper that the
+%%	amount of memory required by a task is proportional to its
+%%	communication time, and without loss of generality we consider
+%%	that memory size of a task is equal to its communication time.
+
+ We assume through out the paper that communication time of a task is proportional to memory required by it, and follow \textit{Comm Time = Latency + (Comm Volume)/Bandwidth} model.
+
+	We call a task $i$ compute intensive if $COMP_i \ge COMM_i$, and
 	communication intensive otherwise.
@@
 
-		As \textit{Transfer time = Latency + (Data Volume)/Bandwidth}.
+%%		As \textit{Transfer time = Latency + (Data Volume)/Bandwidth}. 
 		For simplicity, we consider input transfer time is same as input data volume (i.e., \textit{Latency = 0} and \textit{Bandwidth = 1}).
@@
 		$K_i$. Since the memory capacity is $C=b'+3$, all tasks from a triplet
-		can fit in memory with a task $K_i$, and their duration are exactly
+		can fit in memory with a task $K_i$, and their durations are exactly
 		equal to the communication time of $K_i$. This schedule is thus
@@
 This optimal value indicates a lower bound on the makespan of the constrained case.
-We denote this value with $optimal\_ \allowbreak makespan\_  \allowbreak infinite\_  \allowbreak memory$ ($OMIM$).
-In the present Section, we propose different heuristics for the limited memory case, and we assess their efficiency with respect to this lower bound in Section~\ref{sec:exp}.
+We denote this value with \textit{optimal makespan infinite memory} ($OMIM$).
+In the present Section, we propose different heuristics for the limited memory case, and we assess their efficiency with respect to this lower bound in Section~\ref{sec:expResults}.
 
@@
 	\subsection{Static Ordering}
-	In this class of strategies, we compute the order of processing in advance based on criteria such as communication time and compute time.
+	In this class of strategies, we compute the order of processing in advance based on criteria such as communication time and computation time.
 After computing the order, we follow the same order on computation and communication resources and make sure that the memory constraint is respected at each point in the schedule.
@@
 	\begin{enumerate}[label=\roman*)]
-		\item \textit{Order  of  optimal strategy infinite memory} ($OOSIM$): This heuristic uses the order given by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}, but respects the memory constraint at each point in the schedule.
+		\item \textit{order  of  optimal strategy infinite memory} ($OOSIM$): This heuristic uses the order given by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}, but respects the memory constraint at each point in the schedule.
 Hence the makespan of this heuristic may be completely different from $OMIM$.
@@
 	Dynamic strategies are based on the following principle: when the communication resource is idle, a task is chosen based on a ranking criterion which differ depending on the heuristic, among those which fit in memory.
-For example, if the selection criteria is to choose a highly compute intensive task, then we compute the ratio of compute time and communication time for all tasks, and we select the task which fit in the currently available memory and whose ratio is maximum (ties are broken arbitrarily).
-If no task satisfies the selection criteria thee we leave the resource idle at that point and proceed to the next event point.
+For example, if the selection criteria is to choose a highly compute intensive task, then we compute the ratio of computation time and communication time for all tasks, and we select the task which induces minimum idle time on the computing resource, fit in the currently available memory and whose ratio is maximum (ties are broken arbitrarily).
+If no task fits in memory then we leave the resource idle at that point and proceed to the next event point.
 We also ensure that the order on both resources is the same, by ordering tasks on the computing resource accordingly.
@@
 		\item \textit{smallest communication task respects memory restriction} ($SCMR$): a task with the smallest communication time is chosen.
-		\item \textit{maximum accelerated task respects memory restriction} ($MAMR$): a task with the maximum ratio of compute time to communication time is chosen.
+		\item \textit{maximum accelerated task respects memory restriction} ($MAMR$): a task with the maximum ratio of computation time to communication time is chosen.
 	\end{enumerate}
@@
 		\end{tikzpicture}
-		\caption{ \label{fig:dynamicSelectionExample} Different dynamic heuristic schedules for a task set of Table~\ref{tab:dynamicSelectionExample} for a memory capacity of 6.}
+		\caption{ \label{fig:dynamicSelectionExample} Different dynamic heuristic schedules for a task set of Table~\ref{tab:dynamicSelectionExample} with a memory capacity of 6.}
 		%%		 Optimal schedule length is 23.
@@
 	In all strategies, the initial order is obtained by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}.
-We define the following heuristics based on how we select a task from the set of tasks which fit in memory.
-If not any task fits in the memory then we leave the resource idle and forward to the next event point.
+We define the following heuristics based on how we select a task from the set of tasks which fit in memory and induces minimum idle time on the computing resource.
+If no task fits in memory then we leave the resource idle and forward to the next event point.
 	%%	\todo[inline]{LED: What happens if no task fit in memory?}
@@
 		\item \textit{optimal order infinite memory smallest communication task respects memory restriction} ($OOSCMR$): a task with the smallest communication time is chosen from the set.
-		\item \textit{optimal order infinite memory maximum accelerated task respects memory restriction} ($OOMAMR$): a task  with the highest ratio of compute time to communication time is chosen from the set.
+		\item \textit{optimal order infinite memory maximum accelerated task respects memory restriction} ($OOMAMR$): a task  with the highest ratio of computation time to communication time is chosen from the set.
 	\end{enumerate}
@@
 		\begin{scope}[yshift=-2.75cm]
-		\schedule{36}{OOSCMR}{2,5,8,11,14,18,26,34}
+%%		\schedule{36}{OOSCMR}{2,5,8,11,14,18,26,34}
+%%		\taskB{0}
+%%		\taskE[3]{2}
+%%		\taskA[1]{5}
+%%		\taskD{9}
+%%		\taskC{18}
+%%		\end{scope}
+		\schedule{36}{OOSCMR}{2,5,8,11,15,19,27,35}
 		\taskB{0}
@@
 		\taskA[1]{5}
-		\taskD{9}
-		\taskC{18}
+		\taskD{10}
+		\taskC{19}
 		\end{scope}
@@
 		\end{tikzpicture}
-		\caption{ \label{fig:staticOrderDynamicCorrectionsExample} Different static order dynamic corrections heuristic schedules for a task set of Table~\ref{tab:staticOrderDynamicCorrectionsExample} .
+		\caption{ \label{fig:staticOrderDynamicCorrectionsExample} Different static order dynamic corrections heuristic schedules for a task set of Table~\ref{tab:staticOrderDynamicCorrectionsExample} with a memory capacity of 9.
 The $OMIM$ order is $BCDAE$.}
@@
 
+		\subsection{Additional heuristics from previous work}
+
+We also consider two other static heuristics for evaluation.
+The first heuristic is based on an algorithm, proposed by Gilmore and Gomory, to obtain the minimal cost sequence for a set of jobs~\cite{Gilmore-Gomory:1964}.
+This is a classic algorithm for 2-machine no-wait flow shop.
+In this algorithm, each job has a start and end state and a cost is associated to change the state.
+In our context, this cost can be seen as non-overlap time of computation for two adjacent tasks.
+Here is the main idea of this algorithm.
+Initially, a partial sequence of jobs is represented by a graph such that their overlap is maximum.
+Subsequently edges are greedily added to this graph to connect two components while minimizing the total non-overlap cost.
+When the graph is  connected, an edge interchange mechanism is used to determine the sequence of jobs, which ensures that the sequence has minimal cost.
+More details can be found in the original paper~\cite{Gilmore-Gomory:1964} and our implementation is publicly available~\cite{gitworkrepo}.
+This algorithm does not take memory constraints into account and only provides the sequence of processing.
+We use this sequence with a memory capacity restriction just like for other static heuristcs, and we call this heuristic \textit{Gilmore-Gomory} ($GG$).
+
+The second heuristic is based on the First-Fit algorithm for the bin packing problem.
+The idea of this heuristic is to identify groups of tasks which can fit in memory together, called \emph{bins}.
+In First-Fit, tasks are considered in an arbitrary order and added to the first bin in which they can fit.
+If no suitable bin is found then a new bin is created and this task is added to it.
+When all tasks have been assigned to bins, we consider the sequence made of all tasks from the first bin, then tasks for the second bin, and so on.
+We call this heuristic \textit{Bin Packing} ($BP$).
+
 	\subsection{Solving Linear Program Iteratively}
@@
 	We use a mixed integer linear program to obtain the order of communications and computations.
-Recall that $COMP_i$ and $COMM_i$ represent computation and communication timings of task $i$, and that the memory capacity of the target system is $C$.
+Recall that $COMP_i$ and $COMM_i$ represent computation and communication times of task $i$, and that the memory capacity of the target system is $C$.
 In the linear program formulation, $s_i$ and $e_i$ (resp.
@@
 	We compute various $lp.k$ values for different memory capacities and observe that most of the other heuristics perform better than this heuristic.
-Hence, we do not include this heuristic for the comparison in Section~{\ref{sec:exp}.
+Hence, we do not include this heuristic for the comparison in Section~{\ref{sec:expResults}.
 Performance comparison of different heuristics with MILP based heuristics is available in an extended version(cite).
@@
 		\subsection{Favorable Situations for Heuristics}
-		Based on the definition of proposed strategies and the optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}, we present favorable scenarios for different heuristics in Table~\ref{tab:heuristicsAndFavorableScenarios}.
+		Based on the definition of proposed strategies and the optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}, we present the scenarios which should be more favorable for each heuristic in Table~\ref{tab:heuristicsAndFavorableScenarios}.
 This allows programmers to use appropriate strategies to maximize communication-computation overlap for their applications.
+In this table, ``moderate memory capacity'' refers to the case where memory is constrained, but is close to the maximal memory requirement of the $OMIM$ schedule.
 
@@
 				$DOCCS$ & Moderate memory capacity and most tasks are highly communication intensive \\ \hline
-				$LCMR$ & Limited memory capacity and significant percentage of tasks with large communication timings are compute intensive\\ \hline
-				$SCMR$ & Limited memory capacity and significant percentage of tasks with small communication timings are compute intensive\\ \hline
+				$LCMR$ & Limited memory capacity and significant percentage of tasks with large communication times are compute intensive\\ \hline
+				$SCMR$ & Limited memory capacity and significant percentage of tasks with small communication times are compute intensive\\ \hline
 				$MAMR$ & Limited memory capacity and significant percentage of tasks of both types\\ \hline
@@
 
-		Here moderate memory capacity refers to the case where memory is limited but close to the total memory requirement of all tasks in $OMIM$.
-We can clearly observe the favorable scenarios for a few heuristics in Figures~\ref{fig:ratio_to_optimal_hf} and ~\ref{fig:ratio_to_optimal_ccsd}.
-For example, HF compute intensive tasks have small communication timings, hence $SCMR$ heuristic exhibits very good performance in limited memory cases.
-CCSD has significant percentage of both types of tasks, therefore $OOLCMR$ and $OOSCMR$ heuristics performance is very close to optimal in moderate memory cases.
-		\todo[inline]{Skumar: Initially I placed this table after results.
+		Some of these favorable scenarios can be clearly observed in our experimental results, on Figures~\ref{fig:ratio_to_optimal_hf} and~\ref{fig:ratio_to_optimal_ccsd}.
+For example, HF compute intensive tasks have small communication times, which explains why the $SCMR$ heuristic exhibits very good performance in limited memory cases.
+CCSD has significant percentage of both types of tasks, and indeed the performance of $OOLCMR$ and $OOSCMR$ is very close to optimality in moderate memory cases.
+%%		\todo[inline]{Skumar: Initially I placed this table after results.
 Then I realized that this is our hypothesis not conclusion.
@@
 We do not have enough results to show favorable scenarios for all of them.}
-		\todo[inline]{LED: Since this is based on experimental results, should this go to a Section 5.5 or 5.6?}
-
-		\section{Experimental Results}
-		\label{sec:exp}
+%%		\todo[inline]{LED: Ok. I did a rephrasing there to go in this direction, make sure it fits the message you wanted to say.}
+
 		\subsection{Experimental Settings}
+		\label{sec:expSetting}
 
@@
 CPU) ).
-		\todo[inline]{More about tiling}
+
+%%		\todo[inline]{More about tiling}
 		Both applications mainly perform two types of computations, tensor transpose and tensor contraction.
@@
 			\caption{HF and CCSD tasks characteristics.}
-%%				\todo[inline]{ylab(``Ratio to optimal'') (or to OSIM). Ideally remove underscores from the X axis.}
 			\label{fig:ApplicationProperties}
@@
 
-		\subsection{Additional heuristics from previous work}
-
-		%%	\todo[inline]{Scheduled based on Gilmore-Gomory algorithm and its performance }
-		We also consider two other static heuristics for evaluation.
-The first heuristic is based on an algorithm, proposed by Gilmore and Gomory, to obtain the minimal cost sequence for a set of jobs~\cite{Gilmore-Gomory:1964}.
-This is a classic algorithm for 2-machine no-wait flow shop.
-In this algorithm, each job has a start and end state and a cost is associated to change the state.
-In our context, this cost can be seen as non-overlap time of computation for two adjacent tasks.
-Here is the main idea of this algorithm.
-Initially, a partial sequence of jobs is represented by a graph such that their overlap is maximum.
-Subsequently edges are greedily added to this graph to connect two components while minimizing the total non-overlap cost.
-When the graph is  connected, an edge interchange mechanism is used to determine the sequence of jobs, which ensures that the sequence has minimal cost.
-More details can be found in the original paper~\cite{Gilmore-Gomory:1964} and our implementation is publicly available~\cite{gitworkrepo}.
-This algorithm does not take memory constraints into account and only provides the sequence of processing.
-We use this sequence with a memory capacity restriction just like for other static heuristcs, and we call this heuristic \textit{Gilmore-Gomory} ($GG$).
-
-		The second heuristic is based on the first fit algorithm for the bin packing problem.
-The idea of this heuristic is to identify groups of tasks which can fit in memory together, called \emph{bins}.
-In First-Fit, tasks are considered in an arbitrary order and added to the first bin in which they can fit.
-If no suitable bin is found then a new bin is created and this task is added to it.
-When all tasks have been assigned to bins, we consider the sequence made of all tasks from the first bin, then tasks for the second bin, and so on.
-We call this heuristic \textit{Bin Packing} ($BP$).
-
-		\subsection{Experimental results}
+		\section{Experimental Results}
+		\label{sec:expResults}
 		We evaluate our scheduling heuristics for several memory capacities.
@@
 			\includegraphics[scale=0.5]{./all-binpack/ratio_to_optimal_selected_hf.pdf}
-			\caption{Comparison of different heuristics for HF.\todo[inline]{LED: Wouldn't it be easier to read if facet labels were expressed as ratios of $m_c$ ($1$, $1.125$, $1.25$, ...) instead of absolute values?
-Skumar: It'll provide a nice view but $m_c$ values of both experiments are quite different.
-In that case, we have to explicitly mention $m_c$ values.}}
+			\caption{Comparison of different heuristics for HF with $m_c=..$.}
 			\label{fig:ratio_to_optimal_hf}
@@
 			\caption{Comparision of best variants of all categories for HF.}
-%%			\todo[inline]{LED: I still believe you should plot the actual ratio $r$ and not $1/r$.
-Since I am not sure how to redo the plots I will let you do it.
-Also ylab(``Ratio to optimal'') please (or more explicitley, to OSIM?).
-And make sure to write ``Best static'' and remove underscores.
-You can use plyr::revalue for that.}
 			\label{fig:ratio_to_optimal_best_hf}
@@
 Static strategies are expected to perform better when there is not any memory capacity restriction, and indeed this plot shows that static strategies face capacity bottleneck and underperform with limited memory.
-Dynamic strategies achieve better performance with limited memory capacity, and static order with dynamic correction strategies are suitable for scenarios with moderate memory capacity.
-
-		\todo[inline]{LED: I do not understand, on Figure~\ref{fig:ratio_to_optimal_best_hf} it seems that \textit{static dynamic best} is always the best option.}
-		\todo[inline]{SKumar: If you look at Figure~\ref{fig:ratio_to_optimal_best_hf} carefully,  in the beginning dynamics variants outperform others.
+Dynamic strategies achieve slightly better performance with limited memory capacity, but when memory capacity is larger, static order with dynamic correction strategies outperform all others.
+
+%%		\todo[inline]{SKumar: If you look at Figure~\ref{fig:ratio_to_optimal_best_hf} carefully,  in the beginning dynamics variants outperform others.
 This behavior is easily noticeable in Figure~\ref{fig:ratio_to_optimal_hf}.
 }
+%%		\todo[inline]{LED: Ok, I rephrased here a bit to mention this.}
 
@@
 			\includegraphics[scale=0.5]{./all-binpack/ratio_to_optimal_selected_ccsd.pdf}
-			\caption{Comparison of different heuristics for CCSD.}
+			\caption{Comparison of different heuristics for CCSD with $m_c=$.}
 			\label{fig:ratio_to_optimal_ccsd}
@@
 		The CCSD application operates on tasks of different sizes, hence different heuristics exhibit distinct behaviors even at minimum memory capacity $m_c$.
-Heterogeneity favors dynamic strategies, as can be seen by the fact that both dynamic and static order with dynamic correction based strategies perform better than static based strategies.
+Heterogeneity favors dynamic strategies, as can be seen by the fact that both dynamic and static order with dynamic corrections based strategies perform better than static based strategies.
 Similar to HF, static order with dynamic corrections based strategies outperform others as memory capacity becomes moderate.
@@
 Figure~\ref{fig:best_variants_batch} shows the performance of the best variants of each category for both applications.
-The plots exhibit behavior similar to Figures~\ref{fig:ratio_to_optimal_best_hf} and~\ref{fig:ratio_to_optimal_best_ccsd}: static order with dynamic correction variants attain maximum communication-computation overlap and outperform other heuristics.
+The plots exhibit behavior similar to Figures~\ref{fig:ratio_to_optimal_best_hf} and~\ref{fig:ratio_to_optimal_best_ccsd}: static order with dynamic corrections variants attain maximum communication-computation overlap and outperform other heuristics.
 
@@
 			\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
-%%			\todo[inline]{LED: Here also I believe you should plot the actual ratio $r$ and not $1/r$.}
 			\label{fig:best_variants_batch}
@@
 
-		In this paper, we consider the problem of deciding the order of data transfers between two memory nodes such that overlap of communication and computation is maximized.
+		In this paper, we consider the problem of deciding the order of data transfers between two memory nodes such that overlap of communications and computations is maximized.
 With Exascale computing, applications face bottlenecks due to communications.
-Hence, it is extremely important to achieve the maximum overlap of computation and communication in order to exploit the full potential of the system.
-We show that determining the order of data transfers is an NP complete problem.
+Hence, it is extremely important to achieve the maximum  communication-computation overlap in order to exploit the full potential of the system.
+We show that determining the order of data transfers is a NP complete problem.
 We propose several data transfer heuristics and evaluate them on two molecular chemistry kernels, HF and CCSD.
@@
 			We are grateful to Ajay Panyala for his help in installation of  NWChem on Cascade machine and providing internal details about the package and its inputs.
-This material is based upon work supported by the U.S.
-Department of Energy, Office of Science, Office of Advanced Scientific Computing Research .......
-			%% 			Identification of funding sources and other support, and thanks to individuals and groups that assisted in the research and the preparation of the work should be included in an acknowledgment section, which is placed just before the reference section in your document.
-
+This work was supported in part by the U.S.
+Department of Energy’s (DOE), Office of Science, Office of Advanced Scientific Computing Research, under awards 63823.
+Pacific Northwest National Laboratory is operated by Battelle for DOE under Contract DE-AC05-76RL01830.
 		\end{acks}

### 2019-04-12 ICPP-19/communications.tex
word rephrasing

@@
 		\todo[inline]{Initial submission deadline: April 15}
-		With increasing complexity of hardwares, systems with different memory nodes are ubiquitous in high performance computing (HPC).
+		With increasing complexity of hardwares, systems with different memory nodes are ubiquitous in High Performance Computing (HPC).
 It is paramount to develop strategies to overlap the data transfers between memory nodes with computations in order to exploit the full potential of these systems.
@@
 Stanisic et.
-al~\cite{luka-dmdar} proposed a heuristic to schedule tasks on a computing resource where most of its data is available.
+al~\cite{luka-dmdar} proposed a heuristic to schedule tasks on a computational resource where most of its data is available.
 A similar approach has been adopted by Agullo et.
@@
 
- We assume through out the paper that communication time of a task is proportional to memory required by it, and follow \textit{Comm Time = Latency + (Comm Volume)/Bandwidth} model.
+ We assume through out the paper that communication time of a task is proportional to memory required by it, and follow conventional \textit{Comm Time = Latency + (Comm Volume)/Bandwidth} model.
 
@@
 
-	When the computing resource has a very large memory, our problem
+	When the computational resource has a very large memory, our problem
 	becomes a classic 2-machine flowshop problem: communication time is
@@
 	Dynamic strategies are based on the following principle: when the communication resource is idle, a task is chosen based on a ranking criterion which differ depending on the heuristic, among those which fit in memory.
-For example, if the selection criteria is to choose a highly compute intensive task, then we compute the ratio of computation time and communication time for all tasks, and we select the task which induces minimum idle time on the computing resource, fit in the currently available memory and whose ratio is maximum (ties are broken arbitrarily).
+For example, if the selection criteria is to choose a highly compute intensive task, then we compute the ratio of computation time and communication time for all tasks, and we select a task with the maximum ratio among which induce minimum idle time on the computation resource and fit in the currently available memory.
 If no task fits in memory then we leave the resource idle at that point and proceed to the next event point.
-We also ensure that the order on both resources is the same, by ordering tasks on the computing resource accordingly.
+We also ensure that the order on both resources is the same, by ordering tasks on the computation resource accordingly.
+
+%%	If $COMM_A = 1, COMP_A=1, COMM_B=2, COMP_B=4$, then $MAMR$ heuristic first selects task $A$ (A induces less idle tim eon the computation resource).
 
@@
 	In all strategies, the initial order is obtained by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}.
-We define the following heuristics based on how we select a task from the set of tasks which fit in memory and induces minimum idle time on the computing resource.
+We define the following heuristics based on how we select a task from the set of tasks which fit in memory and induces minimum idle time on the computation resource.
 If no task fits in memory then we leave the resource idle and forward to the next event point.

### 2019-04-12 ICPP-19/communications.tex
minor

@@
 %%	\todo[inline]{SKumar: We do not need this assumption throughout the paper. CommVolume=CommTime is not true for experimental section. We used this assumption only in NP-hard proof for simplicity.}
-%%	For simplicity, we assume in all of this paper that the
-%%	amount of memory required by a task is proportional to its
-%%	communication time, and without loss of generality we consider
-%%	that memory size of a task is equal to its communication time.
-
- We assume through out the paper that communication time of a task is proportional to memory required by it, and follow conventional \textit{Comm Time = Latency + (Comm Volume)/Bandwidth} model.
-
+	For simplicity, we assume in all of this paper that the
+	amount of memory required by a task is proportional to its
+	communication time, and without loss of generality we consider
+	that memory size of a task is equal to its communication volume.
+
+%% We assume through out the paper that communication time of a task is proportional to memory required by it, and follow conventional \textit{Comm Time = Latency + (Comm Volume)/Bandwidth} model.
+%%	
 	We call a task $i$ compute intensive if $COMP_i \ge COMM_i$, and
@@
 
-%%		As \textit{Transfer time = Latency + (Data Volume)/Bandwidth}. 
+		As \textit{Transfer time = Latency + (Data Volume)/Bandwidth}.
 For simplicity, we consider input transfer time is same as input data volume (i.e., \textit{Latency = 0} and \textit{Bandwidth = 1}).
@@
 This work was supported in part by the U.S.
-Department of Energy’s (DOE), Office of Science, Office of Advanced Scientific Computing Research, under awards 63823.
+Department of Energy’s (DOE), Office of Science, Office of Advanced Scientific Computing Research, under award 63823.
 Pacific Northwest National Laboratory is operated by Battelle for DOE under Contract DE-AC05-76RL01830.

### 2019-04-12 ICPP-19/communications.tex
Citation indicating 3 Machine Flowshop is NP-complete

@@
 	and processing time on the third machine is output data transfer time; and the objective is 
-	to minimize the total makespan. This is a well known hard problem~\cite{NPComplete3Machine,johnson}.
+	to minimize the total makespan. This is a well known NP-complete problem~\cite{3machineFlowShopNPComplete}.
 
@@
 
-	\todo[inline]{Find a citation saying 3-machine flowshop problem is NP-Complete.}
+%%	\todo[inline]{Find a citation saying 3-machine flowshop problem is NP-Complete.}
 	%%%%	done:\todo[inline]{Rewrite both paragraphs together.}
@@
 	$C$. 
-%%	\todo[inline]{SKumar: We do not need this assumption throughout the paper. CommVolume=CommTime is not true for experimental section. We used this assumption only in NP-hard proof for simplicity.}
+	\todo[inline]{SKumar: Why not a direct statement?  For simplicity, we assume in all of this paper that the amount of memory required by a task is equal to its communication volume.}
 	For simplicity, we assume in all of this paper that the
@@
 	communication time, and without loss of generality we consider
-	that memory size of a task is equal to its communication volume.
+	that memory size of a task is equal to its communication time.
 
@@
 				\hline
-				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
+%%				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
+				\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
+				&=Comm Volume && \\ \hline
 				A & 0 & 0 & 5\\ \hline
@@
 				%%				&=Comm Volume& \\ \hline
-				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
+%%				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
+				\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
+				&=Comm Volume && \\ \hline
 				A & 3 & 3 &  2\\ \hline
@@
 				\hline
-				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
+%%				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
+				\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
+				&=Comm Volume && \\ \hline
 				A & 3 & 3 & 2\\ \hline
@@
 				\hline
-				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
+%%				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
+				\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
+				&=Comm Volume && \\ \hline
 				A & 4 & 4 &  1\\ \hline

### 2019-04-12 ICPP-19/communications.tex
minor

@@
 	$C$. 
-	\todo[inline]{SKumar: Why not a direct statement?  For simplicity, we assume in all of this paper that the amount of memory required by a task is equal to its communication volume.}
+	\todo[inline]{SKumar: How about this?
+For simplicity, we assume throughout the paper that tasks do not have any intermediate memory requirement.
+Hence, amount of memory required by a task is equal to its communication volume.}
+	\todo[inline]{Skumar2LED: Actually adding internal memory requirement will make NP-completeness proof straightforward. I started with this problem ;).}
 	For simplicity, we assume in all of this paper that the
@@
 
-		As \textit{Transfer time = Latency + (Data Volume)/Bandwidth}.
-For simplicity, we consider input transfer time is same as input data volume (i.e., \textit{Latency = 0} and \textit{Bandwidth = 1}).
+		\todo[inline]{SKumar: Do we need to mention here separately that memory requirement is equal to communication volume? I think no. right?}
+		As \textit{Transfer time = Latency + (Comm Volume)/Bandwidth}.
+For simplicity, we consider  transfer time is same as communication volume (i.e., \textit{Latency = 0} and \textit{Bandwidth = 1}).
 Otherwise, we can adjust $C$ such that at any point in a schedule at max one $K_i$ and three $A_i$ tasks can be active.
@@
 		tasks must fit without preemption. We can thus define triplet $TR_i$
-		as the setof tasks which execute during the communication phase of
+		as the set of tasks which execute during the communication phase of
 		task $K_i$. Since at each point in $S$, exactly one $K_i$ task is
@@
 	\subsection{Dynamic Selection}
-	Dynamic strategies are based on the following principle: when the communication resource is idle, a task is chosen based on a ranking criterion which differ depending on the heuristic, among those which fit in memory.
-For example, if the selection criteria is to choose a highly compute intensive task, then we compute the ratio of computation time and communication time for all tasks, and we select a task with the maximum ratio among which induce minimum idle time on the computation resource and fit in the currently available memory.
+	Dynamic strategies are based on the following principle: when the communication resource is idle, a task is chosen based on a selection criterion which differ depending on the heuristic, among those which fit in memory and induce minimum idle time on the computation resource.
+For example, if the selection criterion is to choose a highly compute intensive task, then we compute the ratio of computation time and communication time for all tasks, and we select a task with the maximum ratio among those which induce minimum idle time on the computation resource and fit in the currently available memory.
 If no task fits in memory then we leave the resource idle at that point and proceed to the next event point.
@@
 
-	In all strategies, the initial order is obtained by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}.
-We define the following heuristics based on how we select a task from the set of tasks which fit in memory and induces minimum idle time on the computation resource.
+	In all strategies, the initial order is $OMIM$ order,  obtained by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}.
+We define the following heuristics based on how we select a task from the set of tasks which fit in memory and induce minimum idle time on the computation resource.
 If no task fits in memory then we leave the resource idle and forward to the next event point.
@@
 
-		\subsection{Experimental Settings}
+		\section{Experimental Settings}
 		\label{sec:expSetting}
@@
 
-		Figures ~\ref{fig:ratio_to_optimal_hf} and ~\ref{fig:ratio_to_optimal_ccsd} show the distribution of the performance of each heuristic for all considered memory capacities, where plots are categorized by memory capacities.
+		Figures ~\ref{fig:ratio_to_optimal_hf} and ~\ref{fig:ratio_to_optimal_ccsd} show the distribution of the performance of each heuristic for different memory capacities, where plots are categorized by memory capacities.
 For each memory capacity and each heuristic, the box on the plot displays the median, first and last quartile, and the whiskers indicate minimum and maximum values, with outliers are shown by black dots.
@@
 As memory capacity is increased further, dynamic variants of heuristics start performing better.
-For the moderate memory capacities (close to $2m_c$), static order with dynamic correction variants outperform others.
+For the moderate memory capacities (close to $2m_c$), static order with dynamic corrections variants outperform others.
 $GG$ heuristic does not achieve good performance, because its task sequence is obtained considering no extra memory is available, but is then applied in a different scenario where memory is limited.
@@
 
-		Figure~\ref{fig:ratio_to_optimal_best_hf} shows the performance comparison of the best variant in each category, in addition to the \textit{order of submission} ($OS$) strategy which orders tasks in the (arbitrary) order in which they are given.
+		Figure~\ref{fig:ratio_to_optimal_best_hf} shows the performance comparison of the best variant in each category, in addition to the \textit{order of submission} ($OS$) strategy which orders tasks in the (arbitrary) sequence in which they are given.
 Static strategies are expected to perform better when there is not any memory capacity restriction, and indeed this plot shows that static strategies face capacity bottleneck and underperform with limited memory.
@@
 Therefore we organize tasks of each trace file in batches of 100 (the last batch may have less than 100 tasks).
-We apply each heuristic on each group independently.
+We apply each heuristic on each group in succession.
 Figure~\ref{fig:best_variants_batch} shows the performance of the best variants of each category for both applications.

### 2019-04-12 ICPP-19/communications.tex
label_parser

@@
 	$C$. 
-	\todo[inline]{SKumar: How about this?
-For simplicity, we assume throughout the paper that tasks do not have any intermediate memory requirement.
-Hence, amount of memory required by a task is equal to its communication volume.}
-	\todo[inline]{Skumar2LED: Actually adding internal memory requirement will make NP-completeness proof straightforward. I started with this problem ;).}
-	For simplicity, we assume in all of this paper that the
-	amount of memory required by a task is proportional to its
-	communication time, and without loss of generality we consider
-	that memory size of a task is equal to its communication time.
+	For simplicity, we assume throughout he paper that tasks
+	require memory only to store their input data, and thus that
+	the amount of memory required by a task is proportional to its
+	communication time. Without loss of generality, we consider in
+	all examples of Sections~\ref{sec:theoreticalProof}
+	and~\ref{sec:heuristics} that the memory requirement of a task
+	is equal to its communication time.
 
@@
 
-		\todo[inline]{SKumar: Do we need to mention here separately that memory requirement is equal to communication volume? I think no. right?}
-		As \textit{Transfer time = Latency + (Comm Volume)/Bandwidth}.
+		%% \todo[inline]{SKumar: Do we need to mention here separately that memory requirement is equal to communication volume? I think no. right?}
+		%% As \textit{Transfer time = Latency + (Comm Volume)/Bandwidth}.
 For simplicity, we consider  transfer time is same as communication volume (i.e., \textit{Latency = 0} and \textit{Bandwidth = 1}).
@@
 			\includegraphics[scale=0.5]{./all-binpack/ratio_to_optimal_selected_hf.pdf}
-			\caption{Comparison of different heuristics for HF with $m_c=..$.}
+			\caption{Comparison of different heuristics for HF with $m_c=176KB$.}
 			\label{fig:ratio_to_optimal_hf}
@@
 			\includegraphics[scale=0.5]{./all-binpack/ratio_to_optimal_selected_ccsd.pdf}
-			\caption{Comparison of different heuristics for CCSD with $m_c=$.}
+			\caption{Comparison of different heuristics for CCSD with $m_c=1.8GB$.}
 			\label{fig:ratio_to_optimal_ccsd}
@@
 This work was supported in part by the U.S.
-Department of Energy’s (DOE), Office of Science, Office of Advanced Scientific Computing Research, under award 63823.
+Department of Energy (DOE), Office of Science, Office of Advanced Scientific Computing Research, under award 63823.
 Pacific Northwest National Laboratory is operated by Battelle for DOE under Contract DE-AC05-76RL01830.

### 2019-04-12 ICPP-19/all-binpack/ratio_to_optimal.R

@@ -8,17 +8,20 @@ dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
 dftest[,2:6]<-NULL
 dftestMelted<-melt(dftest, "capacity")
 names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
+#dftestMelted$mc <- factor(dftestMelted$capacity, labels = c('m_c', "1.125m_c", "1.375m_c", "1.5m_c", "1.625m_c", "1.75m_c", "1.875m_c", "2m_c"))
+dftestMelted$mc <- factor(dftestMelted$capacity, labels = c("m[c]", "1.125~m[c]", "1.375~m[c]", "1.5~m[c]", "1.625~m[c]", "1.75~m[c]", "1.875~m[c]", "2~m[c]"))
 p<-ggplot(dftestMelted, aes(x=Heuristic, y=ratio_to_optimal, color=Heuristic)) + geom_boxplot(outlier.color="black") +
-facet_wrap(~capacity, ncol=4)  + theme(axis.ticks = element_blank(), axis.text.x = element_blank()) + xlab("") +
+#facet_wrap(~capacity, ncol=4)  + theme(axis.ticks = element_blank(), axis.text.x = element_blank()) + xlab("") +
+facet_wrap(~mc, labeller=label_parsed, ncol=4)  + theme(axis.ticks = element_blank(), axis.text.x = element_blank()) + xlab("") +
 ylab("Ratio to Optimal")
 #p <- p + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Ratio to Optimal")
 return (p)
 }
-p<-ratio_to_optimal_func('all_results_hf.txt')
-ggsave(file="ratio_to_optimal_hf.pdf", p, width=14.25, height=6.5)
-
-p<-ratio_to_optimal_func('all_results_ccsd.txt')
-ggsave(file="ratio_to_optimal_ccsd.pdf", p, width=14.25, height=6.5)
+#p<-ratio_to_optimal_func('all_results_hf.txt')
+#ggsave(file="ratio_to_optimal_hf.pdf", p, width=14.25, height=6.5)
+#
+#p<-ratio_to_optimal_func('all_results_ccsd.txt')
+#ggsave(file="ratio_to_optimal_ccsd.pdf", p, width=14.25, height=6.5)
 
 p<-ratio_to_optimal_func('selected_results_hf.txt')
[…]

### 2019-04-12 ICPP-19/results/scripts/insights.R

@@ -33,6 +33,7 @@ colnames(dftest)[colnames(dftest) == "sum_comm_comp" ] <- "sum comm + sum comp"
 colnames(dftest)[colnames(dftest) == "max.sum_comm.sum_comp." ] <- "max(sum comm, sum comp)"
 dftest[,1:ncol(dftest)]<-dftest[,1:ncol(dftest)]/dftest[,5]
 dftest[,5]<-NULL
+dftest<-dftest[,c(3,4,2,1)]
 dftestMelted<-melt(dftest)
 names(dftestMelted)<-c( "Parameter", "ratio_to_optimal")
 return (dftestMelted)
@@ -45,7 +46,7 @@ dfMelted <- rbind(dfMelted1, dfMelted2)
 library(ggplot2)
 p<-ggplot(dfMelted, aes(x=Parameter, y=ratio_to_optimal, color=Parameter))  + geom_boxplot(outlier.color="black") + geom_hline(yintercept=1, linetype="dashed", color = "red") +
           facet_wrap(~application) + scale_y_continuous(breaks=seq(0.0, 2.0, 0.5), limits=c(0, 2)) +
-          theme(legend.position='none', axis.text.x = element_text(angle = 45, hjust=1, vjust = 1)) + xlab(" ") +
+          theme(legend.position='none', axis.text.x = element_text(angle = 25, hjust=1, vjust = 1)) + xlab(" ") +
           ylab("Ratio to Optimal")
 ggsave(file="application_properties.pdf", p, width=7, height=4)
 

### 2019-04-14 ICPP-19/results/scripts/insights.R
cleaning old results

@@ -1,52 +1,0 @@
-#!/usr/bin/env Rscript
-insights_func <-function(file_name)
-{
-library(reshape2)
-dftest<-read.table(file_name, header=T)
-
-
-dftest[,1:ncol(dftest)]<-dftest[,1:ncol(dftest)]/dftest[,5]
-dftest[,5]<-NULL
-dftestMelted<-melt(dftest)
-names(dftestMelted)<-c( "Parameter", "ratio_to_optimal")
-p<-ggplot(dftestMelted, aes(x=Parameter, y=ratio_to_optimal, color=Parameter))  + geom_boxplot(outlier.color="black") + geom_hline(yintercept=1, linetype="dashed", color = "red")
-p <- p + theme(plot.title = element_text(hjust = 0.5), legend.position='none') +  ggtitle("Application Properties") + scale_y_continuous(breaks=seq(0.0, 2.0, 0.5), limits=c(0, 2))
-#p <- p + theme(plot.title = element_text(hjust = 0.5), legend.position='none') +  ggtitle("Application Properties") 
-
-return (p)
-}
-#p<-insights_func('insight_hf.txt')
-#w=20
-#h=10
-#ggsave(file="application_properties_hf.pdf", p, width=w, height=h)
-#
-#p<-insights_func('insight_ccsd.txt')
-#ggsave(file="application_properties_ccsd.pdf", p, width=w, height=h)
-
-get_melted_data_frame<-function(file_name)
-{
-library(reshape2)
-dftest<-read.table(file_name, header=T)
-colnames(dftest)[colnames(dftest) == "sum_comm" ] <- "sum comm"
-colnames(dftest)[colnames(dftest) == "sum_comp" ] <- "sum comp"
-colnames(dftest)[colnames(dftest) == "sum_comm_comp" ] <- "sum comm + sum comp"
-colnames(dftest)[colnames(dftest) == "max.sum_comm.sum_comp." ] <- "max(sum comm, sum comp)"
-dftest[,1:ncol(dftest)]<-dftest[,1:ncol(dftest)]/dftest[,5]
-dftest[,5]<-NULL
-dftest<-dftest[,c(3,4,2,1)]
-dftestMelted<-melt(dftest)
-names(dftestMelted)<-c( "Parameter", "ratio_to_optimal")
-return (dftestMelted)
-}
-dfMelted1<-get_melted_data_frame('insight_hf.txt');
-dfMelted1$application <- "HF Workload"
[…]

### 2019-04-14 ICPP-19/results/scripts/inverse_ratio_to_optimal-best.R

@@ -1,29 +1,0 @@
-#!/usr/bin/env Rscript
-inverse_ratio_to_optimal_best_func <-function(file_name)
-{
-library(ggplot2)
-library(reshape2)
-dftest<-read.table(file_name, header=T)
-dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
-
-dftest[,8]<-NULL
-dftest[,c(2:6)]<-NULL
-dftest$static_best<-do.call('pmin', c(dftest[,3:7]))
-dftest$dynamic_best<-do.call('pmin', c(dftest[,8:10]))
-dftest$static_dynamic_best<-do.call('pmin', c(dftest[,11:13]))
-dftest<-dftest[,c(1,2,14:16)]
-dftestMelted<-melt(dftest, "capacity")
-names(dftestMelted)<-c("Capacity", "Heuristic", "ratio_to_optimal")
-#p<-ggplot(dftestMelted, aes(x=jitter(capacity), y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth()
-p<-ggplot(dftestMelted, aes(x=Capacity, y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth(method="loess")
-#p<-p + ylab("inverse(ratio_to_optimal)") + theme(plot.title = element_text(hjust = 0.5), legend.position="bottom") +  ggtitle("Performance With Best of all categories")
-p<-p + ylab("inverse(ratio_to_optimal)") + xlab ("Memory Capacity") + theme(legend.position="bottom")
-return (p)
-}
-
-p<-inverse_ratio_to_optimal_best_func('all_results_hf.txt')
-ggsave(file="inverse_ratio_to_optimal_hf-best.pdf", p + xlim(NA, 340000), width=6.5, height=5)
-
-p<-inverse_ratio_to_optimal_best_func('all_results_ccsd.txt')
-ggsave(file="inverse_ratio_to_optimal_ccsd-best.pdf", p, width=6.5, height=5)
-

### 2019-04-14 ICPP-19/results/scripts/inverse_ratio_to_optimal_batch-best.R

@@ -1,55 +1,0 @@
-#!/usr/bin/env Rscript
-inverse_ratio_to_optimal_best_func <-function(file_name)
-{
-library(ggplot2)
-library(reshape2)
-dftest<-read.table(file_name, header=T)
-dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
-
-dftest[,c(2:6)]<-NULL
-dftest$static_best<-do.call('pmin', c(dftest[,3:7]))
-dftest$dynamic_best<-do.call('pmin', c(dftest[,8:10]))
-dftest$static_dynamic_best<-do.call('pmin', c(dftest[,11:13]))
-dftest<-dftest[,c(1,2,14:16)]
-dftestMelted<-melt(dftest, "capacity")
-names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
-p<-ggplot(dftestMelted, aes(x=capacity, y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth(method="loess")
-p<-p + ylab("inverse(ratio_to_optimal)") + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Performance With Best of all categories")
-return (p)
-}
-#p<-inverse_ratio_to_optimal_best_func('results_batch_hf.txt')
-#ggsave(file="inverse_ratio_to_optimal_hf_batch-best.pdf", p, width=23.6, height=13.4)
-#
-#p<-inverse_ratio_to_optimal_best_func('results_batch_ccsd.txt')
-#ggsave(file="inverse_ratio_to_optimal_ccsd_batch-best.pdf", p, width=23.6, height=13.4)
-
-get_melted_data_frame <-function(file_name)
-{
-library(ggplot2)
-library(reshape2)
-dftest<-read.table(file_name, header=T)
-dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
-
-dftest[,c(2:6)]<-NULL
-dftest$static_best<-do.call('pmin', c(dftest[,3:7]))
-dftest$dynamic_best<-do.call('pmin', c(dftest[,8:10]))
-dftest$static_dynamic_best<-do.call('pmin', c(dftest[,11:13]))
-dftest<-dftest[,c(1,2,14:16)]
-dftestMelted<-melt(dftest, "capacity")
-names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
[…]

### 2019-04-14 ICPP-19/results/scripts/ratio_to_optimal-best.R

@@ -1,30 +1,0 @@
-#!/usr/bin/env Rscript
-ratio_to_optimal_best_func <-function(file_name)
-{
-library(ggplot2)
-library(reshape2)
-dftest<-read.table(file_name, header=T)
-dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
-
-dftest[,8]<-NULL
-dftest[,c(2:6)]<-NULL
-dftest$"Best Static"<-do.call('pmin', c(dftest[,3:7]))
-dftest$"Best Dynamic" <-do.call('pmin', c(dftest[,8:10]))
-dftest$"Best Static Dynamic"<-do.call('pmin', c(dftest[,11:13]))
-dftest<-dftest[,c(1,2,14:16)]
-dftestMelted<-melt(dftest, "capacity")
-names(dftestMelted)<-c("Capacity", "Heuristic", "ratio_to_optimal")
-#p<-ggplot(dftestMelted, aes(x=jitter(capacity), y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth()
-#p<-ggplot(dftestMelted, aes(x=Capacity, y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth(method="loess")
-p<-ggplot(dftestMelted, aes(x=Capacity, y=ratio_to_optimal, color=Heuristic))  + geom_smooth(method="loess")
-#p<-p + ylab("inverse(ratio_to_optimal)") + theme(plot.title = element_text(hjust = 0.5), legend.position="bottom") +  ggtitle("Performance With Best of all categories")
-p<-p + ylab("Ratio to Optimal") + xlab ("Memory Capacity") + theme(legend.position="bottom")
-return (p)
-}
-
-p<-ratio_to_optimal_best_func('all_results_hf.txt')
-ggsave(file="ratio_to_optimal_hf-best.pdf", p + xlim(NA, 340000), width=6.5, height=5)
-
-p<-ratio_to_optimal_best_func('all_results_ccsd.txt')
-ggsave(file="ratio_to_optimal_ccsd-best.pdf", p, width=6.5, height=5)
-

### 2019-04-14 ICPP-19/results/scripts/ratio_to_optimal.R

@@ -1,31 +1,0 @@
-#!/usr/bin/env Rscript
-ratio_to_optimal_func <-function(file_name)
-{
-library(ggplot2)
-library(reshape2)
-dftest<-read.table(file_name, header=T)
-dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
-dftest[,2:6]<-NULL
-dftestMelted<-melt(dftest, "capacity")
-names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
-p<-ggplot(dftestMelted, aes(x=Heuristic, y=ratio_to_optimal, color=Heuristic)) + geom_boxplot(outlier.color="black") + facet_wrap(~capacity, ncol=4)  + theme(axis.ticks = element_blank(), axis.text.x = element_blank()) + xlab("")
-p <- p + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Ratio to Optimal")
-return (p)
-}
-p<-ratio_to_optimal_func('all_results_hf.txt')
-ggsave(file="ratio_to_optimal_hf.pdf", p, width=23.6, height=13.4)
-
-p<-ratio_to_optimal_func('all_results_ccsd.txt')
-ggsave(file="ratio_to_optimal_ccsd.pdf", p, width=23.6, height=13.4)
-
-p<-ratio_to_optimal_func('selected_results_hf.txt')
-ggsave(file="ratio_to_optimal_selected_hf.pdf", p, width=23.6, height=13.4)
-
-p<-ratio_to_optimal_func('selected_results_ccsd.txt')
-ggsave(file="ratio_to_optimal_selected_ccsd.pdf", p, width=23.6, height=13.4)
-
-p<-ratio_to_optimal_func('all_results_random_ccsd.txt')
-ggsave(file="ratio_to_optimal_random_ccsd.pdf", p, width=23.6, height=13.4)
-
-p<-ratio_to_optimal_func('selected_results_random_ccsd.txt')
-ggsave(file="ratio_to_optimal_random_selected_ccsd.pdf", p, width=23.6, height=13.4)

### 2019-04-14 ICPP-19/results/scripts/ratio_to_optimal_batch-best.R

@@ -1,55 +1,0 @@
-#!/usr/bin/env Rscript
-ratio_to_optimal_best_func <-function(file_name)
-{
-library(ggplot2)
-library(reshape2)
-dftest<-read.table(file_name, header=T)
-dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
-
-dftest[,c(2:6)]<-NULL
-dftest$static_best<-do.call('pmin', c(dftest[,3:7]))
-dftest$dynamic_best<-do.call('pmin', c(dftest[,8:10]))
-dftest$static_dynamic_best<-do.call('pmin', c(dftest[,11:13]))
-dftest<-dftest[,c(1,2,14:16)]
-dftestMelted<-melt(dftest, "capacity")
-names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
-p<-ggplot(dftestMelted, aes(x=capacity, y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth(method="loess")
-p<-p + ylab("inverse(ratio_to_optimal)") + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Performance With Best of all categories")
-return (p)
-}
-#p<-ratio_to_optimal_best_func('results_batch_hf.txt')
-#ggsave(file="ratio_to_optimal_hf_batch-best.pdf", p, width=23.6, height=13.4)
-#
-#p<-ratio_to_optimal_best_func('results_batch_ccsd.txt')
-#ggsave(file="ratio_to_optimal_ccsd_batch-best.pdf", p, width=23.6, height=13.4)
-
-get_melted_data_frame <-function(file_name)
-{
-library(ggplot2)
-library(reshape2)
-dftest<-read.table(file_name, header=T)
-dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
-
-dftest[,c(2:6)]<-NULL
-dftest$"Best Static"<-do.call('pmin', c(dftest[,3:7]))
-dftest$"Best Dynamic"<-do.call('pmin', c(dftest[,8:10]))
-dftest$"Best Static Dynamic"<-do.call('pmin', c(dftest[,11:13]))
-dftest<-dftest[,c(1,2,14:16)]
-dftestMelted<-melt(dftest, "capacity")
-names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
-return (dftestMelted)
-}
-
[…]

### 2019-04-14 ICPP-19/communications.tex
polishing arrangement of results

@@
 Third, due to shared buses and parallel resources, it is challenging to obtain a precise model based on prediction of computation and communication times.
-Fourth, then number of architectures has increased drastically in recent years, therefore it is almost impossible to develop hand tuned optimized code for all these architectures.
+Fourth, the number of architectures has increased drastically in recent years, therefore it is almost impossible to develop hand tuned optimized code for all these architectures.
 All these observations led to the development of different task based runtime systems.
@@
 al worked on the scheduling of graphs of smaller-grain tasks with limited memory, where each task requires homogeneous data size~\cite{vsarkar-pact}.
-The same work has been extend by Marchal et.
+The same work has been extended by Marchal et.
 al for task graphs where memory requirement of each task is highly irregular~\cite{loris-ipdps18}.
@@
 	units where all of their data does not reside. A task may require all of its input data
-	in local memory before starting the execution. There may be multiple tasks
+	in local memory before starting the computation. There may be multiple tasks
 	scheduled on a processing unit, which require to transfer data from the same
@@
 	viewed as a 3-machine flowshop problem, where processing time on the first machine is 
-	input data transfer time, processing time on the second machine is task execution time, 
+	input data transfer time, processing time on the second machine is task computation time, 
 	and processing time on the third machine is output data transfer time; and the objective is 
@@
 	transfer input data from $M'$ to $M$ for task $i$ and $COMP_i$
-	is the execution time of task $i$ on $P$. We assume that these
+	is the computation time of task $i$ on $P$. We assume that these
 	tasks do not produce any output data. There can be only one
@@
 			\STATE $\scomm(T) \gets \tau_{\text{COMM}}$
-			\STATE $\scomp(T) \gets max(\scomm(T) + CM_T, \tau_{\text{COMP}})$
-			\STATE $\tau_{\text{COMM}} \gets \scomm(T) + CM_T$
-			\STATE $\tau_{\text{COMP}} \gets \scomp(T) + CP_T$
+			\STATE $\scomp(T) \gets max(\scomm(T) + COMM_T, \tau_{\text{COMP}})$
+			\STATE $\tau_{\text{COMM}} \gets \scomm(T) + COMM_T$
+			\STATE $\tau_{\text{COMP}} \gets \scomp(T) + COMP_T$
 			\ENDWHILE
@@
 		can check in linear time that at each start of a communication, the
-		memory constraint is satisfied, and that task starts execution only
+		memory constraint is satisfied, and that task starts computation only
 		after its input data is transferred to $M$.
@@
 		\noindent \textbf{Three Partition Problem} (\threepart): Given a set of
-		$3m$ integers $A = \{ a_1, \cdots, a_{3m }\}$ with $a_i > 1$, is there a partition
+		$3m$ integers $A = \{ a_1, \cdots, a_{3m }\}$, is there a partition
 		of $A$ into $m$ triplets $TR_i = \{a_{i_1}, a_{i_2}, a_{i_3}\}$,
@@
 				\hline
-				Task & Transfer time ($comm_i$)& Computation time ($e_i$)\\ \hline
+				Task & Communication time & Computation time \\ \hline
 				$K_0$ & $0$ & $3$ \\ \hline
@@
 			\end{tabular}
+
 			\noindent Memory capacity: $C=b'+3$\\
@@
 
-		%% \todo[inline]{SKumar: Do we need to mention here separately that memory requirement is equal to communication volume? I think no. right?}
-		%% As \textit{Transfer time = Latency + (Comm Volume)/Bandwidth}.
-For simplicity, we consider  transfer time is same as communication volume (i.e., \textit{Latency = 0} and \textit{Bandwidth = 1}).
-Otherwise, we can adjust $C$ such that at any point in a schedule at max one $K_i$ and three $A_i$ tasks can be active.
+		\todo[inline]{SKumar: I understand that proving for an instance with memory requirement = communication time, also proves that, in general, DT problem is NP-hard.
+I was thinking we can directly prove the general version by adding a single line saying what to change.
+I am not sure whether it is good to explicitly mention how to prove the general version.
+I added a line below.
+Feel free to remove it.}
+		As mentioned previously, we consider memory requirement of a task is equal to its communication time.
+If it is not the case, we can adjust $C$ such that at any point in a schedule at max one $K_i$ and three $A_i$ tasks can be active.
 
@@
 		only if the original \threepart instance has a solution. Notice that
-		the sum of transfer times and the sum of computation times are both
+		the sum of communication times and the sum of computation times are both
 		equal to $L$, therefore a valid schedule of makespan at most $L$ has
@@
 		active, and since $S$ has no idle time on the computation resource,
-		the total execution time of tasks in $TR_i$ is exactly $b'$, and thus
+		the total computation time of tasks in $TR_i$ is exactly $b'$, and thus
 		$a_{i_1} + a_{i_2} + a_{i_3} = b$. This partition is thus a valid
@@
 		\caption{Schedules for the instance of
-			Table~\ref{table:different.order}}
+			Table~\ref{table:different.order} with a memory capacity of 10.}
 		\label{fig:different.order}
@@
 	In this class of strategies, we compute the order of processing in advance based on criteria such as communication time and computation time.
-After computing the order, we follow the same order on computation and communication resources and make sure that the memory constraint is respected at each point in the schedule.
+After computing the order, we follow the same sequence on computation and communication resources and make sure that the memory constraint is respected at each point in the schedule.
 
@@
 
-		\item \textit{increasing order of communication strategy} ($IOCMS$): tasks are ordered  in non-decreasing order of communication time.
-
-		\item \textit{decreasing order of computation strategy} ($DOCPS$): tasks are ordered in non-increasing order of computation time. 
-		\item \textit{increasing order of communication plus computation strategy} ($IOCCS$): tasks are ordered in non-decreasing order of the sum of their communication and computation times.
-		\item \textit{decreasing order of communication plus computation strategy} ($DOCCS$): tasks are ordered in non-increasing order of the sum of their communication and computation times.
+		\item \textit{increasing order of communication strategy} ($IOCMS$): Tasks are ordered  in non-decreasing order of communication time.
+
+		\item \textit{decreasing order of computation strategy} ($DOCPS$): Tasks are ordered in non-increasing order of computation time. 
+		\item \textit{increasing order of communication plus computation strategy} ($IOCCS$): Tasks are ordered in non-decreasing order of the sum of their communication and computation times.
+		\item \textit{decreasing order of communication plus computation strategy} ($DOCCS$): Tasks are ordered in non-increasing order of the sum of their communication and computation times.
 
@@
 	\begin{enumerate}[label=\roman*)]
-		\item \textit{largest communication task respects memory restriction} ($LCMR$): a task with the largest communication time is chosen. 
-		\item \textit{smallest communication task respects memory restriction} ($SCMR$): a task with the smallest communication time is chosen.
-		\item \textit{maximum accelerated task respects memory restriction} ($MAMR$): a task with the maximum ratio of computation time to communication time is chosen.
+		\item \textit{largest communication task respects memory restriction} ($LCMR$): A task with the largest communication time is chosen. 
+		\item \textit{smallest communication task respects memory restriction} ($SCMR$): A task with the smallest communication time is chosen.
+		\item \textit{maximum accelerated task respects memory restriction} ($MAMR$): A task with the maximum ratio of computation time to communication time is chosen.
 	\end{enumerate}
@@
 
-	In all strategies, the initial order is $OMIM$ order,  obtained by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}.
+	In all strategies of this class, the initial order is $OMIM$ order,  obtained by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}.
 We define the following heuristics based on how we select a task from the set of tasks which fit in memory and induce minimum idle time on the computation resource.
@@
 	\begin{enumerate}[label=\roman*)]
-		\item \textit{optimal order infinite memory largest communication task respects memory restriction} ($OOLCMR$): a task with the largest communication time is chosen from the set.
-		\item \textit{optimal order infinite memory smallest communication task respects memory restriction} ($OOSCMR$): a task with the smallest communication time is chosen from the set.
-		\item \textit{optimal order infinite memory maximum accelerated task respects memory restriction} ($OOMAMR$): a task  with the highest ratio of computation time to communication time is chosen from the set.
+		\item \textit{optimal order infinite memory largest communication task respects memory restriction} ($OOLCMR$): A task with the largest communication time is chosen from the set.
+		\item \textit{optimal order infinite memory smallest communication task respects memory restriction} ($OOSCMR$): A task with the smallest communication time is chosen from the set.
+		\item \textit{optimal order infinite memory maximum accelerated task respects memory restriction} ($OOMAMR$): A task  with the highest ratio of computation time to communication time is chosen from the set.
 	\end{enumerate}
@@
 The first heuristic is based on an algorithm, proposed by Gilmore and Gomory, to obtain the minimal cost sequence for a set of jobs~\cite{Gilmore-Gomory:1964}.
-This is a classic algorithm for 2-machine no-wait flow shop.
+This is a classical algorithm for 2-machine no-wait flow shop.
 In this algorithm, each job has a start and end state and a cost is associated to change the state.
@@
 The solver was unable to  solve this MILP at the scale of our interest in limited time.
-Hence, we solve the linear program iteratively for a small subset of size $k=3,4,5$: at the boundary of two iterations we fix the event (communication or computation) of an unfinished task started before the boundary point and consider other events flexible.
+Hence, we solve the linear program iteratively for a small subset of size $k=3, 4, 5, 6$: at the boundary of two iterations we fix the event (communication or computation) of an unfinished task started before the boundary point and consider other events flexible.
 The subsets are formed in the order in which tasks are submitted, which is arbitrary.
@@
 			%\begin{tabular}{c}
-			\includegraphics[scale=0.5]{./results/plots/application_properties.pdf}
+			\includegraphics[scale=0.5]{./results/application_properties.pdf}
 			\caption{HF and CCSD tasks characteristics.}
@@
 		\begin{figure*}[htb]
-			\includegraphics[scale=0.5]{./all-binpack/ratio_to_optimal_selected_hf.pdf}
+			\includegraphics[scale=0.5]{./results/ratio_to_optimal_selected_hf.pdf}
 			\caption{Comparison of different heuristics for HF with $m_c=176KB$.}
@@
 		\begin{figure}[htb]
-			%%			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_hf-best.pdf}
-			\includegraphics[scale=0.5]{./results/plots/ratio_to_optimal_hf-best.pdf}
+			%%			\includegraphics[scale=0.5]{./results/inverse_ratio_to_optimal_hf-best.pdf}
+			\includegraphics[scale=0.5]{./results/ratio_to_optimal_hf-best.pdf}
 			\caption{Comparision of best variants of all categories for HF.}
@@
 		\begin{figure*}[htb]
-			\includegraphics[scale=0.5]{./all-binpack/ratio_to_optimal_selected_ccsd.pdf}
+			\includegraphics[scale=0.5]{./results/ratio_to_optimal_selected_ccsd.pdf}
 			\caption{Comparison of different heuristics for CCSD with $m_c=1.8GB$.}
@@
 		\begin{figure}[htb]
-			%%			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_ccsd-best.pdf}
-			\includegraphics[scale=0.5]{./results/plots/ratio_to_optimal_ccsd-best.pdf}
+			%%			\includegraphics[scale=0.5]{./results/inverse_ratio_to_optimal_ccsd-best.pdf}
+			\includegraphics[scale=0.5]{./results/ratio_to_optimal_ccsd-best.pdf}
 			\caption{Comparision of best variants of all categories for CCSD.}
@@
 		\begin{figure*}[htb]
-			%%			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_batch-best.pdf}
-			\includegraphics[scale=0.5]{./results/plots/ratio_to_optimal_batch-best.pdf}
+			%%			\includegraphics[scale=0.5]{./results/inverse_ratio_to_optimal_batch-best.pdf}
+			\includegraphics[scale=0.5]{./results/ratio_to_optimal_batch-best.pdf}
 			\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
@@
 		%%	\begin{figure*}[htb]
-		%%		\includegraphics[scale=0.25]{./results/plots/ratio_to_optimal_random_selected_ccsd.pdf}
+		%%		\includegraphics[scale=0.25]{./results/ratio_to_optimal_random_selected_ccsd.pdf}
 		%%		\caption{Comparison of different heuristics for CCSD with highly heterogeneous tasks.}

### 2019-04-14 ICPP-19/results/scripts/insights.R

@@ -1,0 +1,52 @@
+#!/usr/bin/env Rscript
+insights_func <-function(file_name)
+{
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+
+
+dftest[,1:ncol(dftest)]<-dftest[,1:ncol(dftest)]/dftest[,5]
+dftest[,5]<-NULL
+dftestMelted<-melt(dftest)
+names(dftestMelted)<-c( "Parameter", "ratio_to_optimal")
+p<-ggplot(dftestMelted, aes(x=Parameter, y=ratio_to_optimal, color=Parameter))  + geom_boxplot(outlier.color="black") + geom_hline(yintercept=1, linetype="dashed", color = "red")
+p <- p + theme(plot.title = element_text(hjust = 0.5), legend.position='none') +  ggtitle("Application Properties") + scale_y_continuous(breaks=seq(0.0, 2.0, 0.5), limits=c(0, 2))
+#p <- p + theme(plot.title = element_text(hjust = 0.5), legend.position='none') +  ggtitle("Application Properties") 
+
+return (p)
+}
+#p<-insights_func('insight_hf.txt')
+#w=20
+#h=10
+#ggsave(file="application_properties_hf.pdf", p, width=w, height=h)
+#
+#p<-insights_func('insight_ccsd.txt')
+#ggsave(file="application_properties_ccsd.pdf", p, width=w, height=h)
+
+get_melted_data_frame<-function(file_name)
+{
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+colnames(dftest)[colnames(dftest) == "sum_comm" ] <- "sum comm"
+colnames(dftest)[colnames(dftest) == "sum_comp" ] <- "sum comp"
+colnames(dftest)[colnames(dftest) == "sum_comm_comp" ] <- "sum comm + sum comp"
+colnames(dftest)[colnames(dftest) == "max.sum_comm.sum_comp." ] <- "max(sum comm, sum comp)"
+dftest[,1:ncol(dftest)]<-dftest[,1:ncol(dftest)]/dftest[,5]
+dftest[,5]<-NULL
+dftest<-dftest[,c(3,4,2,1)]
+dftestMelted<-melt(dftest)
+names(dftestMelted)<-c( "Parameter", "ratio_to_optimal")
+return (dftestMelted)
+}
+dfMelted1<-get_melted_data_frame('insight_hf.txt');
+dfMelted1$application <- "HF Workload"
[…]

### 2019-04-14 ICPP-19/results/scripts/ratio_to_optimal-best.R

@@ -1,0 +1,30 @@
+#!/usr/bin/env Rscript
+ratio_to_optimal_best_func <-function(file_name)
+{
+library(ggplot2)
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
+
+#dftest[,8]<-NULL
+dftest[,c(2:6)]<-NULL
+dftest$"Best Static"<-do.call('pmin', c(dftest[,3:9]))
+dftest$"Best Dynamic" <-do.call('pmin', c(dftest[,10:12]))
+dftest$"Best Static Dynamic"<-do.call('pmin', c(dftest[,13:15]))
+dftest<-dftest[,c(1,2,16:18)]
+dftestMelted<-melt(dftest, "capacity")
+names(dftestMelted)<-c("Capacity", "Heuristic", "ratio_to_optimal")
+#p<-ggplot(dftestMelted, aes(x=jitter(capacity), y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth()
+#p<-ggplot(dftestMelted, aes(x=Capacity, y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth(method="loess")
+p<-ggplot(dftestMelted, aes(x=Capacity, y=ratio_to_optimal, color=Heuristic))  + geom_smooth(method="loess")
+#p<-p + ylab("inverse(ratio_to_optimal)") + theme(plot.title = element_text(hjust = 0.5), legend.position="bottom") +  ggtitle("Performance With Best of all categories")
+p<-p + ylab("Ratio to Optimal") + xlab ("Memory Capacity") + theme(legend.position="bottom")
+return (p)
+}
+
+p<-ratio_to_optimal_best_func('all_results_hf.txt')
+ggsave(file="ratio_to_optimal_hf-best.pdf", p + xlim(NA, 340000), width=6.5, height=5)
+
+p<-ratio_to_optimal_best_func('all_results_ccsd.txt')
+ggsave(file="ratio_to_optimal_ccsd-best.pdf", p, width=6.5, height=5)
+

### 2019-04-14 ICPP-19/results/scripts/ratio_to_optimal.R

@@ -1,0 +1,36 @@
+#!/usr/bin/env Rscript
+ratio_to_optimal_func <-function(file_name)
+{
+library(ggplot2)
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
+dftest[,2:6]<-NULL
+dftestMelted<-melt(dftest, "capacity")
+names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
+#dftestMelted$mc <- factor(dftestMelted$capacity, labels = c('m_c', "1.125m_c", "1.375m_c", "1.5m_c", "1.625m_c", "1.75m_c", "1.875m_c", "2m_c"))
+dftestMelted$mc <- factor(dftestMelted$capacity, labels = c("m[c]", "1.125~m[c]", "1.375~m[c]", "1.5~m[c]", "1.625~m[c]", "1.75~m[c]", "1.875~m[c]", "2~m[c]"))
+p<-ggplot(dftestMelted, aes(x=Heuristic, y=ratio_to_optimal, color=Heuristic)) + geom_boxplot(outlier.color="black") +
+#facet_wrap(~capacity, ncol=4)  + theme(axis.ticks = element_blank(), axis.text.x = element_blank()) + xlab("") +
+facet_wrap(~mc, labeller=label_parsed, ncol=4)  + theme(axis.ticks = element_blank(), axis.text.x = element_blank()) + xlab("") +
+ylab("Ratio to Optimal")
+#p <- p + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Ratio to Optimal")
+return (p)
+}
+#p<-ratio_to_optimal_func('all_results_hf.txt')
+#ggsave(file="ratio_to_optimal_hf.pdf", p, width=14.25, height=6.5)
+#
+#p<-ratio_to_optimal_func('all_results_ccsd.txt')
+#ggsave(file="ratio_to_optimal_ccsd.pdf", p, width=14.25, height=6.5)
+
+p<-ratio_to_optimal_func('selected_results_hf.txt')
+ggsave(file="ratio_to_optimal_selected_hf.pdf", p, width=14.25, height=6.5)
+
+p<-ratio_to_optimal_func('selected_results_ccsd.txt')
+ggsave(file="ratio_to_optimal_selected_ccsd.pdf", p, width=14.25, height=6.5)
+
[…]

### 2019-04-14 ICPP-19/communications.tex
proofread

@@
 We propose several heuristics for this problem and provide details about their favorable situations.
-We present analysis of our heuristics on traces, obtained by running 2 molecular chemistry kernels, namely, Hartree–Fock (HF) and Coupled Cluster Single Double (CCSD) on 10 nodes of an HPC system.
+We present an analysis of our heuristics on traces, obtained by running 2 molecular chemistry kernels, namely, Hartree–Fock (HF) and Coupled Cluster Single Double (CCSD) on 10 nodes of an HPC system.
 Our results show that some of our heuristics achieve significant overlap for moderate memory capacities and are very close to the lower bound of makespan.
@@
 The main difference between both approaches is that they consider all tasks have the same occupation on the second machine and the memory occupation starts when the processing finishes on the first machine.
-On the contrary, our approach is designed for tasks appearing in scientific workloads whose memory requirements are highly irregular and we consider that memory is acquired before starting the data transfer on communication resource.
+On the contrary, our approach is designed for tasks appearing in scientific workloads whose memory requirements are highly irregular and we consider that memory is acquired before starting the data transfer on the communication resource.
 We propose different runtime strategies in order to maximize the overlap of computations and communications.
@@
 Hence, we do not consider output data explicitely in our analysis and assume that output data is negligible or stored in a separate buffer for each task.
-Thus problem considered here is thus more similar to a 2-machine flowshop problem.
-We prove that ordering the execution of such tasks with finite memory capacity is an NP-complete problem: %%We also present an optimal algorithm to determine the order of execution of tasks when there is not any restriction on memory limit.
+Thus problem considered here is more similar to a 2-machine flowshop problem.
+We prove that ordering the execution of such tasks with finite memory capacity is a NP-complete problem: %%We also present an optimal algorithm to determine the order of execution of tasks when there is not any restriction on memory limit.
 
@@
 	memory unit $M$ of capacity $C$. Input data for tasks of $ST$
-	reside on another memory unit $M'$. $COMM_i$ is the time to
+	reside on another memory unit $M'$. $COMM_i$ is the communication time to
 	transfer input data from $M'$ to $M$ for task $i$ and $COMP_i$
@@
 	$C$. 
-	For simplicity, we assume throughout he paper that tasks
+	For simplicity, we assume throughout the paper that tasks
 	require memory only to store their input data, and thus that
@@
 
-	This Theorem shows that adding a memory constraint to our
+	This theorem shows that adding a memory constraint to our
 	problem makes it more difficult. One additional difficulty
 	compared to limited capacity 2-machine
-	flowshop~\cite{Papadimitriou:1980:FSL:322203.322213} is that
+	flowshop~\cite{Papadimitriou:1980:FSL:322203.322213}  \todo{I think you mean: infinite memory capacity 2-machine flowshop~\cite{johnson}} is that
 	it may not be optimal to consider the same ordering on both
@@
 	\subsection{Dynamic Selection}
-	Dynamic strategies are based on the following principle: when the communication resource is idle, a task is chosen based on a selection criterion which differ depending on the heuristic, among those which fit in memory and induce minimum idle time on the computation resource.
+	Dynamic strategies are based on the following principle: when the communication resource is idle, a task is chosen based on a selection criterion which differs depending on the heuristic, among those which fit in memory and induce minimum idle time on the computation resource.
 For example, if the selection criterion is to choose a highly compute intensive task, then we compute the ratio of computation time and communication time for all tasks, and we select a task with the maximum ratio among those which induce minimum idle time on the computation resource and fit in the currently available memory.
@@
 	We use a mixed integer linear program to obtain the order of communications and computations.
-Recall that $COMP_i$ and $COMM_i$ represent computation and communication times of task $i$, and that the memory capacity of the target system is $C$.
+Recall that $COMP_i$ and $COMM_i$ represent computation and communication times of task $i$, and the memory capacity of the target system is $C$.
 In the linear program formulation, $s_i$ and $e_i$ (resp.
 $s'_i$ and $e'_i$) represent the start and end times of communication (resp.
-computation) for task $i$.
+computation) for task $i$, and $MC(i)$ is the memory capacity requirement of task $i$.
 The formulation also contains for each pair of tasks $i$ and $j$ \textit{i)} a boolean variable $a_{ij}$ to denote the order of $i$ and $j$ on the communication resource \textit{ii)} a boolean variables $b_{ij}$ to denote the order of $i$ and $j$ on the computation resource, and \textit{iii)} a boolean variables $c_{ij}$ to denote the order of $s_i$ and $e'_j$.
@@
 	\forall i, \quad & e'_i \leq l && \text{(task $i$ completes)}\\
-	\forall i, \quad & e_i \leq s'_i&& \text{(valid ordering for task $i$)}\\
+	\forall i, \quad & e_i \leq s'_i&& \text{(task $i$ valid ordering)}\\
 	\forall i, \forall j\ne i, \quad & \left\{\begin{aligned}
@@
 	\end{aligned}\\
-	\forall i, \quad & \sum_{r\ne i} (a_{ir} - c_{ir})CM(r) + CM(i) \le C && \text{(memory constraint)}\\
+	\forall i, \quad & \sum_{r\ne i} (a_{ir} - c_{ir})MC(r) + MC(i) \le C && \text{(memory constraint)}\\
 	%% %%\forall i, \forall j\ne i, \quad & \text{task }T_i \text{ respects memory capacity on computation resource:}\\
@@
 This allows programmers to use appropriate strategies to maximize communication-computation overlap for their applications.
-In this table, ``moderate memory capacity'' refers to the case where memory is constrained, but is close to the maximal memory requirement of the $OMIM$ schedule.
+In this table, ``moderate memory capacity'' refers to the case where memory is constrained, but close to the maximal memory requirement of the $OMIM$ schedule.
 
@@
 		We consider a machine called Cascade~\cite{Cascade}, available at PNNL, for our experiments.
-We obtain traces by running two molecular chemistry applications, double precision version of Hartree-Fock (HF) and Coupled Cluster Single Double (CCSD) of NWChem~\cite{NWChem} package on 10 nodes of this machine.
+We obtain traces by running two molecular chemistry applications, double precision version of  HF and CCSD of NWChem~\cite{NWChem} package on 10 nodes of this machine.
 Each node is composed of 16 Intel Xeon E5-2670 cores.
@@
 
-		To get more insights into the considered workloads, we provide in Figure~\ref{fig:ApplicationProperties} information about
-		the instances we consider.
+		To get more insights into the considered workloads, we provide  information about the instances we consider in Figure~\ref{fig:ApplicationProperties}.
 For each instance, we compute the sum of communication times (\textit{sum comm}) and sum of computation times  (\textit{sum comp}), and normalize it relatively to the $OMIM$ value.
@@
 Static strategies are expected to perform better when there is not any memory capacity restriction, and indeed this plot shows that static strategies face capacity bottleneck and underperform with limited memory.
-Dynamic strategies achieve slightly better performance with limited memory capacity, but when memory capacity is larger, static order with dynamic correction strategies outperform all others.
+Dynamic strategies achieve slightly better performance with limited memory capacity, but when memory capacity is larger, static order with dynamic corrections strategies outperform all others.
 

### 2019-04-15 report/article.tex
A report based on communication work

--- 2019-04-14 ICPP-19/communications.tex
@@
-\documentclass[sigconf]{acmart}
-
-%%%
-%%% \BibTeX command to typeset BibTeX logo in the docs
-%%\AtBeginDocument{%
-%% \providecommand\BibTeX{{%
-%% \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
-
-\copyrightyear{2019}
-\acmYear{2019}
-\setcopyright{acmlicensed}
-\acmConference[ICPP '19]{ICPP 2019: 48th International Conference on Parallel Processing}{August 05--08, 2019}{Kyoto, Japan}
-%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
-%%\acmPrice{15.00}
-%%\acmDOI{10.1145/1122445.1122456}
-%%\acmISBN{978-1-4503-9999-9/18/06}
-
+%
+\documentclass[runningheads]{llncs} %
 \usepackage{graphicx}
@@
 \usepackage{multirow}
+\usepackage{amsmath}
+\usepackage{hyperref}
+%%\usepackage{url}
 
@@
 
-%%\newcommand{\scomm}{\ensuremath{{\cal S}_{\text{COMM}}}}
-%%\newcommand{\scomp}{\ensuremath{{\cal S}_{\text{COMP}}}}
-
-\newcommand{\scomm}{\ensuremath{{S}_{\text{COMM}}}}
-\newcommand{\scomp}{\ensuremath{{S}_{\text{COMP}}}}
+\makeatletter
+\newcommand{\pushright}[1]{\ifmeasuring@#1\else\omit\hfill$\displaystyle#1$\fi\ignorespaces}
+\newcommand{\pushleft}[1]{\ifmeasuring@#1\else\omit$\displaystyle#1$\hfill\fi\ignorespaces}
+\makeatother
+
+\newcommand{\scomm}{\ensuremath{{\cal S}_{\text{COMM}}}}
+\newcommand{\scomp}{\ensuremath{{\cal S}_{\text{COMP}}}}
+
+%%\newcommand{\scomm}{\ensuremath{{S}_{\text{COMM}}}}
+%%\newcommand{\scomp}{\ensuremath{{S}_{\text{COMP}}}}
+
 \newcommand{\threepart}{\textsc{3Par}\xspace}
@@
 
-\begin{document}
-
+\begin{document} %
+	%	\title{Contribution Title\thanks{Supported by organization x.}}
 	\title{Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels}
-
-	\author{Suraj Kumar}
-	\affiliation{%
-		\institution{Pacific Northwest National Laboratory}
-		\city{Richland, Washington, USA}}
-	\email{suraj.kumar@pnnl.gov}
-
-	\author{Lionel Eyraud-Dubois}
-	\affiliation{\institution{Inria Bordeaux -- Sud-Ouest}\institution{Université de Bordeaux, France}}
-	\email{lionel.eyraud-dubois@inria.fr}
-
-	\author{Sriram Krishnamoorthy}
-	\affiliation{
-		\institution{Pacific Northwest National Laboratory}
-		\city{Richland, Washington, USA}}
-	\email{sriram@pnnl.gov}
-
-	\renewcommand{\shortauthors}{Kumar and Eyraud-Dubois, et al.}
-
+	\titlerunning{Performance Models for Data Transfers}
+	% If the article title is too long for the running head, you can set
+	% an abbreviated article title here
 	%
-	% The abstract is a short summary of the work to be presented in the article.
+%%	\author{}
+	\author{Suraj Kumar \inst{1}\and 
+		Lionel Eyraud-Dubois \inst{2}\and 
+		Sriram Krishnamoorthy \inst{1}} %
+	\authorrunning{Kumar and Eyraud-Dubois, et al.} % First names are abbreviated in the running
+%%	% head.
+%%	% If there are more than two authors, 'et al.' is used.
+%%	%
+	\institute{Pacific Northwest National Laboratory, Richland, Washington, USA \\
+		\email{\{suraj.kumar, sriram\}@pnnl.gov}
+		\and
+		 Inria Bordeaux -- Sud-Ouest, Université de Bordeaux, France\\
+		\email{lionel.eyraud-dubois@inria.fr}} %
+	\maketitle              % typeset the header of the contribution
+	%
 	\begin{abstract} 
-		\todo[inline]{Initial submission deadline: April 15}
+%%		
 		With increasing complexity of hardwares, systems with different memory nodes are ubiquitous in High Performance Computing (HPC).
 It is paramount to develop strategies to overlap the data transfers between memory nodes with computations in order to exploit the full potential of these systems.
-In this paper, we consider the problem of deciding the order of data transfers between two memory nodes for a set of independent tasks with the objective to minimize the makespan.
+In this article, we consider the problem of deciding the order of data transfers between two memory nodes for a set of independent tasks with the objective to minimize the makespan.
 We prove that with limited memory capacity, obtaining the optimal order of data transfers is a NP-complete problem.
@@
 Our results show that some of our heuristics achieve significant overlap for moderate memory capacities and are very close to the lower bound of makespan.
-	\end{abstract}
-
-	%%\begin{CCSXML}
-	%%	<ccs2012>
-	%%	<concept>
-	%%	<concept_id>10010520.10010553.10010562</concept_id>
-	%%	<concept_desc>Computer systems organization~Embedded systems</concept_desc>
-	%%	<concept_significance>500</concept_significance>
-	%%	</concept>
-	%%	<concept>
-	%%	<concept_id>10010520.10010575.10010755</concept_id>
-	%%	<concept_desc>Computer systems organization~Redundancy</concept_desc>
-	%%	<concept_significance>300</concept_significance>
-	%%	</concept>
-	%%	<concept>
-	%%	<concept_id>10010520.10010553.10010554</concept_id>
-	%%	<concept_desc>Computer systems organization~Robotics</concept_desc>
-	%%	<concept_significance>100</concept_significance>
-	%%	</concept>
-	%%	<concept>
-	%%	<concept_id>10003033.10003083.10003095</concept_id>
-	%%	<concept_desc>Networks~Network reliability</concept_desc>
-	%%	<concept_significance>100</concept_significance>
-	%%	</concept>
-	%%	</ccs2012>
-	%%\end{CCSXML}
-	\ccsdesc[100]{Computer systems organization~ High Performance Computing }
-	\ccsdesc[100]{Computing Methodologies~Modeling and Simulation}
-	\ccsdesc[100]{General ~ Performance}
-
-	\keywords{Communication Scheduling, Memory Nodes, Runtime Systems, Communication-Computation Overlap, Molecular Chemistry}
-
-	\maketitle
+
+		\keywords{Communication Scheduling  \and Memory Nodes \and Runtime Systems \and Communication-Computation Overlap \and Molecular Chemistry.}
+	\end{abstract} %
 
@@
 It is extremely important for runtimes to decide the order of data transfers for these scheduled computations so as to maximize the overlap between computations and communications.
-This is the main topic of this paper.
+This is the main topic of this article.
 We prove that the order of communications on two memory nodes with the objective of minimizing the makespan is a NP-Complete problem if the memory of the target node is limited.
@@
 However, our approach is generic and easily adaptable to any system which operates on different memory spaces.
-Here are the important contributions of this paper:
+Here are the important contributions of this article:
 
@@
 
-	The outline of the paper is the following.
+The outline of the article is the following.
 Section~\ref{sec:relatedWork} describes past work on the computations with limited memory and similar problems in the literature.
@@
 
-	The problem considered in this paper also can be viewed as a flow shop problem: the communication link can be seen as a processing resource, and each task needs to first be handled by the communication link and then by the computational resource.
+The problem considered in this article also can be viewed as a flow shop problem: the communication link can be seen as a processing resource, and each task needs to first be handled by the communication link and then by the computational resource.
 Communication and computation times of a task can thus be considered as processing times on different machines.
@@
 al for task graphs where memory requirement of each task is highly irregular~\cite{loris-ipdps18}.
-
-	%	\todo[inline]{theoretical/performance work on molecular chemistry kernels}
 
@@
 memory unit $M$ of capacity $C$. Input data for tasks of $ST$
-	reside on another memory unit $M'$. $COMM_i$ is the communication time to
-	transfer input data from $M'$ to $M$ for task $i$ and $COMP_i$
+reside on another memory unit $M'$. $CM_i$ is the communication time to
+transfer input data from $M'$ to $M$ for task $i$ and $CP_i$
 is the computation time of task $i$ on $P$. We assume that these
@@
 amount of memory required by all tasks such that $\scomm(i) \leq t
-	\leq \scomp(i) + COMP_i$ is not more than the memory capacity
+\leq \scomp(i) + CP_i$ is not more than the memory capacity
 $C$. 
-	For simplicity, we assume throughout the paper that tasks
+For simplicity, we assume throughout the article that tasks
 require memory only to store their input data, and thus that
@@
 
-	%% We assume through out the paper that communication time of a task is proportional to memory required by it, and follow conventional \textit{Comm Time = Latency + (Comm Volume)/Bandwidth} model.
+%% We assume through out the article that communication time of a task is proportional to memory required by it, and follow conventional \textit{Comm Time = Latency + (Comm Volume)/Bandwidth} model.
 %%	
-	We call a task $i$ compute intensive if $COMP_i \ge COMM_i$, and
+We call a task $i$ compute intensive if $CP_i \ge CM_i$, and
 communication intensive otherwise.
@@
 		\STATE $\scomm(T) \gets \tau_{\text{COMM}}$
-			\STATE $\scomp(T) \gets max(\scomm(T) + COMM_T, \tau_{\text{COMP}})$
-			\STATE $\tau_{\text{COMM}} \gets \scomm(T) + COMM_T$
-			\STATE $\tau_{\text{COMP}} \gets \scomp(T) + COMP_T$
+		\STATE $\scomp(T) \gets max(\scomm(T) + CM_T, \tau_{\text{COMP}})$
+		\STATE $\tau_{\text{COMM}} \gets \scomm(T) + CM_T$
+		\STATE $\tau_{\text{COMP}} \gets \scomp(T) + CP_T$
 		\ENDWHILE
@@
 
-	We also prove optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} differently in an extended version(cite).
+We  prove optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}  differently. Our proof rely on the following lemma.
+
+\begin{lemma}\label{lemma:swappingOfTasks}
+	Swapping two contiguous tasks $A$ and $B$ in a schedule does not improve the makespan if one of the conditions is true.
+	\begin{enumerate}[label=\roman*)]
+		\item  $CP_A \ge CM_A, CP_B \ge CM_B, CM_A \le CM_B$
+		\item $CP_A < CM_A, CP_B < CM_B, CP_A \ge CP_B$
+		\item $CP_A \ge CM_A, CP_B < CM_B$
+	\end{enumerate}
+\end{lemma}
+\begin{proof}
+	Let $t_1$ and $t_2$ be the early start time on communication and computation resources just before the task $A$ starts.
+
+	\begin{figure}[htb]
+		\centering
+		\includegraphics[scale=0.35]{./original_swapped_schedules-eps-converted-to.pdf}
+		\caption{ \label{fig:bothSchedule} Original and Swapped Schedules.}
+	\end{figure}
+	We write the following constraints based on the two schedules of the Fig~\ref{fig:bothSchedule}.
+
+	\noindent $\scomp(A) = max(t_1 + CM_A, t_2)$ \\
+	\noindent $\scomp(B) = max(\scomp(A) + CP_A,  t_1 + CM_A + CM_B)$\\
+
+	\noindent Completion time of $B$ in original Schedule = $\scomm(B) + CP_B$\\
+	\noindent Completion time of $B$ in swapped Schedule,  $\scomp '(B)  =  max(t_1 + CM_B, t_2)$\\
+	\noindent Completion time of $A$ in swapped Schedule, $ \scomp '(A)$ \newline
+	 \hspace*{0pt}\hfill $ = max(\scomp'(B) + CP_B, t_1 + CM_B + CM_A)$
+
+	\noindent In both schedules, early available time on communication resource after scheduling $A$ and $B$ is same.
+If we show that early available time on computation resource in swapped schedule after scheduling both tasks is not less than the time of original schedule, then the proof is complete.
+Hence our goal is to prove that,
+	$$\scomp(B) + CP_B \le \scomp'(A) + CP_A $$
+
+%%	\begin{eqnarray*}
+%%		\scomp(B) + CP_B & = & max(\scomp(A) + CP_A + CP_B,  t_1 + CM_A + CM_B + CP_B)\\
+%%		& = & max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A\\
+%%		&& + CM_B + CP_B) 
+%%	\end{eqnarray*}
+{\small
+		\begin{align*}
+				\scomp(B) + CP_B & =  &max(\scomp(A) + CP_A + CP_B,  t_1 + CM_A + CM_B + CP_B)\\
+				& = & max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A\\
+				& &+ CM_B + CP_B) 
+		\end{align*}
+	Case I: $CP_A \ge CM_A, CP_B \ge CM_B, CM_A \le CM_B$
+	\begin{align*}
+		\scomp(B) + CP_B & =  max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A \\
+		&\pushright{+ CM_B + CP_B)}\\
+		& \le max(t_1 + CM_A + CP_B, t_2  + CP_B, t_1  + CM_B + CP_B) + CP_A\\
+		& =  max( t_1  + CM_B + CP_B, t_2  + CP_B) + CP_A \\
+		& =  max(max(t_1 + CM_B, t_2) + CP_B, t_1 + CM_A + CM_B) + CP_A\\
+		& =  max(\scomp'(B) + CP_B, t_1 + CM_A + CM_B) + CP_A \\
+		& =  \scomp'(A) + CP_A
+	\end{align*}
+	Case II: $CP_A < CM_A, CP_B < CM_B, CP_A \ge CP_B$
+	\begin{align*}
+		\scomp(B) + CP_B & =  max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A \\
+		& \pushright{+ CM_B + CP_B)}\\
+		& \le  max(t_1 + CM_A + CP_B, t_2+CP_B, t_1 + CM_A + CM_B) + CP_A\\
+		& =  max(t_1 + CM_A + CM_B, t_2+ CP_B) + CP_A \\
+		& =  max(t_1 + CM_B + CP_B, t_2 + CP_B, t_1 + CM(A) + CM_B) + CP_A \\
+		& =  max(max(t_1 + CM_B, t_2) + CP_B, t_1 + CM_A + CM_B) + CP_A \\
+		& =  max(\scomp'(B) + CP_B, t_1 + CM_A +CM_B) + CP_A \\
+		& =  \scomp'(A) + CP_A
+	\end{align*}
+	Case III: $CP_A \ge CM_A, CP_B < CM_B$
+%%	\begin{eqnarray*}
+%%		\scomp(B) + CP_B & = & max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A + CM_B + CP_B)\\
+%%		& \le & max(t_1 + CM_A + CP_B, t_2 + CP_B, t_1 + CM_B + CP_B) + CP_A\\
+%%		& \le & max(t_1 + CM_A + CM_B, t_2 + CP_B, t_1 + CM_B + CP_B) + CP_A \\
+%%		& = & max(max(t_1 + CM_B, t_2) + CP_B, t_1 + CM_A + CM_B) + CP_A \\
+%%		& = & max(\scomp'(B) + CP_B, t_1 + CM_A +CM_B) + CP_A \\
+%%		& = & \scomp'(A) + CP_A
+%%	\end{eqnarray*}
+	\begin{align*}
+	\scomp(B) + CP_B & =  max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A\\ 
+	&\pushright{+ CM_B + CP_B)}\\
+	& \le  max(t_1 + CM_A + CP_B, t_2 + CP_B, t_1 + CM_B + CP_B) + CP_A\\
+	& \le  max(t_1 + CM_A + CM_B, t_2 + CP_B, t_1 + CM_B + CP_B) + CP_A \\
+	& =  max(max(t_1 + CM_B, t_2) + CP_B, t_1 + CM_A + CM_B) + CP_A \\
+	& =  max(\scomp'(B) + CP_B, t_1 + CM_A +CM_B) + CP_A \\
+	& =  \scomp'(A) + CP_A
+\end{align*}
+}
+
+\end{proof}
+
+\begin{theorem}
+	Scheduled constructed by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} achieves optimal makespan.
+\end{theorem}
+
+\begin{proof}
+
+	Let $O$ be an optimal schedule.
+We assume that $O$ is a permuation schedule, If it is not the case, we make the order of computations same as the order of communications without increasing the makespan.
+Suppose two tasks have opposite order on both resources then we position the second task just before the first task on the computation resource.
+It is evident that this change does not alter the optimal  makespan, we repeat this procedure until order of communications and computations is same in $O$.
+
+	Let $S$ be the  schedule obtained from Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}.
+We prove the theorem by converting $S$ to $O$ and showing that at each step makespan of intermediate schedule is not less than the original makespan.
+We rely on Lemma~\ref{lemma:swappingOfTasks} to convert $S$ to $O$.
+
+	We traverse schedule $O$ from left to right and for each $ith$ task in sequence, we apply Lemma~\ref{lemma:swappingOfTasks} repetitively until order of task in the swapped schedule is same.
+It is obvious that after moving the $ith$ task at the beginning remaining schedule (schedule after $ith$ task) still satisfies one of the conditions of Lemma~\ref{lemma:swappingOfTasks}.
+
+	Let the final swapped schedule is $S_{final}$.
+From Lemma~\ref{lemma:swappingOfTasks}, $makespan(S_{final})$ $ \ge $ $makesapn(S)$.
+From the construction, $makespan(S_{final})$ $ \le$ $ makesapn(O)$.
+As $O$ is an optimal schedule, hence $makespan(S) = makesapn(O)$.
+This completes our proof.
+\end{proof}
+
 \subsection{Finite Memory}
@@
 
-		\todo[inline]{SKumar: I understand that proving for an instance with memory requirement = communication time, also proves that, in general, DT problem is NP-hard.
-I was thinking we can directly prove the general version by adding a single line saying what to change.
-I am not sure whether it is good to explicitly mention how to prove the general version.
-I added a line below.
-Feel free to remove it.}
 	As mentioned previously, we consider memory requirement of a task is equal to its communication time.
@@
 problem makes it more difficult. One additional difficulty
-	compared to limited capacity 2-machine
-	flowshop~\cite{Papadimitriou:1980:FSL:322203.322213}  \todo{I think you mean: infinite memory capacity 2-machine flowshop~\cite{johnson}} is that
+compared to infinite memory capacity 2-machine flowshop~\cite{johnson} is that
 it may not be optimal to consider the same ordering on both
@@
 %%	
-	%%	\includegraphics[scale=0.05]{Figs/staticOrderSchedules}
+%%	\includegraphics[scale=0.05]{./staticOrderSchedules}
 %%			\caption{Task set and schedules where orders are precomputed based on different heuristics.}
@@
 \begin{figure}[htb]
+	\begin{center}
 	\newcommand{\taskA}[2][0]{\task[#1]{$A$}{#2}{4}{1}{cyan}}
@@
 	\end{scope}
-		\begin{scope}[yshift=-2.75cm]
+	\begin{scope}[yshift=-3cm]
 	%%		\schedule{36}{OOSCMR}{2,5,8,11,14,18,26,34}
@@
 	\end{scope}
-		\begin{scope}[yshift=-5.5cm]
+	\begin{scope}[yshift=-6cm]
 	\schedule{36}{OOMAMR}{2,8,11,14,17,25,33}
@@
 The $OMIM$ order is $BCDAE$.}
+	\end{center}
 \end{figure}
@@
 %%\begin{figure}[htb]
-	%%\includegraphics[scale=0.05]{Figs/staticOrderDynamicCorrectionsSchedules}
+%%\includegraphics[scale=0.05]{./staticOrderDynamicCorrectionsSchedules}
 %%\caption{Task set and schedules where orders are precomputed based on different heuristics.}
@@
 We use a mixed integer linear program to obtain the order of communications and computations.
-Recall that $COMP_i$ and $COMM_i$ represent computation and communication times of task $i$, and the memory capacity of the target system is $C$.
+Recall that $CP_i$ and $CM_i$ represent computation and communication times of task $i$, and the memory capacity of the target system is $C$.
 In the linear program formulation, $s_i$ and $e_i$ (resp.
@@
 
-	\noindent Let $L=\sum_i (COMP_i + COMM_i)$. It is evident that $e_i =s_i + COMM_i$ and $e'_i =s'_i + COMP_i$. The linear program is given below.
+\noindent Let $L=\sum_i (CP_i + CM_i)$. It is evident that $e_i =s_i + CM_i$ and $e'_i =s'_i + CP_i$. The linear program is given below.
 
@@
 We compute various $lp.k$ values for different memory capacities and observe that most of the other heuristics perform better than this heuristic.
-Hence, we do not include this heuristic for the comparison in Section~{\ref{sec:expResults}.
-Performance comparison of different heuristics with MILP based heuristics is available in an extended version(cite).
-
-		%%		\todo[inline]{SKumar: Move to an extended version and more clear about results and implementation}
-		%%		Figure~\ref{fig:iterativeLpSolution} shows the performance of different heuristics with MILP based heuristics for various memory capacities of a single trace file.
-		%%		%%	\subsection{MILP Based Strategy}
-		%%		%%We use GLPK solver v4.65 to solve the MILP formulation described in Section~\ref{subsec:linearprogrammingformulation}.
-The solver was unable to handle number of variables required to solve MILP at the scale of our interest.
-Hence, we solve the linear program iteratively for a small subset of size $k=3,4,5$ (solver was unable to handle number of variables required for $k\ge6$ ) and represent the makespan calculated by this heuristic as $lp.k$.
-At the boundary of two iterations we fixed the event (communication or computation) of an unfinished task who has started before the boundary point and consider other events flexible.
-We compute various $lp.k$ values for different memory capacities and observe that most of the other heuristics perform better than this heuristic.
-Figure~\ref{fig:iterativeLpSolution} shows the comparison of different heuristics with MILP based heuristic for various memory capacities of a single trace file.
-		%%		\todo[inline]{SKumar: Figure~\ref{fig:iterativeLpSolution} would be removed and I will redraw this or similar figure for extended version}
-		%%		\begin{figure}[htb]
-		%%			\includegraphics[scale=0.5]{./results/makespan_with_lp.pdf}
-		%%			\caption{Comparision of different heuristics with MILP solution based heuristic.\todo[inline]{LED: I understand that this figure will be removed?
-Otherwise, use aes(fill=) instead of aes(color=) to have color filled bars.}}
-		%%			\label{fig:iterativeLpSolution}
-		%%		\end{figure}
+Figure~\ref{fig:iterativeLpSolution} shows the performance of different heuristics with MILP based heuristics for various memory capacities of a single trace file.
+
+			\begin{figure}[htb]
+				\begin{center}
+				\includegraphics[scale=0.5]{./makespan_with_lp.pdf}
+				\caption{Comparision of proposed heuristics heuristics with MILP solution based heuristic for different memory capacities of a single trace file .
+Here  minimum memory requirement to process all tasks is $m_c=176KB$.}
+				\label{fig:iterativeLpSolution}
+				\end{center}
+			\end{figure}
 
@@
 	\begin{table}[htb]
-			\begin{tabular}{|c|p{6.5cm}|}
+		\begin{center}
+		\begin{tabular}{|c|p{10.25cm}|}
 			\hline
@@
 		\end{tabular}\caption{~\label{tab:heuristicsAndFavorableScenarios}Heuristics and their favorable scenarios.}
+		\end{center}
 	\end{table}
@@
 CCSD has significant percentage of both types of tasks, and indeed the performance of $OOLCMR$ and $OOSCMR$ is very close to optimality in moderate memory cases.
-		%%		\todo[inline]{Skumar: Initially I placed this table after results.
-Then I realized that this is our hypothesis not conclusion.
-Only few favorable scenarios are matched with results.
-We do not have enough results to show favorable scenarios for all of them.}
-		%%		\todo[inline]{LED: Ok. I did a rephrasing there to go in this direction, make sure it fits the message you wanted to say.}
 
@@
 
-		\subsection{Workload Characteristics}
-
 		\begin{figure}[htb]
-			%\begin{tabular}{c}
-			\includegraphics[scale=0.5]{./results/application_properties.pdf}
+		\begin{center}
+			\includegraphics[scale=0.5]{./application_properties.pdf}
 			\caption{HF and CCSD tasks characteristics.}
 			\label{fig:ApplicationProperties}
+		\end{center}
 		\end{figure}
+
+	\subsection{Workload Characteristics}
 
@@
 	\label{sec:expResults}
+
+		\begin{figure*}[htb]
+		\includegraphics[scale=0.5]{./ratio_to_optimal_hf.pdf}
+		\caption{Comparison of different heuristics for HF with $m_c=176KB$.}
+		\label{fig:ratio_to_optimal_hf}
+		\end{figure*}	
 		We evaluate our scheduling heuristics for several memory capacities.
@@
 	\subsection{HF Performance}
-		\begin{figure*}[htb]
-			\includegraphics[scale=0.5]{./results/ratio_to_optimal_selected_hf.pdf}
-			\caption{Comparison of different heuristics for HF with $m_c=176KB$.}
-			\label{fig:ratio_to_optimal_hf}
-		\end{figure*}
+
+	\begin{figure}[htb]
+	\begin{center}
+		\includegraphics[scale=0.7]{./ratio_to_optimal_hf-best.pdf}
+		\caption{Comparision of best variants of all categories for HF.}
+		\label{fig:ratio_to_optimal_best_hf}
+	\end{center}
+	\end{figure}
 
@@
 Surprisingly, the $BP$ heuristic which considers only memory constraint obtains good performance for a static heuristic, but is outperformed by more dynamic approaches.
-		%%		\todo{you mean infinite memory? SKumar: GG is classic in no-wait (or no buffer) 2-macine flowshop}
-
-		\begin{figure}[htb]
-			%%			\includegraphics[scale=0.5]{./results/inverse_ratio_to_optimal_hf-best.pdf}
-			\includegraphics[scale=0.5]{./results/ratio_to_optimal_hf-best.pdf}
-			\caption{Comparision of best variants of all categories for HF.}
-			\label{fig:ratio_to_optimal_best_hf}
-		\end{figure}
 
@@
 Dynamic strategies achieve slightly better performance with limited memory capacity, but when memory capacity is larger, static order with dynamic corrections strategies outperform all others.
-
-		%%		\todo[inline]{SKumar: If you look at Figure~\ref{fig:ratio_to_optimal_best_hf} carefully,  in the beginning dynamics variants outperform others.
-This behavior is easily noticeable in Figure~\ref{fig:ratio_to_optimal_hf}.
-}
-		%%		\todo[inline]{LED: Ok, I rephrased here a bit to mention this.}
-
-		\subsection{CCSD Performance}
-		\begin{figure*}[htb]
-			\includegraphics[scale=0.5]{./results/ratio_to_optimal_selected_ccsd.pdf}
+		\begin{figure}[htb]
+		\begin{center}
+			\includegraphics[scale=0.5]{./ratio_to_optimal_ccsd.pdf}
 			\caption{Comparison of different heuristics for CCSD with $m_c=1.8GB$.}
 			\label{fig:ratio_to_optimal_ccsd}
-		\end{figure*}
+	\end{center}
+	\end{figure}
+
+	\subsection{CCSD Performance}
 
@@
 	\begin{figure}[htb]
-			%%			\includegraphics[scale=0.5]{./results/inverse_ratio_to_optimal_ccsd-best.pdf}
-			\includegraphics[scale=0.5]{./results/ratio_to_optimal_ccsd-best.pdf}
+		\begin{center}
+		\includegraphics[scale=0.7]{./ratio_to_optimal_ccsd-best.pdf}
 		\caption{Comparision of best variants of all categories for CCSD.}
 		\label{fig:ratio_to_optimal_best_ccsd}
+		\end{center}
 	\end{figure}
 
+			\begin{figure}[!ht]
+		\begin{center}
+			\includegraphics[scale=0.65]{./ratio_to_optimal_batch-best.pdf}
+			\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
+			\label{fig:best_variants_batch}
+		\end{center}
+		\end{figure}
 	Figure~\ref{fig:ratio_to_optimal_best_ccsd} shows that best variants of dynamic and static order with dynamic corrections strategies achieve similar performance at minimum memory capacity $m_c$.
@@
 The plots exhibit behavior similar to Figures~\ref{fig:ratio_to_optimal_best_hf} and~\ref{fig:ratio_to_optimal_best_ccsd}: static order with dynamic corrections variants attain maximum communication-computation overlap and outperform other heuristics.
-
-		\begin{figure*}[htb]
-			%%			\includegraphics[scale=0.5]{./results/inverse_ratio_to_optimal_batch-best.pdf}
-			\includegraphics[scale=0.5]{./results/ratio_to_optimal_batch-best.pdf}
-			\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
-			\label{fig:best_variants_batch}
-		\end{figure*}
-
-		%%\begin{figure}[htb]
-		%%	\centering
-		%%	\begin{subfigure}{.5\textwidth}
-		%%		\centering
-		%%		\includegraphics[width=.95\linewidth]{../ExperimentalResults/batch-100/inverse_ratio_to_optimal_hf_batch-best.pdf}
-		%%		\caption{Best variants of HF.}
-		%%		\label{fig:hf_best_variants_batch}
-		%%	\end{subfigure}%
-		%%	\begin{subfigure}{.5\textwidth}
-		%%		\centering
-		%%		\includegraphics[width=.95\linewidth]{../ExperimentalResults/batch-100/inverse_ratio_to_optimal_ccsd_batch-best.pdf}
-		%%		\caption{Best variants of CCSD.}
-		%%		\label{fig:ccsd_best_variants_batch}
-		%%	\end{subfigure}
-		%%	\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
-		%%	\label{fig:best_variants_batch}
-		%%\end{figure}
 
@@
 
-		In this paper, we consider the problem of deciding the order of data transfers between two memory nodes such that overlap of communications and computations is maximized.
+		In this article, we consider the problem of deciding the order of data transfers between two memory nodes such that overlap of communications and computations is maximized.
 With Exascale computing, applications face bottlenecks due to communications.
@@
 
-		\begin{acks}
-
-			We are grateful to Ajay Panyala for his help in installation of  NWChem on Cascade machine and providing internal details about the package and its inputs.
-This work was supported in part by the U.S.
-Department of Energy (DOE), Office of Science, Office of Advanced Scientific Computing Research, under award 63823.
-Pacific Northwest National Laboratory is operated by Battelle for DOE under Contract DE-AC05-76RL01830.
-		\end{acks}
-
-		%
-		% The next two lines define the bibliography style to be used, and the bibliography file.
-		\bibliographystyle{ACM-Reference-Format}
-		\bibliography{communications}
+\bibliographystyle{IEEEtran}
+% argument is your BibTeX string definitions and bibliography database(s)
+\bibliography{article}
 

### 2019-04-15 report/plots/all_heuristics_with_lp.R

@@ -1,0 +1,11 @@
+#!/usr/bin/env Rscript
+library(reshape2)
+library(ggplot2)
+dftest<-read.table('single_trace_results_withlp.txt', header=T)
+dftest[,c(2:5)]<-NULL
+dftestMelted<-melt(dftest, "capacity")
+names(dftestMelted)<-c("capacity", "Heuristic", "makespan")
+dftestMelted$mc <- factor(dftestMelted$capacity, labels = c("m[c]", "1.125~m[c]", "1.25~m[c]","1.375~m[c]", "1.5~m[c]", "1.625~m[c]", "1.75~m[c]", "1.875~m[c]", "2~m[c]"))
+p <- ggplot(dftestMelted, aes(x=Heuristic, y=makespan, fill=Heuristic)) + geom_bar(stat="identity") + facet_wrap(~mc,
+        labeller=label_parsed)  + theme(axis.ticks = element_blank(), axis.text.x = element_text(angle=75, hjust=1)) + xlab("")
+ggsave(file="makespan_with_lp.pdf", p,  width=10.5, height=9)

### 2019-04-15 report/plots/insights.R

@@ -1,0 +1,52 @@
+#!/usr/bin/env Rscript
+insights_func <-function(file_name)
+{
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+
+
+dftest[,1:ncol(dftest)]<-dftest[,1:ncol(dftest)]/dftest[,5]
+dftest[,5]<-NULL
+dftestMelted<-melt(dftest)
+names(dftestMelted)<-c( "Parameter", "ratio_to_optimal")
+p<-ggplot(dftestMelted, aes(x=Parameter, y=ratio_to_optimal, color=Parameter))  + geom_boxplot(outlier.color="black") + geom_hline(yintercept=1, linetype="dashed", color = "red")
+p <- p + theme(plot.title = element_text(hjust = 0.5), legend.position='none') +  ggtitle("Application Properties") + scale_y_continuous(breaks=seq(0.0, 2.0, 0.5), limits=c(0, 2))
+#p <- p + theme(plot.title = element_text(hjust = 0.5), legend.position='none') +  ggtitle("Application Properties") 
+
+return (p)
+}
+#p<-insights_func('insight_hf.txt')
+#w=20
+#h=10
+#ggsave(file="application_properties_hf.pdf", p, width=w, height=h)
+#
+#p<-insights_func('insight_ccsd.txt')
+#ggsave(file="application_properties_ccsd.pdf", p, width=w, height=h)
+
+get_melted_data_frame<-function(file_name)
+{
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+colnames(dftest)[colnames(dftest) == "sum_comm" ] <- "sum comm"
+colnames(dftest)[colnames(dftest) == "sum_comp" ] <- "sum comp"
+colnames(dftest)[colnames(dftest) == "sum_comm_comp" ] <- "sum comm + sum comp"
+colnames(dftest)[colnames(dftest) == "max.sum_comm.sum_comp." ] <- "max(sum comm, sum comp)"
+dftest[,1:ncol(dftest)]<-dftest[,1:ncol(dftest)]/dftest[,5]
+dftest[,5]<-NULL
+dftest<-dftest[,c(3,4,2,1)]
+dftestMelted<-melt(dftest)
+names(dftestMelted)<-c( "Parameter", "ratio_to_optimal")
+return (dftestMelted)
+}
+dfMelted1<-get_melted_data_frame('insight_hf.txt');
+dfMelted1$application <- "HF Workload"
[…]

### 2019-04-15 report/plots/ratio_to_optimal-best.R

@@ -1,0 +1,31 @@
+#!/usr/bin/env Rscript
+ratio_to_optimal_best_func <-function(file_name)
+{
+library(ggplot2)
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
+
+#dftest[,8]<-NULL
+dftest[,c(2:6)]<-NULL
+dftest$"Best Static"<-do.call('pmin', c(dftest[,3:9]))
+dftest$"Best Dynamic" <-do.call('pmin', c(dftest[,10:12]))
+dftest$"Best Static Dynamic"<-do.call('pmin', c(dftest[,13:15]))
+dftest<-dftest[,c(1,2,16:18)]
+dftestMelted<-melt(dftest, "capacity")
+names(dftestMelted)<-c("Capacity", "Heuristic", "ratio_to_optimal")
+#p<-ggplot(dftestMelted, aes(x=jitter(capacity), y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth()
+#p<-ggplot(dftestMelted, aes(x=Capacity, y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth(method="loess")
+p<-ggplot(dftestMelted, aes(x=Capacity, y=ratio_to_optimal, color=Heuristic))  + geom_smooth(method="loess") +
+geom_point()
+#p<-p + ylab("inverse(ratio_to_optimal)") + theme(plot.title = element_text(hjust = 0.5), legend.position="bottom") +  ggtitle("Performance With Best of all categories")
+p<-p + ylab("Ratio to Optimal") + xlab ("Memory Capacity") + theme(legend.position="bottom")
+return (p)
+}
+
+p<-ratio_to_optimal_best_func('all_results_hf.txt')
+ggsave(file="ratio_to_optimal_hf-best.pdf", p, width=6.5, height=5)
+
+p<-ratio_to_optimal_best_func('all_results_ccsd.txt')
+ggsave(file="ratio_to_optimal_ccsd-best.pdf", p, width=6.5, height=5)
+

### 2019-04-15 report/plots/ratio_to_optimal.R

@@ -1,0 +1,36 @@
+#!/usr/bin/env Rscript
+ratio_to_optimal_func <-function(file_name)
+{
+library(ggplot2)
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
+dftest[,2:6]<-NULL
+dftestMelted<-melt(dftest, "capacity")
+names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
+#dftestMelted$mc <- factor(dftestMelted$capacity, labels = c('m_c', "1.125m_c", "1.375m_c", "1.5m_c", "1.625m_c", "1.75m_c", "1.875m_c", "2m_c"))
+dftestMelted$mc <- factor(dftestMelted$capacity, labels = c("m[c]", "1.125~m[c]", "1.25~m[c]","1.375~m[c]", "1.5~m[c]", "1.625~m[c]", "1.75~m[c]", "1.875~m[c]", "2~m[c]"))
+p<-ggplot(dftestMelted, aes(x=Heuristic, y=ratio_to_optimal, color=Heuristic)) + geom_boxplot(outlier.color="black") +
+#facet_wrap(~capacity, ncol=4)  + theme(axis.ticks = element_blank(), axis.text.x = element_blank()) + xlab("") +
+facet_wrap(~mc, labeller=label_parsed)  + theme(axis.ticks = element_blank(), axis.text.x = element_blank()) + xlab("") +
+ylab("Ratio to Optimal")
+#p <- p + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Ratio to Optimal")
+return (p)
+}
+p<-ratio_to_optimal_func('all_results_hf.txt')
+ggsave(file="ratio_to_optimal_hf.pdf", p, width=9.5, height=7.5)
+
+p<-ratio_to_optimal_func('all_results_ccsd.txt')
+ggsave(file="ratio_to_optimal_ccsd.pdf", p, width=9.5, height=7.5)
+
+#p<-ratio_to_optimal_func('selected_results_hf.txt')
+#ggsave(file="ratio_to_optimal_selected_hf.pdf", p, width=14.25, height=6.5)
+#
+#p<-ratio_to_optimal_func('selected_results_ccsd.txt')
+#ggsave(file="ratio_to_optimal_selected_ccsd.pdf", p, width=14.25, height=6.5)
[…]

### 2019-04-15 report/plots/ratio_to_optimal_batch-best.R

@@ -1,0 +1,55 @@
+#!/usr/bin/env Rscript
+ratio_to_optimal_best_func <-function(file_name)
+{
+library(ggplot2)
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
+
+dftest[,c(2:6)]<-NULL
+dftest$static_best<-do.call('pmin', c(dftest[,3:7]))
+dftest$dynamic_best<-do.call('pmin', c(dftest[,8:10]))
+dftest$static_dynamic_best<-do.call('pmin', c(dftest[,11:13]))
+dftest<-dftest[,c(1,2,14:16)]
+dftestMelted<-melt(dftest, "capacity")
+names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
+p<-ggplot(dftestMelted, aes(x=capacity, y=1/ratio_to_optimal, color=Heuristic))  + geom_smooth(method="loess")
+p<-p + ylab("inverse(ratio_to_optimal)") + theme(plot.title = element_text(hjust = 0.5)) +  ggtitle("Performance With Best of all categories")
+return (p)
+}
+#p<-ratio_to_optimal_best_func('results_batch_hf.txt')
+#ggsave(file="ratio_to_optimal_hf_batch-best.pdf", p, width=23.6, height=13.4)
+#
+#p<-ratio_to_optimal_best_func('results_batch_ccsd.txt')
+#ggsave(file="ratio_to_optimal_ccsd_batch-best.pdf", p, width=23.6, height=13.4)
+
+get_melted_data_frame <-function(file_name)
+{
+library(ggplot2)
+library(reshape2)
+dftest<-read.table(file_name, header=T)
+dftest[,2:ncol(dftest)]<-dftest[,2:ncol(dftest)]/dftest[,6]
+
+dftest[,c(2:6)]<-NULL
+dftest$"Best Static"<-do.call('pmin', c(dftest[,3:7]))
+dftest$"Best Dynamic"<-do.call('pmin', c(dftest[,8:10]))
+dftest$"Best Static Dynamic"<-do.call('pmin', c(dftest[,11:13]))
+dftest<-dftest[,c(1,2,14:16)]
+dftestMelted<-melt(dftest, "capacity")
+names(dftestMelted)<-c("capacity", "Heuristic", "ratio_to_optimal")
+return (dftestMelted)
+}
+
[…]

### 2019-04-15 ICPP-19/communications.tex
table decription

@@
 
-	We also prove optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} differently in an extended version(cite).
+	We also prove optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} differently in an extended version~\cite{waitingForExactBib}.
 	\subsection{Finite Memory}
@@
 Hence, we do not include this heuristic for the comparison in Section~{\ref{sec:expResults}.
-Performance comparison of different heuristics with MILP based heuristics is available in an extended version(cite).
+Performance comparison of different heuristics with MILP based heuristics is available in an extended version~\cite{waitingForExactBib}.
 
@@
 				$SCMR$ & Limited memory capacity and significant percentage of tasks with small communication times are compute intensive\\ \hline
-				$MAMR$ & Limited memory capacity and significant percentage of tasks of both types\\ \hline
-				$OOLCMR$ & Moderate memory capacity and significant percentage of tasks are communication intensive\\ \hline
-				$OOSCMR$ & Moderate memory capacity and significant percentage of tasks are compute intensive \\ \hline
-				$OOMAMR$ & Moderate memory capacity and significant percentage of highly compute and communication intensive tasks \\ \hline
+				$MAMR$ & Limited memory capacity and significant percentage of all types of tasks\\ \hline
+				$OOLCMR$ & Moderate memory capacity and significant percentage of slightly communication intensive tasks have large communication times\\ \hline
+				$OOSCMR$ & Moderate memory capacity and significant percentage of slightly communication intensive tasks have small communication times\\ \hline
+				$OOMAMR$ & Moderate memory capacity and significant percentage of all types of tasks \\ \hline
 			\end{tabular}\caption{~\label{tab:heuristicsAndFavorableScenarios}Heuristics and their favorable scenarios.}
@@
 For example, HF compute intensive tasks have small communication times, which explains why the $SCMR$ heuristic exhibits very good performance in limited memory cases.
-CCSD has significant percentage of both types of tasks, and indeed the performance of $OOLCMR$ and $OOSCMR$ is very close to optimality in moderate memory cases.
+CCSD has significant percentage of large as well as small types of slightly communication intensive tasks, and indeed the performance of $OOLCMR$ and $OOSCMR$ is very close to optimality in moderate memory cases.
 		%%		\todo[inline]{Skumar: Initially I placed this table after results.

### 2019-04-15 ICPP-19/communications.tex
minor

@@
 It is also possible that all output data can be stored in a preallocated separate buffer on a memory node.
-Hence, we do not consider output data explicitely in our analysis and assume that output data is negligible or stored in a separate buffer for each task.
+Hence, we do not consider output data explicitly in our analysis and assume that output data is negligible or stored in a separate buffer for each task.
 Thus problem considered here is more similar to a 2-machine flowshop problem.
@@
 
-		\todo[inline]{SKumar: I understand that proving for an instance with memory requirement = communication time, also proves that, in general, DT problem is NP-hard.
+		%%		\todo[inline]{SKumar: I understand that proving for an instance with memory requirement = communication time, also proves that, in general, DT problem is NP-hard.
 I was thinking we can directly prove the general version by adding a single line saying what to change.
@@
 Feel free to remove it.}
-		As mentioned previously, we consider memory requirement of a task is equal to its communication time.
+		%%                \todo[inline]{I feel like it does not add anything, and risks confusing the reader.}
+		%% As mentioned previously, we consider memory requirement of a task is equal to its communication time.
 If it is not the case, we can adjust $C$ such that at any point in a schedule at max one $K_i$ and three $A_i$ tasks can be active.
@@
 		$K_i$. Since the memory capacity is $C=b'+3$, all tasks from a triplet
-		can fit in memory with a task $K_i$, and their durations are exactly
+		can fit in memory with a task $K_i$, and their computation times are exactly
 		equal to the communication time of $K_i$. This schedule is thus
@@
 		first show that no other $K_i$ task can be active with $K_0$,
-		otherwise we would get idle time on computation resource. Indeed, the
+		otherwise we would get idle time on the computation resource. Indeed, the
 		communication of such a task $K_i$ would end at time at least $b'>3 +
@@
 		resource contains $m$ slots of length exactly $b'$, in which all $A_i$
-		tasks must fit without preemption. We can thus define triplet $TR_i$
+		tasks must fit without preemption. \todo[inline]{SKumar: It is not clear why it would be triplet}
+		\todo[inline]{At each point in $S$, exactly one $K_i$ task is active, hence we define triplet $TR_{i+}$ as the set of tasks which complete their data transfers when $K_i$ task is in computation phase.
+As $C=b'+3$ and $S$ has no idle time on the communication resource, total computation time of tasks in $TR_{i+1}$ must not be more than $b'$.
+$S$ also has no idle time on the computation resource, therefore total computation time of tasks in $TR_i$ is exactly $b'$, and thus $a_{i_1} + a_{i_2} + a_{i_3} = b$.
+} We can thus define triplet $TR_i$
 		as the set of tasks which execute during the communication phase of
@@
 	This theorem shows that adding a memory constraint to our
-	problem makes it more difficult. One additional difficulty
-	compared to limited capacity 2-machine
-	flowshop~\cite{Papadimitriou:1980:FSL:322203.322213}  \todo{I think you mean: infinite memory capacity 2-machine flowshop~\cite{johnson}} is that
-	it may not be optimal to consider the same ordering on both
-	machines:
+	problem makes it more difficult, just like it does for limited capacity 2-machine
+	flowshop~\cite{Papadimitriou:1980:FSL:322203.322213}. One additional difficulty of our problem however 
+	%%       \todo[inline]{I think you mean: infinite memory capacity 2-machine flowshop~\cite{johnson} ? LED: No, I really mean this one. Does this rephrasing help ?} 
+	is that it may not be
+	optimal to consider the same order on both machines.
 
@@
 		\item \textit{optimal order infinite memory smallest communication task respects memory restriction} ($OOSCMR$): A task with the smallest communication time is chosen from the set.
-		\item \textit{optimal order infinite memory maximum accelerated task respects memory restriction} ($OOMAMR$): A task  with the highest ratio of computation time to communication time is chosen from the set.
+		\item \textit{optimal order infinite memory maximum accelerated task respects memory restriction} ($OOMAMR$): A task  with the maximum ratio of computation time to communication time is chosen from the set.
 	\end{enumerate}
@@
 We apply each heuristic on each group in succession.
-Figure~\ref{fig:best_variants_batch} shows the performance of the best variants of each category for both applications.
+Figure~\ref{fig:best_variants_batch} shows the performance of the best variant of each category for both applications.
 The plots exhibit behavior similar to Figures~\ref{fig:ratio_to_optimal_best_hf} and~\ref{fig:ratio_to_optimal_best_ccsd}: static order with dynamic corrections variants attain maximum communication-computation overlap and outperform other heuristics.

### 2019-04-16 ICPP-19/communications.tex
minor

@@
 		tasks must fit without preemption. \todo[inline]{SKumar: It is not clear why it would be triplet}
-		\todo[inline]{At each point in $S$, exactly one $K_i$ task is active, hence we define triplet $TR_{i+}$ as the set of tasks which complete their data transfers when $K_i$ task is in computation phase.
-As $C=b'+3$ and $S$ has no idle time on the communication resource, total computation time of tasks in $TR_{i+1}$ must not be more than $b'$.
+		\todo[inline]{At each point in $S$, exactly one $K_i$ task is active, hence we define triplet $TR_{i}$ as the set of tasks which complete their data transfers when $K_i$ task is in computation phase.
+As $C=b'+3$ and $S$ has no idle time on the communication resource, total computation time of tasks in $TR_{i}$ must not be more than $b'$.
 $S$ also has no idle time on the computation resource, therefore total computation time of tasks in $TR_i$ is exactly $b'$, and thus $a_{i_1} + a_{i_2} + a_{i_3} = b$.

### 2019-04-16 ICPP-19/communications.tex
minor

@@
 \usepackage{multirow}
+\usepackage{dblfloatfix}
 
@@
 
-	\section{Data Transfer Problem Formulation}
+%%	\section{Data Transfer Problem Formulation}
+	\section{Problem Formulation}
 	\label{sec:theoreticalProof}
@@
 
-	\subsection{Special case: Infinite Memory}
+	\subsection{Special Case: Infinite Memory}
 
@@
 
-	We also prove optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} differently in an extended version~\cite{waitingForExactBib}.
+	We also prove optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} differently in an extended version~\cite{extendedVersion}.
 	\subsection{Finite Memory}
@@
 
-		\caption{ \label{fig:staticOrderExample} Different static order heuristic schedules for Table~\ref{tab:staticOrderExample}}. 
+		\caption{ \label{fig:staticOrderExample} Different static order heuristic schedules for Table~\ref{tab:staticOrderExample}.} 
 		%%			Optimal schedule length	is 14. 
@@
 
-	\subsection{Additional heuristics from previous work}
+	\subsection{Additional Heuristics from Previous Work}
 
@@
 Hence, we do not include this heuristic for the comparison in Section~{\ref{sec:expResults}.
-Performance comparison of different heuristics with MILP based heuristics is available in an extended version~\cite{waitingForExactBib}.
+Performance comparison of different heuristics with MILP based heuristics is available in an extended version~\cite{extendedVersion}.
 
@@
 		%%			\includegraphics[scale=0.5]{./results/makespan_with_lp.pdf}
-		%%			\caption{Comparision of different heuristics with MILP solution based heuristic.\todo[inline]{LED: I understand that this figure will be removed?
+		%%			\caption{Comparison of different heuristics with MILP solution based heuristic.\todo[inline]{LED: I understand that this figure will be removed?
 Otherwise, use aes(fill=) instead of aes(color=) to have color filled bars.}}
@@
 			\includegraphics[scale=0.5]{./results/ratio_to_optimal_hf-best.pdf}
-			\caption{Comparision of best variants of all categories for HF.}
+			\caption{Best variants of all categories for HF.}
 			\label{fig:ratio_to_optimal_best_hf}
@@
 			\includegraphics[scale=0.5]{./results/ratio_to_optimal_ccsd-best.pdf}
-			\caption{Comparision of best variants of all categories for CCSD.}
+			\caption{Best variants of all categories for CCSD.}
 			\label{fig:ratio_to_optimal_best_ccsd}

### 2019-04-18 ICPP-19/communications.tex
rephrasing few things

@@
 	\begin{abstract}
-		\todo[inline]{Initial submission deadline: April 15}
+		%%		\todo[inline]{Initial submission deadline: April 15}
 		With increasing complexity of hardwares, systems with different memory nodes are ubiquitous in High Performance Computing (HPC).
@@
 		With these $K_i$ tasks in place, the schedule on the computation
-		resource contains $m$ slots of length exactly $b'$, in which all $A_i$
-		tasks must fit without preemption. \todo[inline]{SKumar: It is not clear why it would be triplet}
-		\todo[inline]{At each point in $S$, exactly one $K_i$ task is active, hence we define triplet $TR_{i}$ as the set of tasks which complete their data transfers when $K_i$ task is in computation phase.
+		resource contains $m$ slots of length exactly $b'$, in which all $3m$ $A_i$ tasks must fit without preemption. 
+		%%\todo[inline]{SKumar: It is not clear why it would be triplet.\\ LED: because two tasks last at most $2\max a'_i =6x$, whereas $b'>6x$.
+And if any triplet actually contains $4$ tasks, it means one contains only two tasks, and cannot fit in $b'$.
+Or equivalently, the number of tasks per triplet is at least $3$, and the average number is $3$, hence each triplet contains $3$ tasks.}
+		%%	\todo[inline]{At each point in $S$, exactly one $K_i$ task is active, hence we define triplet $TR_{i}$ as the set of tasks which complete their data transfers when $K_i$ task is in computation phase.
 As $C=b'+3$ and $S$ has no idle time on the communication resource, total computation time of tasks in $TR_{i}$ must not be more than $b'$.
 $S$ also has no idle time on the computation resource, therefore total computation time of tasks in $TR_i$ is exactly $b'$, and thus $a_{i_1} + a_{i_2} + a_{i_3} = b$.
-} We can thus define triplet $TR_i$
-		as the set of tasks which execute during the communication phase of
-		task $K_i$. Since at each point in $S$, exactly one $K_i$ task is
-		active, and since $S$ has no idle time on the computation resource,
-		the total computation time of tasks in $TR_i$ is exactly $b'$, and thus
+}
+		We thus define $TR_i$ as the set of tasks which execute during the communication phase of task $K_i$.
+At each point in $S$, exactly one $K_i$ task is active and the total memory capacity is $b' +3$, hence $TR_i$ contains exactly 3 tasks.
+Since $S$ has no idle time on the computation resource, the total computation time of tasks in $TR_i$ is exactly $b'$, and thus
 		$a_{i_1} + a_{i_2} + a_{i_3} = b$. This partition is thus a valid
@@
 
-		\caption{ \label{fig:staticOrderExample} Different static order heuristic schedules for Table~\ref{tab:staticOrderExample}.} 
+		\caption{ \label{fig:staticOrderExample} Static order heuristic schedules for Table~\ref{tab:staticOrderExample}.} 
 		%%			Optimal schedule length	is 14. 
@@
 If no task fits in memory then we leave the resource idle at that point and proceed to the next event point.
-We also ensure that the order on both resources is the same, by ordering tasks on the computation resource accordingly.
+%%	We also ensure that the order on both resources is the same, by ordering tasks on the computation resource accordingly.
 
@@
 			%\begin{tabular}{c}
-			\includegraphics[scale=0.5]{./results/application_properties.pdf}
+			\includegraphics[scale=0.48]{./results/application_properties.pdf}
 			\caption{HF and CCSD tasks characteristics.}

### 2019-04-20 ICPP-19/communications.tex
attempt to fit the document in 10 pages

@@
 		%%		\todo[inline]{Initial submission deadline: April 15}
-		With increasing complexity of hardwares, systems with different memory nodes are ubiquitous in High Performance Computing (HPC).
-It is paramount to develop strategies to overlap the data transfers between memory nodes with computations in order to exploit the full potential of these systems.
-In this paper, we consider the problem of deciding the order of data transfers between two memory nodes for a set of independent tasks with the objective to minimize the makespan.
-We prove that with limited memory capacity, obtaining the optimal order of data transfers is a NP-complete problem.
-We propose several heuristics for this problem and provide details about their favorable situations.
-We present an analysis of our heuristics on traces, obtained by running 2 molecular chemistry kernels, namely, Hartree–Fock (HF) and Coupled Cluster Single Double (CCSD) on 10 nodes of an HPC system.
-Our results show that some of our heuristics achieve significant overlap for moderate memory capacities and are very close to the lower bound of makespan.
+		%With increasing hardware complexity and systems with different memory nodes are ubiquitous in High Performance Computing (HPC). 
+		In distributed memory systems, it is paramount to develop strategies to overlap the data transfers between memory nodes with the computation in order to exploit the full potential of these systems.
+In this paper, we consider the problem of determining the order of data transfers between two memory nodes for a set of independent tasks with the objective of minimizing the makespan.
+We prove that, with limited memory capacity, the problem of obtaining the optimal order of data transfers is NP-complete.
+We propose several heuristics to determine this order and discuss the conditions that might be favorable to different heuristics.
+We analyze our heuristics on traces obtained by running 2 molecular chemistry kernels, namely, Hartree–Fock (HF) and Coupled Cluster Single Double (CCSD) on 10 nodes of an HPC system.
+Our results show that some of our heuristics achieve significant overlap for moderate memory capacities and resulting in makespans that are very close to the lower bound.
 	\end{abstract}
@@
 In irregular applications, programmers do not know the precise structure of the task graphs in advance: tasks are added recursively based on certain sentinel constraints.
-For such applications, the runtime system sees a set of independent tasks and schedules them on different processing units.
+For such applications, the runtime system sees a set of independent tasks and schedules them on processing units of different memory spaces.
 It is extremely important for runtimes to decide the order of data transfers for these scheduled computations so as to maximize the overlap between computations and communications.
@@
 Then, we also prove that in general data transfer problem is NP-complete.
-In Section~\ref{sec:heuristics}, we propose several heuristics and describe their favorable scenarios.
+In Section~\ref{sec:heuristics}, we propose several heuristics and discuss the conditions that might be favorable to them.
 We mainly consider three categories of heuristics: static heuristics, dynamic heuristics and static heuristics with dynamic corrections.
@@
 	The problem of scheduling tasks has been highly studied in the literature and many formulations are known to be NP-Complete~\cite{GareyJohnson}.
-Many static and dynamic strategies have been proposed and analyzed for scheduling tasks on heterogeneous resources~\cite{heft-Topcuoglu,hipc16multiresource,ipdps16starpu}.
+Many static and dynamic strategies have been proposed and analyzed for scheduling tasks on heterogeneous resources~\cite{heft-Topcuoglu,ipdps16starpu}.
 There is also a number of studies in the direction of task scheduling with the emphasis on improving locality and minimizing the communication cost~\cite{starpu,heft-Topcuoglu}.
@@
 We prove that ordering the execution of such tasks with finite memory capacity is a NP-complete problem: %%We also present an optimal algorithm to determine the order of execution of tasks when there is not any restriction on memory limit.
-
-	%%	\todo[inline]{Find a citation saying 3-machine flowshop problem is NP-Complete.}
-	%%%%	done:\todo[inline]{Rewrite both paragraphs together.}
-	%%	In general, order of task execution with input and output data transfers can be 
-	%%	viewed as 3-machine flowshop problem, where processing time on 1st machine is 
-	%%	input data transfer time, processing time on 2nd machine is task execution time, 
-	%%	processing time on 3rd machine is output data transfer time and the objective is 
-	%%	to minimize the total makespan.
-This is a well known hard problem~\cite{NPComplete3Machine,johnson}.
-As stated earlier, we do not consider output data separately in our analysis and assume that output data is negligible or stored in a separate buffer.
-Hence, problem considered in this article is simpler than general 3-machine flowshop problem.
 
@@
 	\end{algorithm}
-
+	\vspace*{-0.35cm}
 	We also prove optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} differently in an extended version~\cite{extendedVersion}.
@@
 			\noindent Target makespan: $L=m(b'+3)$
-			\caption{Definition of tasks in the reduction from \threepart.}
+			\vspace*{-0.25cm}\caption{Definition of tasks in the reduction from \threepart.\vspace*{-0.5cm}}
 			\label{table:np.completeness.tasks}
@@
 			\end{tikzpicture}
-			\caption{ \label{fig:firstSegment} Pattern of feasible schedule $S$.}
+			\caption{ \label{fig:firstSegment} Pattern of feasible schedule $S$.\vspace*{-0.3cm}}
 		\end{figure}
@@
 		We thus define $TR_i$ as the set of tasks which execute during the communication phase of task $K_i$.
-At each point in $S$, exactly one $K_i$ task is active and the total memory capacity is $b' +3$, hence $TR_i$ contains exactly 3 tasks.
+At each point in $S$, exactly one $K_i$ task is active and the total memory capacity is $b' +3$, hence $TR_i$ contains exactly 3 $A_i$ tasks.
 Since $S$ has no idle time on the computation resource, the total computation time of tasks in $TR_i$ is exactly $b'$, and thus
@@
 	problem makes it more difficult, just like it does for limited capacity 2-machine
-	flowshop~\cite{Papadimitriou:1980:FSL:322203.322213}. One additional difficulty of our problem however 
-	%%       \todo[inline]{I think you mean: infinite memory capacity 2-machine flowshop~\cite{johnson} ? LED: No, I really mean this one. Does this rephrasing help ?} 
-	is that it may not be
+	flowshop~\cite{Papadimitriou:1980:FSL:322203.322213}. One additional difficulty of our problem however is that it may not be
 	optimal to consider the same order on both machines.
@@
 
-	\begin{table}
+	\begin{table}[!ht]
 		\begin{center}
@@
 		\caption{Example instance where ordering on both resources
-			has to be different.}
+			has to be different\vspace*{-0.9cm}.}
 		\label{table:different.order}
@@
 
-	\begin{figure}
+	\begin{figure}[!htb]
 		\centering
@@
 		\caption{Schedules for the instance of
-			Table~\ref{table:different.order} with a memory capacity of 10.}
+			Table~\ref{table:different.order} with a memory capacity of 10.\vspace*{-0.75cm}}
 		\label{fig:different.order}
@@
 We denote this value with \textit{optimal makespan infinite memory} ($OMIM$).
-In the present Section, we propose different heuristics for the limited memory case, and we assess their efficiency with respect to this lower bound in Section~\ref{sec:expResults}.
+In this section, we propose different heuristics for the limited memory case, and we assess their efficiency with respect to $OMIM$ in Section~\ref{sec:expResults}.
 
@@
 In the first category, the order of all computations and communications is computed in advance and the same order is followed on both resources.
-In the second category, the next task to schedule is dyanmically chosen based on different criteria.
+In the second category, the next task to schedule is dynamically chosen based on different criteria.
 The final category is based on combining strategies from the first two categories: a static ordering is precomputed and corrected dynamically to avoid idle time caused by memory limitations.
@@
 
-	\begin{enumerate}[label=\roman*)]
-		\item \textit{order  of  optimal strategy infinite memory} ($OOSIM$): This heuristic uses the order given by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}, but respects the memory constraint at each point in the schedule.
-Hence the makespan of this heuristic may be completely different from $OMIM$.
-
-		\item \textit{increasing order of communication strategy} ($IOCMS$): Tasks are ordered  in non-decreasing order of communication time.
-
-		\item \textit{decreasing order of computation strategy} ($DOCPS$): Tasks are ordered in non-increasing order of computation time. 
-		\item \textit{increasing order of communication plus computation strategy} ($IOCCS$): Tasks are ordered in non-decreasing order of the sum of their communication and computation times.
-		\item \textit{decreasing order of communication plus computation strategy} ($DOCCS$): Tasks are ordered in non-increasing order of the sum of their communication and computation times.
-
-	\end{enumerate}
-	\begin{table}[htb]
-		\begin{center}
-
-			\begin{tabular}{|c|c|c|c|}
-				\hline
-				%%				\multirow{2}{*}{Task} & Comm Time & \multirow{2}{*}{Comp Time}\\ 
-				%%				&=Comm Volume& \\ \hline
-				%%				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
-				\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
-				&=Comm Volume && \\ \hline
-				A & 3 & 3 &  2\\ \hline
-				B & 1 & 1 & 3\\ \hline
-				C & 4 & 4 & 4\\ \hline
-				D & 2 & 2 & 1\\ \hline
-			\end{tabular}
-			\caption{\label{tab:staticOrderExample} A task set for static order schedules.}
-		\end{center}
-	\end{table}
-
-	\begin{figure}[htb]
+\begin{figure}[!tb]
 	\newcommand{\taskA}[2][0]{\task[#1]{$A$}{#2}{3}{2}{cyan}}
@@
 	\newcommand{\taskD}[2][0]{\task[#1]{$D$}{#2}{2}{1}{blue}}
-
+\vspace*{-0.25cm}	
 	\centering
@@
 
-		\caption{ \label{fig:staticOrderExample} Static order heuristic schedules for Table~\ref{tab:staticOrderExample}.} 
+	\caption{\vspace*{-0.2cm} \label{fig:staticOrderExample} Static order heuristic schedules for Table~\ref{tab:staticOrderExample}.} 
 	%%			Optimal schedule length	is 14. 
 \end{figure}
+
+	\begin{table}[!tb]
+	\begin{center}
+%%\vspace*{-0.10cm}		
+		\begin{tabular}{|c|c|c|c|}
+			\hline
+			%%				\multirow{2}{*}{Task} & Comm Time & \multirow{2}{*}{Comp Time}\\ 
+			%%				&=Comm Volume& \\ \hline
+			%%				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
+			\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
+			&=Comm Volume && \\ \hline
+			A & 3 & 3 &  2\\ \hline
+			B & 1 & 1 & 3\\ \hline
+			C & 4 & 4 & 4\\ \hline
+			D & 2 & 2 & 1\\ \hline
+		\end{tabular}
+		\caption{\label{tab:staticOrderExample} A task set for static order schedules.\vspace*{-0.75cm}}
+	\end{center}
+\end{table}
+
+	\begin{enumerate}[label=\roman*)]
+		\item \textit{order  of  optimal strategy infinite memory} ($OOSIM$): This heuristic uses the order given by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}, but respects the memory constraint at each point in the schedule.
+Hence the makespan of this heuristic may be completely different from $OMIM$.
+
+		\item \textit{increasing order of communication strategy} ($IOCMS$): Tasks are ordered  in non-decreasing order of communication time.
+
+		\item \textit{decreasing order of computation strategy} ($DOCPS$): Tasks are ordered in non-increasing order of computation time. 
+		\item \textit{increasing order of communication plus computation strategy} ($IOCCS$): Tasks are ordered in non-decreasing order of the sum of their communication and computation times.
+		\item \textit{decreasing order of communication plus computation strategy} ($DOCCS$): Tasks are ordered in non-increasing order of the sum of their communication and computation times.
+
+	\end{enumerate}
 
@@
 	\end{enumerate}
-	\begin{table}[htb]
-		\begin{center}
-
-			\begin{tabular}{|c|c|c|c|}
-				\hline
-				%%				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
-				\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
-				&=Comm Volume && \\ \hline
-				A & 3 & 3 & 2\\ \hline
-				B & 1 & 1 &  6\\ \hline
-				C & 4 & 4 & 6\\ \hline
-				D & 5 & 5 & 1\\ \hline
-			\end{tabular}
-			\caption{\label{tab:dynamicSelectionExample} A task set for dynamic schedules.}
-		\end{center}
-	\end{table}
-
-	\begin{figure}[htb]
+
+	\begin{figure}[!t]
 		\centering
@@
 		\end{tikzpicture}
-		\caption{ \label{fig:dynamicSelectionExample} Different dynamic heuristic schedules for a task set of Table~\ref{tab:dynamicSelectionExample} with a memory capacity of 6.}
+		\caption{ \label{fig:dynamicSelectionExample} Different dynamic heuristic schedules for a task set of Table~\ref{tab:dynamicSelectionExample} with a memory capacity of 6.\vspace*{-0.25cm}}
 		%%		 Optimal schedule length is 23.
 	\end{figure}
+
+	\begin{table}[!tb]
+	\begin{center}
+		\begin{tabular}{|c|c|c|c|}
+			\hline
+			%%				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
+			\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
+			&=Comm Volume && \\ \hline
+			A & 3 & 3 & 2\\ \hline
+			B & 1 & 1 &  6\\ \hline
+			C & 4 & 4 & 6\\ \hline
+			D & 5 & 5 & 1\\ \hline
+		\end{tabular}
+		\caption{\label{tab:dynamicSelectionExample} A task set for dynamic schedules.\vspace*{-0.5cm}}
+	\end{center}
+	\end{table}
 
@@
 
-	\begin{table}[htb]
-		\begin{center}
-
-			\begin{tabular}{|c|c|c|c|}
-				\hline
-				%%				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
-				\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
-				&=Comm Volume && \\ \hline
-				A & 4 & 4 &  1\\ \hline
-				B & 2 & 2 & 6\\ \hline
-				C & 8 & 8 & 8\\ \hline
-				D & 5 & 5 & 4\\ \hline
-				E & 3 & 3 & 2\\ \hline
-			\end{tabular}
-			\caption{\label{tab:staticOrderDynamicCorrectionsExample} A task set for static order dynamic corrections schedules.}
-		\end{center}
-	\end{table}
-
-	\begin{figure}[htb]
+	%%\begin{figure}[htb]
+	%%\includegraphics[scale=0.05]{Figs/staticOrderDynamicCorrectionsSchedules}
+	%%\caption{Task set and schedules where orders are precomputed based on different heuristics.}
+	%%\label{fig:staticOrderDynamicCorrectionsExample}
+	%%\end{figure}
+\begin{figure}[!htb]
 	\newcommand{\taskA}[2][0]{\task[#1]{$A$}{#2}{4}{1}{cyan}}
@@
 	\caption{ \label{fig:staticOrderDynamicCorrectionsExample} Different static order dynamic corrections heuristic schedules for a task set of Table~\ref{tab:staticOrderDynamicCorrectionsExample} with a memory capacity of 9.
-The $OMIM$ order is $BCDAE$.}
+The $OMIM$ order is $BCDAE$.\vspace*{-0.5cm}}
 \end{figure}
 
-	%%\begin{figure}[htb]
-	%%\includegraphics[scale=0.05]{Figs/staticOrderDynamicCorrectionsSchedules}
-	%%\caption{Task set and schedules where orders are precomputed based on different heuristics.}
-	%%\label{fig:staticOrderDynamicCorrectionsExample}
-	%%\end{figure}
+\begin{table}[!b]
+	\begin{center}
+		\begin{tabular}{|c|c|c|c|}
+			\hline
+			%%				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
+			\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
+			&=Comm Volume && \\ \hline
+			A & 4 & 4 &  1\\ \hline
+			B & 2 & 2 & 6\\ \hline
+			C & 8 & 8 & 8\\ \hline
+			D & 5 & 5 & 4\\ \hline
+			E & 3 & 3 & 2\\ \hline
+		\end{tabular}
+		\caption{\label{tab:staticOrderDynamicCorrectionsExample} A task set for static order dynamic corrections schedules.}
+	\end{center}
+\end{table}
 
 	As previously, we propose on Table~\ref{tab:staticOrderDynamicCorrectionsExample} an example instance for this class of strategies, and provide on Figure~\ref{fig:staticOrderDynamicCorrectionsExample} the corresponding schedules.
-
-	\subsection{Additional Heuristics from Previous Work}
-
-	We also consider two other static heuristics for evaluation.
-The first heuristic is based on an algorithm, proposed by Gilmore and Gomory, to obtain the minimal cost sequence for a set of jobs~\cite{Gilmore-Gomory:1964}.
-This is a classical algorithm for 2-machine no-wait flow shop.
-In this algorithm, each job has a start and end state and a cost is associated to change the state.
-In our context, this cost can be seen as non-overlap time of computation for two adjacent tasks.
-Here is the main idea of this algorithm.
-Initially, a partial sequence of jobs is represented by a graph such that their overlap is maximum.
-Subsequently edges are greedily added to this graph to connect two components while minimizing the total non-overlap cost.
-When the graph is  connected, an edge interchange mechanism is used to determine the sequence of jobs, which ensures that the sequence has minimal cost.
-More details can be found in the original paper~\cite{Gilmore-Gomory:1964} and our implementation is publicly available~\cite{gitworkrepo}.
-This algorithm does not take memory constraints into account and only provides the sequence of processing.
-We use this sequence with a memory capacity restriction just like for other static heuristcs, and we call this heuristic \textit{Gilmore-Gomory} ($GG$).
-
-	The second heuristic is based on the First-Fit algorithm for the bin packing problem.
-The idea of this heuristic is to identify groups of tasks which can fit in memory together, called \emph{bins}.
-In First-Fit, tasks are considered in an arbitrary order and added to the first bin in which they can fit.
-If no suitable bin is found then a new bin is created and this task is added to it.
-When all tasks have been assigned to bins, we consider the sequence made of all tasks from the first bin, then tasks for the second bin, and so on.
-We call this heuristic \textit{Bin Packing} ($BP$).
 
@@
 	\end{align*} 
+	\vspace*{-0.75cm}
 
@@
 
+	\subsection{Additional Heuristics from Previous Work}
+
+We also consider two other static heuristics for evaluation.
+The first heuristic is based on an algorithm, proposed by Gilmore and Gomory, to obtain the minimal cost sequence for a set of jobs~\cite{Gilmore-Gomory:1964}.
+This is a classical algorithm for 2-machine no-wait flow shop problem.
+In this algorithm, each job has a start and end state and a cost is associated to change the state.
+In our context, this cost can be seen as non-overlap time of computation for two adjacent tasks.
+Here is the main idea of this algorithm.
+Initially, a partial sequence of jobs is represented by a graph such that their overlap is maximum.
+Subsequently edges are greedily added to this graph to connect two components while minimizing the total non-overlap cost.
+When the graph is  connected, an edge interchange mechanism is used to determine the sequence of jobs, which ensures that the sequence has minimal cost.
+More details can be found in the original paper~\cite{Gilmore-Gomory:1964} and our implementation is publicly available~\cite{gitworkrepo}.
+This algorithm does not take memory constraints into account and only provides the sequence of processing.
+We use this sequence with a memory capacity restriction just like for other static heuristics, and we call this heuristic \textit{Gilmore-Gomory} ($GG$).
+
+The second heuristic is based on the First-Fit algorithm for the bin packing problem.
+The idea of this heuristic is to identify groups of tasks which can fit in memory together, called \emph{bins}.
+In First-Fit, tasks are considered in an arbitrary order and added to the first bin in which they can fit.
+If no suitable bin is found then a new bin is created and this task is added to it.
+When all tasks have been assigned to bins, we consider the sequence made of all tasks from the first bin, then tasks for the second bin, and so on.
+We call this heuristic \textit{Bin Packing} ($BP$).
+
 		\subsection{Favorable Situations for Heuristics}
-		Based on the definition of proposed strategies and the optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}, we present the scenarios which should be more favorable for each heuristic in Table~\ref{tab:heuristicsAndFavorableScenarios}.
-This allows programmers to use appropriate strategies to maximize communication-computation overlap for their applications.
-In this table, ``moderate memory capacity'' refers to the case where memory is constrained, but close to the maximal memory requirement of the $OMIM$ schedule.
-
-		\begin{table}[htb]
+
+		\begin{table}[!h]
 			\begin{tabular}{|c|p{6.5cm}|}
@@
 		\end{table}
+			Based on the definition of proposed strategies and the optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}, we discuss the scenarios which might be more favorable for each heuristic in Table~\ref{tab:heuristicsAndFavorableScenarios}.
+This allows programmers to use appropriate strategies to maximize communication-computation overlap for their applications.
+In this table, ``moderate memory capacity'' refers to the case where memory is constrained, but close to the maximal memory requirement of the $OMIM$ schedule.
 
@@
 For example, HF compute intensive tasks have small communication times, which explains why the $SCMR$ heuristic exhibits very good performance in limited memory cases.
-CCSD has significant percentage of large as well as small types of slightly communication intensive tasks, and indeed the performance of $OOLCMR$ and $OOSCMR$ is very close to optimality in moderate memory cases.
+CCSD has significant percentage of large as well as small types of slightly communication intensive tasks, and indeed the performance of $OOLCMR$ and $OOSCMR$ is very close to optimal in moderate memory cases.
 		%%		\todo[inline]{Skumar: Initially I placed this table after results.
@@
 Hence, HF operates on almost homogeneous tiles while CCSD uses more heterogeneous tiles.
-
+\begin{figure*}[!t]
+	\includegraphics[scale=0.5]{./results/ratio_to_optimal_selected_hf.pdf}
+	\vspace*{-0.85cm}\caption{Comparison of different heuristics for HF with $m_c=176KB$.			\vspace*{-0.35cm}}
+	\label{fig:ratio_to_optimal_hf}
+\end{figure*}			
 		\subsection{Workload Characteristics}
@@
 		\begin{figure}[htb]
-			%\begin{tabular}{c}
+\begin{center}
 			\includegraphics[scale=0.48]{./results/application_properties.pdf}
-			\caption{HF and CCSD tasks characteristics.}
+			\vspace*{-0.9cm}\caption{HF and CCSD tasks characteristics.\vspace*{-0.5cm}}
 			\label{fig:ApplicationProperties}
+\end{center}
 		\end{figure}
@@
 		To get more insights into the considered workloads, we provide  information about the instances we consider in Figure~\ref{fig:ApplicationProperties}.
-For each instance, we compute the sum of communication times (\textit{sum comm}) and sum of computation times  (\textit{sum comp}), and normalize it relatively to the $OMIM$ value.
+For each instance, we compute the sum of communication times (\textit{sum comm}) and the sum of computation times  (\textit{sum comp}), and normalize it relatively to the $OMIM$ value.
 Figure~\ref{fig:ApplicationProperties} also shows the maximum of both values, which is a lower bound on the possible makespan of a schedule for this instance, and their sum, which is an upper bound: this represents the makespan of the sequential schedule, obtained with zero overlap between computation and communication.
@@
 Our performance metric is the ratio to optimal $r$: if heuristic $H$ has makespan $M_H$ on an instance, and the optimal makespan for the infinite memory case is $OMIM$, then $r(H)=\frac{M_H}{OMIM}$ (lower values are better).
-This ratio is at least $1$, and a value close to $1$ indicates a well-suited  heuristic which achives maximum possible communication-computation overlap.
+This ratio is at least $1$, and a value close to $1$ indicates a well-suited  heuristic which achieves maximum possible communication-computation overlap.
 
@@
 		\subsection{HF Performance}
-		\begin{figure*}[htb]
-			\includegraphics[scale=0.5]{./results/ratio_to_optimal_selected_hf.pdf}
-			\caption{Comparison of different heuristics for HF with $m_c=176KB$.}
-			\label{fig:ratio_to_optimal_hf}
-		\end{figure*}
 
@@
 
-		\begin{figure}[htb]
+\begin{figure*}[htb]
+	\includegraphics[scale=0.5]{./results/ratio_to_optimal_selected_ccsd.pdf}
+	\vspace*{-0.95cm}\caption{Comparison of different heuristics for CCSD with $m_c=1.8GB$.\vspace*{-0.15cm}}
+	\label{fig:ratio_to_optimal_ccsd}
+\end{figure*}	
+	\begin{figure}[!h]
 	%%			\includegraphics[scale=0.5]{./results/inverse_ratio_to_optimal_hf-best.pdf}
-			\includegraphics[scale=0.5]{./results/ratio_to_optimal_hf-best.pdf}
-			\caption{Best variants of all categories for HF.}
+	\includegraphics[scale=0.45]{./results/ratio_to_optimal_hf-best.pdf}
+	\vspace*{-0.45cm}\caption{Best variants of all categories for HF.\vspace*{-0.45cm}}
 	\label{fig:ratio_to_optimal_best_hf}
@@
 
-		%%		\todo[inline]{SKumar: If you look at Figure~\ref{fig:ratio_to_optimal_best_hf} carefully,  in the beginning dynamics variants outperform others.
-This behavior is easily noticeable in Figure~\ref{fig:ratio_to_optimal_hf}.
-}
-		%%		\todo[inline]{LED: Ok, I rephrased here a bit to mention this.}
-
 		\subsection{CCSD Performance}
-		\begin{figure*}[htb]
-			\includegraphics[scale=0.5]{./results/ratio_to_optimal_selected_ccsd.pdf}
-			\caption{Comparison of different heuristics for CCSD with $m_c=1.8GB$.}
-			\label{fig:ratio_to_optimal_ccsd}
-		\end{figure*}
 
@@
 
-		\begin{figure}[htb]
-			%%			\includegraphics[scale=0.5]{./results/inverse_ratio_to_optimal_ccsd-best.pdf}
-			\includegraphics[scale=0.5]{./results/ratio_to_optimal_ccsd-best.pdf}
-			\caption{Best variants of all categories for CCSD.}
+		\begin{figure}[!t]
+			\includegraphics[scale=0.45]{./results/ratio_to_optimal_ccsd-best.pdf}
+			\vspace*{-0.45cm}\caption{Best variants of all categories for CCSD.\vspace*{-0.45cm}}
 			\label{fig:ratio_to_optimal_best_ccsd}
@@
 		\subsection{Scheduling in Batches}
+
+		\begin{figure*}[!t]
+			%%			\includegraphics[scale=0.5]{./results/inverse_ratio_to_optimal_batch-best.pdf}
+			\includegraphics[scale=0.45]{./results/ratio_to_optimal_batch-best.pdf}
+			\vspace*{-0.5cm}\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.\vspace*{-0.25cm}}
+			\label{fig:best_variants_batch}
+		\end{figure*}
 		In most applications, the runtime scheduler may only observe a limited batch of independent tasks.
-Therefore we organize tasks of each trace file in batches of 100 (the last batch may have less than 100 tasks).
+Therefore we organize tasks of each trace file in the batches of 100 (the last batch may have less than 100 tasks).
 We apply each heuristic on each group in succession.
@@
 The plots exhibit behavior similar to Figures~\ref{fig:ratio_to_optimal_best_hf} and~\ref{fig:ratio_to_optimal_best_ccsd}: static order with dynamic corrections variants attain maximum communication-computation overlap and outperform other heuristics.
-
-		\begin{figure*}[htb]
-			%%			\includegraphics[scale=0.5]{./results/inverse_ratio_to_optimal_batch-best.pdf}
-			\includegraphics[scale=0.5]{./results/ratio_to_optimal_batch-best.pdf}
-			\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
-			\label{fig:best_variants_batch}
-		\end{figure*}
 
@@
 We propose several data transfer heuristics and evaluate them on two molecular chemistry kernels, HF and CCSD.
-Our results show that some of our heuristics achieve significant overlap and perform very close to the lower bound.
+Our results show that some of our heuristics achieve significant overlap and their makespans are very close to the lower bound.
 We plan to evaluate our strategies on different applications coming from multiple domains.
 We also plan to study the behavior of our strategies in the context of overlapping CPU-GPU communications with computations.
-A runtime system aiming at exposing different heuristics to maximize the communication-computation overlap at the developer level and automatically selecting the best one is currently underway.
-
-		\begin{acks}
-
-			We are grateful to Ajay Panyala for his help in installation of  NWChem on Cascade machine and providing internal details about the package and its inputs.
+A runtime system aiming to expose different heuristics to maximize the communication-computation overlap at the developer level and automatically select the best one is currently underway.
+
+%%		\begin{acks}			
+%%			We are grateful to Ajay Panyala for his help in installation of  NWChem on Cascade machine and providing internal details about the package and its inputs.
 This work was supported in part by the U.S.
 Department of Energy (DOE), Office of Science, Office of Advanced Scientific Computing Research, under award 63823.
-Pacific Northwest National Laboratory is operated by Battelle for DOE under Contract DE-AC05-76RL01830.
-		\end{acks}
+%%			 Pacific Northwest National Laboratory is operated by Battelle for DOE under Contract DE-AC05-76RL01830.
+%%		\end{acks}
 

### 2019-04-21 ICPP-19/communications.tex
attempt to fit the document in 10 pages

@@
 In Section~\ref{sec:heuristics}, we propose several heuristics and discuss the conditions that might be favorable to them.
-We mainly consider three categories of heuristics: static heuristics, dynamic heuristics and static heuristics with dynamic corrections.
+We mainly consider three categories of heuristics: static order based heuristics, dynamic selection based heuristics, and static order with dynamic correction based heuristics.
 Sections~\ref{sec:expSetting} describes our experimental setup and we evaluate our proposed strategies on two molecular chemistry kernels in Section~\ref{sec:expResults}.
-Our results show that static heuristics with dynamic corrections achieve good performance in most cases.
+Our results show that static order with dynamic correction based heuristics achieve good performance in most cases.
 We finally propose conclusions and perspectives in Section~\ref{sec:conclusion}.
@@
 
+	\medskip
 	\noindent\textbf{Problem $DT$} : A set of tasks $ST=\{T_1,
@@
 
+	\vspace*{-0.25cm}
 	\begin{algorithm}
@@
 				\hline
-				%%				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
-				\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
-				&=Comm Volume && \\ \hline
+				Task & Memory Req & Comm Time & Comp Time\\ \hline 
+%%				\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
+%%				&=Comm Volume && \\ \hline
 				A & 0 & 0 & 5\\ \hline
@@
 In the second category, the next task to schedule is dynamically chosen based on different criteria.
-The final category is based on combining strategies from the first two categories: a static ordering is precomputed and corrected dynamically to avoid idle time caused by memory limitations.
+The final category is based on combining strategies from the first two categories: a static order is precomputed and corrected dynamically to avoid idle time caused by memory limitations.
 In all of our strategies (except linear programming based strategy), communication and computations take place in the same order.
@@
 	\newcommand{\taskD}[2][0]{\task[#1]{$D$}{#2}{2}{1}{blue}}
-\vspace*{-0.25cm}	
+\vspace*{-0.30cm}	
 	\centering
 	\subfloat[][Infinite Memory Capacity]{
-		\begin{tikzpicture}[scale=0.6]
+		\begin{tikzpicture}[yscale=0.5, xscale=0.6]
 		\schedule{12.5}{OMIM}{1,4,5,8,9,10,11,12}
@@
 	\subfloat[][Memory Capacity: 6]{
-		\begin{tikzpicture}[yscale=0.6, xscale=0.45]
+		\begin{tikzpicture}[yscale=0.5, xscale=0.45]
 		\begin{scope}
@@
 			%%				&=Comm Volume& \\ \hline
-			%%				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
-			\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
-			&=Comm Volume && \\ \hline
+	    	Task & Memory Req & Comm Time & Comp Time\\ \hline 
+%%			\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
+%%			&=Comm Volume && \\ \hline
 			A & 3 & 3 &  2\\ \hline
@@
 		\centering
-		\begin{tikzpicture}[yscale=0.6,xscale=0.3]
+		\begin{tikzpicture}[yscale=0.5,xscale=0.3]
 		\begin{scope}
@@
 			\hline
-			%%				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
-			\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
-			&=Comm Volume && \\ \hline
+			Task & Memory Req & Comm Time & Comp Time\\ \hline 
+%%			\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
+%%			&=Comm Volume && \\ \hline
 			A & 3 & 3 & 2\\ \hline
@@
 		\end{tabular}
-		\caption{\label{tab:dynamicSelectionExample} A task set for dynamic schedules.\vspace*{-0.5cm}}
+		\caption{\label{tab:dynamicSelectionExample} A task set for dynamic schedules.\vspace*{-0.75cm}}
 	\end{center}
@@
 
-	\subsection{Static Order with Dynamic Corrections}
+	\subsection{Static Order with Dynamic Correction}
 
@@
 After a task is dynamically selected, we update the remaining order without this task.
-This class of strategy takes advantage of static information in the form of precomputed order and dynamic corrections to minimize the idle time due to memory constraint.
+This class of strategy takes advantage of static information in the form of precomputed order and dynamic correction to minimize the idle time due to memory constraint.
 
@@
 	%%\begin{figure}[htb]
-	%%\includegraphics[scale=0.05]{Figs/staticOrderDynamicCorrectionsSchedules}
+	%%\includegraphics[scale=0.05]{Figs/staticOrderDynamiccorrectionSchedules}
 	%%\caption{Task set and schedules where orders are precomputed based on different heuristics.}
-	%%\label{fig:staticOrderDynamicCorrectionsExample}
+	%%\label{fig:staticOrderDynamiccorrectionExample}
 	%%\end{figure}
@@
 	\newcommand{\taskE}[2][0]{\task[#1]{$E$}{#2}{3}{2}{blue}}
-	\begin{tikzpicture}[yscale=0.6,xscale=0.2]
+	\vspace*{-0.35cm}
+	\begin{tikzpicture}[yscale=0.5,xscale=0.2]
 	\begin{scope}
@@
 	\end{tikzpicture}
-	\caption{ \label{fig:staticOrderDynamicCorrectionsExample} Different static order dynamic corrections heuristic schedules for a task set of Table~\ref{tab:staticOrderDynamicCorrectionsExample} with a memory capacity of 9.
-The $OMIM$ order is $BCDAE$.\vspace*{-0.5cm}}
+	\caption{ \label{fig:staticOrderDynamiccorrectionExample} Different static order dynamic correction heuristic schedules for a task set of Table~\ref{tab:staticOrderDynamiccorrectionExample} with a memory capacity of 9.
+The $OMIM$ order is $BCDEA$.\vspace*{-0.5cm}}
 \end{figure}
 
-\begin{table}[!b]
+\begin{table}[!htb]
 	\begin{center}
@@
 			\hline
-			%%				Task & Comm Volume & Comm Time & Comp Time\\ \hline 
-			\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
-			&=Comm Volume && \\ \hline
+			Task & Memory Req & Comm Time & Comp Time\\ \hline 
+%%			\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
+%%			&=Comm Volume && \\ \hline
 			A & 4 & 4 &  1\\ \hline
@@
 		\end{tabular}
-		\caption{\label{tab:staticOrderDynamicCorrectionsExample} A task set for static order dynamic corrections schedules.}
+		\caption{\label{tab:staticOrderDynamiccorrectionExample} A task set for static order dynamic correction schedules.\vspace*{-0.75cm}}
 	\end{center}
@@
 
-	As previously, we propose on Table~\ref{tab:staticOrderDynamicCorrectionsExample} an example instance for this class of strategies, and provide on Figure~\ref{fig:staticOrderDynamicCorrectionsExample} the corresponding schedules.
+	As previously, we propose on Table~\ref{tab:staticOrderDynamiccorrectionExample} an example instance for this class of strategies, and provide on Figure~\ref{fig:staticOrderDynamiccorrectionExample} the corresponding schedules.
+
+	\subsection{Additional Heuristics from Previous Work}
+
+We also consider two other static heuristics for evaluation.
+The first heuristic is based on an algorithm, proposed by Gilmore and Gomory, to obtain the minimal cost sequence for a set of jobs~\cite{Gilmore-Gomory:1964}.
+This is a classical algorithm for 2-machine no-wait flow shop problem.
+In this algorithm, each job has a start and end state and a cost is associated to change the state.
+In our context, this cost can be seen as non-overlap time of computation for two adjacent tasks.
+Here is the main idea of this algorithm.
+Initially, a partial sequence of jobs is represented by a graph such that their overlap is maximum.
+Subsequently edges are greedily added to this graph to connect two components while minimizing the total non-overlap cost.
+When the graph is  connected, an edge interchange mechanism is used to determine the sequence of jobs, which ensures that the sequence has minimal cost.
+More details can be found in the original paper~\cite{Gilmore-Gomory:1964} and our implementation is publicly available~\cite{gitworkrepo}.
+This algorithm does not take memory constraints into account and only provides the sequence of processing.
+We use this sequence with a memory capacity restriction just like for other static heuristics, and we call this heuristic \textit{Gilmore-Gomory} ($GG$).
+
+The second heuristic is based on the First-Fit algorithm for the bin packing problem.
+The idea of this heuristic is to identify groups of tasks which can fit in memory together, called \emph{bins}.
+In First-Fit, tasks are considered in an arbitrary order and added to the first bin in which they can fit.
+If no suitable bin is found then a new bin is created and this task is added to it.
+When all tasks have been assigned to bins, we consider the sequence made of all tasks from the first bin, then tasks for the second bin, and so on.
+We call this heuristic \textit{Bin Packing} ($BP$).
 
@@
 
-	\subsection{Additional Heuristics from Previous Work}
-
-We also consider two other static heuristics for evaluation.
-The first heuristic is based on an algorithm, proposed by Gilmore and Gomory, to obtain the minimal cost sequence for a set of jobs~\cite{Gilmore-Gomory:1964}.
-This is a classical algorithm for 2-machine no-wait flow shop problem.
-In this algorithm, each job has a start and end state and a cost is associated to change the state.
-In our context, this cost can be seen as non-overlap time of computation for two adjacent tasks.
-Here is the main idea of this algorithm.
-Initially, a partial sequence of jobs is represented by a graph such that their overlap is maximum.
-Subsequently edges are greedily added to this graph to connect two components while minimizing the total non-overlap cost.
-When the graph is  connected, an edge interchange mechanism is used to determine the sequence of jobs, which ensures that the sequence has minimal cost.
-More details can be found in the original paper~\cite{Gilmore-Gomory:1964} and our implementation is publicly available~\cite{gitworkrepo}.
-This algorithm does not take memory constraints into account and only provides the sequence of processing.
-We use this sequence with a memory capacity restriction just like for other static heuristics, and we call this heuristic \textit{Gilmore-Gomory} ($GG$).
-
-The second heuristic is based on the First-Fit algorithm for the bin packing problem.
-The idea of this heuristic is to identify groups of tasks which can fit in memory together, called \emph{bins}.
-In First-Fit, tasks are considered in an arbitrary order and added to the first bin in which they can fit.
-If no suitable bin is found then a new bin is created and this task is added to it.
-When all tasks have been assigned to bins, we consider the sequence made of all tasks from the first bin, then tasks for the second bin, and so on.
-We call this heuristic \textit{Bin Packing} ($BP$).
-
 		\subsection{Favorable Situations for Heuristics}
 
+			Based on the definition of proposed strategies and the optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}, we discuss the scenarios which might be more favorable for each heuristic in Table~\ref{tab:heuristicsAndFavorableScenarios}.
+This allows programmers to use appropriate strategies to maximize communication-computation overlap for their applications.
+In this table, ``moderate memory capacity'' refers to the case where memory is constrained, but close to the maximal memory requirement of the $OMIM$ schedule.
+
 		\begin{table}[!h]
+			\begin{center}
 			\begin{tabular}{|c|p{6.5cm}|}
@@
 				$OOMAMR$ & Moderate memory capacity and significant percentage of all types of tasks \\ \hline
-			\end{tabular}\caption{~\label{tab:heuristicsAndFavorableScenarios}Heuristics and their favorable scenarios.}
+			\end{tabular}\caption{~\label{tab:heuristicsAndFavorableScenarios}Heuristics and their favorable scenarios.\vspace*{-0.75cm}}
+			\end{center}
 		\end{table}
-			Based on the definition of proposed strategies and the optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}, we discuss the scenarios which might be more favorable for each heuristic in Table~\ref{tab:heuristicsAndFavorableScenarios}.
-This allows programmers to use appropriate strategies to maximize communication-computation overlap for their applications.
-In this table, ``moderate memory capacity'' refers to the case where memory is constrained, but close to the maximal memory requirement of the $OMIM$ schedule.
 
@@
 Hence, HF operates on almost homogeneous tiles while CCSD uses more heterogeneous tiles.
+
+		\subsection{Workload Characteristics}
+		\begin{figure}[htb]
+			\vspace*{-0.3cm}
+			\begin{center}
+				\includegraphics[scale=0.48]{./results/application_properties.pdf}
+				\vspace*{-0.9cm}\caption{HF and CCSD tasks characteristics.\vspace*{-0.35cm}}
+				\label{fig:ApplicationProperties}
+			\end{center}
+		\end{figure}
 			\begin{figure*}[!t]
@@
 		\end{figure*}
-		\subsection{Workload Characteristics}
-
-		\begin{figure}[htb]
-\begin{center}
-			\includegraphics[scale=0.48]{./results/application_properties.pdf}
-			\vspace*{-0.9cm}\caption{HF and CCSD tasks characteristics.\vspace*{-0.5cm}}
-			\label{fig:ApplicationProperties}
-\end{center}
-		\end{figure}
-
-		To get more insights into the considered workloads, we provide  information about the instances we consider in Figure~\ref{fig:ApplicationProperties}.
+
+		\noindent To get more insights into the considered workloads, we provide  information about the instances we consider in Figure~\ref{fig:ApplicationProperties}.
 For each instance, we compute the sum of communication times (\textit{sum comm}) and the sum of computation times  (\textit{sum comp}), and normalize it relatively to the $OMIM$ value.
@@
 As memory capacity is increased further, dynamic variants of heuristics start performing better.
-For the moderate memory capacities (close to $2m_c$), static order with dynamic corrections variants outperform others.
+For the moderate memory capacities (close to $2m_c$), static order with dynamic correction variants outperform others.
 $GG$ heuristic does not achieve good performance, because its task sequence is obtained considering no extra memory is available, but is then applied in a different scenario where memory is limited.
@@
 		%%		\todo{you mean infinite memory? SKumar: GG is classic in no-wait (or no buffer) 2-macine flowshop}
+	\begin{figure}[!tb]
+	\includegraphics[scale=0.5]{./results/ratio_to_optimal_hf-best.pdf}
+	\vspace*{-0.85cm}\caption{Best variants of all categories for HF.\vspace*{-0.8cm}}
+	\label{fig:ratio_to_optimal_best_hf}
+\end{figure}
 
@@
 \end{figure*}
-	\begin{figure}[!h]
-	%%			\includegraphics[scale=0.5]{./results/inverse_ratio_to_optimal_hf-best.pdf}
-	\includegraphics[scale=0.45]{./results/ratio_to_optimal_hf-best.pdf}
-	\vspace*{-0.45cm}\caption{Best variants of all categories for HF.\vspace*{-0.45cm}}
-	\label{fig:ratio_to_optimal_best_hf}
-\end{figure}
 
@@
 Static strategies are expected to perform better when there is not any memory capacity restriction, and indeed this plot shows that static strategies face capacity bottleneck and underperform with limited memory.
-Dynamic strategies achieve slightly better performance with limited memory capacity, but when memory capacity is larger, static order with dynamic corrections strategies outperform all others.
+Dynamic strategies achieve slightly better performance with limited memory capacity, but when memory capacity is larger, static order with dynamic correction strategies outperform all others.
 
@@
 		The CCSD application operates on tasks of different sizes, hence different heuristics exhibit distinct behaviors even at minimum memory capacity $m_c$.
-Heterogeneity favors dynamic strategies, as can be seen by the fact that both dynamic and static order with dynamic corrections based strategies perform better than static based strategies.
-Similar to HF, static order with dynamic corrections based strategies outperform others as memory capacity becomes moderate.
-
-		\begin{figure}[!t]
-			\includegraphics[scale=0.45]{./results/ratio_to_optimal_ccsd-best.pdf}
-			\vspace*{-0.45cm}\caption{Best variants of all categories for CCSD.\vspace*{-0.45cm}}
+Heterogeneity favors dynamic strategies, as can be seen by the fact that both dynamic and static order with dynamic correction based strategies perform better than static based strategies.
+Similar to HF, static order with dynamic correction based strategies outperform others as memory capacity becomes moderate.
+
+\begin{figure}[htb]
+	\includegraphics[scale=0.5]{./results/ratio_to_optimal_ccsd-best.pdf}
+	\vspace*{-0.25cm}\caption{Best variants of all categories for CCSD.\vspace*{-0.25cm}}
 	\label{fig:ratio_to_optimal_best_ccsd}
@@
 
-		Figure~\ref{fig:ratio_to_optimal_best_ccsd} shows that best variants of dynamic and static order with dynamic corrections strategies achieve similar performance at minimum memory capacity $m_c$.
-But as memory capacity increases, heterogeneity allows static order with dynamic corrections based strategies to take advantage of static knowledge to get maximum overlap and dynamic correction to select another task in case of memory capacity limitation.
+		\noindent Figure~\ref{fig:ratio_to_optimal_best_ccsd} shows that best variants of dynamic and static order with dynamic correction strategies achieve similar performance at minimum memory capacity $m_c$.
+But as memory capacity increases, heterogeneity allows static order with dynamic correction based strategies to take advantage of static knowledge to get maximum overlap and dynamic correction to select another task in case of memory capacity limitation.
 Static strategies also start performing better at the end, which indicates that this application has potential for significant communication-computation overlap and pure dynamic strategies are unable to take this information into account while making scheduling decisions.
-
-		\subsection{Scheduling in Batches}
 
@@
 			%%			\includegraphics[scale=0.5]{./results/inverse_ratio_to_optimal_batch-best.pdf}
-			\includegraphics[scale=0.45]{./results/ratio_to_optimal_batch-best.pdf}
+			\includegraphics[scale=0.5]{./results/ratio_to_optimal_batch-best.pdf}
 			\vspace*{-0.5cm}\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.\vspace*{-0.25cm}}
@@
 		\end{figure*}
+
+		\subsection{Scheduling in Batches}
+
 		In most applications, the runtime scheduler may only observe a limited batch of independent tasks.
 Therefore we organize tasks of each trace file in the batches of 100 (the last batch may have less than 100 tasks).
-We apply each heuristic on each group in succession.
+We apply each heuristic on the batches in sequential order.
 Figure~\ref{fig:best_variants_batch} shows the performance of the best variant of each category for both applications.
-The plots exhibit behavior similar to Figures~\ref{fig:ratio_to_optimal_best_hf} and~\ref{fig:ratio_to_optimal_best_ccsd}: static order with dynamic corrections variants attain maximum communication-computation overlap and outperform other heuristics.
+The plots exhibit behavior similar to Figures~\ref{fig:ratio_to_optimal_best_hf} and~\ref{fig:ratio_to_optimal_best_ccsd}: static order with dynamic correction variants attain maximum communication-computation overlap and outperform other heuristics.
 
@@
 
-%%		\begin{acks}			
-%%			We are grateful to Ajay Panyala for his help in installation of  NWChem on Cascade machine and providing internal details about the package and its inputs.
+		\begin{acks}			
+			We are grateful to Ajay Panyala for his help in installation of  NWChem on Cascade machine and providing internal details about the package and its inputs.
 This work was supported in part by the U.S.
@@
 %%			 Pacific Northwest National Laboratory is operated by Battelle for DOE under Contract DE-AC05-76RL01830.
-%%		\end{acks}
+		\end{acks}
 

### 2019-04-21 ICPP-19/communications.tex
proofread

@@
 We mainly consider three categories of heuristics: static order based heuristics, dynamic selection based heuristics, and static order with dynamic correction based heuristics.
-Sections~\ref{sec:expSetting} describes our experimental setup and we evaluate our proposed strategies on two molecular chemistry kernels in Section~\ref{sec:expResults}.
+Sections~\ref{sec:expSetting} describes our experimental setup and we evaluate our proposed heuristics on two molecular chemistry kernels in Section~\ref{sec:expResults}.
 Our results show that static order with dynamic correction based heuristics achieve good performance in most cases.
@@
 		6x$, but at most two $A_i$ tasks can be computed, and they end at time
-		at most $3+2max\{a_i':1\le i\le 3m\} = 3 + 6x$
+		at most $3+2max\{a_i':1\le i\le 3m\} = 3 + 6x$.
 
@@
 
-	\section{Data Transfer Order heuristics}
+	\section{Data Transfer Order Heuristics}
 	\label{sec:heuristics}
@@
 
-	In order to highlight the different behaviors of these static strategies, we propose on Table~\ref{tab:staticOrderExample} an example instance, and on Figure~\ref{fig:staticOrderExample} the corresponding schedules for all these heuristics.
+	In order to highlight the different behaviors of these static heuristics, we propose on Table~\ref{tab:staticOrderExample} an example instance, and on Figure~\ref{fig:staticOrderExample} the corresponding schedules for all these heuristics.
 
@@
 
-	In this class of strategy, we precompute the order of tasks based on some criterion and then follow this ordering as much as possible.
+	In this class of strategies, we precompute the order of tasks based on some criterion and then follow this ordering as much as possible.
 But when the communication resource is idle because the memory requirement of the next task is too high, then we select a task  with a dynamic strategy.
 After a task is dynamically selected, we update the remaining order without this task.
-This class of strategy takes advantage of static information in the form of precomputed order and dynamic correction to minimize the idle time due to memory constraint.
+This class of strategies take advantage of static information in the form of precomputed order and dynamic correction to minimize the idle time due to memory constraint.
 
@@
 
-	As previously, we propose on Table~\ref{tab:staticOrderDynamiccorrectionExample} an example instance for this class of strategies, and provide on Figure~\ref{fig:staticOrderDynamiccorrectionExample} the corresponding schedules.
+	As previously, we propose on Table~\ref{tab:staticOrderDynamiccorrectionExample} an example instance for this class of heuristics, and provide on Figure~\ref{fig:staticOrderDynamiccorrectionExample} the corresponding schedules.
 
@@
 		\forall i, \quad & \sum_{r\ne i} (a_{ir} - c_{ir})MC(r) + MC(i) \le C && \text{(memory constraint)}\\
-		%% %%\forall i, \forall j\ne i, \quad & \text{task }T_i \text{ respects memory capacity on computation resource:}\\
-		%% %%& s_j < e'_i +(1-d_{ij})L\\
-		%% %%& e'_i\leq s_j +d_{ij}L\\
-		%% %%& \sum_r (d_{ir} - b_{ir})CM(r) + TM(i) \le C\\
 	\end{align*} 
@@
 
-		%%		\todo[inline]{SKumar: Move to an extended version and more clear about results and implementation}
-		%%		Figure~\ref{fig:iterativeLpSolution} shows the performance of different heuristics with MILP based heuristics for various memory capacities of a single trace file.
-		%%		%%	\subsection{MILP Based Strategy}
-		%%		%%We use GLPK solver v4.65 to solve the MILP formulation described in Section~\ref{subsec:linearprogrammingformulation}.
-The solver was unable to handle number of variables required to solve MILP at the scale of our interest.
-Hence, we solve the linear program iteratively for a small subset of size $k=3,4,5$ (solver was unable to handle number of variables required for $k\ge6$ ) and represent the makespan calculated by this heuristic as $lp.k$.
-At the boundary of two iterations we fixed the event (communication or computation) of an unfinished task who has started before the boundary point and consider other events flexible.
-We compute various $lp.k$ values for different memory capacities and observe that most of the other heuristics perform better than this heuristic.
-Figure~\ref{fig:iterativeLpSolution} shows the comparison of different heuristics with MILP based heuristic for various memory capacities of a single trace file.
-		%%		\todo[inline]{SKumar: Figure~\ref{fig:iterativeLpSolution} would be removed and I will redraw this or similar figure for extended version}
-		%%		\begin{figure}[htb]
-		%%			\includegraphics[scale=0.5]{./results/makespan_with_lp.pdf}
-		%%			\caption{Comparison of different heuristics with MILP solution based heuristic.\todo[inline]{LED: I understand that this figure will be removed?
-Otherwise, use aes(fill=) instead of aes(color=) to have color filled bars.}}
-		%%			\label{fig:iterativeLpSolution}
-		%%		\end{figure}
-
 		\subsection{Favorable Situations for Heuristics}
 
-			Based on the definition of proposed strategies and the optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}, we discuss the scenarios which might be more favorable for each heuristic in Table~\ref{tab:heuristicsAndFavorableScenarios}.
+			Based on the definition of proposed heuristics and the optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}, we discuss the scenarios which might be more favorable for each heuristic in Table~\ref{tab:heuristicsAndFavorableScenarios}.
 This allows programmers to use appropriate strategies to maximize communication-computation overlap for their applications.
@@
 			%%			\includegraphics[scale=0.5]{./results/inverse_ratio_to_optimal_batch-best.pdf}
-			\includegraphics[scale=0.5]{./results/ratio_to_optimal_batch-best.pdf}
-			\vspace*{-0.5cm}\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.\vspace*{-0.25cm}}
+			\includegraphics[scale=0.485]{./results/ratio_to_optimal_batch-best.pdf}
+			\vspace*{-0.5cm}\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.\vspace*{-0.1cm}}
 			\label{fig:best_variants_batch}

### 2019-04-21 ICPP-19/communications.tex
Abstract Proofread

@@
 		%With increasing hardware complexity and systems with different memory nodes are ubiquitous in High Performance Computing (HPC). 
-		In distributed memory systems, it is paramount to develop strategies to overlap the data transfers between memory nodes with the computation in order to exploit the full potential of these systems.
+		In distributed memory systems, it is paramount to develop strategies to overlap the data transfers between memory nodes with the computations in order to exploit the full potential of these systems.
 In this paper, we consider the problem of determining the order of data transfers between two memory nodes for a set of independent tasks with the objective of minimizing the makespan.

### 2019-04-21 ExperimentalData/communicationWithTemporaryMemory_lp.h
LP formulation to decide the order of communications and computations

@@ -12,10 +12,10 @@ static int counter = 0;
 void formulate_lp(int n, unsigned int capacity, double* CM, double* CP, unsigned int* cap, unsigned int* tm, int* fixed_start_comm_time, double* start_comm_time, int* fixed_start_comp_time, double* start_comp_time)
 {
     glp_prob *lp;
-    int ia[1+100000];
-    int ja[1+100000];
+    int ia[1+1000];
+    int ja[1+1000];
 
-    double ar[1+100000];
+    double ar[1+1000];
 
 
     int iter1, iter2;
@@ -29,8 +29,7 @@ void formulate_lp(int n, unsigned int capacity, double* CM, double* CP, unsigned
     glp_set_prob_name(lp, "lp_formulation_for_communication_proble");
     glp_set_obj_dir(lp, GLP_MIN);
 
-    //int ncols = 4 * n * (n+1) + 1 + 1;
-    int ncols = 4 * n + 3 * n* n + 1 + 1;
+    int ncols = 4 * n * (n+1) + 1 + 1;
     glp_add_cols(lp, ncols);
 
     int icol = 0;
@@ -161,7 +160,7 @@ void formulate_lp(int n, unsigned int capacity, double* CM, double* CP, unsigned
             
         }
     }
-/*
+
 
     //n*n binary variables to denote computation order with other communications
     //d_i_j = 1 => s_j <= e'_i
@@ -181,7 +180,7 @@ void formulate_lp(int n, unsigned int capacity, double* CM, double* CP, unsigned
             
         }
     }
-*/
+
     // objective variable to minimize
     {
         ++icol;
@@ -208,25 +207,11 @@ void formulate_lp(int n, unsigned int capacity, double* CM, double* CP, unsigned
 
     assert(icol == ncols); 
 
-    //int nrows = n * (8*n - 2) + n;
-    int nrows = n * (6*n - 1) + n;
+    int nrows = n * (8*n - 2) + n;
     
     //a_i_j >= c_i_j  and d_i_j >= b_i_j
     // a/b_i_j + a/b_j_i = 1
-    //nrows += 2*n*n + n*(n-1);
-
-
-    //a_i_j > = c_i_j
-    nrows += n*n -n;
-
-    //b_i_j > = c_i_j
-    nrows += n*n -n;
[…]

### 2019-04-22 ICPP-19/communications.tex
Proofread

@@
 After a task is dynamically selected, we update the remaining order without this task.
-This class of strategies take advantage of static information in the form of precomputed order and dynamic correction to minimize the idle time due to memory constraint.
-
-	In all strategies of this class, the initial order is $OMIM$ order,  obtained by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}.
+This class of strategies takes advantage of static information in the form of precomputed order and dynamic correction to minimize the idle time due to memory constraint.
+
+	In all strategies of this class, the initial order is $OMIM$ order obtained by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}.
 We define the following heuristics based on how we select a task from the set of tasks which fit in memory and induce minimum idle time on the computation resource.
@@
 computation) for task $i$, and $MC(i)$ is the memory capacity requirement of task $i$.
-The formulation also contains for each pair of tasks $i$ and $j$ \textit{i)} a boolean variable $a_{ij}$ to denote the order of $i$ and $j$ on the communication resource \textit{ii)} a boolean variables $b_{ij}$ to denote the order of $i$ and $j$ on the computation resource, and \textit{iii)} a boolean variables $c_{ij}$ to denote the order of $s_i$ and $e'_j$.
+The formulation also contains for each pair of tasks $i$ and $j$ \textit{i)} a boolean variable $a_{ij}$ to denote the order of $i$ and $j$ on the communication resource \textit{ii)} a boolean variable $b_{ij}$ to denote the order of $i$ and $j$ on the computation resource, and \textit{iii)} a boolean variable $c_{ij}$ to denote the order of $s_i$ and $e'_j$.
 
@@
 Hence, it is extremely important to achieve the maximum  communication-computation overlap in order to exploit the full potential of the system.
-We show that determining the order of data transfers is a NP complete problem.
+We show that the problem of determining the optimal order of data transfers is NP complete.
 We propose several data transfer heuristics and evaluate them on two molecular chemistry kernels, HF and CCSD.

### 2019-04-22 ICPP-19/communications.tex
Proofread

@@
 Therefore, a steep learning curve is required for programmers to take good utilization of all resources.
-Second, scheduling is a well known NP-Complete optimization problem, and hybrid and distributed resources make this problem harder (we refer ~\cite{webpagescheduling} for a survey on the complexity of scheduling problems and ~\cite{bleuse2015scheduling} for a recent survey in the case of hybrid nodes).
+Second, scheduling is a well known NP-complete optimization problem, and hybrid and distributed resources make this problem harder (we refer ~\cite{webpagescheduling} for a survey on the complexity of scheduling problems and ~\cite{bleuse2015scheduling} for a recent survey in the case of hybrid nodes).
 Third, due to shared buses and parallel resources, it is challenging to obtain a precise model based on prediction of computation and communication times.
@@
 This is the main topic of this paper.
-We prove that the order of communications on two memory nodes with the objective of minimizing the makespan is a NP-Complete problem if the memory of the target node is limited.
+We prove that the order of communications on two memory nodes with the objective of minimizing the makespan is a NP-complete problem if the memory of the target node is limited.
 Our proof is inspired from work by~\cite{Papadimitriou:1980:FSL:322203.322213}, which applies a similar technique for 2-machine flowshop problem with bounded capacity.
@@
 	\begin{itemize}
-		\item NP-Completeness proof for the general data-transfer problem 
+		\item NP-completeness proof for the general data-transfer problem 
 		\item Proposed different scheduling strategies with the objective to minimize the makespan
@@
 
-	The problem of scheduling tasks has been highly studied in the literature and many formulations are known to be NP-Complete~\cite{GareyJohnson}.
+	The problem of scheduling tasks has been highly studied in the literature and many formulations are known to be NP-complete~\cite{GareyJohnson}.
 Many static and dynamic strategies have been proposed and analyzed for scheduling tasks on heterogeneous resources~\cite{heft-Topcuoglu,ipdps16starpu}.
@@
 Johnson has provided scheduling strategies for 2 and 3-machine flow shop problems with infinite memory capacity~\cite{johnson}.
-2-machine flow shop problem with finite buffer has been proven NP-Complete by Papadimitriou et.
+2-machine flow shop problem with finite buffer has been proven NP-complete by Papadimitriou et.
 al~\cite{Papadimitriou:1980:FSL:322203.322213}, in which a constraint is imposed on the number of tasks that can await execution on the second machine.
@@
 Hence, it is extremely important to achieve the maximum  communication-computation overlap in order to exploit the full potential of the system.
-We show that the problem of determining the optimal order of data transfers is NP complete.
+We show that the problem of determining the optimal order of data transfers is NP-complete.
 We propose several data transfer heuristics and evaluate them on two molecular chemistry kernels, HF and CCSD.

### 2019-04-23 ICPP-19/communications.tex
Proofread

@@
 		\item NP-completeness proof for the general data-transfer problem 
-		\item Proposed different scheduling strategies with the objective to minimize the makespan
+		\item Different scheduling strategies with the objective to minimize the makespan
 		%%		\item An optimal strategy and its proof, when there is not any memory capacity constraint on the target machine
@@
 We show that the problem of determining the optimal order of data transfers is NP-complete.
-We propose several data transfer heuristics and evaluate them on two molecular chemistry kernels, HF and CCSD.
+We proposed several data transfer heuristics and evaluated them on two molecular chemistry kernels, HF and CCSD.
 Our results show that some of our heuristics achieve significant overlap and their makespans are very close to the lower bound.

### 2019-06-08 ICPP-19/communications.tex
Camera ready version

@@
 
-	\renewcommand{\shortauthors}{Kumar and Eyraud-Dubois, et al.}
+	\renewcommand{\shortauthors}{Kumar, Eyraud-Dubois, and Krishnamoorthy}
 
@@
 		%With increasing hardware complexity and systems with different memory nodes are ubiquitous in High Performance Computing (HPC). 
-		In distributed memory systems, it is paramount to develop strategies to overlap the data transfers between memory nodes with the computations in order to exploit the full potential of these systems.
+		In distributed memory systems, it is paramount to develop strategies to overlap the data transfers between memory nodes with the computations in order to exploit their full potential.
 In this paper, we consider the problem of determining the order of data transfers between two memory nodes for a set of independent tasks with the objective of minimizing the makespan.
-We prove that, with limited memory capacity, the problem of obtaining the optimal order of data transfers is NP-complete.
+We prove that, with limited memory capacity, the problem of obtaining the optimal data transfer order is NP-complete.
 We propose several heuristics to determine this order and discuss the conditions that might be favorable to different heuristics.
-We analyze our heuristics on traces obtained by running 2 molecular chemistry kernels, namely, Hartree–Fock (HF) and Coupled Cluster Single Double (CCSD) on 10 nodes of an HPC system.
+We analyze our heuristics on traces obtained by running two molecular chemistry kernels, namely, Hartree–Fock (HF) and Coupled Cluster Singles Doubles (CCSD), on 10 nodes of an HPC system.
 Our results show that some of our heuristics achieve significant overlap for moderate memory capacities and resulting in makespans that are very close to the lower bound.
@@
 First, every architecture provides its own efficacy and interface.
-Therefore, a steep learning curve is required for programmers to take good utilization of all resources.
-Second, scheduling is a well known NP-complete optimization problem, and hybrid and distributed resources make this problem harder (we refer ~\cite{webpagescheduling} for a survey on the complexity of scheduling problems and ~\cite{bleuse2015scheduling} for a recent survey in the case of hybrid nodes).
+Therefore, a steep learning curve is required for programmers to effectively utilize all resources.
+Second, scheduling is a well known NP-complete optimization problem, and hybrid and distributed resources make this problem harder (we refer \citet{webpagescheduling} for a survey on the complexity of scheduling problems and \citet{bleuse2015scheduling} for a recent survey in the case of hybrid nodes).
 Third, due to shared buses and parallel resources, it is challenging to obtain a precise model based on prediction of computation and communication times.
-Fourth, the number of architectures has increased drastically in recent years, therefore it is almost impossible to develop hand tuned optimized code for all these architectures.
-All these observations led to the development of different task based runtime systems.
-Among several runtimes, we may cite QUARK~\cite{YarKhan:2011:Quark:Manual} and PaRSEC~\cite{parsec} from from ICL, Univ.
-of Tennessee Knoxville (USA), StarPU~\cite{starpu} form Inria Bordeaux (France), Legion~\cite{legion12} from Stanford Univ.
+Fourth, the number of architectures has increased drastically in recent years, making it almost impossible to develop hand-tuned optimized code for all these architectures.
+All these observations led to the development of different task-based runtime systems.
+Among several runtimes, we may cite QUARK~\cite{quark} and PaRSEC~\cite{parsec} from  ICL, Univ.
+of Tennessee Knoxville (USA), StarPU~\cite{starpu} from Inria Bordeaux (France), Legion~\cite{legion12} from Stanford Univ.
 (USA), StarSs~\cite{ompss} from Barcelona Supercomputing Center (Spain), KAAPI~\cite{kaapi} from Inria Grenoble (France).
 All these runtime systems allow programmers to express their algorithms at the abstract level in the form of direct acyclic graphs (DAG), where vertices represent computations and edges represent dependencies among them.
-Sometimes some static information is also provided along with the DAG, such as distance to exit (last) node as a priority or affinity of computation towards resources.
-The runtime is then responsible for managing scheduling of computations and communications, data transfers among different memories, computation-communication overlap, and load balance.
+Sometimes some static information is also provided along with the DAG, such as distance to exit (last) node as a priority or affinity of computation toward resources.
+The runtime is then responsible for managing the schedule of computations and communications, data transfer among different memories, computation-communication overlap, and load balance.
 
@@
 With extreme scale computing, supercomputers face bottlenecks due to ever growing need of data.
-Therefore focus of HPC community is now changing towards avoiding, hiding and minimizing communications.
+Therefore focus of HPC community is now changing toward avoiding, hiding and minimizing communications.
 (Kyelick work and http://science.energy.gov/~/media/ascr/ ascac/pdf/meetings/20140210/Top10reportFEB14.pdf )
@@
 	In the last few decades, we have witnessed a drastic improvement in the hardware to provide higher rate of computation, but comparatively smaller improvement has been achieved for the rate of data movement.
-With extreme scale computing, supercomputers face bottlenecks due to the need of large amount of data~\cite{ascaccommitteereport2014,yelick2016}.
-Therefore, the HPC community is now focusing on avoiding, hiding and minimizing communication costs.
+With extreme-scale computing, supercomputers face bottlenecks due to the need for large amount of data~\cite{ascaccommitteereport2014,yelick2016}.
+Therefore, the HPC community is now focused on avoiding, hiding, and minimizing communication costs.
 
@@
 In irregular applications, programmers do not know the precise structure of the task graphs in advance: tasks are added recursively based on certain sentinel constraints.
-For such applications, the runtime system sees a set of independent tasks and schedules them on processing units of different memory spaces.
-It is extremely important for runtimes to decide the order of data transfers for these scheduled computations so as to maximize the overlap between computations and communications.
+For such applications, the runtime system sees a set of tasks and schedules them on processing units of different memory spaces.
+It is extremely important for runtimes to decide the order of data transfers for these scheduled computations so as to maximize the overlap between computation and communication.
 This is the main topic of this paper.
-We prove that the order of communications on two memory nodes with the objective of minimizing the makespan is a NP-complete problem if the memory of the target node is limited.
-Our proof is inspired from work by~\cite{Papadimitriou:1980:FSL:322203.322213}, which applies a similar technique for 2-machine flowshop problem with bounded capacity.
+We prove that determining the order of communications on two memory nodes with the objective of minimizing the makespan is a NP-complete problem if the memory of the target node is limited.
+Our proof is inspired by~\cite{Papadimitriou:1980:FSL:322203.322213}, which applies a similar technique for 2-machine flowshop problem with bounded capacity.
 The main difference between both approaches is that they consider all tasks have the same occupation on the second machine and the memory occupation starts when the processing finishes on the first machine.
 On the contrary, our approach is designed for tasks appearing in scientific workloads whose memory requirements are highly irregular and we consider that memory is acquired before starting the data transfer on the communication resource.
-We propose different runtime strategies in order to maximize the overlap of computations and communications.
+We propose different runtime strategies in order to maximize the  computation-communication overlap.
 We evaluate our strategies on the context of a cluster of homogeneous nodes.
-However, our approach is generic and easily adaptable to any system which operates on different memory spaces.
+However, our approach is generic and easily adaptable to any system that operates on different memory spaces.
 Here are the important contributions of this paper:
@@
 
-	The outline of the paper is the following.
+	The rest of the paper is organized as follows.
 Section~\ref{sec:relatedWork} describes past work on the computations with limited memory and similar problems in the literature.
-In section~\ref{sec:theoreticalProof}, we present an algorithm to obtain the order of data transfers when there is not any memory capacity restriction.
-Then, we also prove that in general data transfer problem is NP-complete.
+In Section~\ref{sec:theoreticalProof}, we present an algorithm to obtain the order of data transfers when there is not any memory capacity restriction.
+Also, we prove that, in general, the data transfer problem is NP-complete.
 In Section~\ref{sec:heuristics}, we propose several heuristics and discuss the conditions that might be favorable to them.
@@
 Our results show that static order with dynamic correction based heuristics achieve good performance in most cases.
-We finally propose conclusions and perspectives in Section~\ref{sec:conclusion}.
+We finally present conclusions and perspectives in Section~\ref{sec:conclusion}.
 
@@
 	Historically there has been a great emphasis on the development of parallel algorithms and minimizing the complexity of computations.
-As the number of computation cores has increased drastically in recent years, supercomputers face bottleneck due to communication required by an application.
-Hence, in recent years the focus has changed towards developing communication avoiding algorithms, strategies to hiding communications and minimizing the data accessed by applications~\cite{yelick2016}.
+As the number of computation cores has increased in recent years, supercomputers face bottlenecks due to the communication required by an application.
+Hence, the focus has shifted toward developing communication avoiding algorithms, strategies to hiding communications, and minimizing the data accessed by applications~\cite{yelick2016}.
 
 	The problem of scheduling tasks has been highly studied in the literature and many formulations are known to be NP-complete~\cite{GareyJohnson}.
-Many static and dynamic strategies have been proposed and analyzed for scheduling tasks on heterogeneous resources~\cite{heft-Topcuoglu,ipdps16starpu}.
+Many static and dynamic strategies have been proposed and analyzed for scheduling tasks on heterogeneous resources~\cite{heft-Topcuoglu,ipdps16starpu, hipc16multiresource}.
 There is also a number of studies in the direction of task scheduling with the emphasis on improving locality and minimizing the communication cost~\cite{starpu,heft-Topcuoglu}.
-Stanisic et.
-al~\cite{luka-dmdar} proposed a heuristic to schedule tasks on a computational resource where most of its data is available.
-A similar approach has been adopted by Agullo et.
-al for the scheduling of sparse linear algebra kernels~\cite{agullo_fmm}.
-Predari et.
-al proposed heuristics to partition the task graph across a number of processors such that inter-processor communication can be minimized~\cite{predari:tel-01518956}.
-
-	The problem considered in this paper also can be viewed as a flow shop problem: the communication link can be seen as a processing resource, and each task needs to first be handled by the communication link and then by the computational resource.
+Stanisic et al.~\cite{luka-dmdar} proposed a heuristic to schedule tasks on a computational resource where most of its data is available.
+A similar approach has been adopted by Agullo et al.
+for the scheduling of sparse linear algebra kernels~\cite{agullo_fmm}.
+Predari et al.
+proposed heuristics to partition the task graph across a number of processors such that inter-processor communication can be minimized~\cite{predari:tel-01518956}.
+
+	The problem we consider also can be viewed as a flowshop problem: the communication link can be seen as a processing resource, and each task needs to first be handled by the communication link and then by the computational resource.
 Communication and computation times of a task can thus be considered as processing times on different machines.
-Johnson has provided scheduling strategies for 2 and 3-machine flow shop problems with infinite memory capacity~\cite{johnson}.
-2-machine flow shop problem with finite buffer has been proven NP-complete by Papadimitriou et.
-al~\cite{Papadimitriou:1980:FSL:322203.322213}, in which a constraint is imposed on the number of tasks that can await execution on the second machine.
+Johnson presented scheduling strategies for 2 and 3-machine flowshop problems with infinite memory capacity~\cite{johnson}.
+Two-machine flowshop problem with finite buffer was proven NP-complete by %Papadimitriou et
+	\citet{Papadimitriou:1980:FSL:322203.322213}, in which a constraint is imposed on the number of tasks that can await execution on the second machine.
 
 	A number of other studies have focused on scheduling with limited memory and storage, starting with the work of register allocation for arithmetic expressions by Sethi and Ulman~\cite{Sethi:1970:GOC:321607.321620}.
-Sarkar et.
-al worked on the scheduling of graphs of smaller-grain tasks with limited memory, where each task requires homogeneous data size~\cite{vsarkar-pact}.
-The same work has been extended by Marchal et.
-al for task graphs where memory requirement of each task is highly irregular~\cite{loris-ipdps18}.
+Sarkar et al.
+worked on the scheduling of graphs of smaller-grain tasks with limited memory, where each task requires homogeneous data size~\cite{vsarkar-pact}.
+The same work has been extended by Marchal et al.
+for task graphs where per-task memory requirements are highly irregular~\cite{loris-ipdps18}.
 
@@
 	and processing time on the third machine is output data transfer time; and the objective is 
-	to minimize the total makespan. This is a well known NP-complete problem~\cite{3machineFlowShopNPComplete}.
-
-	In many cases, output data that needs to be retrieved after task execution is much smaller than the input data.
+	to minimize the total makespan. This is a well-known NP-complete problem~\cite{3machineFlowShopNPComplete}.
+
+	In many cases, output data to be retrieved after task execution is much smaller than the input data.
 It is often the case that future tasks running on the same memory node require output data of the past tasks.
@@
 It is also possible that all output data can be stored in a preallocated separate buffer on a memory node.
-Hence, we do not consider output data explicitly in our analysis and assume that output data is negligible or stored in a separate buffer for each task.
-Thus problem considered here is more similar to a 2-machine flowshop problem.
+We do not consider output data explicitly in our analysis and assume that output data is negligible or stored in a separate buffer for each task.
+Thus the problem we consider is more similar to a 2-machine flowshop problem.
 We prove that ordering the execution of such tasks with finite memory capacity is a NP-complete problem: %%We also present an optimal algorithm to determine the order of execution of tasks when there is not any restriction on memory limit.
@@
 	\vspace*{-0.35cm}
-	We also prove optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} differently in an extended version~\cite{extendedVersion}.
+	We provide an alternative optimality proof of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} in the extended version~\cite{extendedVersion}.
 	\subsection{Finite Memory}
@@
 	constraint for the schedule. This is related to previous work by
-	Papadimitriou et. al~\cite{Papadimitriou:1980:FSL:322203.322213}, in which the second machine
+	%Papadimitriou et al.~ 
+	\citet{Papadimitriou:1980:FSL:322203.322213}, in which the second machine
 	can only handle a bounded number of tasks. Our problem generalizes this
@@
 	first part of a task (instead of at the end of the first part). This
-	requires to provide a slightly different NP-completeness proof, as
+	requires us to provide a slightly different NP-completeness proof, as
 	given below.
@@
 
-		In order to prove NP-hardness, we use a reduction from the
-		well-known NP-complete problem 3 Partition~\cite{GareyJohnson}:
+		To prove NP-hardness, we use a reduction from the
+		well-known 3-Partition NP-complete problem ~\cite{GareyJohnson}:
 
@@
 	problem makes it more difficult, just like it does for limited capacity 2-machine
-	flowshop~\cite{Papadimitriou:1980:FSL:322203.322213}. One additional difficulty of our problem however is that it may not be
+	flowshop~\cite{Papadimitriou:1980:FSL:322203.322213}. One additional difficulty for our problem is that it may not be
 	optimal to consider the same order on both machines.
@@
 The final category is based on combining strategies from the first two categories: a static order is precomputed and corrected dynamically to avoid idle time caused by memory limitations.
-In all of our strategies (except linear programming based strategy), communication and computations take place in the same order.
+In all of our strategies (except linear programming based strategy), communication and computation orders of tasks are same.
 
@@
 
-	We highlight the different dynamic heuristics with the instance described on Table~\ref{tab:dynamicSelectionExample} (these heuristics are too similar on the instance from the previous class), and Figure~\ref{fig:dynamicSelectionExample} shows the corresponding schedules.
+	Similar to the schedules of the previous class, Figure~\ref{fig:dynamicSelectionExample}  highlights the  schedules of this class of heuristics for the example instance of Table~\ref{tab:dynamicSelectionExample}.
+	%%	We highlight the different dynamic heuristics with the instance described on Table~\ref{tab:dynamicSelectionExample} (these heuristics are similar on the instance from the previous class), and Figure~\ref{fig:dynamicSelectionExample} shows the corresponding schedules.
 
@@
 But when the communication resource is idle because the memory requirement of the next task is too high, then we select a task  with a dynamic strategy.
-After a task is dynamically selected, we update the remaining order without this task.
+After a task is selected, we update the remaining order without this task.
 This class of strategies takes advantage of static information in the form of precomputed order and dynamic correction to minimize the idle time due to memory constraint.
@@
 
+%%	\vspace*{0.05cm}
 	%%\begin{figure}[htb]
@@
 		\end{tikzpicture}
-	\caption{ \label{fig:staticOrderDynamiccorrectionExample} Different static order dynamic correction heuristic schedules for a task set of Table~\ref{tab:staticOrderDynamiccorrectionExample} with a memory capacity of 9.
-The $OMIM$ order is $BCDEA$.\vspace*{-0.5cm}}
+		\vspace*{-0.25cm}\caption{ \label{fig:staticOrderDynamiccorrectionExample} Different static order dynamic correction heuristic schedules for a task set of Table~\ref{tab:staticOrderDynamiccorrectionExample} with a memory capacity of 9.
+The $OMIM$ order is $BCDEA$.\vspace*{-0.25cm}}
 	\end{figure}
-
+%%\vspace*{2mm}
 	\begin{table}[!htb]
-	\begin{center}
+%%		\begin{center}
+\vspace*{-0.25cm}
 			\begin{tabular}{|c|c|c|c|}
@@
 				E & 3 & 3 & 2\\ \hline
-		\end{tabular}
-		\caption{\label{tab:staticOrderDynamiccorrectionExample} A task set for static order dynamic correction schedules.\vspace*{-0.75cm}}
-	\end{center}
+			\end{tabular}\vspace*{-0.05cm}
+			\caption{\label{tab:staticOrderDynamiccorrectionExample}A task set for static order dynamic correction schedules.\vspace*{-0.85cm}}
+%%		\end{center}
 	\end{table}	
-
-	As previously, we propose on Table~\ref{tab:staticOrderDynamiccorrectionExample} an example instance for this class of heuristics, and provide on Figure~\ref{fig:staticOrderDynamiccorrectionExample} the corresponding schedules.
+	%%	As previously, we propose on Table~\ref{tab:staticOrderDynamiccorrectionExample} an example instance for this class of heuristics, and provide on Figure~\ref{fig:staticOrderDynamiccorrectionExample} the corresponding schedules.
+	As previously, we propose on Table~\ref{tab:staticOrderDynamiccorrectionExample} an example instance for this class of heuristics, and the corresponding schedules in Figure~\ref{fig:staticOrderDynamiccorrectionExample}.
 
@@
 The first heuristic is based on an algorithm, proposed by Gilmore and Gomory, to obtain the minimal cost sequence for a set of jobs~\cite{Gilmore-Gomory:1964}.
-This is a classical algorithm for 2-machine no-wait flow shop problem.
+This is a classical algorithm for 2-machine no-wait flowshop problem.
 In this algorithm, each job has a start and end state and a cost is associated to change the state.
@@
 Subsequently edges are greedily added to this graph to connect two components while minimizing the total non-overlap cost.
-When the graph is  connected, an edge interchange mechanism is used to determine the sequence of jobs, which ensures that the sequence has minimal cost.
-More details can be found in the original paper~\cite{Gilmore-Gomory:1964} and our implementation is publicly available~\cite{gitworkrepo}.
+When the graph is  connected, an edge interchange mechanism is used to \newline determine the sequence of jobs, which ensures that the sequence has minimal cost.
+We refer the original paper~\cite{Gilmore-Gomory:1964} for more details.
+	%% and our implementation is publicly available~\cite{gitworkrepo}. 
 	This algorithm does not take memory constraints into account and only provides the sequence of processing.
@@
 	&\text{ of variables $c_{ij}$)}
-		\end{aligned}\\
-		\forall i, \quad & \sum_{r\ne i} (a_{ir} - c_{ir})MC(r) + MC(i) \le C && \text{(memory constraint)}\\
+	\end{aligned}
+	%%		\forall i, \quad & \sum_{r\ne i} (a_{ir} - c_{ir})MC(r) + MC(i) \le C && \text{(memory constraint)}\\
 	\end{align*} 
-	\vspace*{-0.75cm}
+	\vspace*{-0.35cm}
+	\begin{align*}
+	\forall i, \quad & \sum_{r\ne i} (a_{ir} - c_{ir})MC(r) + MC(i) \le C && \text{(memory constraint)}
+	\end{align*}
+%%	\vspace*{-0.3cm}
+
+	%%	\todo[inline]{The values $0$ and $1$ for $a_{ij}$ (resp.
+$b_{ij}$) indicate that task $i$ ends before task $j$ starts and task $j$ ends before task $i$ starts respectively on the communication (resp.
+computation) resource.
+If task $j$ ends on the computation resource after task $i$ starts on the communication resource then $c_{ij}$ attains the value $0$ otherwise $1$.}
+
+	\noindent The value $0$ for $a_{ij}$ (resp.
+$b_{ij}$) indicates that task $i$ ends before task $j$ starts on the communication (resp.
+computation) resource, while $1$ indicates task $j$ ends before task $i$ starts.
+If task $j$ ends on the computation resource after task $i$ starts on the communication resource then $c_{ij}$ attains the value $0$ else $1$.
 
@@
 The solver was unable to  solve this MILP at the scale of our interest in limited time.
-Hence, we solve the linear program iteratively for a small subset of size $k=3, 4, 5, 6$: at the boundary of two iterations we fix the event (communication or computation) of an unfinished task started before the boundary point and consider other events flexible.
+Hence, we solve the linear program iteratively for a small subset of size $k=3, 4, 5, 6$: at the boundary of successive iterations we fix the event (communication or computation) of an unfinished task started before the boundary point and consider other events flexible.
 The subsets are formed in the order in which tasks are submitted, which is arbitrary.
-For a given size $k$, we represent the makespan calculated by this heuristic as $lp.k$.
-	We compute various $lp.k$ values for different memory capacities and observe that most of the other heuristics perform better than this heuristic.
+We compute the makespan of the complete set by applying above linear program iteratively on a subset of size $k$ and represent it by $lp.k$.
+We assess various $lp.k$ values for different memory capacities and observe that most of the other heuristics perform better than this heuristic.
 Hence, we do not include this heuristic for the comparison in Section~{\ref{sec:expResults}.
-Performance comparison of different heuristics with MILP based heuristics is available in an extended version~\cite{extendedVersion}.
+Performance comparison of different heuristics with MILP based heuristics is available in the extended version~\cite{extendedVersion}.
 
@@
 		\begin{table}[!h]
-			\begin{center}
-			\begin{tabular}{|c|p{6.5cm}|}
+			\vspace*{-0.1cm}
+			%%			\begin{center}
+			\begin{tabular}{|c|p{6.4cm}|}
 				\hline
@@
 				$OOMAMR$ & Moderate memory capacity and significant percentage of all types of tasks \\ \hline
-			\end{tabular}\caption{~\label{tab:heuristicsAndFavorableScenarios}Heuristics and their favorable scenarios.\vspace*{-0.75cm}}
-			\end{center}
+			\end{tabular}\vspace*{-0.25cm}
+			\caption{\label{tab:heuristicsAndFavorableScenarios}Heuristics and their favorable scenarios.\vspace*{-0.7cm}}
+			%%			\end{center}
 		\end{table}		
-
-		Some of these favorable scenarios can be clearly observed in our experimental results, on Figures~\ref{fig:ratio_to_optimal_hf} and~\ref{fig:ratio_to_optimal_ccsd}.
+		%%	\vspace*{-0.15cm}
+		\noindent Some of these favorable scenarios can be clearly observed in our experimental results, on Figures~\ref{fig:ratio_to_optimal_hf} and~\ref{fig:ratio_to_optimal_ccsd}.
 For example, HF compute intensive tasks have small communication times, which explains why the $SCMR$ heuristic exhibits very good performance in limited memory cases.
@@
 		%%		\todo[inline]{LED: Ok. I did a rephrasing there to go in this direction, make sure it fits the message you wanted to say.}
-
 		\section{Experimental Settings}
@@
 
-		We consider a machine called Cascade~\cite{Cascade}, available at PNNL, for our experiments.
+		We consider a machine called Cascade\footnote{https://www.emsl.pnl.gov/emslweb/10.25582/inst.34218}, available at PNNL, for our experiments.
 We obtain traces by running two molecular chemistry applications, double precision version of  HF and CCSD of NWChem~\cite{NWChem} package on 10 nodes of this machine.
@@
 NWChem takes advantages of a Partitioned Global Address Space Programming Model called Global Arrays (GA)~\cite{GlobalArray} to use shared-memory programming APIs on distributed memory computers.
-GA dedicates one core of each node to handle other cores, hence we can view a node as being composed of 15 computational cores.
+GA dedicates one core of each node to handle communication, hence we can view a node as being composed of 15 computational cores.
 We use 150 processes for each application and obtain 150 trace files.
@@
 				\includegraphics[scale=0.48]{./results/application_properties.pdf}
-				\vspace*{-0.9cm}\caption{HF and CCSD tasks characteristics.\vspace*{-0.35cm}}
+				\vspace*{-0.9cm}\caption{Characteristics of HF and CCSD tasks workloads. Outliers are shown with black dots. \vspace*{-0.35cm}}
 				\label{fig:ApplicationProperties}
@@
 We can see that HF is a communication intensive application and at most 20\% overlap can be expected in the best scenario.
-On the other hand, in the CCSD workload, communications and computations are almost evenly distributed and a more significant overlap is possible.
+On the other hand, in the CCSD workload, communication and computation are almost evenly distributed and a more significant overlap is possible.
 
@@
 			\includegraphics[scale=0.5]{./results/ratio_to_optimal_selected_ccsd.pdf}
-	\vspace*{-0.95cm}\caption{Comparison of different heuristics for CCSD with $m_c=1.8GB$.\vspace*{-0.15cm}}
+			\vspace*{-0.95cm}\caption{Comparison of different heuristics for CCSD with $m_c=1.8GB$.}
 			\label{fig:ratio_to_optimal_ccsd}
@@
 		\begin{figure}[htb]
+			\vspace*{-0.25cm}
+			\begin{center}
 				\includegraphics[scale=0.5]{./results/ratio_to_optimal_ccsd-best.pdf}
-	\vspace*{-0.25cm}\caption{Best variants of all categories for CCSD.\vspace*{-0.25cm}}
-	\label{fig:ratio_to_optimal_best_ccsd}
+				\vspace*{-0.25cm}\caption{\label{fig:ratio_to_optimal_best_ccsd}Best variants of all categories for CCSD.\vspace*{-0.35cm}}
+			\end{center}
 		\end{figure}		
-
 		\noindent Figure~\ref{fig:ratio_to_optimal_best_ccsd} shows that best variants of dynamic and static order with dynamic correction strategies achieve similar performance at minimum memory capacity $m_c$.
@@
 
-		\section{Conclusion and Perspectives}
+		\section{Conclusions and Perspectives}
 		\label{sec:conclusion}
@@
 		In this paper, we consider the problem of deciding the order of data transfers between two memory nodes such that overlap of communications and computations is maximized.
-With Exascale computing, applications face bottlenecks due to communications.
+With exascale computing, applications face bottlenecks due to communications.
 Hence, it is extremely important to achieve the maximum  communication-computation overlap in order to exploit the full potential of the system.
 We show that the problem of determining the optimal order of data transfers is NP-complete.
-We proposed several data transfer heuristics and evaluated them on two molecular chemistry kernels, HF and CCSD.
+We proposed several data transfer heuristics and evaluated them on the context of a cluster of homogeneous nodes for two molecular chemistry kernels, HF and CCSD.
+We did not account output data explicitly in our evaluation and assumed that output data is negligible or stored in a separate buffer for each task.
 Our results show that some of our heuristics achieve significant overlap and their makespans are very close to the lower bound.
@@
 We also plan to study the behavior of our strategies in the context of overlapping CPU-GPU communications with computations.
-A runtime system aiming to expose different heuristics to maximize the communication-computation overlap at the developer level and automatically select the best one is currently underway.
+
+		%%		A runtime system aiming to expose different heuristics to maximize the communication-computation overlap at the developer level and automatically select the best one is currently underway.
 
@@
 Department of Energy (DOE), Office of Science, Office of Advanced Scientific Computing Research, under award 63823.
-%%			 Pacific Northwest National Laboratory is operated by Battelle for DOE under Contract DE-AC05-76RL01830.
+			Pacific Northwest National Laboratory is operated by Battelle for DOE under Contract DE-AC05-76RL01830.
 		\end{acks}

### 2019-06-12 ICPP-19/DataTransferModels/dataTransferModels.tex
ICPP-19 submitted files

--- 2019-06-08 ICPP-19/communications.tex
@@
 \acmYear{2019}
-\setcopyright{acmlicensed}
-\acmConference[ICPP '19]{ICPP 2019: 48th International Conference on Parallel Processing}{August 05--08, 2019}{Kyoto, Japan}
-%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
-%%\acmPrice{15.00}
-%%\acmDOI{10.1145/1122445.1122456}
-%%\acmISBN{978-1-4503-9999-9/18/06}
+\setcopyright{licensedusgovmixed}
+\acmConference[ICPP 2019]{48th International Conference on Parallel Processing}{August 5--8, 2019}{Kyoto, Japan}
+\acmBooktitle{48th International Conference on Parallel Processing (ICPP 2019), August 5--8, 2019, Kyoto, Japan}
+\acmPrice{15.00}
+\acmDOI{10.1145/3337821.3337921}
+\acmISBN{978-1-4503-6295-5/19/08}
 
@@
 		\bibliographystyle{ACM-Reference-Format}
-		\bibliography{communications}
+		\bibliography{dataTransferModels}
 

### 2019-06-12 ICPP-19/communications.tex
ICPP-19 submitted files

@@
 
+%%\copyrightyear{2019}
+%%\acmYear{2019}
+%%\setcopyright{acmlicensed}
+%%\acmConference[ICPP '19]{ICPP 2019: 48th International Conference on Parallel Processing}{August 05--08, 2019}{Kyoto, Japan}
+%%%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
+%%%%\acmPrice{15.00}
+%%%%\acmDOI{10.1145/1122445.1122456}
+%%%%\acmISBN{978-1-4503-9999-9/18/06}
+
 \copyrightyear{2019}
 \acmYear{2019}
-\setcopyright{acmlicensed}
-\acmConference[ICPP '19]{ICPP 2019: 48th International Conference on Parallel Processing}{August 05--08, 2019}{Kyoto, Japan}
-%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
-%%\acmPrice{15.00}
-%%\acmDOI{10.1145/1122445.1122456}
-%%\acmISBN{978-1-4503-9999-9/18/06}
+%%\setcopyright{acmlicensed}
+%%\setcopyright{llicensedusgovmixed}
+\setcopyright{licensedusgovmixed}
+
+%%none,%
+%%acmcopyright,acmlicensed,rightsretained,%
+%%usgov,usgovmixed,cagov,cagovmixed,licensedusgovmixed,%
+%%licensedcagov,licensedcagovmixed,othergov,licensedothergov,%
+%%iw3c2w3,iw3c2w3g
+
+\acmConference[ICPP 2019]{48th International Conference on Parallel Processing}{August 5--8, 2019}{Kyoto, Japan}
+\acmBooktitle{48th International Conference on Parallel Processing (ICPP 2019), August 5--8, 2019, Kyoto, Japan}
+\acmPrice{15.00}
+\acmDOI{10.1145/3337821.3337921}
+\acmISBN{978-1-4503-6295-5/19/08}
 

### 2019-08-07 slides/performanceModels.tex
ICPP presentation for our communication-computation overlap work

\documentclass[mathserif,hyperref={pdfpagemode=FullScreen}]{beamer}
% \documentclass[handout]{beamer}
% \usetheme{Dresden}
\usetheme{340}
\beamertemplatetransparentcovereddynamic
\usepackage[latin1]{inputenc}
\usepackage{pgf}
\usepackage{multirow}
\usepackage{comment}
\usepackage{epsfig,color}
\usepackage{hyperref}
% \usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath,color}

\usepackage{tcolorbox}
%\usepackage{wasysym}
\usepackage{tikz}
\usepackage[export]{adjustbox}

%\usepackage{subfig}
%\usepackage{colortbl}
%\usepackage{array}
\usepackage{booktabs}
%\usepackage{floatrow}
%\usepackage{balance}

\usepackage{float}
\usepackage{tikz}

%%\usepackage{enumitem}
%%\setlist[description]{leftmargin=*}

\usetikzlibrary{patterns}
\usetikzlibrary{fit,calc,positioning,decorations.pathreplacing,matrix}
\tikzset{xtick/.style={inner xsep=0pt, inner ysep=3pt, minimum
		size=0pt, draw, label=below:#1},%
	comm/.style args={#1start#2length#3color#4}{rounded corners=1mm, draw, inner
		sep=0pt, fill=#4, label=center:#1, fit={(#2,0.75)
			(#2+#3,1.5)}},%
	comp/.style args={#1start#2length#3color#4}{rounded corners=1mm, draw, inner
		sep=0pt, fill=#4, label=center:#1, fit={(#2,0)
			(#2+#3,0.75)}},%
}

\newcommand{\schedule}[3]{
	\draw[->] (-0.2, 0) -- (#1, 0) node[below] {$t$};
	\draw (0, 0) -- (0, 1.5);
	\node at (-0.8, 0.75)[rotate=90] {#2};
	\draw[dashed,gray] (0, 0.75) -- (#1, 0.75);
	\foreach \t in {0,#3} {
		\node[xtick=\t] at (\t, 0){};
	}
}
\newcommand{\task}[6][0]{
	\node[comm=#2 start #3 length #4 color #6]{};
	\node[comp=#2 start #3+#4+#1 length #5 color #6]{}; 
}

\newcommand{\continue}{{\bf continue}}

\newcommand{\gem}{{\sc dgemm}\xspace}
\newcommand{\trsm}{{\sc dtrsm}\xspace}
\newcommand{\potrf}{{\sc dpotrf}\xspace}
\newcommand{\syrk}{{\sc dsyrk}\xspace}

\newcommand{\tto}{ {T}_{\textsc FirstIdle}\xspace}
%\newcommand{\ttG}{ {T}_{\textsc GPUNoSpoliation}\xspace}
%\newcommand{\ttC}{ {T}_{\textsc CPUNoSpoliation}\xspace}
%%\newcommand{\HEG}{{\textsc HP}_{\textsc GPU}\xspace}
%\newcommand{\HEC}{{\textsc HP}_{\textsc CPU}\xspace}
%\newcommand{\HE}{{\textsc HP}_{\textsc MakeSpan}\xspace}
\newcommand{\HE}{C_{\max}^{\textsc HP}\xspace}

%\newcommand{\WC}{ {\sc W}_{\textsc CPU}\xspace}
%\newcommand{\WG}{ {\sc W}_{\textsc GPU}\xspace}
%\newcommand{\AG}{ {\cal A}_{\textsc GPU}\xspace}
%\newcommand{\AC}{ {\cal A}_{\textsc CPU}\xspace}
\newcommand{\copt}{{C_{\max}^{\textsc Opt}}\xspace}
\newcommand{\abd}{{AreaBound}\xspace}
%\newcommand{\wls}{{WorstListSchedule}\xspace}

\newcommand{\I}{{\cal I}\xspace}

\newcommand{\hpsched}{\ensuremath{{\cal S}_{\text{HP}}}\xspace}
\newcommand{\hpschedns}{\ensuremath{{\cal S}_{\text{HP}}^{\text{NS}}}\xspace}

\newcommand{\mkl}{{\sc Mkl}\xspace}
\newcommand{\pmkl}{{\sc Parallel Mkl}\xspace}
\newcommand{\maphys}{{\sc MaPHyS}\xspace}
\newcommand{\pdslin}{{\sc PDSLin}\xspace}
%%\newcommand{\superlu}{{\sc SuperLU\_D\IST}\xspace}
\newcommand{\hips}{{\sc Hips}\xspace}
%%\newcommand{\shylu}{{\sc ShyLU}\xspace}
%%\newcommand{\pastix}{{\sc PaStiX}\xspace}
%%\newcommand{\mumps}{{\sc Mumps}\xspace}
%%\newcommand{\pardiso}{{\sc Pardiso}\xspace}
%%\newcommand{\scotch}{{\sc Scotch}\xspace}
%%\newcommand{\metis}{MET\IS\xspace}
%%\newcommand{\chameleon}{{\sc Chameleon}\xspace}
%%\newcommand{\hwloc}{hwloc\xspace}
%%\newcommand{\plasma}{{\sc Plasma}\xspace}
%%\newcommand{\magma}{{\sc Magma}\xspace}
%%\newcommand{\cublas}{{\sc cuBLAS}\xspace}
%%\newcommand{\dplasma}{DPLASMA\xspace}
%%\newcommand{\qrm}{\texttt{qr\_mumps}\xspace}
%%\newcommand{\qrs}{\texttt{qrm\_starpu}\xspace}
%%\newcommand{\qrp}{\texttt{qrm\_parsec}\xspace}
%%\newcommand{\spqr}{\texttt{spqr}\xspace}
%%\newcommand{\lws}{{\sc lws}\xspace}
%%\newcommand{\quark}{{QUARK}\xspace}
%%\newcommand{\starpu}{{StarPU}\xspace}
%%\newcommand{\starss}{{StarSs}\xspace}
%%\newcommand{\parsec}{{PaRSEC}\xspace}
%%\newcommand{\simgrid}{{SimGrid}\xspace}
%%\newcommand{\openmp}{{OpenMP}\xspace}
%%\newcommand{\stf}{{STF}\xspace}
%%\newcommand{\ptg}{{PTG}\xspace}
\newcommand{\heftp}{\emph{heftp}\xspace}
%%\newcommand{\heteroprio}{{HeteroPrio}\xspace}
\newcommand{\heteroprio}{{HeteroPrio}\xspace}
\newcommand{\spoliation}{{spoliation}\xspace}
\newcommand{\preemption}{{preemption}\xspace}

\date{\includegraphics[width=.25\linewidth]{icpp.png}\\August 8, 2019}
\newcommand{\highlight}[1]{\colorbox{red}{$\displaystyle #1$}}
\pdfcompresslevel=2             %-- 0 = none, 9 = best

\input{common.tex}

\title[Performance Models for Data Transfers: A Case Study]{Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels}
%% \author[{\sc Inria Bordeaux}]{Olivier {\sc Beaumont}, 
%% Lionel {\sc Eyraud-Dubois}, and\\ \underline{Suraj {\sc Kumar}}
%%%\author[{\sc Inria}]{Suraj {\sc Kumar}
%%%%\author[shortname]{author1 \inst{1} \and author2 \inst{2}}
%%%%\institute[shortinst]{\inst{1} affiliation for author1 \and %
%%%%	\inst{2} affiliation for author2}
%%} 
\author[ICPP-2019]{\underline{Suraj {\sc Kumar}}\inst{1}, Lionel {\sc Eyraud-Dubois}\inst{2}, and\\ Sriram {\sc Krishnamoorthy}\inst{1}}
\institute[shortinst]{\inst{1} Pacific Northwest National Laboratory, Richland, USA\and %
	\inst{2} Inria Bordeaux -- Sud-Ouest, France}

%%Suraj Kumar (Paci c Northwest National Laboratory), Lionel Eyraud-Dubois (Inria Bordeaux Sud- Ouest), Sriram Krishnamoorthy (Paci c Northwest National Laboratory)

\vfill
%\logo{
%\includegraphics[width=.3\linewidth]{logo/logo_inria}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
%%\raisebox{0.5cm}{\includegraphics[width=.20\linewidth]{logo/logo_labri}}
%% \includegraphics[width=.3\linewidth]{logo_labri}
%\hfill
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
%\includegraphics[width=.3\linewidth]{logo/logo_UBordeaux}
%}

\logo{%
	\makebox[0.95\paperwidth]{%
		\includegraphics[width=.3\linewidth]{logo_pnnl.png}
		\hfill%
		\includegraphics[width=.3\linewidth]{logo_inria.png}
	}%
}

% \date{\small Inria Team\\~\\~\\~\\}
% first argument: slide number to appear from, second argument: content of header 
\newcommand{\hiddencell}[2]{\action<#1->{#2}}
\begin{document}

% Page de garde
\frame{\titlepage}
\logo{}

%%\frame{
%%  \frametitle{Outline}
%%  \tableofcontents
%%}
%%\begin{frame}[fragile]{Test}
%%%%	\begin{figure}
%%	\begin{tikzpicture}
%%	\schedule{24}{}{4,8,10,20}
%%	\end{tikzpicture}
%%	\begin{block}{title}
%%	\newcommand{\taskA}[1]{\node[comp=$A$ start #1 length 5 color cyan] {};}
%%\newcommand{\taskB}[2][0]{\task[#1]{$B$}{#2}{4}{3}{blue!25!white}}
%%\newcommand{\taskC}[2][0]{\task[#1]{$C$}{#2}{1}{6}{blue!50!white}}
%%\newcommand{\taskD}[2][0]{\task[#1]{$D$}{#2}{3}{7}{blue!75!white}}
%%\newcommand{\taskE}[2][0]{\node[comm=$E$ start #2 length 6 color green!25!white]{};%
%%	\node[comp={} start #2+6+#1 length 0.5 color green!25!white]{};}
%%\newcommand{\taskF}[2][0]{\node[comm=$F$ start #2 length 7 color green!50!white]{};%
%%	\node[comp={} start #2+7+#1 length 0.5 color green!50!white]{};}
%%\begin{tikzpicture}[yscale=0.7, thick, xscale=0.3]
%%\schedule{24}{}{5,8,15,21.5,23}
%%\taskA{0}
%%\taskB[1]{0}
%%\taskD[1]{4}
%%\taskE[1]{8}
%%\taskC[0.5]{14}
%%\taskF{15.5}
%%\end{tikzpicture}
%%	\end{block}
%%%%\end{figure}
%%\end{frame}

%%%%%%%%%%%%%%
\section{Introduction} 
\begin{frame}{Introduction}
 \begin{itemize}
 	\vfill
  \item Distributed memory systems are very common
  \vfill
 \item Rate of computation vs rate of data movement
 \vfill
  \item Focus: Avoid, Hide, and Minimize communication costs
  \vfill

 \end{itemize}
\end{frame}

\begin{frame}{Task Graphs and Runtime Systems}
%%   \begin{itemize}
%%   	 \item Applications can be expressed as task graphs
%%\end{itemize}
		\begin{columns}
	\null \hfill
	\begin{column}{0.4\linewidth}
		\begin{center}
			\includegraphics[scale=0.2]{diagrams/taskGraph.eps}
		\end{center}
	\end{column}
	\begin{column}{0.5\linewidth}
		\begin{itemize}
			   	 \item Applications can be expressed as task graphs
			   	 \item Vertices represent tasks
			   	 \item Edges represent dependencies among tasks
		\end{itemize}
	\end{column}
\end{columns}
%%		\begin{center}
%%	\includegraphics[scale=0.2]{diagrams/taskGraph.eps}
%%\end{center}
\begin{block}{Task Based Runtime Systems}
		\begin{itemize}
	\item StarPU, QUARK, PaRSEC, StarSs, Legion, KAAPI
%%	\item Manages scheduling of computations and communications
	\item May only see a set of ready (independent) tasks
	\item A memory node may require data from other memory nodes 
%%	\item Output data is managed by runtime based on demand

	\only<1>{ \item Order of data transfers such that communication-computation overlap is maximized}
	\only<2>{\item Order of data transfers \textcolor{red}{between two memory nodes} such that communication-computation overlap is maximized}
\end{itemize}
\end{block}

\end{frame}

\section{Problem Definition}
\begin{frame}{Problem Definition}
\begin{itemize}
	\item Communication and computation times are known in advance
	\begin{itemize}
		\item Approximated based on number of computations and hardware details
		\item Obtained from previous executions
	\end{itemize}
%%\item Tasks do not produce output data (or store in a separate buffer)
\end{itemize}
\begin{block}{Problem $DT$ }
	\begin{itemize}
		\item A set of tasks $ST=\{T_1, \cdots, T_n\}$ is scheduled on a processing unit $P$ with
		memory unit $M$ of capacity $C$
		\item Input data for tasks of $ST$
		reside on another memory unit
		\item Tasks do not produce output data
		\item Tasks do not require intermediate memory
		\item A tasks uses an amount of memory in $M$ from the
		start of its communication to the end of its computation
	\end{itemize}
\noindent Given $L$, is there a feasible schedule $S$ for $ST$ such that
makespan of $S$, $\mu(S) \le L$?
\end{block}

\end{frame}

\begin{frame}{Relevant Problem in Literature}
\begin{block}{Machine Flowshop Problem}
	\begin{itemize}
		\item $n$ machines and $m$ tasks 
		\item Each task contains exactly $n$ operations
		\item $i$-th operation of a task must be processed on the $i$-th machine
		\item Each machine can perform at-max one operation at a time
		\item $i$-th operation of a task starts after the completion of $(i-1)$-th operation
	\end{itemize}
	The problem is to obtain the arrangement that achieves shortest possible makespan.
\end{block}

\begin{block}{}
	\begin{itemize}
		\item 	Johnson provided an optimal algorithm for 2-machine flow shop problem
		\item Our  problem $DT$ adds one extra dimension (memory capacity) to 2-machine flowshop problem
	\end{itemize}
\end{block}

\end{frame}

\subsection{Unlimited Memory Capacity}

\begin{frame}
	\frametitle{Table of Contents}
	\tableofcontents[currentsubsection]
\end{frame}

\newcommand{\scomm}{\ensuremath{{S}_{\text{COMM}}}}
\newcommand{\scomp}{\ensuremath{{S}_{\text{COMP}}}}

\begin{frame}{Unlimited Memory Capacity}{Johnson's Algorithm}
\begin{algorithm}[H]
\begin{algorithmic}[1]
	\STATE Divide ready tasks in two sets $S_1$ and $S_2$. If computation time of a task $T$ is not less than its communication time, then $T$ is in $S_1$ otherwise in $S_2$.
	\STATE Sort $S_1$ in queue $Q$ by non-decreasing communication times
	\STATE Sort $S_2$ in queue $Q'$ by non-increasing computation times
	\STATE Append $Q'$ to $Q$
	\STATE $\tau_{\text{COMM}} \gets 0$ \hfill\COMMENT{Available time of communication resource}
	\STATE $\tau_{\text{COMP}} \gets 0$\hfill \COMMENT{Available time of computation resource}
	\WHILE{$Q \neq \emptyset$}
	\STATE Remove a task $T$ from beginning of $Q$ for processing
	\STATE $\scomm(T) \gets \tau_{\text{COMM}}$
	\STATE $\scomp(T) \gets max(\scomm(T) + COMM_T, \tau_{\text{COMP}})$
	\STATE $\tau_{\text{COMM}} \gets \scomm(T) + COMM_T$
	\STATE $\tau_{\text{COMP}} \gets \scomp(T) + COMP_T$
	\ENDWHILE
\end{algorithmic}
\end{algorithm}
$\bullet$ $OMIM$ denotes the makespan of this algorithm
\end{frame}

\begin{frame}{Approach for the optimality proof}
\vspace*{-0.5cm}
\begin{center}
\includegraphics[scale=0.32]{./diagrams/original_swapped_schedules-eps-converted-to.pdf}
\end{center}

\end{frame}

\subsection{Limited Memory Capacity}
\begin{frame}
\frametitle{Table of Contents}
\tableofcontents[currentsubsection]
\end{frame}
\newcommand{\threepart}{\textsc{3Par}\xspace}
\begin{frame}{Limited Memory Capacity}
\begin{itemize}
	\item Memory is required only to store input data (from the definition of our problem)
	\item As Communication time $\propto$ amount of communication, for each task:
	\begin{itemize}
		\item Communication time = Amount of communication  (\textcolor{green}{for simplification})
		\item Communication time = Amount of input data
	\end{itemize}
\end{itemize}

\begin{block}{Reduction Problem}
\textbf{Three Partition Problem} (\threepart): Given a set of
$3m$ integers $A = \{ a_1, \cdots, a_{3m }\}$, is there a partition
of $A$ into $m$ triplets $TR_i = \{a_{i_1}, a_{i_2}, a_{i_3}\}$,
such that $\forall i, a_{i_1} + a_{i_2} + a_{i_3} = b$, where
$b=(1/m) \sum a_i $?
\end{block}
\end{frame}

\begin{frame}{Reduction: \threepart to $DT$ }
\begin{block}{Definition of tasks in the reduction from \threepart}

 $\qquad x = max\{a_i:1\le i\le 3m\}$
\begin{center}
\begin{tabular}{ |c|c|c| }
	\hline
	Task & Communication time & Computation time \\ \hline
	$K_0$ & $0$ & $3$ \\ \hline
	$K_1, \cdots, K_{m-1}$ & $b'=b+6x$ & $3$\\ \hline
	$K_m$ & $b'=b+6x$ & $0$ \\ \hline
	$1\le i \le 3m, A_i$ & $1$ & $a_i' = a_i + 2x$\\ \hline
\end{tabular}
\end{center}
\begin{center}
\noindent Total memory capacity: $C=b'+3$\\
\noindent Target makespan: $L=m(b'+3)$
\end{center}
\end{block}
\end{frame}

\begin{frame}[fragile]{Pattern of Feasible Schedule}
\tikzset{xtick/.style={inner xsep=0pt, inner ysep=3pt, minimum size=0pt, draw},%
	task/.style args={#1start#2length#3res#4color#5}{rounded corners, draw, inner
		sep=0pt, fill=#5, label=center:#1, fit={(#2,#4*0.75) (#2+#3,#4*0.75+0.75)}},%
	vert/.style={inner sep=1pt, fill=black, circle, draw, label=#1}
}
\newcommand{\scheduleNoName}[1]{
	\draw[->] (-0.4, 0) -- (#1, 0) node[below] {$t$};
	\draw (0, 0) -- (0, 1.5) node[pos=0.25, left] {Comp.}
	node[pos=0.75, left] {Comm.};
	\draw[dashed,gray] (0, 0.75) -- (#1, 0.75);
}
%%		\begin{figure}[htb]
%%	\centering
\begin{center}
	\begin{tikzpicture}[yscale=0.7, thick, xscale=0.6]
	\scheduleNoName{12.5}
	\node[task=$A_{1,1}$ start 0 length 1 res 1 color cyan]{};
	\node[task=$A_{1,2}$ start 1 length 1 res 1 color blue!40!white]{};
	\node[task=$A_{1,3}$ start 2 length 1 res 1 color blue!70!white]{};
	\node[task=$K_0$ start 0 length 3 res 0 color gray!40!white]{};
	\node[task=$K_1$ start 3 length 6 res 1 color green]{}; 
	\node[task=$A_{1,1}$ start 3 length 1.8 res 0 color cyan]{};
	\node[task=$A_{1,2}$ start 4.8 length 2.3 res 0 color blue!40!white]{};
	\node[task=$A_{1,3}$ start 7.1 length 1.9 res 0 color blue!70!white]{};
	\node[task=$A_{2,1}$ start 9 length 1 res 1 color cyan]{};
	\node[task=$A_{2,2}$ start 10 length 1 res 1 color blue!40!white]{};
	\node[task=$A_{2,3}$ start 11 length 1 res 1 color blue!70!white]{};
	\node[task=$K_1$ start 9 length 3 res 0 color green]{};
	\draw[<->,thin] (0, -0.2) -- node[below]{$3$} (3, -0.2) ;
	\draw[<->,thin] (9, -0.2) -- node[below]{$3$} (12, -0.2) ;
	\draw[<->,thin] (3, -0.2) -- node[below]{$b'$} (9, -0.2) ;
	\end{tikzpicture}
\end{center}
	\begin{block}{}
		\begin{itemize}
			\item Problem $DT$ is NP-Complete.
			\item Our proof is inspired from  work  by Papadimitriou et al. (on 2-machine flowshop  with limited buffer problem)
		\end{itemize}
	\end{block}
%%\end{figure}
\end{frame}

\setlength{\tabcolsep}{3pt}

\begin{frame}[fragile]{Order of Processing on Communication and Computation Resources in Optimal Schedules}
\begin{columns}

	\begin{column}[c]{.35\linewidth}
		\footnotesize
		\begin{center}
\begin{tabular}{|c|c|c|c|}
	\hline
	Task & Memory & Comm & Comp\\
	& Req & Time & Time\\ \hline 
	%%				\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
	%%				&=Comm Volume && \\ \hline
	A & 0 & 0 & 5\\ \hline
	B & 4 & 4 & 3\\ \hline
	C & 1 & 1 & 6\\ \hline
	D & 3 & 3 & 7\\ \hline
	E & 6 & 6 & 0.5\\ \hline
	F & 7 & 7 & 0.5\\ \hline
\end{tabular}
		\end{center}
	\end{column}

	\newcommand{\taskA}[1]{\node[comp=$A$ start #1 length 5 color cyan] {};}
	\newcommand{\taskB}[2][0]{\task[#1]{$B$}{#2}{4}{3}{blue!25!white}}
	\newcommand{\taskC}[2][0]{\task[#1]{$C$}{#2}{1}{6}{blue!50!white}}
	\newcommand{\taskD}[2][0]{\task[#1]{$D$}{#2}{3}{7}{blue!75!white}}
	\newcommand{\taskE}[2][0]{\node[comm=$E$ start #2 length 6 color green!25!white]{};%
	\node[comp={} start #2+6+#1 length 0.5 color green!25!white]{};}
	\newcommand{\taskF}[2][0]{\node[comm=$F$ start #2 length 7 color green!50!white]{};%
	\node[comp={} start #2+7+#1 length 0.5 color green!50!white]{};}

	\begin{column}[c]{.65\linewidth}
%%%%	\begin{figure}[!htb]
%%	\centering
\footnotesize
	\begin{block}{Common ordering on both
			resources}
%%\renewcommand{\schedule}[3]{
%%	\draw[->] (-0.2, 0) -- (#1, 0) node[below] {$t$};
%%	\draw (0, 0) -- (0, 1.5);
%%	\node at (-0.8, 0.75)[rotate=90] {#2};
%%	\draw[dashed,gray] (0, 0.75) -- (#1, 0.75);
%%	\foreach \t in {0,#3} {
%%		\node[xtick=\t] at (\t, 0){};
%%	}
%%}
\begin{tikzpicture}[yscale=0.7, thick, xscale=0.3]
\schedule{24}{}{5,8,15,21.5,23}
\taskA{0}
\taskB[1]{0}
\taskD[1]{4}
\taskE[1]{8}
\taskC[0.5]{14}
\taskF{15.5}
\end{tikzpicture}
	\end{block}
\begin{block}{Different ordering on both
		resources}
\begin{tikzpicture}[yscale=0.7, thick, xscale=0.3]
\schedule{24}{}{5,8,14,22}
\taskA{0}
\taskB[1]{0}
\taskC[3]{4}
\taskD[6.5]{5}
\taskE{8}
\taskF{14.5}
\end{tikzpicture}
\end{block}
%%%%	\caption{Schedules for the instance ofTable~\ref{table:different.order} with a memory capacity of 10.\vspace*{-0.75cm}}
%%\end{figure}
	\end{column}
\end{columns}
\end{frame}

\section{Classes of Heuristics}
\begin{frame}
\frametitle{Table of Contents}
\tableofcontents[currentsection]
\end{frame}

\begin{frame}{Our Heuristics}
\begin{itemize}
	\vfill
	\item Static order based strategies
	\vfill
	\item Dynamic selection based strategies
	\vfill
	\item Static order with dynamic correction based strategies
	\vfill
\end{itemize}
We consider common order on both resources for all of our heuristics.
\end{frame}
\subsection{Static Order Based Strategies}
\begin{frame}{Static Order Based Strategies}
\begin{itemize}
	\vfill
	\item \textit{order of optimal strategy infinite memory} ($OOSIM$)
	\vfill
	\item \textit{increasing order of communication strategy} ($IOCMS$)
	\vfill
	\item \textit{decreasing order of computation strategy} ($DOCPS$)
	\vfill
	\item \textit{increasing order of communication plus computation strategy} ($IOCCS$)
	\vfill
	\item \textit{decreasing order of communication plus computation strategy} ($DOCCS$)
	\vfill
\end{itemize}
\end{frame}
\begin{frame}[fragile]{Static Order Based Strategies}
\begin{columns}
	\footnotesize
\begin{column}[c]{0.4\linewidth}
	\begin{tabular}{|c|c|c|c|}
		\hline
	Task & Memory & Comm & Comp\\
& Req & Time & Time\\ \hline 
		A & 3 & 3 &  2\\ \hline
		B & 1 & 1 & 3\\ \hline
		C & 4 & 4 & 4\\ \hline
		D & 2 & 2 & 1\\ \hline
	\end{tabular}
\vspace*{0.5cm}
\begin{block}{Unlimited Memory Capacity}
	\newcommand{\taskA}[2][0]{\task[#1]{$A$}{#2}{3}{2}{cyan}}
	\newcommand{\taskB}[2][0]{\task[#1]{$B$}{#2}{1}{3}{blue!40!white}}
	\newcommand{\taskC}[2][0]{\task[#1]{$C$}{#2}{4}{4}{blue!70!white}}
	\newcommand{\taskD}[2][0]{\task[#1]{$D$}{#2}{2}{1}{blue}}
\begin{tikzpicture}[yscale=0.45, xscale=0.325]
\schedule{12.5}{OMIM}{1,4,5,8,9,10,11,12}
\taskB{0}
\taskC{1}
\taskA[1]{5}
\taskD[1]{8}
\end{tikzpicture}
\end{block}
\end{column}
\begin{column}[c]{0.6\linewidth}
	\begin{block}{Memory Capacity: 6}
	\newcommand{\taskA}[2][0]{\task[#1]{$A$}{#2}{3}{2}{cyan}}
	\newcommand{\taskB}[2][0]{\task[#1]{$B$}{#2}{1}{3}{blue!40!white}}
	\newcommand{\taskC}[2][0]{\task[#1]{$C$}{#2}{4}{4}{blue!70!white}}
	\newcommand{\taskD}[2][0]{\task[#1]{$D$}{#2}{2}{1}{blue}}
\begin{tikzpicture}[yscale=0.45, xscale=0.32]
\begin{scope}
\schedule{15.5}{OOSIM}{1,4,5,9,12,14,15}
\taskB{0}
\taskC{1}
\taskA{9}
\taskD{12}
\end{scope}
\begin{scope}[yshift=-2.75cm]
\schedule{16.5}{IOCMS}{1,3,4,5,6,8,12,16}
\taskB{0}
\taskD[1]{1}
\taskA{3}
\taskC{8}
\end{scope}
\begin{scope}[yshift=-5.5cm]
\schedule{14.5}{DOCPS}{4,5,8,11,13,14}
\taskC{0}
\taskB[3]{4}
\taskA{8}
\taskD{11}
\end{scope}
\begin{scope}[yshift=-8.25cm]
\schedule{16.5}{IOCCS}{2,3,6,8,12,16}
\taskD{0}
\taskB{2}
\taskA{3}
\taskC{8}
\end{scope}
\begin{scope}[yshift=-11cm]
\schedule{17.5}{DOCCS}{4,8,11,12,13,14,16,17}
\taskC{0}
\taskA{8}
\taskB[1]{11}
\taskD[2]{12}
\end{scope}
\end{tikzpicture}
	\end{block}
\end{column}
\end{columns}
\end{frame}

\subsection{Dynamic Selection Based Strategies}
\begin{frame}{Dynamic Selection Based Strategies}
\begin{itemize}
	\vfill
	\item \textit{largest communication task respects memory restriction} ($LCMR$)
	\vfill
	\item \textit{smallest communication task respects memory restriction} ($SCMR$)
	\vfill
	\item \textit{maximum accelerated task respects memory restriction} ($MAMR$)
	\vfill
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Dynamic Selection Based Strategies}
\begin{columns}
	\footnotesize
	\begin{column}[c]{0.4\linewidth}
		\begin{tabular}{|c|c|c|c|}
			\hline
	Task & Memory & Comm & Comp\\
& Req & Time & Time\\ \hline 
			%%			\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
			%%			&=Comm Volume && \\ \hline
			A & 3 & 3 & 2\\ \hline
			B & 1 & 1 &  6\\ \hline
			C & 4 & 4 & 6\\ \hline
			D & 5 & 5 & 1\\ \hline
		\end{tabular}
	\end{column}
	\begin{column}[c]{0.6\linewidth}
		\begin{block}{Memory Capacity = $6$}
			\newcommand{\taskA}[2][0]{\task[#1]{$A$}{#2}{3}{2}{cyan}}
			\newcommand{\taskB}[2][0]{\task[#1]{$B$}{#2}{1}{6}{blue!40!white}}
			\newcommand{\taskC}[2][0]{\task[#1]{$C$}{#2}{4}{6}{blue!70!white}}
			\newcommand{\taskD}[2][0]{\task[#1]{$D$}{#2}{5}{1}{blue}}
		\begin{tikzpicture}[yscale=0.45,xscale=0.25]
			\begin{scope}
			\schedule{24}{LCMR}{1,6,7,8,11,13,17,23}
			\taskB{0}
			\taskD[1]{1}
			\taskA{8}
			\taskC{13}
			\end{scope}
			\begin{scope}[yshift=-2.75cm]
			\schedule{26}{SCMR}{1,4,7,9,13,19,24,25}
			\taskB{0}
			\taskA[3]{1}
			\taskC{9}
			\taskD{19}
			\end{scope}
			\begin{scope}[yshift=-5.5cm]
			\schedule{25}{MAMR}{1,5,7,13,16,18,23,24}
			\taskB{0}
			\taskC[2]{1}
			\taskA{13}
			\taskD{18}
			\end{scope}
	\end{tikzpicture}
		\end{block}

	\end{column}
\end{columns}
\end{frame}

\subsection{Static Order with Dynamic Corrections Based Strategies}
\begin{frame}{Static Order with Dynamic Corrections Based Strategies}
\begin{itemize}
	\vfill
	\item \textit{optimal order infinite memory largest communication task respects memory restriction} ($OOLCMR$)
	\vfill
	\item \textit{optimal order infinite memory smallest communication task respects memory restriction} ($OOSCMR$)
	\vfill
	\item \textit{optimal order infinite memory maximum accelerated task respects memory restriction} ($OOMAMR$)
	\vfill
\end{itemize}
\end{frame}

\begin{frame}{Static Order with Dynamic Corrections Based Strategies}
\begin{columns}
	\footnotesize
	\begin{column}[c]{0.4\linewidth}
		\begin{tabular}{|c|c|c|c|}
			\hline
	Task & Memory & Comm & Comp\\
& Req & Time & Time\\ \hline 
			%%			\multirow{2}{*}{Task} & Memory Req & \multirow{2}{*}{Comm Time} & \multirow{2}{*}{Comp Time}\\  
			%%			&=Comm Volume && \\ \hline
			A & 4 & 4 &  1\\ \hline
			B & 2 & 2 & 6\\ \hline
			C & 8 & 8 & 8\\ \hline
			D & 5 & 5 & 4\\ \hline
			E & 3 & 3 & 2\\ \hline
		\end{tabular}
	\end{column}
	\begin{column}[c]{0.6\linewidth}
		\begin{block}{Memory Capacity=9}
%%\newcommand{\taskA}[2][0]{\task[#1]{$A$}{#2}{4}{1}{cyan}}
%%\newcommand{\taskB}[2][0]{\task[#1]{$B$}{#2}{2}{6}{cyan!50!black}}
%%\newcommand{\taskC}[2][0]{\task[#1]{$C$}{#2}{8}{8}{blue!40!white}}
%%\newcommand{\taskD}[2][0]{\task[#1]{$D$}{#2}{5}{4}{blue!70!white}}
%%\newcommand{\taskE}[2][0]{\task[#1]{$E$}{#2}{3}{2}{blue}}
\newcommand{\taskA}[2][0]{\task[####1]{$A$}{####2}{4}{1}{cyan}}
\newcommand{\taskB}[2][0]{\task[####1]{$B$}{####2}{2}{6}{cyan!50!black}}
\newcommand{\taskC}[2][0]{\task[####1]{$C$}{####2}{8}{8}{blue!40!white}}
\newcommand{\taskD}[2][0]{\task[####1]{$D$}{####2}{5}{4}{blue!70!white}}
\newcommand{\taskE}[2][0]{\task[####1]{$E$}{####2}{3}{2}{blue}}
\begin{tikzpicture}[yscale=0.6,xscale=0.18]
\begin{scope}
\schedule{35}{OOLCMR}{2,8,12,15,17,25,33}
\taskB{0}
\taskD[1]{2}
\taskA{8}
\taskE{12}
\taskC{17}
\end{scope}
\begin{scope}[yshift=-2.75cm]
\schedule{36}{OOSCMR}{2,5,8,11,15,19,27,35}
\taskB{0}
\taskE[3]{2}
\taskA[1]{5}
\taskD{10}
\taskC{19}
\end{scope}
\begin{scope}[yshift=-5.5cm]
\schedule{36}{OOMAMR}{2,8,11,14,17,25,33}
\taskB{0}
\taskD[1]{2}
\taskE[1]{8}
\taskA{12}
\taskC{17}
\end{scope}
\end{tikzpicture}
		\end{block}
	\end{column}	
\end{columns}
\end{frame}

\begin{frame}{Favorable Situations for Heuristics}
\scriptsize
%%\vspace*{-0.5cm}
\begin{center}
\begin{tabular}{|c|p{9 cm}|}
	\hline
	\textbf{Heuristic} & \textbf{\hspace{2cm}Favorable Situation} \\ \hline
	$OOSIM$ & Memory capacity is not a restriction (\textcolor{green}{Optimal}) \\ \hline
	$IOCMS$ & Memory capacity is not a restriction and tasks are compute intensive (\textcolor{green}{Optimal}) \\ \hline
	$DOCPS$ & Memory capacity is not a restriction and tasks are communication intensive (\textcolor{green}{Optimal}) \\ \hline
	$IOCCS$ & Moderate memory capacity and most tasks are highly compute intensive \\ \hline
	$DOCCS$ & Moderate memory capacity and most tasks are highly communication intensive \\ \hline
	$LCMR$ & Limited memory capacity and significant percentage of tasks with large communication times are compute intensive\\ \hline
	$SCMR$ & Limited memory capacity and significant percentage of tasks with small communication times are compute intensive\\ \hline
	$MAMR$ & Limited memory capacity and significant percentage of all types of tasks\\ \hline
	$OOLCMR$ & Moderate memory capacity and significant percentage of slightly communication intensive tasks have large communication times\\ \hline
	$OOSCMR$ & Moderate memory capacity and significant percentage of slightly communication intensive tasks have small communication times\\ \hline
	$OOMAMR$ & Moderate memory capacity and significant percentage of all types of tasks \\ \hline
\end{tabular}
\end{center}
\end{frame}

\begin{frame}{Additional Heuristics from Previous Work}
\begin{block}{\textit{Gilmore-Gomory} ($GG$)}
	\begin{itemize}
		\item A classical algorithm for 2-machine no-wait flowshop problem
		\item Problem is represented by a graph
		\item An optimal sequence of vertices is obtained 
		\item Does not take memmory constraints into account
	\end{itemize}
\end{block}

\begin{block}{\textit{Bin Packing} ($BP$)}
	\begin{itemize}
		\item First-Fit algorithm for the bin packing problem
		\item Tasks added to the first bin in which they fit
		\item If no bin is found then a new bin is created
		\item Sequence made of all tasks from consecutive bins
	\end{itemize}
\end{block}
\end{frame}

\section{Workloads \& Hardware Configurations}
\begin{frame}
\frametitle{Table of Contents}
\tableofcontents[currentsection]
\end{frame}
\begin{frame}{Workload Characteristics}
\begin{block}{Molecular Chemistry Kernels}
\begin{itemize}
	\item 	Hartree--Fock (HF)  with SiOSi molecules and Coupled Cluster Singles Doubles (CCSD) with Uracil molecules
	\item Tensor operations: transpose and contraction
\end{itemize}
\end{block}
%%\begin{columns}
%%	\begin{column}[c]{0.5\linewidth}
%%		\includegraphics[scale=0.48]{./results/application_properties.pdf}
%%	\end{column}
%%\begin{column}[c]{0.5\linewidth}
%%\end{column}
%%\end{columns}

	\begin{block}{}
	\begin{center}
		\includegraphics[scale=0.5]{./diagrams/results/application_properties.pdf}
%%		\includegraphics[scale=0.48]{./diagrams/results/test1.pdf}
	\end{center}
	\end{block}

\end{frame}

\begin{frame}{Configuration Parameters to Obtain Traces}
\begin{itemize}
	\item 10 nodes of Cascade machine
	\item Each node contains 16 Intel Xeon E5-2670 cores
	\item Double precision version of  HF and CCSD of NWChem
	\item NWChem takes advantages of Global Arrays (GA) 
%%	a Partitioned Global Address Space Programming Model -- Global Arrays (GA)
	\item 150 processes for each application,  300-800 tasks for each process

\end{itemize}

\begin{block}{Simulation Parameters}
\begin{itemize}
	\item $m_c$: minimum memory capacity requirement to execute all tasks of an application
	\item Evaluation criteria for a heuristic $H$, $r(H)=\frac{\text{makespan of $H$}}{OMIM}$ (lower values are better)
	\item All data transfers between the local memory of each process and the GA memory take the same route
%%	\item Only one route for the same source-destination pair
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{HF Performance with $m_c=176KB$.}
%%			\includegraphics[scale=0.5]{./diagrams/results/ratio_to_optimal_selected_hf.pdf}
\begin{center}
%%			\includegraphics[scale=0.335]{./diagrams/results/ratio_to_optimal_selected_hf.pdf}
\includegraphics[width=1.05\linewidth]{./diagrams/results/ratio_to_optimal_selected_hf.pdf}
%%	\includegraphics[scale=0.335]{./diagrams/results/test1.pdf}
\end{center}
$\bullet$ Dynamic strategies are best suited for limited memory capacities\\
$\bullet$ Static order with dynamic correction variants outperform others for moderate memory capacities
\end{frame}

\begin{frame}{CCSD performance with $m_c=1.8GB$}
\begin{center}
	\includegraphics[width=1.05\linewidth]{./diagrams/results/ratio_to_optimal_selected_ccsd.pdf}
\end{center}
$\bullet$ Highly heterogeneous tasks\\
$\bullet$ Static order with dynamic correction variants outperform others in most cases
\end{frame}

\begin{frame}{Best variants of all categories}
%%\begin{columns}
%%	\begin{column}{0.55\linewidth}
\begin{block}{\only<1>{HF} \only<2>{CCSD} Performance}
	\begin{center}
\only<1>{\includegraphics[width=0.85\linewidth]{./diagrams/results/ratio_to_optimal_hf-best.pdf}}
\only<2>{\includegraphics[width=0.85\linewidth]{./diagrams/results/ratio_to_optimal_ccsd-best.pdf}}
	\end{center}
\end{block}
\end{frame}

\begin{frame}{Implementation challenges}
\begin{itemize}
	\vfill
	\item Impact of Congestion on communication/computation times
	\vfill
	\item Output data of a task
	\vfill
	\item Routes between two memory nodes
	\vfill
	\item Communications from multiple memory nodes can happen at the same time
	\vfill
\end{itemize}
\end{frame}

 \section{Conclusion and Ongoing Work}
 \begin{frame}
\frametitle{Table of Contents}
\tableofcontents[currentsection]
\end{frame}
 \begin{frame}{Conclusion and Ongoing Work}
Conclusion:
 \begin{itemize}
  \item Problem of determining the optimal order of data transfers is NP-complete
  \item Our heuristics achieve significant overlap for HF and CCSD applications
 \end{itemize}
\vfill
Ongoing work: 
%% \end{frame}
%% \begin{frame}{Future work}
 \begin{itemize}
  \item Evaluation of our heuristics in the context of accelerators
  \item Implementation of the proposed heuristics
 \item Automatic selection of the best heuristic
 \item Model bandwidth sharing to support multiple simultaneous communications
 \end{itemize}
 \end{frame}

%% \begin{frame}
%%  \begin{center}
%%   {\huge Thank \newline You!}
%%    
%%  \end{center}
%% \end{frame}

\end{document}

### 2019-08-08 slides/performanceModels.tex
presented slides

@@
 
-\date{\includegraphics[width=.25\linewidth]{icpp.png}\\August 8, 2019}
+\date{\includegraphics[width=.25\linewidth]{./diagrams/icpp.png}\\August 8, 2019\\ Kyoto, Japan}
 \newcommand{\highlight}[1]{\colorbox{red}{$\displaystyle #1$}}
@@
 	\makebox[0.95\paperwidth]{%
-		\includegraphics[width=.3\linewidth]{logo_pnnl.png}
+		\includegraphics[width=.3\linewidth]{./logo/logo_pnnl.png}
 		\hfill%
-		\includegraphics[width=.3\linewidth]{logo_inria.png}
+		\includegraphics[width=.3\linewidth]{./logo/logo_inria.png}
 	}%
@@
 		\begin{itemize}
-			   	 \item Applications can be expressed as task graphs
+			   	 \item Application can be expressed as a task graph
 			   	 \item Vertices represent tasks
@@
 		\begin{itemize}
-	\item StarPU, QUARK, PaRSEC, StarSs, Legion, KAAPI
+	\item QUARK, PaRSEC, StarPU, StarSs, Legion
 %%	\item Manages scheduling of computations and communications
@@
 \end{block}
-
 \end{frame}
@@
 \section{Problem Definition}
+
+\begin{frame}
+\frametitle{Table of Contents}
+\tableofcontents[currentsection, subsectionstyle=shaded]
+\end{frame}
+
 \begin{frame}{Problem Definition}
 \begin{itemize}
-	\item Communication and computation times are known in advance
+	\item Communication and computation times are known
 	\begin{itemize}
-		\item Approximated based on number of computations and hardware details
-		\item Obtained from previous executions
+		\item Based on number of computations and hardware details
+		\item Obtained from previous executions (or iterations)
 	\end{itemize}
@@
 
-\begin{frame}{Approach for the optimality proof}
+\begin{frame}{Approach for the Optimality Proof}
 \vspace*{-0.5cm}
@@
 	\item Memory is required only to store input data (from the definition of our problem)
-	\item As Communication time $\propto$ amount of communication, for each task:
+	\item As communication time $\propto$ amount of communication, for each task:
 	\begin{itemize}
@@
 		\end{center}
+
+Memory Capacity = $10$
 	\end{column}
@@
 \footnotesize
-	\begin{block}{Common ordering on both
-			resources}
+	\begin{block}{Common ordering on both resources}
 %%\renewcommand{\schedule}[3]{
@@
 	\begin{column}[c]{0.4\linewidth}
+		\begin{center}
 		\begin{tabular}{|c|c|c|c|}
@@
 		\end{tabular}
+\end{center}
+
+$OMIM$ order = $BCDEA$
 	\end{column}
@@
 		\item If no bin is found then a new bin is created
-		\item Sequence made of all tasks from consecutive bins
+		\item Sequence is made of all tasks from consecutive bins
 	\end{itemize}
@@
 
-\begin{frame}{CCSD performance with $m_c=1.8GB$}
+\begin{frame}{CCSD Performance with $m_c=1.8GB$}
 \begin{center}
@@
 
-\begin{frame}{Best variants of all categories}
+\begin{frame}{Best Variants of All Categories}
 %%\begin{columns}
@@
 
-\begin{frame}{Implementation challenges}
+\begin{frame}{Implementation Challenges}
 \begin{itemize}
 	\vfill
-	\item Impact of Congestion on communication/computation times
+	\item Impact of congestion on communication/computation times
 	\vfill
@@
 	\vfill
-	\item Routes between two memory nodes
+	\item Multiple routes between two memory nodes
 	\vfill
@@
  \item Automatic selection of the best heuristic
- \item Model bandwidth sharing to support multiple simultaneous communications
+%% \item Model bandwidth sharing to support multiple simultaneous communications
  \end{itemize}
@@
 
-%% \begin{frame}
-%%  \begin{center}
-%%   {\huge Thank \newline You!}
-%%    
-%%  \end{center}
-%% \end{frame}
+ \begin{frame}
+  \begin{center}
+   {\huge Thank \newline You!}
+
+  \end{center}
+ \end{frame}
 
